### 2018-03-02 code/heterogeneity.rmd
Code to estimate (un)standardized heterogeneity
Also minor changes to data collation:
- Gave distinct names to rrr1 & 2 effects to facilitate coding
- Changed outcomes1_2 NA to "NA _ NA" to facilitate coding

---
title: "Heterogeneity in pregregistered multi-lab studies"
author: "Anton Ohlsson Collentine"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r load data}
library(readr)

dat <- read_csv("../data/collated_summary_data.csv")
```

```{r metafor}
library(metafor)
library(dplyr)
library(purrr)

est_heterogen_smd_raw <- function(x){
  if(any(x[, "outcomes1_2"] == "mean _ SD")){ #without the 'any' we will get warnings because we apply 'if' to a vector

    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives Hedge's g as outcome
               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives Hedge's g as outcome
               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){  #this currently gives us the estimate for the raw effect, but with SE should be possible to back-transform to smd

    fit <- fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)

    I2_1 <- rep(NA, 3)
    I2_2 <- confint(fit2)$random[3, ]
    #In this case, stop function and return dataframe below
    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3])) #output is for smd, r, and 1 raw difference

  } else if(any(x[, "effect_type"] == "r")){

    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)

    I2_1 <- confint(fit2)$random[3, ]
    I2_2 <- rep(NA, 3)
    #In this case, stop function and return dataframe below
    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3])) #output is for smd, r, and 1 raw difference

  } else{ #for all two-group count effects

    fit <- rma(measure = "OR2D", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #transformed to smd
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

    fit2 <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #transformed to smd
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
  }

  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
  I2_2 <- confint(fit2)$random[3, ] #Gives us the I2 estimate and CI for raw values

  data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #output is for smd, r, and 1 raw difference
}

res <- dat %>% 
  filter(!rs == "RRR5") %>% #Remove RRR5 for now because have not been able to extract sufficient data for it
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), 
  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two

#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect) %>% 
  group_by(rs, effect) %>% 
  summarize() %>% 
  left_join(res) %>% 
  arrange(rs, desc(s_I2)) #sort by rs and I2 for standardized effect

```

```{r table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 2, "Standardized" = 3, "Unstandardized" = 3, " " = 1))

```
**Note**: NA in unstandardized columns comes from correlations which I don't think is possible to calculate the unstandardized version for with the available information. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs. RRR8 I only have the SE for the raw mean difference and have yet to figure out how use this to estimate a standardized effect.

### 2018-03-02 code/collate_summary_data.r

@@ -272,7 +272,7 @@ math_cor <- math_cor %>%
          design = "Implicit with explicit attitude", 
          or_stat_test = "Correlation", 
          effect_type = "r",
-         outcomes1_2 = NA,  #Describes the content of outcome1 and outcome2 variables
+         outcomes1_2 = "NA _ NA",  #Describes the content of outcome1 and outcome2 variables, as character instead of simply NA to facilitate working with data
          outcome_t1 = NA, 
          outcome_c1 = NA, 
          outcome_t2 = NA, 
@@ -330,15 +330,15 @@ ml3_stroop <- ml3[[7]]
 
 ml3_stroop <- ml3_stroop %>% 
   rename(Ntotal = N, #Assign names consistent with other datasets
-         effect_size = ES) %>% 
+         effect_size = r) %>% #The correlation used instead of cohen's d because that is what Ml3 use in their meta-analysis (https://osf.io/yhdau/ -> "ML3 Meta Script.R")
   mutate(rs = "ML3", #Add some descriptive information 
          in_lab = ifelse(Site == "mTurk", 0, 1), #mturk sample is only non-lab sample in this study
          effect = "Stroop effect", 
          B_or_W = "Within", 
          design = "Repeated measurements", 
          or_stat_test = "one sample t-test of std. mean diff", 
-         effect_type = "d",
-         outcomes1_2 = NA, 
+         effect_type = "r",
+         outcomes1_2 = "NA _ NA", #as character instead of simply 'NA' to facilitate later analysis
          outcome_c1 = NA, 
          outcome_t1 = NA, 
          outcome_c2 = NA, 
@@ -512,7 +512,7 @@ for(i in seq_along(internames)){
            design = interdesign[i], 
            or_stat_test = interstat[i], 
            effect_type = "r",
-           outcomes1_2 = NA, 
+           outcomes1_2 = "NA _ NA", #as character instead of simply NA to facilitate working with data
            outcome_c1 = NA, 
            outcome_t1 = NA, 
            outcome_c2 = NA, 
@@ -546,7 +546,7 @@ cons_cor <- cons_cor %>%
          design = "Conscientiousness with persistance", 
          or_stat_test = "correlation", 
          effect_type = "r",
-         outcomes1_2 = NA, 
+         outcomes1_2 = "NA _ NA", #as character instead of simply NA to facilitate working with data
          outcome_c1 = NA, 
          outcome_t1 = NA, 
[…]

### 2018-03-02 code/heterogeneity.rmd
Standardized RRR8

@@
 
+#this function is for transforming RRR8 which only has raw mean difference and SE to a standardized version
+transform_SE <- function(ES, SE, n1, n2){ #Based on meta-analysis lecture 02
+  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2))
+  d <- ES / sdpooled
+  g <- (1 - 3 / (4*(n1 + n2) - 9))*d
+  v <- 1 / n1 + 1/ n2 + g^2 / (2*(n1 + n2))
+  data.frame(g = g, v = v)
+}
+
 est_heterogen_smd_raw <- function(x){
@@
 
-    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives Hedge's g as outcome
+    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives raw outcome
                n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
 
-  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){  #this currently gives us the estimate for the raw effect, but with SE should be possible to back-transform to smd
+  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){
 
-    fit <- fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)
+    standardized <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)
 
-    I2_1 <- rep(NA, 3)
-    I2_2 <- confint(fit2)$random[3, ]
-    #In this case, stop function and return dataframe below
-    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3])) #output is for smd, r, and 1 raw difference
+    fit <- rma(yi = g, vi = v, test = "knha", data = standardized) #standardized effect estimate
+
+    fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x) #raw effect estimate
 
@@
 
-    fit <- rma(measure = "OR2D", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #transformed to smd
+    fit <- rma(measure = "OR2D", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized
                n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
 
-    fit2 <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #transformed to smd
+    fit2 <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #unstandardized
                n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
@@
 ```
-**Note**: NA in unstandardized columns comes from correlations which I don't think is possible to calculate the unstandardized version for with the available information.
+**Note**: I am uncertain if we can speak of standardized/unstandardized in regards to 2x2 tables?
+For now these correspond to OR/Risk difference for the following five effects {Allowed vs forbidden, gain vs.
+loss framing, norm of reciprocity, low vs.
+high category scale, verbal overshadowing}.
+NA in unstandardized columns comes from correlations which don't seem possible to calculate the unstandardized version for with the available information.
 RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.
-RRR8 I only have the SE for the raw mean difference and have yet to figure out how use this to estimate a standardized effect.

### 2018-03-16 code/heterogeneity.rmd
Fixed incorrect conditional for countries for ml3
Heterogeneity table also updated to be more consistent

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
 ```
@@
 
-    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)
-
-    I2_1 <- confint(fit2)$random[3, ]
-    I2_2 <- rep(NA, 3)
-    #In this case, stop function and return dataframe below
-    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3])) #output is for smd, r, and 1 raw difference
+    fit <-rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #Fisher's r-to-z transformed correlation coefficient
+    fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation
 
@@
 
-    fit <- rma(measure = "OR2D", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized
+    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but this = 'OR2DL'
                n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
@@
 
+#--------------
 res <- dat %>% 
@@
   split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), 
+  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
   mutate(dif = s_I2 - r_I2) #Gives us the difference between the two
 
+clarify <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales")
+
+#-----------TEST
+test <- dat %>% filter(effect == "IAT correlation math")
+fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, test = "knha", data = test)
+fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = test)
+
+#---------
 #Add rs to the data-frame
 het <- dat %>% 
-  select(rs, effect) %>% 
+  select(rs, effect, effect_type) %>% 
   group_by(rs, effect) %>% 
-  summarize() %>% 
+  summarize(effect_type = unique(effect_type)) %>% 
   left_join(res) %>% 
-  arrange(rs, desc(s_I2)) #sort by rs and I2 for standardized effect
+  mutate(effect_type = recode(effect_type, 
+                              d = "Mean diff.",
+                              r = "Correlation",
+                              'Raw mean difference' = "Mean diff.",
+                              'Risk difference' = "OR / RD"),
+         effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
+  arrange(desc(s_I2)) #sort by rs and I2 for standardized effect
 
@@
 library(kableExtra)
-het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
+het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
   kable_styling() %>% 
-  add_header_above(c(" " = 2, "Standardized" = 3, "Unstandardized" = 3, " " = 1))
+  add_header_above(c(" " = 3, "Standardized" = 3, "Unstandardized" = 3, " " = 1))
 
 ```
-**Note**: I am uncertain if we can speak of standardized/unstandardized in regards to 2x2 tables?
-For now these correspond to OR/Risk difference for the following five effects {Allowed vs forbidden, gain vs.
-loss framing, norm of reciprocity, low vs.
-high category scale, verbal overshadowing}.
-NA in unstandardized columns comes from correlations which don't seem possible to calculate the unstandardized version for with the available information.
+**Note**: "OR / RD" indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns.
+Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios.
+For correlations the standardized version correspond to Fisher's r-to-z transformed correlation and unstandardized to raw correlations.
+All original authors used raw correlations in their meta-analyzes.
+For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences.
+Original authors used different approaches for mean differences.
 RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.
+Effects were estimated in metafor using REML with the "knha" correction.
+
+For RRR8 the analysis includes data from all 40 laboratories, the preregistered RRR8 analysis only included 23 laboratories (the rest didn't collect enough male participants) - needs fixing.

### 2018-03-16 code/collate_summary_data.r

@@ -345,9 +345,7 @@ ml3_stroop <- ml3_stroop %>%
          outcome_t2 = NA,
          ntreatment = NA, 
          ncontrol = NA,
-         country = ifelse("mTurk" %in% Site, #if effect includes mturk sample add country label for that sample
-                          c("USA","USA", "CAN", rep("USA", 14), "CAN", "USA", "USA", "USA"),
-                          c("USA","USA", "CAN", rep("USA", 14), "CAN", "USA", "USA"))) %>%
+         country = c("USA","USA", "CAN", rep("USA", 14), "CAN", "USA", "USA", "USA")) %>%
   select(rs, effect, Site, country, in_lab, Ntotal, B_or_W, design, or_stat_test, effect_type, effect_size, 
          ncontrol, ntreatment, outcomes1_2, outcome_c1, outcome_t1, outcome_c2, outcome_t2) #select only variables of interest
 
@@ -425,9 +423,8 @@ for(i in seq_along(ml3t_names)){
            effect_type = "d",
            outcomes1_2 = "mean _ SD", #Describes the content of outcome1 and outcome2 variables
            Ntotal = ntreatment + ncontrol,
-           country = ifelse("mTurk" %in% Site, #if dataframe includes mturk sample add one country label for that sample
-                            c("USA","USA", "CAN", rep("USA", 14), "CAN", "USA", "USA", "USA"),
-                            c("USA","USA", "CAN", rep("USA", 14), "CAN", "USA", "USA"))) %>%
+           country = if("mTurk" %in% Site) {c("USA","USA", "CAN", rep("USA", 14), "CAN", "USA", "USA", "USA")} #if dataframe includes mturk sample add one country label for that sample
+                     else{c("USA","USA", "CAN", rep("USA", 14), "CAN", "USA", "USA")}) %>%
     select(rs, effect, Site, country, in_lab, Ntotal, B_or_W, design, or_stat_test, effect_type, effect_size, 
            ncontrol, ntreatment,outcomes1_2, outcome_c1, outcome_t1, outcome_c2, outcome_t2) #select only variables of interest
 }
@@ -473,9 +470,8 @@ for(i in seq_along(nonp_names)){
            outcome_t2 = NA,
            ntreatment = NA, #Assign names consistent with other datasets
            ncontrol = NA,
[…]

### 2018-03-20 code/tables.rmd
RRR8 40 labs -> 23 used in primary analysis
Also created a summary table of data and put in same file aas heterogeneity table

--- 2018-03-16 code/heterogeneity.rmd
@@
 ---
-title: "Heterogeneity in pregregistered multi-lab studies"
+title: "Tables"
 author: "Anton Ohlsson Collentine"
@@
 
-```{r load data}
+```{r load data and packages}
 library(readr)
+library(dplyr)
+library(kableExtra)
+library(purrr)
+library(metafor)
 
@@
 
-```{r metafor}
-library(metafor)
-library(dplyr)
-library(purrr)
+##Summary table
+```{r data-summary-table}
+#library(dplyr)
+#library(kableExtra)
+
+summary.table <- dat %>% 
+  group_by(rs) %>% 
+  summarize(Labs = n_distinct(Site),
+            Countries = n_distinct(country), 
+            Effects = n_distinct(effect),
+            Participants = if(Effects == 1){sum(Ntotal)}
+                           else{sum(Ntotal) / Effects}) %>% #average across effects
+  rename(Study = rs)
+
+summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
+  kable_styling() %>% 
+  footnote(threeparttable = TRUE,
+           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
+Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).")
+
+```
+
+```{r prep-heterogeneity-table}
+#library(metafor)
+#library(dplyr)
+#library(purrr)
 
@@
 
-#--------------
+#Apply function to data
 res <- dat %>% 
@@
 
-clarify <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales")
+clarify <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR
 
-#-----------TEST
-test <- dat %>% filter(effect == "IAT correlation math")
-fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, test = "knha", data = test)
-fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = test)
-
-#---------
 #Add rs to the data-frame
@@
 
-```{r table}
+##Heterogeneity in preregistered multi-lab psychology studies
+```{r heterogeneity-table}
 library(kableExtra)
@@
   kable_styling() %>% 
-  add_header_above(c(" " = 3, "Standardized" = 3, "Unstandardized" = 3, " " = 1))
+  add_header_above(c(" " = 3, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) #%>% 
+  # footnote(threeparttable = TRUE,
+           # general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns.
+Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios.
+For correlations the standardized version correspond to Fisher's r-to-z transformed correlation and unstandardized to raw correlations.
+All original authors used raw correlations in their meta-analyzes.
+For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences.
+Original authors used different approaches for mean differences.
+RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.
+Effects were estimated in metafor using REML with the 'knha' correction.")
 
@@
 Effects were estimated in metafor using REML with the "knha" correction.
-
-For RRR8 the analysis includes data from all 40 laboratories, the preregistered RRR8 analysis only included 23 laboratories (the rest didn't collect enough male participants) - needs fixing.

### 2018-03-20 code/collate_summary_data.r

@@ -1,8 +1,8 @@
 #*************************************************************************************************************************
 
 ##Project: MA heterogeneity project
-##Code: Anton Ohlsson Collentine
 ##Script purpose: This script extracts, cleans and formats summary data from Many labs 1 & 3 and Registered Replication Reports 1 - 8 
+##Code: Anton Ohlsson Collentine
 
 ##Script content:----
 
@@ -904,7 +904,12 @@ rrr7 <- rrr7 %>%
 
 #Extract data
 f <- "../data/RRR8/final_results/tables/all_raw_effects.pdf" #path to table (which includes country names)
-rrr8 <- extract_tables(f)
+rrr8 <- extract_tables(f) #note contains data from all labs, not only the 23 used in main analysis of paper
+
+authors_main23 <- c("Schulte-Mecklenbeck", "Baskin", "Braithwaite", "Vazire", "Newell", "O'Donnell", "Tamayo", #23 labs from main analysis in paper
+                    "Karpinski", "Klein", "Keller", "Shanks", "Bialobrzeska", "Koppel", "Philipp", "Ropovik", #manually coded from Figure 1 in paper https://www.psychologicalscience.org/publications/replication-dijksterhuis-van-knippenberg
+                    "Steele", "Susa", "Steffens", "Aczel", "Saunders", "McLatchie", "Aveyard", "Boot") #also found in final_results/prereg/main.png from OSF
+
 
 #Clean and format data
 rrr8 <- lapply(rrr8, function(x) x[x[,2] == "Main Effect",]) #remove effects that are not the primary effect, note that this drops the headers which are in row 1 of the first list
@@ -912,9 +917,12 @@ rrr8[[1]] <- rrr8[[1]][, -c(4, 6, 8, 10, 18)] #drop a few by extraction incorrec
 
 rrr8 <- as.data.frame(do.call("rbind", rrr8), stringsAsFactors = FALSE)#conmbine into one dataframe
 
+rrr8$V1[22] <- "O'Donnell" #Correct faulty extraction of O'Donnell's name
+
 rrr8[, 3:8] <- sapply(rrr8[,3:8], as.numeric) #change relevant columns to numeric
 
 rrr8 <- rrr8 %>% 
+  filter(V1 %in% authors_main23) %>% #limit to the 23 labs from main analysis in paper
   rename(Site = V1, #rename variables to consistent names
[…]

### 2018-03-20 code/tables.rmd
Removed Fisher's r-to-z from heterogeneity table
Just adjust for bias, so would be incorrect to have it in

@@
 
-    fit <-rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #Fisher's r-to-z transformed correlation coefficient
-    fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation
+    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation
+
+    I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
+    I2_2 <- rep(NA, 3) #No unstandardized version
+
+    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2],      r_ci.ub = I2_2[3]))
 

### 2018-03-21 writing/draft-heterogeneity.rmd
Added initial rough draft of introduction

---
title: "Heterogeneity and I2"
author: "Anton Ohsson Collentine"
date: "March 21, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r load data and packages}
library(readr)
library(dplyr)
library(kableExtra)
library(purrr)
library(metafor)

dat <- read_csv("../data/collated_summary_data.csv")
```

```{r prep-heterogeneity-table}
#library(metafor)
#library(dplyr)
#library(purrr)

#this function is for transforming RRR8 which only has raw mean difference and SE to a standardized version
transform_SE <- function(ES, SE, n1, n2){ #Based on meta-analysis lecture 02
  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2))
  d <- ES / sdpooled
  g <- (1 - 3 / (4*(n1 + n2) - 9))*d
  v <- 1 / n1 + 1/ n2 + g^2 / (2*(n1 + n2))
  data.frame(g = g, v = v)
}

est_heterogen_smd_raw <- function(x){
  if(any(x[, "outcomes1_2"] == "mean _ SD")){ #without the 'any' we will get warnings because we apply 'if' to a vector

    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives Hedge's g as outcome
               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives raw outcome
               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){

    standardized <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)

    fit <- rma(yi = g, vi = v, test = "knha", data = standardized) #standardized effect estimate

    fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x) #raw effect estimate

  } else if(any(x[, "effect_type"] == "r")){

    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation

    I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
    I2_2 <- rep(NA, 3) #No unstandardized version

    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2],      r_ci.ub = I2_2[3]))

  } else{ #for all two-group count effects

    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but this = 'OR2DL'
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

    fit2 <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #unstandardized
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
  }

  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
  I2_2 <- confint(fit2)$random[3, ] #Gives us the I2 estimate and CI for raw values

  data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #output is for smd, r, and 1 raw difference
}

#Apply function to data
res <- dat %>% 
  filter(!rs == "RRR5") %>% #Remove RRR5 for now because have not been able to extract sufficient data for it
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two

clarify <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR

#Add rs to the data-frame
het <- dat %>% 
  select(rs, effect, effect_type) %>% 
  group_by(rs, effect) %>% 
  summarize(effect_type = unique(effect_type)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Mean diff.",
                              r = "Correlation",
                              'Raw mean difference' = "Mean diff.",
                              'Risk difference' = "OR / RD"),
         effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
  arrange(desc(s_I2)) #sort by rs and I2 for standardized effect
```

###Introduction
Replication of research can be an important indicator of an effect's generalizability, ecological validity, or even its very existance [possible ref: make replication mainstream]. As such, replication is sometimes considered vital to scientific progress [e.g., refs: Many labs 1, make rep. mainstream] and meta-analysis is often used as a tool to estimate an underlying 'true', or average, effect size across several replications. Yet the presence of unknown moderators can complicate replication and result in heterogenous effect sizes (henceforth 'heterogeneity') in a meta-analysis.

Heterogeneity is of concern for several reasons. First, it affects the interpretation of the meta-analytic estimate as either _the_ true effect size (homogeneity) or the average of the true effect sizes (heterogeneity). Second, in the presence of heterogeneity, single-laboratory studies have an increased risk of false-positive findings [ref: Inhout]. Moreover, under such circumstances even a well-powered single study may capture the average true effect in less than 50% of cases [ref: Voelkl]. Third, meta-analytic techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht, McShane].

Heterogeniety is often estimated using I2 [e.g., refs]. The I2 index [refs: Higgins and Higgins] ranges from 0% to 100% and is a transformation of the Q-test [ref: Cohran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis. It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects rather than sampling variance. As opposed to tau2, I2 is a relative measure of heterogeneiety and allows comparison of estimates across meta-analyses. Recent large-scale reviews used I2 to argue that heterogeneity is rampant in psychology, reporting average estimates of around 70%. [refs: van Erp (citation), Stanley working paper]

The behavior of I2 is not always well understood. Simulation indicates that I2 like Q has low power with less than 15 - 20 included studies [ref: Huedo-Medina] and confidence intervals often range from 0% to more than 50% [ref: Ioannidis], indicating heterogeneity anywhere between null and intermediate. In their simulations [Huedo-Medina] also demonstrated that for Hedge's g the I2 index maintains a nominal type 1 error rate for all combinations of (un)fulfilled normality and homoscedasticity assumptions. Yet recent simulations by [datacolada] based on real data suggest that this might not be true under all circumstances. In addition, [Huedo-Medina] showed that I2 estimates and type 1 error rates depend on the choice of effect type, by comparing Hedge's g with Glass' delta. It seems probable that other choices of effect type may also affect I2-estimates. For example, we consider standardized versus unstandardized mean differences a likely candidate.

We explore the robustness of I2 as an indicator of heterogeneity using both an empirical and a simulation approach. As a basis for our empirical approach we used data from X pre-registered multi-lab psychology studies available on the Open Science Framework (OSF; osf.io). We perform simulations partly based on real data available from these studies on the OSF and partly with purely simulated data.

###Method
All code and data for this project is available at osf.io/XXXX. We refer to relevant code files on OSF using brackets and links in the sections below, that is (osf.io/XXXX/). We ran all analyses using R version X [R citation].

We downloaded and collated summary data from X pre-registered multi-lab psychology studies (Table 1). Altough some studies (e.g. RRR4) reported results from several outcome variables, we only included primary outcome variables, resulting in a total of Y effects. For each study we collated the data at the level of the lab (osf.io/XXXX/). We extracted information on the country of each lab, whether participants where physically in the lab for the study, total number of participants per lab, type of effect size and additional information related to each effect (see codebook; osf.io/XXXX/). Extracted data was in a variety of formats: Excel (Many labs 1, RRR1 & RRR2), CSV (Many labs 3, RRR3, RRR4, RRR6, RRR5) and as PDF tables (RRR7, RRR8). In two cases (RRR5 and RRR6) it was necessary to download the original studies' R-code and raw data to extract the summary data, and in the case of RRR5 we also had to adapt the study code to be able to extract the summary data (we are grateful to the corresponding author for her help in doing so) [Note: still working on the last bit].

Table 1.
```{r data-summary-table}
#library(dplyr)
#library(kableExtra)

summary.table <- dat %>% 
  group_by(rs) %>% 
  summarize(Labs = n_distinct(Site),
            Countries = n_distinct(country), 
            Effects = n_distinct(effect),
            Participants = if(Effects == 1){sum(Ntotal)}
                           else{sum(Ntotal) / Effects}) %>% #average across effects
  rename(Study = rs)

summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
  kable_styling(position = "left") %>% 
  footnote(threeparttable = TRUE,
           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number. Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).")
```

For each effect in our empirical dataset we estimated heterogeneity using I-square and where applicable (for mean differences) compared I-square estimates for standardized versus unstandardized effect sizes. <!-- We further discuss reasons for heterogeneity in effect sizes -->

To explore the expected distribution of I-square in the case of no heterogeneity we ran simulations both using permutations of empirical data and wholly simulated data. <!-- reasons and simulate data-->

In order to run our permutation simulations we downloaded data at the individual level (rather than summary data) for [two] of the effects in Table 2 ([effect X and effect Y]).

###Results
Table 2.
Heterogeneity in pre-registered multi-lab psychology studies.
```{r heterogeneity-table}
library(kableExtra)
het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
  kable_styling() %>% 
  add_header_above(c(" " = 3, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) %>% 
   footnote(threeparttable = TRUE,
           general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns. Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios. For correlations the standardized version correspond to raw correlations. For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences. Original authors used different approaches for mean differences. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs. Effects were estimated in metafor using REML with the 'knha' correction.")

```

### 2018-03-27 code/collate_summary_data.r
Complete extraction of RRR5

@@ -635,9 +635,15 @@ rrr1_2 <- do.call("rbind", rrr1_2)
 #[4] RRR3 ----
 #******************************************
 ##summary data from Registered Replication Report 3 https://osf.io/d3mw4/
-##Imagery data https://osf.io/be6gd/, intention attribution https://osf.io/7d9yg/ and intentionality https://osf.io/fsmdk/, 
+##Imagery (detailed processing) data https://osf.io/be6gd/, intention attribution https://osf.io/7d9yg/ and intentionality https://osf.io/fsmdk/, 
 
+#Effects extracted in this section
+#[1] "Grammar on detailed processing"  
+#[2] "Grammar on intention attribution"
+#[3] "Grammar on intentionality" 
+#*********************
 #library(dplyr)
+
 
 setwd(wd_path) #reset working directory
 setwd("../data/RRR3") #needs to be set to be able to load all files at once
@@ -721,50 +727,117 @@ rrr4 <- rrr4 %>%
 #[6] RRR5 ----
 #******************************************
 ##summary data from Registered Replication Report 5 https://osf.io/s3hfr/
-##Data extracted from directly from paper http://journals.sagepub.com/doi/pdf/10.1177/1745691616664694
+##Data extracted from raw data files https://osf.io/dvaz7/
 
-#library(tabulizer)
-#library(tidyr)
+#Effects extracted in this section
+#[1] "Commitment on exit"   
+#[2] "Commitment on neglect"
+#*********************
+
+#Additional comment:
+#Note that reported participant numbers of Table 1 in source paper (https://osf.io/s3hfr/) are before listwise deletion due to missing values
+#In addition, source paper appears to do listwise deletion based on missing values in any of the DVs, not only the primary one (exit/neglect)
+#This will result in slight different sample sizes/effects since we only use the stated primary outcomes exit and neglect for listwise deletion
+
+#*********************
+
 #library(dplyr)
 
-#Data extraction
-f <- "http://journals.sagepub.com/doi/pdf/10.1177/1745691616664694"
-rrr5 <- extract_tables(f, pages = 3) #Total sample sizes and lab names
 
-#Had to manually extract the means from Figure 2 ("Exit"). Couldn't figure out how to get the values using the r-code on OSF
[…]

### 2018-03-29 code/collate_summary_data.r
Minor change due to change in folder structure

@@ -74,7 +74,7 @@ library(tabulizer)
 
 
 #extract data on whether in-lab study or not
-lab <- read_excel("../data/Ml1/Table_S1_-_Detailed_Site_and_Sample_Characteristics.xlsx") %>% 
+lab <- read_excel("../data/source/Ml1/Table_S1_-_Detailed_Site_and_Sample_Characteristics.xlsx") %>% 
   select(`Site identifier`, `Online (O) or Lab (L)`) %>% 
   rename(Site = `Site identifier`, in_lab = `Online (O) or Lab (L)`) %>% 
   mutate(in_lab = ifelse(in_lab == "L", 1, 0), Site = tolower(Site))
@@ -97,9 +97,9 @@ lab <- read_excel("../data/Ml1/Table_S1_-_Detailed_Site_and_Sample_Characteristi
 #**************
 
 #sheetnames of effects that use t-tests and have the same data format (Math_art gender does a t-test but has different data format)
-tsheets <- excel_sheets("../data/Ml1/summary/ML-_Summary_Statistics.xlsx")[-c(1:2, 13:18)] 
+tsheets <- excel_sheets("../data/source/Ml1/summary/ML-_Summary_Statistics.xlsx")[-c(1:2, 13:18)] 
 #extract data for these effects
-teffects <- lapply(tsheets, function (X) read_excel("../data/Ml1/summary/ML-_Summary_Statistics.xlsx", sheet = X)) #read data
+teffects <- lapply(tsheets, function (X) read_excel("../data/source/Ml1/summary/ML-_Summary_Statistics.xlsx", sheet = X)) #read data
 
 tfilt <- c("Overall:", "Mean across samples:", "Overall (sum of samples)", "Overall for US participants:") #for removing summary rows
 
@@ -162,9 +162,9 @@ teffects <- do.call("rbind", teffects) #bind into one dataframe
 #*************************
 
 #sheetnames of effects that use chisquare-tests
-chisheets <- excel_sheets("../data/Ml1/summary/ML-_Summary_Statistics.xlsx")[c(15:18)] 
+chisheets <- excel_sheets("../data/source/Ml1/summary/ML-_Summary_Statistics.xlsx")[c(15:18)] 
 #extract data for these effects
-chieffects <- lapply(chisheets, function (X) read_excel("../data/Ml1/summary/ML-_Summary_Statistics.xlsx", sheet = X)) #read data
[…]

### 2018-03-29 code/tables.rmd
Complete heterogeneity table
Including effect sizes and standardized/unstandardized

@@
 summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
-  kable_styling() %>% 
+  kable_styling(position = "left") %>% 
   footnote(threeparttable = TRUE,
@@
 Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).")
-
 ```
@@
 
-    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2],      r_ci.ub = I2_2[3]))
+    return(data.frame(eff_size = fit$b[[1]],
+                      s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], 
+                      r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]))
 
@@
 
-  data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #output is for smd, r, and 1 raw difference
+  data.frame(eff_size = fit$b[[1]], #standardized effect (point estimate)
+             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], #standardized I2 + CI
+             r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #unstandardized I2 + CI
 }
@@
 res <- dat %>% 
-  filter(!rs == "RRR5") %>% #Remove RRR5 for now because have not been able to extract sufficient data for it
   split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
@@
          effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
-  arrange(desc(s_I2)) #sort by rs and I2 for standardized effect
-
+  arrange(desc(s_I2)) #sort by I2 for standardized effect
 ```
@@
 library(kableExtra)
-het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
-  kable_styling() %>% 
-  add_header_above(c(" " = 3, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) #%>% 
-  # footnote(threeparttable = TRUE,
-           # general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns.
+het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
+  kable_styling(latex_options = "scale_down") %>% 
+  add_header_above(c(" " = 4, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) %>%
+  footnote(threeparttable = TRUE,
+           general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns.
 Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios.
-For correlations the standardized version correspond to Fisher's r-to-z transformed correlation and unstandardized to raw correlations.
-All original authors used raw correlations in their meta-analyzes.
+For correlations the standardized version correspond to raw correlations.
 For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences.
@@
 RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.
-Effects were estimated in metafor using REML with the 'knha' correction.")
+Effects were estimated in metafor using REML with the 'knha' correction.
+Estimate column are point estimates of standardized effect sizes.")
 
 ```
-**Note**: "OR / RD" indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns.
-Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios.
-For correlations the standardized version correspond to Fisher's r-to-z transformed correlation and unstandardized to raw correlations.
-All original authors used raw correlations in their meta-analyzes.
-For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences.
-Original authors used different approaches for mean differences.
-RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.
-Effects were estimated in metafor using REML with the "knha" correction.

### 2018-03-29 code/tables.rmd
Paper version of heterogeneity table

@@
 
-#this function is for transforming RRR8 which only has raw mean difference and SE to a standardized version
-transform_SE <- function(ES, SE, n1, n2){ #Based on meta-analysis lecture 02
-  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2))
-  d <- ES / sdpooled
-  g <- (1 - 3 / (4*(n1 + n2) - 9))*d
-  v <- 1 / n1 + 1/ n2 + g^2 / (2*(n1 + n2))
-  data.frame(g = g, v = v)
-}
+est_heterogen_smd_raw <- function(x){
+  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
 
-est_heterogen_smd_raw <- function(x){
-  if(any(x[, "outcomes1_2"] == "mean _ SD")){ #without the 'any' we will get warnings because we apply 'if' to a vector
-
-    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives Hedge's g as outcome
-               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
-
-    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives raw outcome
-               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
+    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
 
@@
 
-    standardized <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)
+    fit <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)
 
-    fit <- rma(yi = g, vi = v, test = "knha", data = standardized) #standardized effect estimate
+  } else if(any(x[, "effect_type"] == "Raw mean difference")){
 
-    fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x) #raw effect estimate
+    fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
+
+  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){
+
+    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
 
@@
 
-    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation
-
-    I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
-    I2_2 <- rep(NA, 3) #No unstandardized version
-
-    return(data.frame(eff_size = fit$b[[1]],
-                      s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], 
-                      r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]))
+    fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)
 
@@
 
-    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but this = 'OR2DL'
+    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but that = 'OR2DL'
                n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
 
-    fit2 <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #unstandardized
-               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
   }
 
-  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
-  I2_2 <- confint(fit2)$random[3, ] #Gives us the I2 estimate and CI for raw values
-
-  data.frame(eff_size = fit$b[[1]], #standardized effect (point estimate)
-             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], #standardized I2 + CI
-             r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #unstandardized I2 + CI
+  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
+  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
+             p = fit$pval,
+             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
 }
@@
   split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
-  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two
+  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
 
-clarify <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR
+OR <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR
 
@@
   mutate(effect_type = recode(effect_type, 
-                              d = "Mean diff.",
+                              d = "Std. mean diff.",
                               r = "Correlation",
-                              'Raw mean difference' = "Mean diff.",
-                              'Risk difference' = "OR / RD"),
-         effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
+                              'Raw mean difference' = "Raw mean diff.")) %>% 
   arrange(desc(s_I2)) #sort by I2 for standardized effect
@@
 library(kableExtra)
-het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
-  kable_styling(latex_options = "scale_down") %>% 
-  add_header_above(c(" " = 4, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) %>%
+het %>% knitr::kable("latex", booktabs = T, digits = 2, col.names = c("RS", "Effect", "Effect type", "Estimate", "p-value", "I2(%)", "ci.lb", "ci.ub")) %>% 
+  kable_styling() %>%
   footnote(threeparttable = TRUE,
-           general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns.
-Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios.
-For correlations the standardized version correspond to raw correlations.
-For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences.
-Original authors used different approaches for mean differences.
-RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.
+           general = "We meta-analyzed effects using the same outcome measures that were used by the original authors.
+Standardized mean difference is Hedge's g.
+The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs.
+forbidden', 'Gain vs.
+loss framing', 'Norm of reciprocity', 'Low vs.
+high category scales'.
 Effects were estimated in metafor using REML with the 'knha' correction.
-Estimate column are point estimates of standardized effect sizes.")
+Estimate column are point estimates of effect sizes.
+Final columns are the upper and lower boundaries of the 90% confidence interval for I2.")
 

### 2018-04-30 code/figures.rmd
Added effect size - I2 figure

---
title: "Figures"
author: "Anton Ohlsson Collentine"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r load data and packages}
library(readr)
library(dplyr)
library(kableExtra)
library(purrr)
library(metafor)

dat <- read_csv("../data/collated_summary_data.csv")
```

I have four different types of effects to transform to raw correlations:
- mean difference + SE
- mean difference + SD
- RD
- OR

Should I first run MA and then transform effect sizes? ->Not sure how how to treat the raw mean differences, since I only get the MA-estimate estimate and the SE.  More straightforward to convert to common metric first. **Kolden + Ihle give formulas.**

```{r transformation_functions}
#For raw mean difference + SE
transform_SE <- function(ES, SE, n1, n2){ #ES -> SDp based on meta-analysis lecture 02
  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2))
  d <- ES / sdpooled
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes
  r <- d / sqrt(d^2 + corr)
  data.frame(r = r, n = n1 + n2)
}

#For mean differrence + SD
transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #taken from Kolden from Esther
  d <- (m1 - m2) / sdpooled
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes
  r <- d / sqrt(d^2 + corr)
  data.frame(r = r, n = n1 + n2)
}

#For Risk difference/OR
transform_RD <- function(ai, bi, ci, di){
  ai <- ifelse(ai == 0, 0.5, ai)  #If value is equal to zero add one half so as to not divide by zero
  bi <- ifelse(bi == 0, 0.5, bi)  #This affects 1 study for Allowed vs. forbidden
  ci <- ifelse(ci == 0, 0.5, ci)  #And several studies for Low vs. high category scales
  di <- ifelse(di == 0, 0.5, di)
  logOR <- log((ai*di) / (bi*ci))
  d = logOR * sqrt(3)/pi
  n1 = ai + bi
  n2 = ci + di
  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes
  r <- d / sqrt(d^2 + corr)
  data.frame(r = r, n = ai + bi + ci +di)
}

#No transformatin needed for correlation

transform_MA <- function(x){
  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector

    transformed <- transform_RD(ai = x$outcome_t1, bi = x$outcome_t2, ci = x$outcome_c1, di = x$outcome_c2)

    #fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)

  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){

     transformed <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)

    #fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)

  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){

     transformed <- transform_SD(x$outcome_t1, x$outcome_c1, x$outcome_t2, x$outcome_c2, x$ntreatment, x$ncontrol)

    # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)

  } else if(any(x[, "effect_type"] == "r")){

     transformed <- data.frame(r = x$effect_size, n = x$Ntotal)

    # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)

   } else{ #For the many labs OR that were transformed to d [double check]

     transformed <- transform_RD(ai = x$outcome_t1, bi = x$outcome_t2, ci = x$outcome_c1, di = x$outcome_c2)

}

  # data.frame(b = fit$b[[1]], I2 = fit$I2) #estimate out
  transformed
}
```

Transform effect sizes to raw correlations
```{r transform_df}
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(transform_MA, .id = "effect")

res %>% filter(!is.na(r) & r > 1) #checks
res %>% filter(is.na(r)) #Checks
```

Seems okay. Metafor takes raw correlations as input for Fisher's z transformed rma.

```{r MA_df}
summarizer <- function(x){
  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, test = "knha", data = x) #takes raw correlation as input
  data.frame(z = fit$b[[1]], I2 = fit$I2, H2 = fit$H2, H2alt = fit$QE / fit$k) #estimate out
}
#Alternative version of calculating I2 does not make conceptual sense because gives negative values. Alternative method for calculating H2 provides information also on excessive homogeneity (i.e, less variability than expected by chance) for those interested. (that is, does not have a lower limit of 1)

res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(z = abs(z)) #We are interested in effect size rather than direction
```

Above seems to do what it should.

```{r plot_res}
library(ggplot2)

ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  ggtitle("I2 increases with effect size in pre-registered multi-lab studies") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.1, y = 75, label = "b = 69.40, R2 = 0.61", size = 3.5)

# ggsave("I2_effect_size.png")

ggplot(res2, aes(x = z, y = H2alt)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  ggtitle("H2 increases with effect size in pre-registered multi-lab studies") +
  xlab("Fisher's z") +
  geom_text(x = 0.1, y = 6, label = "b = 3.81, R2 = 0.53", size = 3.5)

# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61
# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53
```

Note that Fisher's z are the absolute z-scores, because we are interested in effect size rather than direction.

```{r labelled_plot}
library(ggplot2)

ggplot(res2, aes(x = z, y = I2, label = effect)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_text(alpha = 0.3)
```

Qs: Should I keep the I2 based on the original scales, but transform the effect sizes and plot that instead (seems not unreasonable since I2 depends on effect type). -> This seems to make little difference, see below.

```{r}
est_heterogen_smd_raw <- function(x){
  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector

    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){

    fit <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)

  } else if(any(x[, "effect_type"] == "Raw mean difference")){

    fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){

    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "effect_type"] == "r")){

    fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)

  } else{ #for all two-group count effects

    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but that = 'OR2DL'
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

  }

  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
             p = fit$pval,
             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
}

#Apply function to data
res3 <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
  select(effect, s_I2) %>% 
  left_join(res2, .)

```

```{r}
ggplot(res3, aes(x = z, y = s_I2)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

summary(lm(s_I2 ~ z, data = res3)) #b = 68.23, R2 = 0.67
```

### 2018-04-30 writing/draft-heterogeneity.rmd
Draft 2 of introduction

@@
 ---
-title: "Heterogeneity and I2"
-author: "Anton Ohsson Collentine"
-date: "March 21, 2018"
+title: "Insufficient evidence for heterogeneity in psychology"
+author: "Anton Ohlsson Collentine"
 output: pdf_document
@@
 library(kableExtra)
-library(purrr)
-library(metafor)
 
@@
 
-```{r prep-heterogeneity-table}
-#library(metafor)
-#library(dplyr)
-#library(purrr)
-
-#this function is for transforming RRR8 which only has raw mean difference and SE to a standardized version
-transform_SE <- function(ES, SE, n1, n2){ #Based on meta-analysis lecture 02
-  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2))
-  d <- ES / sdpooled
-  g <- (1 - 3 / (4*(n1 + n2) - 9))*d
-  v <- 1 / n1 + 1/ n2 + g^2 / (2*(n1 + n2))
-  data.frame(g = g, v = v)
-}
-
-est_heterogen_smd_raw <- function(x){
-  if(any(x[, "outcomes1_2"] == "mean _ SD")){ #without the 'any' we will get warnings because we apply 'if' to a vector
-
-    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives Hedge's g as outcome
-               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
-
-    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives raw outcome
-               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){
-
-    standardized <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)
-
-    fit <- rma(yi = g, vi = v, test = "knha", data = standardized) #standardized effect estimate
-
-    fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x) #raw effect estimate
-
-  } else if(any(x[, "effect_type"] == "r")){
-
-    fit <- fit2 <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x) #raw correlation
-
-    I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
-    I2_2 <- rep(NA, 3) #No unstandardized version
-
-    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2],      r_ci.ub = I2_2[3]))
-
-  } else{ #for all two-group count effects
-
-    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but this = 'OR2DL'
-               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
-
-    fit2 <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #unstandardized
-               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
-  }
-
-  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval for standardized values
-  I2_2 <- confint(fit2)$random[3, ] #Gives us the I2 estimate and CI for raw values
-
-  data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3]) #output is for smd, r, and 1 raw difference
-}
-
-#Apply function to data
-res <- dat %>% 
-  filter(!rs == "RRR5") %>% #Remove RRR5 for now because have not been able to extract sufficient data for it
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
-  mutate(dif = s_I2 - r_I2) #Gives us the difference between the two
-
-clarify <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR
-
-#Add rs to the data-frame
-het <- dat %>% 
-  select(rs, effect, effect_type) %>% 
-  group_by(rs, effect) %>% 
-  summarize(effect_type = unique(effect_type)) %>% 
-  left_join(res) %>% 
-  mutate(effect_type = recode(effect_type, 
-                              d = "Mean diff.",
-                              r = "Correlation",
-                              'Raw mean difference' = "Mean diff.",
-                              'Risk difference' = "OR / RD"),
-         effect_type = ifelse(effect %in% clarify, "OR / RD", effect_type)) %>% 
-  arrange(desc(s_I2)) #sort by rs and I2 for standardized effect
-```
-
-###Introduction
-Replication of research can be an important indicator of an effect's generalizability, ecological validity, or even its very existance [possible ref: make replication mainstream].
-As such, replication is sometimes considered vital to scientific progress [e.g., refs: Many labs 1, make rep.
-mainstream] and meta-analysis is often used as a tool to estimate an underlying 'true', or average, effect size across several replications.
-Yet the presence of unknown moderators can complicate replication and result in heterogenous effect sizes (henceforth 'heterogeneity') in a meta-analysis.
+In most research there is a natural pattern of studies.
+We first establish belief in the existence of an effect and then wish to know how well it generalizes by exploring its boundary conditions.
+The first we do by using inferential statistics to minimize the risk that a discovery is due to sampling error.
+In the second, we are asking to what extent the effect depends on a particular choice of contextual factors such as 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
+This is often explored through replications of the original study with some slight variation, and once sufficient studies have accumulated through meta-analysis.
+In meta-analysis, the estimated heterogeneity of an effect size (henceforth heterogeneity) is a measure of an effect's susceptibility to changes in these four factors.
+An effect strongly dependent on one or more of the four factors should exhibit high heterogeneity unless controlled for.
 
@@
 First, it affects the interpretation of the meta-analytic estimate as either _the_ true effect size (homogeneity) or the average of the true effect sizes (heterogeneity).
-Second, in the presence of heterogeneity, single-laboratory studies have an increased risk of false-positive findings [ref: Inhout].
-Moreover, under such circumstances even a well-powered single study may capture the average true effect in less than 50% of cases [ref: Voelkl].
+Second, if boundary conditions are unknown, it makes it more difficult to 'successfully' replicate an effect.
+In the presence of heterogeneity even a well-powered single study may capture the average true effect in less than 50% of cases [ref: Voelkl].
 Third, meta-analytic techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht, McShane].
 
-Heterogeniety is often estimated using I2 [e.g., refs].
-The I2 index [refs: Higgins and Higgins] ranges from 0% to 100% and is a transformation of the Q-test [ref: Cohran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis.
-It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects rather than sampling variance.
-As opposed to tau2, I2 is a relative measure of heterogeneiety and allows comparison of estimates across meta-analyses.
-Recent large-scale reviews used I2 to argue that heterogeneity is rampant in psychology, reporting average estimates of around 70%.
-[refs: van Erp (citation), Stanley working paper]
+Several recent papers have argued that heterogeneity is the norm in psychology [ref: Tacket et al, McShane et al].
+These authors argue that, if anywhere, heterogeneity should be minimal in pre-registered multi-lab studies with a common protocol, and the fact that heterogeneity has been found even under such circumstances [e.g., ref: Many Labs 1] is an indication that heterogeneity is widespread in psychology.
+In addition, recent large scale reviews of meta-analyses in psychology [ref: Stanley; van Erp et al] report that much variability in effect sizes can be attributed to heterogeneity, with median estimates of 74% and 70.62% respectively [ref: Stanley].
 
-The behavior of I2 is not always well understood.
-Simulation indicates that I2 like Q has low power with less than 15 - 20 included studies [ref: Huedo-Medina] and confidence intervals often range from 0% to more than 50% [ref: Ioannidis], indicating heterogeneity anywhere between null and intermediate.
-In their simulations [Huedo-Medina] also demonstrated that for Hedge's g the I2 index maintains a nominal type 1 error rate for all combinations of (un)fulfilled normality and homoscedasticity assumptions.
-Yet recent simulations by [datacolada] based on real data suggest that this might not be true under all circumstances.
-In addition, [Huedo-Medina] showed that I2 estimates and type 1 error rates depend on the choice of effect type, by comparing Hedge's g with Glass' delta.
-It seems probable that other choices of effect type may also affect I2-estimates.
-For example, we consider standardized versus unstandardized mean differences a likely candidate.
+We caution against broad claims of particular heterogeneity levels in psychology.
+We have multiple concerns.
+We think that the role of effect sizes is both underestimated (when large) and overestimated (when small) when considering heterogeneity.
+In addition, we think that too much attention is paid to point estimates in view of the uncertainty conferred by accompanying confidence intervals.
+We choose to dwell less on this latter point as it has already been well-made previously [ref: Ioannidis].
+Generally, we argue that the current evidence is insufficient to make general claims about the prevalence of heterogeneity in psychology.
 
-We explore the robustness of I2 as an indicator of heterogeneity using both an empirical and a simulation approach.
-As a basis for our empirical approach we used data from X pre-registered multi-lab psychology studies available on the Open Science Framework (OSF; osf.io).
-We perform simulations partly based on real data available from these studies on the OSF and partly with purely simulated data.
+Larger effect sizes lead to more heterogeneity.
+In classical test theory, an observed correlation $r_{xy}$ is equivalent to the true correlation $\rho_{xy}$ multiplied by the square root of the measurement reliabilities for X ($R_{xx'}$) and Y ($R_{yy'}$): $r_{xy} = \rho_{xy} \times \sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$.
+Across different studies of the same effect the measurement reliabilities will differ due either to sampling variance (that the sample happens to be more or less homogenous) or to small (or large) differences in contextual factors (e.g., location).
+Given that the reliabilities will differ between studies, so will the observed effect sizes even when the underlying effect is the same.
+It follows from the above presented equation that the larger the underlying effect size, the larger the differences between observed effect sizes in studies with differing reliabilities.
+Hence the estimated heterogeneity will increase with effect size.
 
-###Method
-All code and data for this project is available at osf.io/XXXX.
-We refer to relevant code files on OSF using brackets and links in the sections below, that is (osf.io/XXXX/).
-We ran all analyses using R version X [R citation].
+A null meta-analytic effect size does not imply absence of heterogeneity.
+Intuitively, it makes sense to think that if there is no effect there is nothing to moderate (i.e., no heterogeneity).
+However, while this might often be true it is by no means a truism.
+A null or near null effect size estimate may arise from failure to consider contextual factors ('hidden moderators', [ref: van Bavel]) and does not by itself imply the absence of heterogeneity.
+This is especially true when also taking into consideration heterogeneity confidence intervals.
 
-We downloaded and collated summary data from X pre-registered multi-lab psychology studies (Table 1).
-Altough some studies (e.g.
-RRR4) reported results from several outcome variables, we only included primary outcome variables, resulting in a total of Y effects.
-For each study we collated the data at the level of the lab (osf.io/XXXX/).
-We extracted information on the country of each lab, whether participants where physically in the lab for the study, total number of participants per lab, type of effect size and additional information related to each effect (see codebook; osf.io/XXXX/).
-Extracted data was in a variety of formats: Excel (Many labs 1, RRR1 & RRR2), CSV (Many labs 3, RRR3, RRR4, RRR6, RRR5) and as PDF tables (RRR7, RRR8).
-In two cases (RRR5 and RRR6) it was necessary to download the original studies' R-code and raw data to extract the summary data, and in the case of RRR5 we also had to adapt the study code to be able to extract the summary data (we are grateful to the corresponding author for her help in doing so) [Note: still working on the last bit].
+In the following sections we clarify and illustrate our concerns using empirical data and the I2 index as a measure of heterogeneity [ref: Higgins & Higgins].
+We make use of summary data from 10 pre-registered multi-lab replications that examined a total of 37 psychological effects (see Table 1).
+These data arguably represents the best, least biased, meta-analytic data available in psychology.
+The I2 index is an intuitive and much used measure of heterogeneity which ranges from 0% to 100%.
+It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects rather than sampling variance and is a transformation of the Q-test [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis.
+I2 is a relative measure of heterogeneity that allows comparison of estimates across meta-analyses.
 
-Table 1.
+##Table 1
 ```{r data-summary-table}
@@
            general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
-Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).")
+Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
+ML = Many Labs, RRR = Registered Replication Report.")
 ```
 
-For each effect in our empirical dataset we estimated heterogeneity using I-square and where applicable (for mean differences) compared I-square estimates for standardized versus unstandardized effect sizes.
-<!-- We further discuss reasons for heterogeneity in effect sizes -->
+<!-- General thought: Ml1 compares heterogeneity from the perspective of between lab vs.
+between effects and concludes that heterogeneity depends mostly on the effect.
+However, it seems unsurprising that a certain lab (when not perversely motivated) does not systematically bias effects, but rather that a location might have differential effects on different studied effects.
+-->
 
-To explore the expected distribution of I-square in the case of no heterogeneity we ran simulations both using permutations of empirical data and wholly simulated data.
-<!-- reasons and simulate data-->
-
-In order to run our permutation simulations we downloaded data at the individual level (rather than summary data) for [two] of the effects in Table 2 ([effect X and effect Y]).
-
-###Results
-Table 2.
-Heterogeneity in pre-registered multi-lab psychology studies.
-```{r heterogeneity-table}
-library(kableExtra)
-het %>% knitr::kable("latex", booktabs = T, digits = 1, col.names = c("RS", "Effect", "Effect type", "I2(%)", "ci.lb", "ci.ub", "I2(%)", "ci.lb", "ci.ub", "Dif")) %>% 
-  kable_styling() %>% 
-  add_header_above(c(" " = 3, "Standardized" = 3, "Unstandardized" = 3, " " = 1)) %>% 
-   footnote(threeparttable = TRUE,
-           general = "'OR / RD' indicates that the effect was meta-analyzed as odds ratio in 'standardized' columns and risk difference in 'unstandardized' columns.
-Out of these effects 'Verbal overshadowing' was meta-analyzed by original authors as risk difference and the others as odds ratios.
-For correlations the standardized version correspond to raw correlations.
-For 'Mean diff.' the standardized version corresponds to Hedge's g and unstandardized to raw mean differences.
-Original authors used different approaches for mean differences.
-RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.
-Effects were estimated in metafor using REML with the 'knha' correction.")
-
-```
+<!-- This might mean that we have missed an important moderator, or that there is a lot of small moderators missed (thinking about it, this seems to differ from random fluctuations in that they are still systematic in some sense, on the other hand, whether they cancel out or not is in itself due to "chance".
+If an effect (but perhaps not others) is moderated by what time of the day the study is run this can lead to heterogeneity, but say there is also a time-independent moderator such as whether the room is warm -> then we get heterogeneity even if two labs measure at the same time, at what point do these things become "noise" rather than systematic bias?
+Because we have so few labs it is difficult to separate these?) -->

### 2018-05-01 writing/draft-heterogeneity.rmd
Minor language improvements of draft

@@
 
-In most research there is a natural pattern of studies.
+In most research there is a natural pattern of studies which corresponds to two stages.
 We first establish belief in the existence of an effect and then wish to know how well it generalizes by exploring its boundary conditions.
-The first we do by using inferential statistics to minimize the risk that a discovery is due to sampling error.
-In the second, we are asking to what extent the effect depends on a particular choice of contextual factors such as 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
-This is often explored through replications of the original study with some slight variation, and once sufficient studies have accumulated through meta-analysis.
-In meta-analysis, the estimated heterogeneity of an effect size (henceforth heterogeneity) is a measure of an effect's susceptibility to changes in these four factors.
-An effect strongly dependent on one or more of the four factors should exhibit high heterogeneity unless controlled for.
+In the first, we use inferential statistics to minimize the risk that a discovery is due to sampling error.
+In the second stage, we ask to what extent the effect depends on a particular choice of four contextual factors, the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
+This extent is often explored through replications of the original study with some slight variation, and once sufficient studies have accumulated through meta-analysis.
+In meta-analysis, the heterogeneity of an effect size (henceforth referred to as heterogeneity) is a measure of an effect's susceptibility to changes in these four factors.
+An effect strongly dependent on one or more of the four factors, unless controlled for, should exhibit high heterogeneity.
 
 Heterogeneity is of concern for several reasons.
-First, it affects the interpretation of the meta-analytic estimate as either _the_ true effect size (homogeneity) or the average of the true effect sizes (heterogeneity).
-Second, if boundary conditions are unknown, it makes it more difficult to 'successfully' replicate an effect.
+First, it affects the interpretation of the meta-analytic estimate as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity).
+Second, if boundary conditions are unknown, heterogeneity makes it more difficult to 'successfully' replicate an effect.
 In the presence of heterogeneity even a well-powered single study may capture the average true effect in less than 50% of cases [ref: Voelkl].
@@
 Several recent papers have argued that heterogeneity is the norm in psychology [ref: Tacket et al, McShane et al].
-These authors argue that, if anywhere, heterogeneity should be minimal in pre-registered multi-lab studies with a common protocol, and the fact that heterogeneity has been found even under such circumstances [e.g., ref: Many Labs 1] is an indication that heterogeneity is widespread in psychology.
+These authors argue that, if anywhere we would expect heterogeneity to be absent or minimal, it would be in pre-registered multi-lab studies with a common protocol, and the fact that heterogeneity has been found even under such circumstances [e.g., ref: Many Labs 1] is an indication that heterogeneity is widespread in psychology.
 In addition, recent large scale reviews of meta-analyses in psychology [ref: Stanley; van Erp et al] report that much variability in effect sizes can be attributed to heterogeneity, with median estimates of 74% and 70.62% respectively [ref: Stanley].
 
-We caution against broad claims of particular heterogeneity levels in psychology.
-We have multiple concerns.
-We think that the role of effect sizes is both underestimated (when large) and overestimated (when small) when considering heterogeneity.
-In addition, we think that too much attention is paid to point estimates in view of the uncertainty conferred by accompanying confidence intervals.
+As authors, we caution against broad claims of particular heterogeneity levels in psychology and have multiple concerns.
+Namely, we argue that the role of effect sizes is both underestimated (when large) and overestimated (when small) when considering heterogeneity.
+In addition, we believe that too much attention is paid to point estimates in view of the uncertainty conferred by accompanying confidence intervals.
 We choose to dwell less on this latter point as it has already been well-made previously [ref: Ioannidis].
@@
 In classical test theory, an observed correlation $r_{xy}$ is equivalent to the true correlation $\rho_{xy}$ multiplied by the square root of the measurement reliabilities for X ($R_{xx'}$) and Y ($R_{yy'}$): $r_{xy} = \rho_{xy} \times \sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$.
-Across different studies of the same effect the measurement reliabilities will differ due either to sampling variance (that the sample happens to be more or less homogenous) or to small (or large) differences in contextual factors (e.g., location).
-Given that the reliabilities will differ between studies, so will the observed effect sizes even when the underlying effect is the same.
-It follows from the above presented equation that the larger the underlying effect size, the larger the differences between observed effect sizes in studies with differing reliabilities.
+Across different studies of the same effect the measurement reliabilities will differ either due to sampling variance (that the sample happens to be more or less homogenous) or to small (or large) differences in contextual factors (e.g., location).
+Given that the reliabilities will differ between studies, so will the observed effect sizes even when the underlying effect size is the same.
+It follows from the above presented equation that the larger the underlying effect size is, the larger the differences between observed effect sizes in studies with differing reliabilities will be.
 Hence the estimated heterogeneity will increase with effect size.
@@
 A null or near null effect size estimate may arise from failure to consider contextual factors ('hidden moderators', [ref: van Bavel]) and does not by itself imply the absence of heterogeneity.
-This is especially true when also taking into consideration heterogeneity confidence intervals.
+This is especially true when heterogeneity confidence intervals are also taken into account.
 
 In the following sections we clarify and illustrate our concerns using empirical data and the I2 index as a measure of heterogeneity [ref: Higgins & Higgins].
-We make use of summary data from 10 pre-registered multi-lab replications that examined a total of 37 psychological effects (see Table 1).
-These data arguably represents the best, least biased, meta-analytic data available in psychology.
-The I2 index is an intuitive and much used measure of heterogeneity which ranges from 0% to 100%.
+We make use of summary data from 10 pre-registered multi-lab replications that examined a total of 36 psychological effects (see Table 1).
+These data arguably represent the best, least biased, meta-analytic data available in psychology.
+The I2 index is an intuitive and much-used measure of heterogeneity which ranges from 0% to 100%.
 It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects rather than sampling variance and is a transformation of the Q-test [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis.

### 2018-05-17 code/figures.rmd
Formatting tables and figures + new draft with method

@@
 More straightforward to convert to common metric first.
-**Kolden + Ihle give formulas.**
+**Kolden + Ihle give formulas.** From book Cooper & Hedges, 1994.
 
@@
 transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
-  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #taken from Kolden from Esther
+  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #page 226. 
   d <- (m1 - m2) / sdpooled
-  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes
-  r <- d / sqrt(d^2 + corr)
+  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p.234
+  r <- d / sqrt(d^2 + corr) #p. 234
   data.frame(r = r, n = n1 + n2)
@@
   di <- ifelse(di == 0, 0.5, di)
-  logOR <- log((ai*di) / (bi*ci))
-  d = logOR * sqrt(3)/pi
+  logOR <- log((ai*di) / (bi*ci)) #p. 266
+  d = logOR * sqrt(3)/pi #p. 232
   n1 = ai + bi
   n2 = ci + di
-  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes
-  r <- d / sqrt(d^2 + corr)
+  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p. 234
+  r <- d / sqrt(d^2 + corr) #p. 234
   data.frame(r = r, n = ai + bi + ci +di)
@@
   fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, test = "knha", data = x) #takes raw correlation as input
-  data.frame(z = fit$b[[1]], I2 = fit$I2, H2 = fit$H2, H2alt = fit$QE / fit$k) #estimate out
+  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / fit$k) #estimate out
 }
@@
 
-ggplot(res2, aes(x = z, y = I2)) +
+I2 <- ggplot(res2, aes(x = z, y = I2)) +
   geom_point(alpha = 0.5) +
   geom_smooth(method = "lm", se = FALSE, color = "black") +
-  ggtitle("I2 increases with effect size in pre-registered multi-lab studies") +
   xlab("Fisher's z") +
   coord_cartesian(ylim = c(0, 100)) +
-  geom_text(x = 0.1, y = 75, label = "b = 69.40, R2 = 0.61", size = 3.5)
+  geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
+  theme_classic()
 
@@
 
-ggplot(res2, aes(x = z, y = H2alt)) + 
+H2 <- ggplot(res2, aes(x = z, y = H2)) + 
   geom_point(alpha = 0.5) +
   geom_smooth(method = "lm", se = FALSE, color = "black") +
-  ggtitle("H2 increases with effect size in pre-registered multi-lab studies") +
   xlab("Fisher's z") +
-  geom_text(x = 0.1, y = 6, label = "b = 3.81, R2 = 0.53", size = 3.5)
+  geom_text(x = 0.14, y = 6, label = "b = 3.81, R2 = 0.53", size = 3.5) +
+  theme_classic()
+
+# ggsave("H2_effect_size.png")
+library(cowplot)
+
+effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v")
+# save_plot("effect_het.png", effect_het,
+          # nrow = 2, base_aspect_ratio = 1.3)
 

### 2018-05-17 code/tables.rmd
Formatting tables and figures + new draft with method

@@
 
+##Heterogeneity increases with effect size
+```{r effect-size-heterogeneity-table}
+#library(kableExtra)
+rooted_relabilities <- matrix(rep(c(.8, .7,.6), 3), ncol = 3)
+rho <- c(0, .5, .8)
+rel <- c("R = .8", "R = .7", "R = .6")
+
+rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
+diff_row <- data.frame(rel = "Diff.", X1 = 0, X2 = 0.05, X3 = 0.08)
+
+het_demo <- data.frame(rel, rooted_relabilities)
+het_demo <- rbind(het_demo, diff_row)
+
+het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "Rho = 0", "Rho = .5", "Rho = .8")) %>% 
+  kable_styling(position = "left") %>% 
+  footnote(threeparttable = TRUE) %>% 
+  row_spec(3, hline_after = T)
+
+```
+
 ##Summary table
@@
 
+#Shortened version of APA reference
+papers <- c('Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams, R.
+B., Jr., Bahník, S., Bernstein, M.
+J., .
+.
+.
+Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A "many labs" replication project.',
+'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
+'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
+'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
+'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011).',
+'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
+'Cheung, I., Campbell, L., LeBel, E.
+P., Ackerman, R.
+A., Aykutoglu, B., Bahník, S., ...
+& Carcedo, R.
+J.
+(2016).
+Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).',
+'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
+'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
+"O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")
+
+##Full APA reference below
+# c('Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams, R.
+B., Jr., Bahník, S., Bernstein, M.
+J., .
+.
+.
+Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A "many labs" replication project.
+Social Psychology, 45(3), 142-152.',
+# 'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.
+Journal of Experimental Social Psychology, 67, 68-82.',
+# 'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.
+Journal of Experimental Social Psychology, 67, 68-82.',
+# 'Alogna, V.
+K., Attaya, M.
+K., Aucoin, P., Bahník, S., Birch, S., Birt, A.
+R., ...
+& Buswell, K.
+(2014).
+Registered replication report: Schooler and engstler-schooler (1990).
+Perspectives on Psychological Science, 9(5), 556-578.',
+# 'Eerland, A., Sherrill, A.
+M., Magliano, J.
+P., Zwaan, R.
+A., Arnal, J.
+D., Aucoin, P., ...
+& Crocker, C.
+(2016).
+Registered replication report: Hart & Albarracín (2011).
+Perspectives on Psychological Science, 11(1), 158-171.',
+# 'Hagger, M.
+S., Chatzisarantis, N.
+L., Alberts, H., Anggono, C.
+O., Batailler, C., Birt, A.
+R., ...
+& Calvillo, D.
+P.
+(2016).
+A multilab preregistered replication of the ego-depletion effect.
+Perspectives on Psychological Science, 11(4), 546-573.',
+# 'Cheung, I., Campbell, L., LeBel, E.
+P., Ackerman, R.
+A., Aykutoglu, B., Bahník, S., ...
+& Carcedo, R.
+J.
+(2016).
+Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).
+Perspectives on Psychological Science, 11(5), 750-764.',
+# 'Wagenmakers, E.
+J., Beek, T., Dijkhoff, L., Gronau, Q.
+F., Acosta, A., Adams Jr, R.
+B., ...
+& Bulnes, L.
+C.
+(2016).
+Registered Replication Report: Strack, Martin, & Stepper (1988).
+Perspectives on Psychological Science, 11(6), 917-928.',
+# 'Bouwmeester, S., Verkoeijen, P.
+P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ...
+& Evans, A.
+M.
+(2017).
+Registered Replication Report: Rand, Greene, and Nowak (2012).
+Perspectives on Psychological Science, 12(3), 527-542.',
+# "O'Donnell, M., Nelson, L., McLatchie, N.
+M., & Lynott, D.
+J.
+(2017).
+Registered Replication Report: Dijksterhuis & van Knippenberg (1998): Multilab direct replication of: A variant of study 4 from Dijksterhuis, A., & van Knippenberg, A.(1998).
+The relation between perception and behavior, or how to win a game of trivial pursuit.
+Journal of personality and social psychology.
+Perspectives on Psychological Science."
+
 summary.table <- dat %>% 
   group_by(rs) %>% 
-  summarize(Labs = n_distinct(Site),
+  summarize(k = n_distinct(Site),
             Countries = n_distinct(country), 
@@
                            else{sum(Ntotal) / Effects}) %>% #average across effects
-  rename(Study = rs)
+  mutate(Paper = papers) %>% 
+  select(RS = rs, Paper, everything()) #change order of columns
 
 summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
-  kable_styling(position = "left") %>% 
+  kable_styling() %>% 
+  column_spec(2, width = "25em") %>% #specify width of paper column
   footnote(threeparttable = TRUE,
            general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
-Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).")
+Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
+RS = Replication Study, k = no.
+primary studies, ML = Many Labs, RRR = Registered Replication Report.")
 ```
@@
   data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
-             p = fit$pval,
              s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
@@
 het <- dat %>% 
-  select(rs, effect, effect_type) %>% 
+  select(rs, Site, effect, effect_type) %>% 
   group_by(rs, effect) %>% 
-  summarize(effect_type = unique(effect_type)) %>% 
+  summarize(effect_type = unique(effect_type),
+            k = n_distinct(Site)) %>% 
   left_join(res) %>% 
   mutate(effect_type = recode(effect_type, 
-                              d = "Std. mean diff.",
-                              r = "Correlation",
-                              'Raw mean difference' = "Raw mean diff.")) %>% 
-  arrange(desc(s_I2)) #sort by I2 for standardized effect
+                              d = "SMD.",
+                              'Raw mean difference' = "MD",
+                              'Risk difference' = "RD")) %>% 
+  select(rs, effect,k , everything()) %>% 
+  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
 ```
@@
 library(kableExtra)
-het %>% knitr::kable("latex", booktabs = T, digits = 2, col.names = c("RS", "Effect", "Effect type", "Estimate", "p-value", "I2(%)", "ci.lb", "ci.ub")) %>% 
-  kable_styling() %>%
-  footnote(threeparttable = TRUE,
+
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE,digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Size", "I2(%)", "ci.lb", "ci.ub")) %>% 
+  kable_styling("scale_down") %>%
+  footnote(threeparttable = TRUE, escape = FALSE,
            general = "We meta-analyzed effects using the same outcome measures that were used by the original authors.
@@
 Effects were estimated in metafor using REML with the 'knha' correction.
-Estimate column are point estimates of effect sizes.
-Final columns are the upper and lower boundaries of the 90% confidence interval for I2.")
+RS = Replication Study, k = no.
+primary studies, Size = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval.
+SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.")
 

### 2018-05-17 writing/draft-heterogeneity.rmd
Formatting tables and figures + new draft with method

@@
 ---
-title: "Insufficient evidence for heterogeneity in psychology"
+title: "Reviewing evidence for heterogeneity in psychology"
 author: "Anton Ohlsson Collentine"
+header-includes:
+   - \setlength\parindent{24pt}
 output: pdf_document
@@
 library(kableExtra)
+library(metafor)
+library(purrr)
 
@@
 
-In most research there is a natural pattern of studies which corresponds to two stages.
-We first establish belief in the existence of an effect and then wish to know how well it generalizes by exploring its boundary conditions.
-In the first, we use inferential statistics to minimize the risk that a discovery is due to sampling error.
-In the second stage, we ask to what extent the effect depends on a particular choice of four contextual factors, the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
-This extent is often explored through replications of the original study with some slight variation, and once sufficient studies have accumulated through meta-analysis.
+```{r prep-heterogeneity-table}
+#library(metafor)
+#library(dplyr)
+#library(purrr)
+
+est_heterogen_smd_raw <- function(x){
+  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
+
+    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
+
+  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){
+
+    fit <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)
+
+  } else if(any(x[, "effect_type"] == "Raw mean difference")){
+
+    fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
+
+  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){
+
+    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
+
+  } else if(any(x[, "effect_type"] == "r")){
+
+    fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)
+
+  } else{ #for all two-group count effects
+
+    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but that = 'OR2DL'
+               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
+
+  }
+
+  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
+  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
+             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
+}
+
+#Apply function to data
+res <- dat %>% 
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
+
+OR <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR
+
+#Add rs to the data-frame
+het <- dat %>% 
+  select(rs, Site, effect, effect_type) %>% 
+  group_by(rs, effect) %>% 
+  summarize(effect_type = unique(effect_type),
+            k = n_distinct(Site)) %>% 
+  left_join(res) %>% 
+  mutate(effect_type = recode(effect_type, 
+                              d = "SMD.",
+                              'Raw mean difference' = "MD",
+                              'Risk difference' = "RD")) %>% 
+  select(rs, effect,k , everything()) %>% 
+  arrange(desc(s_I2), desc(s_ci.ub)) #sort by I2 and upper CI bound
+```
+Empirical research typically proceeds in two stages.
+First, belief in the existence of an effect is established.
+Second, its generalizability is examined by exploring its boundary conditions.
+In the first stage, inferential statistics are used to minimize the risk that a discovery is due to sampling error.
+In the second stage, we ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
+This extent is often explored through replications of the original study with some variation, and once sufficient studies have accumulated through meta-analysis.
 In meta-analysis, the heterogeneity of an effect size (henceforth referred to as heterogeneity) is a measure of an effect's susceptibility to changes in these four factors.
 An effect strongly dependent on one or more of the four factors, unless controlled for, should exhibit high heterogeneity.
+Heterogeneity is often measured by the I2 index [ref: Higgins & Higgins], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
+It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects (that is, dependency on contextual factors) rather than sampling variance, and ranges from 0-100%.
 
 Heterogeneity is of concern for several reasons.
-First, it affects the interpretation of the meta-analytic estimate as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity).
-Second, if boundary conditions are unknown, heterogeneity makes it more difficult to 'successfully' replicate an effect.
-In the presence of heterogeneity even a well-powered single study may capture the average true effect in less than 50% of cases [ref: Voelkl].
-Third, meta-analytic techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht, McShane].
+First and foremost, unaccounted for heterogeneity can have unacceptable consequences.
+This may be most readily evident for medicine, where in the case of heterogeneity an intervention that is successful for some may have direct negative health consequences for others, but the adoption of psychological research for business, law enforcement, and policymaking in general (e.g., the widespread use of 'nudges'; https://www.knowablemagazine.org/article/society/2018/nudging-grows-and-now-has-government-job) means its impact can be widespread and the consequences of heterogeneity should be no less a concern.
+Second, unaccounted for heterogeneity is an indication of incomplete theory, since it indicates that a theory is unable to predict all contextual factors of importance to its claims.
+While heterogeneity reveals that a theory has flaws, by itself it does not damn a theory, and can be seen as an opportunity for theoretical advancement [ref: Tacket et al].
+Third, heterogeneity can create controversy in the interpretation of replication results.
+The lack of a clear line for the degree of heterogeneity (susceptibility to contextual factors) that would make an effect uninteresting often results in heated discussions between original and replication authors.
+In response to this common polemic [ref Simons et al] recently proposed that authors include a statement to explicitly delineate the level of heterogeneity that would make an effect lose its value.
+Fourth, meta-analytic techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht, McShane].
+This is problematic considering the widespread publication bias [refs] and its biasing impact on meta-analytic estimates.
+Finally, heterogeneity affects the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity)
 
-Several recent papers have argued that heterogeneity is the norm in psychology [ref: Tacket et al, McShane et al].
-These authors argue that, if anywhere we would expect heterogeneity to be absent or minimal, it would be in pre-registered multi-lab studies with a common protocol, and the fact that heterogeneity has been found even under such circumstances [e.g., ref: Many Labs 1] is an indication that heterogeneity is widespread in psychology.
+It is a common belief that heterogeneity is the norm in psychology.
+For example, several authors [ref: Tacket et al, McShane et al] argue that if we would expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab studies with a common protocol, and that heterogeneity has been reported even under such circumstances [e.g., ref: Many Labs 1] is an indication of widespread heterogeneity in psychology.
 In addition, recent large scale reviews of meta-analyses in psychology [ref: Stanley; van Erp et al] report that much variability in effect sizes can be attributed to heterogeneity, with median estimates of 74% and 70.62% respectively [ref: Stanley].
+In comparison, the median heterogeneity estimate in medicine is considerably lower; 21% amongst Cochrane meta-analyses [ref: Ioannidis  "uncertainty in heterogeneity"].
+However, in our experience psychologist tend to include widely varying studies in their meta-analyses, sometimes varying on all four contextual factors (or more), whereas this is less common in medicine.
+This is perhaps unsurprising considering the lack of delineating theory in psychology [ref: Simons et al].
+In support of this notion, Ioannidis reports that, even after excluding meta-analyses of 3 or fewer studies, the median number of studies included in Cochrane meta-analyses is only 7, whereas in the dataset of [ref: van Erp et al] containing 747 meta-analyses in psychology, the median number of studies (effects) per meta-analysis is 12.
 
-As authors, we caution against broad claims of particular heterogeneity levels in psychology and have multiple concerns.
-Namely, we argue that the role of effect sizes is both underestimated (when large) and overestimated (when small) when considering heterogeneity.
-In addition, we believe that too much attention is paid to point estimates in view of the uncertainty conferred by accompanying confidence intervals.
-We choose to dwell less on this latter point as it has already been well-made previously [ref: Ioannidis].
-Generally, we argue that the current evidence is insufficient to make general claims about the prevalence of heterogeneity in psychology.
+Heterogeneity (I2) estimates typically contain considerable uncertainty.
+The I2 index is a transformation of the Q-test [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative I2 is set to zero.
+However, both the Q-test and I2 have low power [ref: Jackson; Huedo-Medina].
+This complicates the discussion of heterogeneity, because while I2 always provides an estimate of heterogeneity, this estimate is typically surrounded by large uncertainty [ref: Ioannidis  "uncertainty in heterogeneity"].
+For example, Ioannidis reports that in a large set of Cochrane meta-analyses all studies with I2 point estimates of 0% had upper 95% confidence intervals that exceeded 33%.
+In addition, under homogeneity Q, and hence I2, has a central chisquare distribution [ref: von Hippel], a distribution that is right-skewed with more than 40% of the distribution falling above the expected value in almost all cases (for all k > 4).
+In other words, even in the absence of heterogeneity, a meta-analysis of 5 or more studies will have an I2 estimate above zero in more than 40% of cases.
+Point estimates (expected values) of heterogeneity may thus be congruent with a wide range of true heterogeneity levels.
+It is unfortunately common to not include confidence intervals in the reporting of I2 [e.g., Ml1 and RRRX].
 
-Larger effect sizes lead to more heterogeneity.
-In classical test theory, an observed correlation $r_{xy}$ is equivalent to the true correlation $\rho_{xy}$ multiplied by the square root of the measurement reliabilities for X ($R_{xx'}$) and Y ($R_{yy'}$): $r_{xy} = \rho_{xy} \times \sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$.
-Across different studies of the same effect the measurement reliabilities will differ either due to sampling variance (that the sample happens to be more or less homogenous) or to small (or large) differences in contextual factors (e.g., location).
-Given that the reliabilities will differ between studies, so will the observed effect sizes even when the underlying effect size is the same.
-It follows from the above presented equation that the larger the underlying effect size is, the larger the differences between observed effect sizes in studies with differing reliabilities will be.
-Hence the estimated heterogeneity will increase with effect size.
+Larger effect sizes can be expected to lead to more heterogeneity.
+Intuitively, it makes sense to think that if there is no meta-analytic effect there is nothing to moderate (i.e., no heterogeneity).
+However, a null or near null effect size estimate may arise from failure to consider contextual factors ('hidden moderators', [ref: van Bavel]) and does not by itself imply the absence of heterogeneity.
+This is especially true when the uncertainty in I2 estimates (see above) is taken into account.
+A large effect size on the other hand, can be expected to lead to more heterogeneity.
+To illustrate, consider a meta-analysis of say, the correlation between neuroticism and procrastination.
+Each included study would need to measure the two variables somehow, hopefully the same way across studies.
+However, because of individual differences, measurement is not equally exact for everyone, and between studies the measurement reliabilities will differ either due to sampling variance (that the sample happens to be more or less homogenous) or to differences in contextual factors (e.g., sampling population, method of measurement).
+This means that even if the underlying effect size is the same, the observed correlation between the two variables will differ between studies.
+If measurement reliabilities stays the same, these differences will increase with the underlying effect, resulting in more variability being ascribed to heterogeneity.
+More formally, an observed correlation $r_{xy}$ is equivalent to the true correlation $\rho_{xy}$ multiplied by the square root of the measurement reliabilities for X ($R_{xx'}$) and Y ($R_{yy'}$): $r_{xy} = \rho_{xy} \times \sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$.
+As such, if $\sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$ stays constant while $\rho_{xy}$ increases, the observed differences between studies will increase (see Table 2).
 
-A null meta-analytic effect size does not imply absence of heterogeneity.
-Intuitively, it makes sense to think that if there is no effect there is nothing to moderate (i.e., no heterogeneity).
-However, while this might often be true it is by no means a truism.
-A null or near null effect size estimate may arise from failure to consider contextual factors ('hidden moderators', [ref: van Bavel]) and does not by itself imply the absence of heterogeneity.
-This is especially true when heterogeneity confidence intervals are also taken into account.
+##Table 1.
+###Heterogeneity may increase with effect size
+```{r effect-size-heterogeneity-table}
+#library(kableExtra)
+rooted_relabilities <- matrix(rep(c(.8, .7,.6), 3), ncol = 3)
+rho <- c(0, .5, .8)
+rel <- c("R = .8", "R = .7", "R = .6")
 
-In the following sections we clarify and illustrate our concerns using empirical data and the I2 index as a measure of heterogeneity [ref: Higgins & Higgins].
-We make use of summary data from 10 pre-registered multi-lab replications that examined a total of 36 psychological effects (see Table 1).
-These data arguably represent the best, least biased, meta-analytic data available in psychology.
-The I2 index is an intuitive and much-used measure of heterogeneity which ranges from 0% to 100%.
-It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects rather than sampling variance and is a transformation of the Q-test [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis.
-I2 is a relative measure of heterogeneity that allows comparison of estimates across meta-analyses.
+rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
+diff_row <- data.frame(rel = "Diff.", X1 = 0, X2 = 0.05, X3 = 0.08)
 
-##Table 1
+het_demo <- data.frame(rel, rooted_relabilities)
+het_demo <- rbind(het_demo, diff_row)
+
+het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "Rho = 0", "Rho = .5", "Rho = .8")) %>% 
+  kable_styling() %>% 
+  footnote(threeparttable = TRUE,
+           general = "R = square root of the multiplied reliabilities") %>% 
+  row_spec(3, hline_after = T)
+
+```
+We explore heterogeneity across 10 pre-registered multi-lab replication projects in psychology (Table 2).
+In light of the uncertainty surrounding I2-estimates we review what can be learnt about heterogeneity in psychology from these projects, as well as explore the relationship between effect size and heterogeneity.
+These 10 projects examine a total of 37 effects and arguably represent the best, least biased, meta-analytic data currently available in psychology.
+All included studies vary on a minimal number of contextual factors [as recognized by e.g., Tacket et al]: only sample population and settings.
+Nonetheless, if an effect is sensitive to changes in these factors we may still expect to find some heterogeneity.
+On the other hand, heterogeneity estimates will only inform us of susceptibility to changes in these two factors, with no information on susceptibility to changes in other contextual factors.
+
+##Table 2.
 ```{r data-summary-table}
@@
 
+#Shortened version of APA reference
+papers <- c('Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams, R.
+B., Jr., Bahník, S., Bernstein, M.
+J., .
+.
+.
+Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A "many labs" replication project.',
+'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
+'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
+'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
+'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011).',
+'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
+'Cheung, I., Campbell, L., LeBel, E.
+P., Ackerman, R.
+A., Aykutoglu, B., Bahník, S., ...
+& Carcedo, R.
+J.
+(2016).
+Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).',
+'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
+'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
+"O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")
+
 summary.table <- dat %>% 
   group_by(rs) %>% 
-  summarize(Labs = n_distinct(Site),
+  summarize(k = n_distinct(Site),
             Countries = n_distinct(country), 
@@
                            else{sum(Ntotal) / Effects}) %>% #average across effects
-  rename(Study = rs)
+  mutate(Paper = papers) %>% 
+  select(RS = rs, Paper, everything()) #change order of columns
 
 summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
-  kable_styling(position = "left") %>% 
+  kable_styling() %>% 
+  column_spec(2, width = "25em") %>% #specify width of paper column
   footnote(threeparttable = TRUE,
@@
 Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
-ML = Many Labs, RRR = Registered Replication Report.")
+RS = Replication Study, k = no.
+primary studies, ML = Many Labs, RRR = Registered Replication Report.")
 ```
+
+###Method
+
+All code and data for this project is available on the Open Science Framework (OSF) at osf.io/XXXX.
+We refer to relevant files on OSF using brackets and links in the sections below, that is (osf.io/XXXX/).
+We ran all analyses using R version X [ref: R citation].
+
+We downloaded and collated summary data from 10 pre-registered multi-lab replication projects in psychology (Table 2).
+Data from all 10 projects were publicly available on the Open Science Framework (osf.io).
+Although some projects (e.g.
+RRR4) reported results from several outcome variables, we only included primary outcome variables as stated in accompanying publications, resulting in a total of 37 effects.
+For each effect we extracted (osf.io/XXXX/) summary data (e.g., means and standard deviations) at the level of the lab as specified by the original authors for their primary analysis (i.e., typically after exclusions).
+We extracted information on the country of each lab, whether participants were physically in the lab for the study, total number of participants per lab, type of effect size and additional information related to each effect (see codebook; osf.io/XXXX/).
+Extracted data were in a variety of formats: Excel (Many labs 1, RRR1 & RRR2), CSV (Many labs 3, RRR3, RRR4, RRR5, RRR6) and as PDF tables (RRR7, RRR8).
+In two cases (RRR5 and RRR6) it was necessary to download the raw data to extract their summary data.
+Although a particular lab may have participated in several projects, the lab indicator was typically not the same across projects.
+Even so, we kept the original lab indicators to facilitate comparing observations in our dataset with the original datasets.
+The summary data for all effects were finally collated into one dataset for analysis (osf.io/XXXX/).
+
+To examine heterogeneity across effects we computed meta-analytic estimates for all 37 effects in our dataset (Table 3).
+We ran each analysis using the specifications of the replication project authors, with the addition of the Knapp & Hartung adjustment [ref] if it was not already used, since we were primarily interested in heterogeneity estimates (osf.io/XXXX/).
+All studies used random-effects models, though with a variety of outcome variable types: Correlations, standardized mean differences, raw mean differences, odds ratios and risk differences.
+For each effect we estimated I2 and its 95% confidence interval.
+
+To examine the relationship between effect size and I2 we converted all effect sizes to a common metric (osf.io/XXXX/).
+We first converted all effects into correlations (r) and used the R-package metafor [ref] to estimate I2 and meta-analytic effects expressed as Fisher's z.
+In doing so, we fit random-effects models with the Knapp and Hartung adjustment and metafor's default estimator of Restricted Maximum Likelihood.
+Fisher's z is a normalizing correlation transformation that ranges from negative to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [ref].
+For mean differences we calculated the pooled standard deviation, [ref Cooper & Hedges, 1994, p.
+226), standardized the effect size and converted it to a correlation (p.
+234) with a correction factor for unequal sample sizes (p.
+234).
+For risk differences and odds ratios we first added 1/2 to a cell if it was empty to avoid dividing by zero [ref?], next calculated the logarithmic odds ratio (p.
+266), converted this to Cohen's d (p.
+232) and then to a correlation.
+All formulas are presented in Appendix A.
+
+##Results
+
+Table 3 presents the meta-analytic estimates and I2 with confidence intervals for each of the 37 included effects.
+
+##Table 3.
+```{r heterogeneity-table}
+library(kableExtra)
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE,digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Size", "I2(%)", "ci.lb", "ci.ub")) %>% 
+  kable_styling("scale_down") %>%
+  footnote(threeparttable = TRUE, escape = FALSE,
+           general = "We meta-analyzed effects using the same outcome measures that were used by the original authors.
+Standardized mean difference is Hedge's g.
+The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs.
+forbidden', 'Gain vs.
+loss framing', 'Norm of reciprocity', 'Low vs.
+high category scales'.
+Effects were estimated in metafor using REML with the 'knha' correction.
+RS = Replication Study, k = no.
+primary studies, Size = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval.
+SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.")
+
+```
+
+What can be learnt from the null I2 point estimates?
+As can be seen from table 3, 13/37 (35%) I2 point estimates are zero.
+If there was no heterogeneity across all effects we would expect approximately 50-55% of point estimates to be zero (based on the chisquare distribution and k across studies), that is around 20/37.
+This supports that there is some heterogeneity across the studied effects.
+Looking at the confidence intervals of the null estimates we see that in all cases the lower bounds of their confidence intervals are zero, whereas the upper bound varies from 13.75% (Stroop effect) up to 70.62% (Grammar on intention attribution).
+The three with the highest upper bounds (70.62%, 54.49%, 53.18%) belong to the two replication studies with the lowest k, possibly indicating a lack of power.
+[ref: Higgins et al] tentatively defined 25% as low heterogeneity, 50% as moderate and 70% as high.
+Of the upper confidence bounds of the null effects 8/13 lie closest to Higgin's low heterogeneity, 4/13 to moderate, and 1/13 to high.
+Thus of the null estimates eight are likely low in heterogeneity, whereas there is considerable uncertainty for the remaining five.
+
+What can be learnt from the non-null I2 point estimates?
+The non-null point estimates of heterogeneity vary from 0.01% to 91.29%.
+Of these, 16/24 have point estimates that are closest to 'low' heterogeneity, 4/24 to medium and 4/24 to high.
+Seventeen (71%) have lower confidence bounds of zero heterogeneity and all have upper confidence bounds approaching medium/large heterogeneity.
+In the majority of non-null I2 point estimates there is thus large uncertainty surrounding heterogeneity levels.
+
+What can be learnt from the significant I2 estimates?
+Seven out of the 37 effects (19%) have confidence intervals whose lower bounds exclude zero.
+The point estimates of these effects all approach at least medium heterogeneity, varying from 40.05% to 91.29%.
+Three of the effects have lower confidence bounds closest to low heterogeneity, and the other four to either medium or high heterogeneity.
+The upper confidence bounds of all seven are consistent with high heterogeneity.
+That is, we can be confident that heterogeneity is medium - large for four effects, whereas the remaining three estimates are consistent with anything from low to high heterogeneity.
+
+What have we learnt from the 10 pre-registered multi-lab replication projects in Table 3 about heterogeneity in psychology?
+Because the included effects are neither a representative nor random sample of effects we cannot make broad claims about heterogeneity in psychology based on these data.
+Nonetheless, we can with some confidence claim that amongst the examined effects there is heterogeneity, or we would have expected to find a higher proportion of null I2 estimates.
+Examining the 95% confidence intervals, we can be confident that 8/37 (22%) have low heterogeneity (as defined by [ref: Higgins]), 4/37 (11%) have moderate to high heterogeneity whereas for the remaining 25 effects (68%) there is considerable uncertainty, with estimates consistent with low-moderate or low-high heterogeneity.
+Because the replication projects only varied on sampling population and settings, we know nothing about the effects' susceptibility to changes in treatment or measurement variables.
+
+Larger effect sizes appear to lead to higher heterogeneity estimates (Figure 1).
+In Table 3, the four effects with highest I2 estimates also have the largest effect sizes.
+As expected, heterogeneity tends to increase with (absolute) effect size, with effect size sufficient to explain 61% of variation in I2 estimates according to a simple regression model.
+The I2 index is truncated at zero, however, the closely related but unbounded heterogeneity estimate H2 provides a similar result (R2 = .53).
+
+##Figure 1
+```{r}
+knitr::include_graphics("../code/effect_het.png")
+```
+
+##Discussion
 

### 2018-06-04 code/figures.rmd
Double-checked computations for table, cleaned up figures file

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.asp = 1.3)
 ```
@@
 ```{r load data and packages}
-library(readr)
-library(dplyr)
-library(kableExtra)
-library(purrr)
-library(metafor)
+library(readr) #To load data
+library(dplyr) #For data transformation
+library(purrr) #For data transformation
+library(metafor) #To run meta-analyses
+library(ggplot2) #Plot data
+library(cowplot) #Combine several plots into one
 
@@
 
-I have four different types of effects to transform to raw correlations:
-- mean difference + SE
-- mean difference + SD
-- RD
-- OR
+```{r transformation_functions}
+#Formulas found in: 
+#Borenstein, M.
+(2009).
+Effect sizes for continuous data.
+In H.
+Cooper, L.
+V.
+Hedges, & J.
+C.
+Valentine (Eds.), The handbook of research synthesis and meta-analysis (2nd ed., pp.
+221-235).
+New York: Russell Sage Foundation.
 
-Should I first run MA and then transform effect sizes?
-->Not sure how how to treat the raw mean differences, since I only get the MA-estimate estimate and the SE.
-More straightforward to convert to common metric first.
-**Kolden + Ihle give formulas.** From book Cooper & Hedges, 1994.
-
-```{r transformation_functions}
 #For raw mean difference + SE
-transform_SE <- function(ES, SE, n1, n2){ #ES -> SDp based on meta-analysis lecture 02
-  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2))
+transform_SE <- function(ES, SE, n1, n2){ 
+  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2)) #Borenstein, M. (2009). In Cooper & Hedges. p. 224
   d <- ES / sdpooled
-  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes
-  r <- d / sqrt(d^2 + corr)
+  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes. p.234
+  r <- d / sqrt(d^2 + corr) #p.234
   data.frame(r = r, n = n1 + n2)
@@
 }
+
 ```
 
-Transform effect sizes to raw correlations
 ```{r transform_df}
+#Transform effect sizes to raw correlations
 res <- dat %>% 
   split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(transform_MA, .id = "effect")
+  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe
 
-res %>% filter(!is.na(r) & r > 1) #checks
-res %>% filter(is.na(r)) #Checks
 ```
-
-Seems okay. Metafor takes raw correlations as input for Fisher's z transformed rma.
 
@@
 summarizer <- function(x){
-  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, test = "knha", data = x) #takes raw correlation as input
-  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / fit$k) #estimate out
+  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
+  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1)) #estimates out
 }
-#Alternative version of calculating I2 does not make conceptual sense because gives negative values.
-Alternative method for calculating H2 provides information also on excessive homogeneity (i.e, less variability than expected by chance) for those interested.
-(that is, does not have a lower limit of 1)
+#Default method of metafor for calculating H2 is truncated at one.
+Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1).
+This method computes H2 as originally specified by Higgins & Thompson instead of using the more general method of metafor (see ?print.rma.uni).
+
+#Higgins, J., & Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. Statistics in medicine, 21(11), 1539-1558.
 
@@
   map_dfr(summarizer, .id = "effect") %>% 
-  mutate(z = abs(z)) #We are interested in effect size rather than direction
+  mutate(z = abs(z)) #Absolute values since we are interested in effect size rather than direction
 ```
 
-Above seems to do what it should.
-
 ```{r plot_res}
-library(ggplot2)
 
@@
 # ggsave("H2_effect_size.png")
-library(cowplot)
 
-effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v")
+effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
+effect_het
 # save_plot("effect_het.png", effect_het,
@@
 
-Note that Fisher's z are the absolute z-scores, because we are interested in effect size rather than direction.
-
-```{r labelled_plot}
-library(ggplot2)
-
+```{r labelled_plot, fig.asp= 0.618}
 ggplot(res2, aes(x = z, y = I2, label = effect)) +
   geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = FALSE) +
-  geom_text(alpha = 0.3)
+  geom_smooth(method = "lm", se = FALSE, color = "black") +
+  xlab("Fisher's z") +
+  coord_cartesian(ylim = c(0, 100)) +
+  theme_classic() +
+  geom_text(alpha = 0.5)
 ```
-
-Qs: Should I keep the I2 based on the original scales, but transform the effect sizes and plot that instead (seems not unreasonable since I2 depends on effect type).
--> This seems to make little difference, see below.
-
-```{r}
-est_heterogen_smd_raw <- function(x){
-  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
-
-    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){
-
-    fit <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)
-
-  } else if(any(x[, "effect_type"] == "Raw mean difference")){
-
-    fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){
-
-    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
-
-  } else if(any(x[, "effect_type"] == "r")){
-
-    fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)
-
-  } else{ #for all two-group count effects
-
-    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but that = 'OR2DL'
-               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
-
-  }
-
-  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
-             p = fit$pval,
-             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
-}
-
-#Apply function to data
-res3 <- dat %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
-  select(effect, s_I2) %>% 
-  left_join(res2, .)
-
-```
-
-```{r}
-ggplot(res3, aes(x = z, y = s_I2)) +
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE)
-
-summary(lm(s_I2 ~ z, data = res3)) #b = 68.23, R2 = 0.67
-```

### 2018-06-04 code/tables.rmd
Double-checked computations for table, cleaned up figures file

@@
 
-    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
+    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol,  data = x)
 
@@
 
-    fit <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)
+    fit <-  rma(yi = effect_size, sei = outcome_c2,  data = x)
 
   } else if(any(x[, "effect_type"] == "Raw mean difference")){
+    if(any(x[, "rs"] %in% c("RRR5", "RRR7"))){ #For these us the Knapp and Hartung adjustment of standard errors
 
-    fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
+      fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, test ="knha", data = x)
+    } else{
+      fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
+    }
 
@@
 
-    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
+    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
 
   } else if(any(x[, "effect_type"] == "r")){
-
-    fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)
+    if(any(x[, "rs"] == "ML1")){
+      fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal,  data = x)
+    } else{ #for ML3
+      fit <- rma(measure = "UCOR", ri = effect_size, ni = Ntotal,  data = x, vtype = "UB")
+      #Note that ML3 specifies measure = "COR" with vtype = "UB", but that this is specified as above in the latest metafor 
+    }
 
@@
 
-    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but that = 'OR2DL'
-               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
+    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, 
+               n1i = ntreatment, n2i = ncontrol,  data = x)
+    #standardized, ML1 used 'OR2D' which = 'OR2DL' in latest version of metafor
 

### 2018-06-06 writing/draft-heterogeneity.rmd
Updated paper draft

@@
 ---
-title: "Reviewing evidence for heterogeneity in psychology"
+title: "Limited evidence for widespread heterogeneity in psychology"
 author: "Anton Ohlsson Collentine"
@@
    - \setlength\parindent{24pt}
+   - \usepackage{setspace}
+   - \doublespacing
 output: pdf_document
@@
 Second, its generalizability is examined by exploring its boundary conditions.
-In the first stage, inferential statistics are used to minimize the risk that a discovery is due to sampling error.
+In the first stage, we use inferential statistics  to minimize the risk that a discovery is due to sampling error.
 In the second stage, we ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
@@
 An effect strongly dependent on one or more of the four factors, unless controlled for, should exhibit high heterogeneity.
-Heterogeneity is often measured by the I2 index [ref: Higgins & Higgins], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
-It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects (that is, dependency on contextual factors) rather than sampling variance, and ranges from 0-100%.
+In this paper we examine what degree of heterogeneity can be expected in replication studies in psychology and explore a proposed relationship with effect size.
 
@@
 First and foremost, unaccounted for heterogeneity can have unacceptable consequences.
-This may be most readily evident for medicine, where in the case of heterogeneity an intervention that is successful for some may have direct negative health consequences for others, but the adoption of psychological research for business, law enforcement, and policymaking in general (e.g., the widespread use of 'nudges'; https://www.knowablemagazine.org/article/society/2018/nudging-grows-and-now-has-government-job) means its impact can be widespread and the consequences of heterogeneity should be no less a concern.
-Second, unaccounted for heterogeneity is an indication of incomplete theory, since it indicates that a theory is unable to predict all contextual factors of importance to its claims.
+This may be most readily evident for medicine, where in the case of heterogeneity an intervention that is successful for some may have direct negative health consequences for others.
+However, the adoption of psychological research for business, law enforcement, and policymaking in general (e.g., the widespread use of 'nudges'; https://www.knowablemagazine.org/article/society/2018/nudging-grows-and-now-has-government-job) means its impact can be widespread and the consequences of heterogeneity should be no less a concern for psychologists.
+Second, unaccounted for heterogeneity is an indication of incomplete theory, since it suggests that a theory is unable to predict all contextual factors of importance to its claims.
 While heterogeneity reveals that a theory has flaws, by itself it does not damn a theory, and can be seen as an opportunity for theoretical advancement [ref: Tacket et al].
@@
 The lack of a clear line for the degree of heterogeneity (susceptibility to contextual factors) that would make an effect uninteresting often results in heated discussions between original and replication authors.
-In response to this common polemic [ref Simons et al] recently proposed that authors include a statement to explicitly delineate the level of heterogeneity that would make an effect lose its value.
-Fourth, meta-analytic techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht, McShane].
-This is problematic considering the widespread publication bias [refs] and its biasing impact on meta-analytic estimates.
-Finally, heterogeneity affects the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity)
+In response to this common area of disagreement [ref Simons et al] recently proposed that authors include a statement to explicitly delineate the level of heterogeneity that would make an effect lose its value.
+Fourth, meta-analytic techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht; McShane].
+This is problematic considering widespread publication bias [refs] and its impact on meta-analytic estimates.
+Finally, heterogeneity affects the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity).
 
 It is a common belief that heterogeneity is the norm in psychology.
-For example, several authors [ref: Tacket et al, McShane et al] argue that if we would expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab studies with a common protocol, and that heterogeneity has been reported even under such circumstances [e.g., ref: Many Labs 1] is an indication of widespread heterogeneity in psychology.
+For example, several authors [ref: Tacket et al, McShane et al] argue that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol, and that heterogeneity has been reported even under such circumstances [e.g., ref: Many Labs 1] is an indication of widespread heterogeneity in psychology.
 In addition, recent large scale reviews of meta-analyses in psychology [ref: Stanley; van Erp et al] report that much variability in effect sizes can be attributed to heterogeneity, with median estimates of 74% and 70.62% respectively [ref: Stanley].
-In comparison, the median heterogeneity estimate in medicine is considerably lower; 21% amongst Cochrane meta-analyses [ref: Ioannidis  "uncertainty in heterogeneity"].
-However, in our experience psychologist tend to include widely varying studies in their meta-analyses, sometimes varying on all four contextual factors (or more), whereas this is less common in medicine.
-This is perhaps unsurprising considering the lack of delineating theory in psychology [ref: Simons et al].
-In support of this notion, Ioannidis reports that, even after excluding meta-analyses of 3 or fewer studies, the median number of studies included in Cochrane meta-analyses is only 7, whereas in the dataset of [ref: van Erp et al] containing 747 meta-analyses in psychology, the median number of studies (effects) per meta-analysis is 12.
+In comparison, the median heterogeneity estimate in medicine is considerably lower: 21% amongst Cochrane meta-analyses [ref: Ioannidis  "uncertainty in heterogeneity"].
+
+Heterogeneity is often measured by the I2 index [ref: Higgins & Higgins], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
+It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects (that is, dependency on contextual factors) rather than sampling variance, and ranges from 0-100%.
+The I2 index is a transformation of the Q-test [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative I2 is set to zero.
 
 Heterogeneity (I2) estimates typically contain considerable uncertainty.
-The I2 index is a transformation of the Q-test [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative I2 is set to zero.
-However, both the Q-test and I2 have low power [ref: Jackson; Huedo-Medina].
-This complicates the discussion of heterogeneity, because while I2 always provides an estimate of heterogeneity, this estimate is typically surrounded by large uncertainty [ref: Ioannidis  "uncertainty in heterogeneity"].
-For example, Ioannidis reports that in a large set of Cochrane meta-analyses all studies with I2 point estimates of 0% had upper 95% confidence intervals that exceeded 33%.
-In addition, under homogeneity Q, and hence I2, has a central chisquare distribution [ref: von Hippel], a distribution that is right-skewed with more than 40% of the distribution falling above the expected value in almost all cases (for all k > 4).
-In other words, even in the absence of heterogeneity, a meta-analysis of 5 or more studies will have an I2 estimate above zero in more than 40% of cases.
+Both the Q-test and I2 have low power [ref: Jackson; Huedo-Medina].
+This complicates the discussion of heterogeneity, because while I2 always provides an estimate of heterogeneity, this estimate is often surrounded by wide confidence intervals [ref: Ioannidis  "uncertainty in heterogeneity"].
+For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with I2 point estimates of 0% had upper 95% confidence intervals that exceeded 33%.
+In addition, under homogeneity I2 has a central chisquare distribution [ref: von Hippel], a distribution that is right-skewed with more than 40% of observations falling above the expected value in almost all cases (for all k > 4).
+In other words, even in the absence of heterogeneity, a meta-analysis of 5 or more studies will have an I2 point estimate above zero in more than 40% of cases.
 Point estimates (expected values) of heterogeneity may thus be congruent with a wide range of true heterogeneity levels.
-It is unfortunately common to not include confidence intervals in the reporting of I2 [e.g., Ml1 and RRRX].
+Despite exhortations to the contrary [ref: Ioannidis "uncertainty in heterogeneity"] , it remains common to omit confidence intervals in the reporting of I2 [e.g., ML1 and ML3].
 
-Larger effect sizes can be expected to lead to more heterogeneity.
+Effect size influences heterogeneity.
 Intuitively, it makes sense to think that if there is no meta-analytic effect there is nothing to moderate (i.e., no heterogeneity).
@@
 To illustrate, consider a meta-analysis of say, the correlation between neuroticism and procrastination.
-Each included study would need to measure the two variables somehow, hopefully the same way across studies.
+Each included study would need to measure the two variables somehow, possibly the same way across studies.
 However, because of individual differences, measurement is not equally exact for everyone, and between studies the measurement reliabilities will differ either due to sampling variance (that the sample happens to be more or less homogenous) or to differences in contextual factors (e.g., sampling population, method of measurement).
 This means that even if the underlying effect size is the same, the observed correlation between the two variables will differ between studies.
-If measurement reliabilities stays the same, these differences will increase with the underlying effect, resulting in more variability being ascribed to heterogeneity.
+If measurement reliabilities stay the same, these differences will increase with the underlying effect, resulting in more variability being ascribed to heterogeneity.
 More formally, an observed correlation $r_{xy}$ is equivalent to the true correlation $\rho_{xy}$ multiplied by the square root of the measurement reliabilities for X ($R_{xx'}$) and Y ($R_{yy'}$): $r_{xy} = \rho_{xy} \times \sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$.
-As such, if $\sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$ stays constant while $\rho_{xy}$ increases, the observed differences between studies will increase (see Table 2).
+As such, if $\sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$ stays constant while $\rho_{xy}$ increases the observed differences between studies will increase (see Table 2).
 
@@
 ```
-We explore heterogeneity across 10 pre-registered multi-lab replication projects in psychology (Table 2).
-In light of the uncertainty surrounding I2-estimates we review what can be learnt about heterogeneity in psychology from these projects, as well as explore the relationship between effect size and heterogeneity.
-These 10 projects examine a total of 37 effects and arguably represent the best, least biased, meta-analytic data currently available in psychology.
+We examine heterogeneity across 10 pre-registered multi-lab replication projects in psychology (Table 2).
+In light of the uncertainty surrounding I2-estimates we explore what conclusions can be drawn about heterogeneity in psychology from these projects, as well as the relationship between effect size and heterogeneity.
+These 10 projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
 All included studies vary on a minimal number of contextual factors [as recognized by e.g., Tacket et al]: only sample population and settings.
-Nonetheless, if an effect is sensitive to changes in these factors we may still expect to find some heterogeneity.
+Nonetheless, contrary to the argument of [Tacket et al], if an effect is sensitive to changes in these factors we may still expect to find some heterogeneity.
 On the other hand, heterogeneity estimates will only inform us of susceptibility to changes in these two factors, with no information on susceptibility to changes in other contextual factors.
@@
 RS = Replication Study, k = no.
-primary studies, ML = Many Labs, RRR = Registered Replication Report.")
+primary studies, ML = Many Labs, RRR = Registered Replication Report.
+(OSF.io/XXXX)")
 ```
@@
 
-All code and data for this project is available on the Open Science Framework (OSF) at osf.io/XXXX.
+All code and data for this project are available on the Open Science Framework (OSF) at osf.io/XXXX.
 We refer to relevant files on OSF using brackets and links in the sections below, that is (osf.io/XXXX/).
@@
 We downloaded and collated summary data from 10 pre-registered multi-lab replication projects in psychology (Table 2).
-Data from all 10 projects were publicly available on the Open Science Framework (osf.io).
+Data from all 10 projects were publicly available on the Open Science Framework (osf.io) and downloaded between 2018/02/01 and 2018/03/31.
 Although some projects (e.g.
@@
 For each effect we extracted (osf.io/XXXX/) summary data (e.g., means and standard deviations) at the level of the lab as specified by the original authors for their primary analysis (i.e., typically after exclusions).
-We extracted information on the country of each lab, whether participants were physically in the lab for the study, total number of participants per lab, type of effect size and additional information related to each effect (see codebook; osf.io/XXXX/).
+We extracted information on the country of each lab, whether participants were physically in the lab for the study, total number of participants per lab, type of effect size, and additional information related to each effect (see codebook; osf.io/XXXX/).
 Extracted data were in a variety of formats: Excel (Many labs 1, RRR1 & RRR2), CSV (Many labs 3, RRR3, RRR4, RRR5, RRR6) and as PDF tables (RRR7, RRR8).
-In two cases (RRR5 and RRR6) it was necessary to download the raw data to extract their summary data.
+In two cases (RRR5 and RRR6) it was necessary to download the raw data to extract summary data.
 Although a particular lab may have participated in several projects, the lab indicator was typically not the same across projects.
 Even so, we kept the original lab indicators to facilitate comparing observations in our dataset with the original datasets.
-The summary data for all effects were finally collated into one dataset for analysis (osf.io/XXXX/).
+Finally, we collated he summary data for all effects into one dataset for analysis (osf.io/XXXX/).
 
-To examine heterogeneity across effects we computed meta-analytic estimates for all 37 effects in our dataset (Table 3).
-We ran each analysis using the specifications of the replication project authors, with the addition of the Knapp & Hartung adjustment [ref] if it was not already used, since we were primarily interested in heterogeneity estimates (osf.io/XXXX/).
-All studies used random-effects models, though with a variety of outcome variable types: Correlations, standardized mean differences, raw mean differences, odds ratios and risk differences.
+To examine heterogeneity across effects, we computed meta-analytic estimates for all 37 effects in our dataset (Table 3).
+We ran all analyses as specified by the replication authors (osf.io/XXXX/).
+All effects were estimated with random-effects models and the Restricted Maximum Likelihood (REML) estimator using the R-package metafor [ref], though with a variety of outcome variables: correlations, standardized mean differences, raw mean differences, odds ratios and risk differences.
+ML1 transformed odd ratios into standardized mean differences when meta-analyzing under the assumption that responses followed logistic distributions [ref: Sanchez-Meca; metafor].
+Two projects (RRR5 and RRR7) used the Knapp and Hartung adjustment of the standard errors [ref: Knapp & Hartung] and ML3 correlations were corrected for bias [ref: Hedges 1989; metafor].
+After estimating effects, Ml3 transformed correlations into eta-squared for reporting, which we did not.
 For each effect we estimated I2 and its 95% confidence interval.
+Confidence intervals were calculated in metafor which uses the Q-profile method [ref Jackson 2014].
 
 To examine the relationship between effect size and I2 we converted all effect sizes to a common metric (osf.io/XXXX/).
+Since I2 is logically and mathematically bounded at zero, we also correlated effect sizes with the closely related heterogeneity estimate H2, which is calculated as $H2 = Q / (k - 1)$.
 We first converted all effects into correlations (r) and used the R-package metafor [ref] to estimate I2 and meta-analytic effects expressed as Fisher's z.
-In doing so, we fit random-effects models with the Knapp and Hartung adjustment and metafor's default estimator of Restricted Maximum Likelihood.
+In doing so, we fit random-effects models with metafor's default REML estimator.
 Fisher's z is a normalizing correlation transformation that ranges from negative to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [ref].
-For mean differences we calculated the pooled standard deviation, [ref Cooper & Hedges, 1994, p.
+For mean differences we calculated the pooled standard deviation, [ref Borenstein in Cooper & Hedges, 2009, p.
 226), standardized the effect size and converted it to a correlation (p.
@@
 234).
-For risk differences and odds ratios we first added 1/2 to a cell if it was empty to avoid dividing by zero [ref?], next calculated the logarithmic odds ratio (p.
+In one case (RRR8), we first had to convert reported standard errors into pooled standard deviation (p.224).
+For risk differences and odds ratios we first added 1/2 to a cell if it was empty to avoid dividing by zero, next calculated the logarithmic odds ratio (p.
 266), converted this to Cohen's d (p.
-232) and then to a correlation.
-All formulas are presented in Appendix A.
+232) and then finally to a correlation.
+All formulas used are presented in Appendix A.
 
@@
 ```{r heterogeneity-table}
-library(kableExtra)
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE,digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Size", "I2(%)", "ci.lb", "ci.ub")) %>% 
+#library(kableExtra)
+
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE,digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub")) %>% 
   kable_styling("scale_down") %>%
   footnote(threeparttable = TRUE, escape = FALSE,
-           general = "We meta-analyzed effects using the same outcome measures that were used by the original authors.
-Standardized mean difference is Hedge's g.
+           general = " Effects were estimated in metafor using REML.
 The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs.
@@
 high category scales'.
-Effects were estimated in metafor using REML with the 'knha' correction.
 RS = Replication Study, k = no.
-primary studies, Size = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval.
-SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.")
+primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval.
+SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
+(OSF.io/XXXX)")
 
@@
 
-What can be learnt from the null I2 point estimates?
-As can be seen from table 3, 13/37 (35%) I2 point estimates are zero.
-If there was no heterogeneity across all effects we would expect approximately 50-55% of point estimates to be zero (based on the chisquare distribution and k across studies), that is around 20/37.
-This supports that there is some heterogeneity across the studied effects.
-Looking at the confidence intervals of the null estimates we see that in all cases the lower bounds of their confidence intervals are zero, whereas the upper bound varies from 13.75% (Stroop effect) up to 70.62% (Grammar on intention attribution).
-The three with the highest upper bounds (70.62%, 54.49%, 53.18%) belong to the two replication studies with the lowest k, possibly indicating a lack of power.
-[ref: Higgins et al] tentatively defined 25% as low heterogeneity, 50% as moderate and 70% as high.
-Of the upper confidence bounds of the null effects 8/13 lie closest to Higgin's low heterogeneity, 4/13 to moderate, and 1/13 to high.
-Thus of the null estimates eight are likely low in heterogeneity, whereas there is considerable uncertainty for the remaining five.
+Few effects show evidence of heterogeneity.
+The lower bound I2 confidence interval excludes zero for only 7/37 effects.
+Heterogeneity in a small number of effects is supported by the distribution of I2 point estimates.
+In a complete absence of heterogeneity, we would expect approximately 46% of point estimates across all effects to be non-zero, based on the chisquare distribution and average k across projects.
+That is, for about 17/37 effects.
+Table 3 shows that 23/37 effects have non-zero point estimates, indicating a small presence of heterogeneity.
 
-What can be learnt from the non-null I2 point estimates?
-The non-null point estimates of heterogeneity vary from 0.01% to 91.29%.
-Of these, 16/24 have point estimates that are closest to 'low' heterogeneity, 4/24 to medium and 4/24 to high.
-Seventeen (71%) have lower confidence bounds of zero heterogeneity and all have upper confidence bounds approaching medium/large heterogeneity.
-In the majority of non-null I2 point estimates there is thus large uncertainty surrounding heterogeneity levels.
-
-What can be learnt from the significant I2 estimates?
-Seven out of the 37 effects (19%) have confidence intervals whose lower bounds exclude zero.
-The point estimates of these effects all approach at least medium heterogeneity, varying from 40.05% to 91.29%.
-Three of the effects have lower confidence bounds closest to low heterogeneity, and the other four to either medium or high heterogeneity.
-The upper confidence bounds of all seven are consistent with high heterogeneity.
-That is, we can be confident that heterogeneity is medium - large for four effects, whereas the remaining three estimates are consistent with anything from low to high heterogeneity.
-
-What have we learnt from the 10 pre-registered multi-lab replication projects in Table 3 about heterogeneity in psychology?
-Because the included effects are neither a representative nor random sample of effects we cannot make broad claims about heterogeneity in psychology based on these data.
-Nonetheless, we can with some confidence claim that amongst the examined effects there is heterogeneity, or we would have expected to find a higher proportion of null I2 estimates.
-Examining the 95% confidence intervals, we can be confident that 8/37 (22%) have low heterogeneity (as defined by [ref: Higgins]), 4/37 (11%) have moderate to high heterogeneity whereas for the remaining 25 effects (68%) there is considerable uncertainty, with estimates consistent with low-moderate or low-high heterogeneity.
-Because the replication projects only varied on sampling population and settings, we know nothing about the effects' susceptibility to changes in treatment or measurement variables.
-
-Larger effect sizes appear to lead to higher heterogeneity estimates (Figure 1).
+Larger effect sizes appear to lead to higher heterogeneity estimates.
 In Table 3, the four effects with highest I2 estimates also have the largest effect sizes.
-As expected, heterogeneity tends to increase with (absolute) effect size, with effect size sufficient to explain 61% of variation in I2 estimates according to a simple regression model.
-The I2 index is truncated at zero, however, the closely related but unbounded heterogeneity estimate H2 provides a similar result (R2 = .53).
+As expected, heterogeneity tends to increase with (absolute) effect size, with effect size sufficient to explain 61% of variation in I2 estimates according to a simple regression model (Figure 1).
+The closely related, but unbounded, heterogeneity estimate H2 provides a similar result (R2 = .53).
 
@@
 
-<!-- General thought: Ml1 compares heterogeneity from the perspective of between lab vs.
-between effects and concludes that heterogeneity depends mostly on the effect.
-However, it seems unsurprising that a certain lab (when not perversely motivated) does not systematically bias effects, but rather that a location might have differential effects on different studied effects.
--->
+There is little evidence of heterogeneity amongst current pre-registered multi-lab replication projects.
+Across 10 projects, only 7/37 (19%) of primary outcomes showed evidence for heterogeneity.
+Moreover, while each replication of an effect only varied on two contextual factors (sampling population and settings), the effects that showed evidence for heterogeneity were primarily effects that might have been expected to be sensitive to the changes in sampling population.
+Save two effects (Anchoring - Everest and IAT correlation math), all other effects that demonstrated heterogeneity were related to the US.
+They either asked questions about the US (anchoring effects), persons related to the US (Quote attribution) or issues where the US is well-known to be exceptional (i.e., free speech; allowed vs.
+forbidden).
+Considering all seven effects belonged to the ML1 replication project, which collected data from labs in 10 different countries, these effects should have been expected to exhibit heterogeneity.
+[note to Jelte and Marcel: I am not sure this argumentation holds up, since ML1 did test US vs.
+non-US as a moderator and found very small effect sizes]
 
-<!-- This might mean that we have missed an important moderator, or that there is a lot of small moderators missed (thinking about it, this seems to differ from random fluctuations in that they are still systematic in some sense, on the other hand, whether they cancel out or not is in itself due to "chance".
-If an effect (but perhaps not others) is moderated by what time of the day the study is run this can lead to heterogeneity, but say there is also a time-independent moderator such as whether the room is warm -> then we get heterogeneity even if two labs measure at the same time, at what point do these things become "noise" rather than systematic bias?
-Because we have so few labs it is difficult to separate these?) -->
+Complicating the discussion of heterogeneity is that there amongst the studied effects was a clear association between effect size and heterogeneity.
+There are thus both good theoretical (see introduction) and empirical reasons to expect larger effect sizes to exhibit comparatively more heterogeneity when using observed effect sizes in a meta-analysis.
+Since not all measurements (e.g., behavioral) admit adjusting for reliability as easily as questionnaires, this can be difficult to control for.
+
+There are some limits to the generalizability of claims based on the data in our study.
+For one, the included effects are neither a representative nor random sample of effects in psychology and as such do not support making strong claims about average heterogeneity levels in psychology.
+In respect to this point we look forward to the forthcoming Many Labs 2 project which should provide considerable new data on the prevalence of heterogeneity in psychology.
+In addition, while both the I2 confidence intervals and distribution of point estimates support a small number of heterogenous effects amongst those studied, most confidence intervals are congruent with anything from low to high heterogeneity as defined by [Higgins et al].
+As always, absence of evidence is not evidence of absence.
+Finally, since the included studies only vary on two contextual factors, the data tell us nothing about the included effects susceptibility to changes in the other two factors (treatment and measurement variables).
+
+Evidence does not appear to support the belief that heterogeneity is the norm in psychology.
+Large-scale reviews of meta-analyses in psychology suggest considerable heterogeneity across the field of psychology [ref: Stanley; van Erp et al].
+However, in our experience psychologist tend to include widely varying studies in their meta-analyses, sometimes varying on all four contextual factors (or more).
+This is perhaps unsurprising considering the lack of delineating theory in psychology [ref: Simons et al].
+In support of this notion, [Ioannidis; uncertainty in heterogeneity] reports that, even after excluding meta-analyses of 3 or fewer studies, the median number of studies included in Cochrane meta-analyses is only 7, whereas in the dataset of [ref: van Erp et al] containing 747 meta-analyses in psychology, the median number of studies (effects) per meta-analysis is 12.].
+Our examination of heterogeneity in pre-registered multi-lab replication projects, arguably the least biased meta-analytic data currently available in psychology, indicates that there is little evidence to support the notion that heterogeneity is widespread in psychology.
+
+##References

### 2018-06-22 writing/draft-heterogeneity.rmd
Updated paper draft

@@
 ```
-Empirical research typically proceeds in two stages.
+Empirical research is typically portrayed as proceeding in two stages.
 First, belief in the existence of an effect is established.
 Second, its generalizability is examined by exploring its boundary conditions.
-In the first stage, we use inferential statistics  to minimize the risk that a discovery is due to sampling error.
-In the second stage, we ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
-This extent is often explored through replications of the original study with some variation, and once sufficient studies have accumulated through meta-analysis.
+In the first stage, inferential statistics are used  to minimize the risk that a discovery is due to sampling error.
+In the second stage, one may ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
+This extent is often explored through replications of the original study that are either as similar as possible to the original (called 'direct' or 'exact' replications) or with some deliberate variation on conceptual factors (so-called 'conceptual' or 'indirect' replications) [ref: Zwaan et al], and once sufficient studies have accumulated through meta-analysis.
 In meta-analysis, the heterogeneity of an effect size (henceforth referred to as heterogeneity) is a measure of an effect's susceptibility to changes in these four factors.
@@
 In this paper we examine what degree of heterogeneity can be expected in replication studies in psychology and explore a proposed relationship with effect size.
+We focus in this paper on direct replications.
 
@@
 This may be most readily evident for medicine, where in the case of heterogeneity an intervention that is successful for some may have direct negative health consequences for others.
-However, the adoption of psychological research for business, law enforcement, and policymaking in general (e.g., the widespread use of 'nudges'; https://www.knowablemagazine.org/article/society/2018/nudging-grows-and-now-has-government-job) means its impact can be widespread and the consequences of heterogeneity should be no less a concern for psychologists.
+However, the adoption of psychological research for business, law enforcement, and policymaking in general (e.g., the widespread use of 'nudges'; https://www.knowablemagazine.org/article/society/2018/nudging-grows-and-now-has-government-job) means its impact can be widespread and the consequences of heterogeneity should be no less of a concern for psychologists.
+
  Second, unaccounted for heterogeneity is an indication of incomplete theory, since it suggests that a theory is unable to predict all contextual factors of importance to its claims.
-While heterogeneity reveals that a theory has flaws, by itself it does not damn a theory, and can be seen as an opportunity for theoretical advancement [ref: Tacket et al].
-Third, heterogeneity can create controversy in the interpretation of replication results.
-The lack of a clear line for the degree of heterogeneity (susceptibility to contextual factors) that would make an effect uninteresting often results in heated discussions between original and replication authors.
-In response to this common area of disagreement [ref Simons et al] recently proposed that authors include a statement to explicitly delineate the level of heterogeneity that would make an effect lose its value.
-Fourth, meta-analytic techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht; McShane].
-This is problematic considering widespread publication bias [refs] and its impact on meta-analytic estimates.
-Finally, heterogeneity affects the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity).
+As such, heterogeneity might imply previously unknown predictors, so called 'hidden moderators' [ref: van Bavel], the discovery of which can be seen as an opportunity for theoretical advancement [ref: Tacket et al].
+The corollary is that, unless a theory has predefined additional assumptions ('auxiliary assumptions' [ref: Earp & Trafimow]) which were not fulfilled in the replications, an absence of heterogeneity should generally preclude referral to hidden moderators.
 
-It is a common belief that heterogeneity is the norm in psychology.
-For example, several authors [ref: Tacket et al, McShane et al] argue that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol, and that heterogeneity has been reported even under such circumstances [e.g., ref: Many Labs 1] is an indication of widespread heterogeneity in psychology.
-In addition, recent large scale reviews of meta-analyses in psychology [ref: Stanley; van Erp et al] report that much variability in effect sizes can be attributed to heterogeneity, with median estimates of 74% and 70.62% respectively [ref: Stanley].
-In comparison, the median heterogeneity estimate in medicine is considerably lower: 21% amongst Cochrane meta-analyses [ref: Ioannidis  "uncertainty in heterogeneity"].
+ Third,  the possibility of heterogeneity can create controversy in the interpretation of single replication results.
+The proclamation of a  'failure' to replicate an effect often seems to imply that the original find was merely a statistical fluke, due to 'p-hacking' [Ref: Simmons et al] or publication bias [ref..
+Inzlicht?].
+Unsurprisingly, some researchers take offense [e.g., ref: Baumeister].
+An alternative explanation for non-replication, often espoused by the original authors [e.g, IJzerman; Strack], is that the effect is more heterogenous than (perhaps implicitly) claimed originally.
+Such explanations may be valid or not, but even if valid, an effect is typically of less general interest the more specific circumstances it requires to appear.
+A way for original authors to align researchers' expectations of heterogeneity is to preemptively specify their own, that is, the degree of heterogeneity that would make they themselves lose interest in an effect (e.g., by declaring 'constraints on generality' [ref Simons et al].
 
+Fourth, meta-analytic techniques are affected by heterogeneity.
+Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht; McShane], which is problematic considering widespread publication bias [refs] and its impact on meta-analytic estimates.
+In addition, heterogeneity alters the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity), though one may question the usefulness of interpreting the average true effect size in the presence of heterogeneity [ref: blog Simonsohn], just as it may be questionable to interpret an average main effect in the context of an interaction effect [ref Aiken and West 1993].
+
+It is a commonly believed that heterogeneity is the norm in psychology.
+In support of this notion, recent large scale reviews of meta-analyses in psychology [ref: Stanley; van Erp et al] report median heterogeneity levels that can best be described as 'large' (see next paragraph).
+In comparison, the median heterogeneity estimate in medicine would be considered 'small' by the same standard [ref: Ioannidis  "uncertainty in heterogeneity"].
+It may simply be that effects in psychology are more heterogenous than those of medicine.
+However, meta-analyses in psychology also typically include more studies than those in medicine, and it could be that they tend to include studies from a much broader spectrum than meta-analyses in medicine.
+The median number of studies (effects) per meta-analysis in the psychology sample of [van Erp et al] was 12, whereas in the medicine sample of  [Ioannidis; uncertainty in heterogeneity] the median number of studies was only 7, despite exclusion of all meta-analyses of 3 or fewer studies.
+It is difficult to separate these explanations.
+To facilitate doing so, in this paper we focus on meta-analyses of only direct replications, which are exempt from the potential problem of including too disparate studies.
+In reference to meta-analyses of direct replications, several authors [ref: McShane et al; Tacket et al] have argued that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol, and that heterogeneity has been reported even under such circumstances [e.g., ref: Many Labs 1] is an indication of widespread heterogeneity in psychology.
+However, even in the case of multi-lab direct replication projects, studies vary on two contextual factors (sample population and settings) and if we believe an effect is sensitive to changes in these two factors we might still expect to find some heterogeneity
+
+One problem lies in the assessment of heterogeneity and its inherent uncertainty.
 Heterogeneity is often measured by the I2 index [ref: Higgins & Higgins], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
-It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects (that is, dependency on contextual factors) rather than sampling variance, and ranges from 0-100%.
-The I2 index is a transformation of the Q-test [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative I2 is set to zero.
+It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects (that is, sensitivity to contextual factors) rather than sampling variance, and ranges from 0-100%.
+The I2 index is a transformation of the well-known Q-test of heterogeneity in meta-analysis [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative I2 is set to zero.
+[Higgins et al] tentatively defined I2-values of 25, 50, and 75% as small/medium/large heterogeneity respectively.
+Tests of heterogeneity typically have low statistical power in many practical situations [ref: Jackson; Huedo-Medina].
+This complicates the discussion of heterogeneity, because while I2 always provides an estimate of heterogeneity, this estimate is often surrounded by wide confidence intervals [ref: Ioannidis  "uncertainty in heterogeneity"].
+For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with I2 point estimates of 0% had upper 95% confidence intervals that exceeded 33%, exceeding what [Higgins] defined as 'small' heterogeneity.
+In addition, under homogeneity I2 has a central chisquare distribution [ref: von Hippel], a distribution that is right-skewed with more than 40% of observations falling above the expected value (for all k > 4).
+In other words, even in the absence of heterogeneity, a meta-analysis of 5 or more studies will have an I2 point estimate above zero in more than 40% of cases.
+Heterogeneity estimates may thus be congruent with a wide range of true heterogeneity levels.
+Despite exhortations to the contrary [ref: Ioannidis "uncertainty in heterogeneity"] , it remains common to omit confidence intervals in the reporting of I2.
+In consideration of such uncertainty and the prevalent belief that heterogeneity is the norm in psychology, we examine the existing evidence for heterogeneity in psychology using a sample of pre-registered multi-lab direct replication projects.
 
-Heterogeneity (I2) estimates typically contain considerable uncertainty.
-Both the Q-test and I2 have low power [ref: Jackson; Huedo-Medina].
-This complicates the discussion of heterogeneity, because while I2 always provides an estimate of heterogeneity, this estimate is often surrounded by wide confidence intervals [ref: Ioannidis  "uncertainty in heterogeneity"].
-For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with I2 point estimates of 0% had upper 95% confidence intervals that exceeded 33%.
-In addition, under homogeneity I2 has a central chisquare distribution [ref: von Hippel], a distribution that is right-skewed with more than 40% of observations falling above the expected value in almost all cases (for all k > 4).
-In other words, even in the absence of heterogeneity, a meta-analysis of 5 or more studies will have an I2 point estimate above zero in more than 40% of cases.
-Point estimates (expected values) of heterogeneity may thus be congruent with a wide range of true heterogeneity levels.
-Despite exhortations to the contrary [ref: Ioannidis "uncertainty in heterogeneity"] , it remains common to omit confidence intervals in the reporting of I2 [e.g., ML1 and ML3].
-
-Effect size influences heterogeneity.
-Intuitively, it makes sense to think that if there is no meta-analytic effect there is nothing to moderate (i.e., no heterogeneity).
+Effect size likely influences heterogeneity.
+Intuitively, it makes sense to believe that if there is no meta-analytic effect there is nothing to moderate (i.e., no heterogeneity).
 However, a null or near null effect size estimate may arise from failure to consider contextual factors ('hidden moderators', [ref: van Bavel]) and does not by itself imply the absence of heterogeneity.
-This is especially true when the uncertainty in I2 estimates (see above) is taken into account.
-A large effect size on the other hand, can be expected to lead to more heterogeneity.
+A large meta-analytic effect size on the other hand, can be expected to be associated with more heterogeneity.
 To illustrate, consider a meta-analysis of say, the correlation between neuroticism and procrastination.
 Each included study would need to measure the two variables somehow, possibly the same way across studies.
-However, because of individual differences, measurement is not equally exact for everyone, and between studies the measurement reliabilities will differ either due to sampling variance (that the sample happens to be more or less homogenous) or to differences in contextual factors (e.g., sampling population, method of measurement).
-This means that even if the underlying effect size is the same, the observed correlation between the two variables will differ between studies.
-If measurement reliabilities stay the same, these differences will increase with the underlying effect, resulting in more variability being ascribed to heterogeneity.
-More formally, an observed correlation $r_{xy}$ is equivalent to the true correlation $\rho_{xy}$ multiplied by the square root of the measurement reliabilities for X ($R_{xx'}$) and Y ($R_{yy'}$): $r_{xy} = \rho_{xy} \times \sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$.
-As such, if $\sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$ stays constant while $\rho_{xy}$ increases the observed differences between studies will increase (see Table 2).
+However, because of individual differences, measurement is not equally exact for everyone, and between studies the measurement reliabilities may differ either due to sampling variance (that the sample happens to be more or less homogenous) or to differences in contextual factors (e.g., sampling population, method of measurement).
+This means that even if the underlying true effect size is the same, the observed correlation between the two variables will differ between studies.
+Keeping measurement reliabilities constant, differences in observed effect sizes will increase with the underlying true effect, resulting in more variability being ascribed to heterogeneity.
+More formally, an observed correlation $r_{xy}$ can be expressed as the product of the true correlation or effect size, $\rho_{xy}$, multiplied by the square root of the measurement reliabilities for X ($R_{xx'}$) and Y ($R_{yy'}$): $r_{xy} = \rho_{xy} \times \sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$.
+As such, if $\sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$ stays constant while $\rho_{xy}$ increases the observed differences between studies will also increase, thereby increasing heterogeneity of observed effect sizes (see Table 1).
+We explore the association between effect size and heterogeneity in a sample of pre-registered multi-lab replication projects.
 
@@
 ```
-We examine heterogeneity across 10 pre-registered multi-lab replication projects in psychology (Table 2).
-In light of the uncertainty surrounding I2-estimates we explore what conclusions can be drawn about heterogeneity in psychology from these projects, as well as the relationship between effect size and heterogeneity.
+
+We examine the evidence for widespread heterogeneity in psychology and explore the correlation between effect size and heterogeneity, using 10 pre-registered multi-lab replication projects in psychology (Table 2).
 These 10 projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
-All included studies vary on a minimal number of contextual factors [as recognized by e.g., Tacket et al]: only sample population and settings.
-Nonetheless, contrary to the argument of [Tacket et al], if an effect is sensitive to changes in these factors we may still expect to find some heterogeneity.
-On the other hand, heterogeneity estimates will only inform us of susceptibility to changes in these two factors, with no information on susceptibility to changes in other contextual factors.
+To better interpret heterogeneity estimates we also estimate power of each project to find zero/small/medium/large heterogeneity as defined by [Higgins et al].
+Of the four contextual factors a study might vary on (sample population, settings,  treatment variables, and measurement variables) the studies in these projects vary only on two: sample population and settings.
+Nonetheless, if we believe an effect is sensitive to changes in these two factors we may still expect to find some heterogeneity.
+For example, the variety of countries and samples involved in some of the replication projects, not all of which are WEIRD (Western, Educated, Industrial, Rich, Democratic [ref: Weird]) might be a reason to expect heterogeneity.
+On the other hand, it may be that the less disparate collection of studies included in the these direct replication meta-analyses as compared to most psychological meta-analyses result in low heterogeneity estimates, similar to estimates in medicine.
+Regardless of outcome, the sampled multi-lab replication projects can only inform us of susceptibility to changes in the varied contextual factors  (sample population and settings), with no information on susceptibility to changes in other contextual factors.
 
@@
 Even so, we kept the original lab indicators to facilitate comparing observations in our dataset with the original datasets.
-Finally, we collated he summary data for all effects into one dataset for analysis (osf.io/XXXX/).
+Finally, we collated the summary data for all effects into one dataset for analysis (osf.io/XXXX/).
 
@@
 Two projects (RRR5 and RRR7) used the Knapp and Hartung adjustment of the standard errors [ref: Knapp & Hartung] and ML3 correlations were corrected for bias [ref: Hedges 1989; metafor].
-After estimating effects, Ml3 transformed correlations into eta-squared for reporting, which we did not.
+After estimating effects, ML3 transformed correlations into eta-squared for reporting, which we did not.
 For each effect we estimated I2 and its 95% confidence interval.
@@
 
-To examine the relationship between effect size and I2 we converted all effect sizes to a common metric (osf.io/XXXX/).
-Since I2 is logically and mathematically bounded at zero, we also correlated effect sizes with the closely related heterogeneity estimate H2, which is calculated as $H2 = Q / (k - 1)$.
+[Ignore the following paragraph - power simulation paragraph - subject to change]
+To facilitate interpreting results, we estimated power and type 1 error for each of the 37 effects under zero/small/medium/large heterogeneity (I2 = 0/25/50/75%  respectively), as well as the expected I2-distributions across effects at these heterogeneity levels (osf.io/XXXX/).
+To do so we simulated results for each effect given the number of studies, k, and the sample sizes of each study, $N_k$, for that effect.
+Our approach consisted of (i) varying the between-studies variance,  $\tau^2$, for each effect to find the values that best corresponded to I2-estimates of 25/50/75% and (ii) using the found values to estimate power and type 1 error by computing the proportion non-significant results over a large number of replications.
+In step (i), we varied $\tau^2$ between 0.000 and 0.250 in increments of 0.005,  and replicated each condition 50 times.
+We then computed the average I2 across the 50 replications, discarding non-converging models, and for each effect saved the $\tau^2$ values that best corresponded to small, medium, and large I2.
+For homogeneity we set $\tau^2$ to zero.
+In step (ii), to estimate power and type 1 error, we ran one thousand replications at each identified level of heterogeneity using the $\tau^2$-values of step (i).
+We considered a result significant when the lower bound of the 95% I2 confidence interval was above zero and save heterogeneity estimates were saved from each replication for plotting I2-distributions.
+
+[Ignore the following paragraph - power simulation paragraph - subject to change]
+In both steps of our simulation, we followed the same data generating procedure.
+For each effect, we generated k effect sizes, $\theta_k$, from a normal distribution with a mean of zero and between-studies variance $\tau^2$: $\theta_k \sim N(0,  \tau^2)$.
+For the sake of simplicity, we made the choice to set the average effect size to zero and treated each effect as consisting of a treatment and control group.
+We thus drew an effect size $\theta_k$ for each replication study of an effect, and within each study we then generated $N_k / 2$ (rounded to closest integer) sample values for a treatment and for a control group from two normal distributions with means $\mu_t = \theta_k$ and $\mu_c = 0$ and equal within-study variances ($\sigma^2 = 1$).
+This provided sample means and standard deviations for all k treatment and control groups of an effect, which we then used to estimate a random effects model for standardized mean differences in metafor using REML.
+This process was repeated the desired number of times for each condition and effect.
+
+To examine the correlation between effect size and I2 we converted all effect sizes to a common metric (osf.io/XXXX/).
+Since I2 is logically and mathematically bounded at zero, we also correlated effect sizes with the closely related heterogeneity estimate H2, which is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - I2)$ for $I2 \geq 0$.
 We first converted all effects into correlations (r) and used the R-package metafor [ref] to estimate I2 and meta-analytic effects expressed as Fisher's z.
-In doing so, we fit random-effects models with metafor's default REML estimator.
-Fisher's z is a normalizing correlation transformation that ranges from negative to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [ref].
+In doing so, we fitted random-effects models with metafor's default REML estimator.
+Fisher's z is a normalizing correlation transformation that ranges from negative infinity to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [ref].
 For mean differences we calculated the pooled standard deviation, [ref Borenstein in Cooper & Hedges, 2009, p.
@@
 
+We examined the evidence for heterogeneity across a set of pre-registered multi-lab replication projects.
 Few effects show evidence of heterogeneity.
-The lower bound I2 confidence interval excludes zero for only 7/37 effects.
-Heterogeneity in a small number of effects is supported by the distribution of I2 point estimates.
-In a complete absence of heterogeneity, we would expect approximately 46% of point estimates across all effects to be non-zero, based on the chisquare distribution and average k across projects.
-That is, for about 17/37 effects.
-Table 3 shows that 23/37 effects have non-zero point estimates, indicating a small presence of heterogeneity.
+The lower bound I2 confidence interval excludes zero for only 7/37 effects (19%; Table 3), all part of the ML1 project.
+The percentage of heterogeneity estimates larger than 0 (23/37; 62%) suggests heterogeneity for at least some effects, as this percentage is higher than the expected frequency of non-zero estimates under homogeneity (46%, or about 17/37), based on the chi-square distribution and average k across projects.
+Of those effects whose lower bound confidence interval includes zero, 15/30 (50%) have confidence intervals that exceed 50% (medium heterogeneity).
 
-Larger effect sizes appear to lead to higher heterogeneity estimates.
+[add segment on power with figures when ready]
+
+Larger effect sizes appear to be associated with higher heterogeneity estimates.
 In Table 3, the four effects with highest I2 estimates also have the largest effect sizes.
@@
 The closely related, but unbounded, heterogeneity estimate H2 provides a similar result (R2 = .53).
+Excluding Anchoring effects as robustness check makes little difference (R2 = .51 for I2).
 
@@
 
-There is little evidence of heterogeneity amongst current pre-registered multi-lab replication projects.
-Across 10 projects, only 7/37 (19%) of primary outcomes showed evidence for heterogeneity.
+There is little evidence for heterogeneity amongst current pre-registered multi-lab replication projects in psychology.
+Across 10 projects, only 7/37 (19%) of primary outcomes had confidence intervals that excluded zero heterogeneity.
 Moreover, while each replication of an effect only varied on two contextual factors (sampling population and settings), the effects that showed evidence for heterogeneity were primarily effects that might have been expected to be sensitive to the changes in sampling population.
 Save two effects (Anchoring - Everest and IAT correlation math), all other effects that demonstrated heterogeneity were related to the US.
-They either asked questions about the US (anchoring effects), persons related to the US (Quote attribution) or issues where the US is well-known to be exceptional (i.e., free speech; allowed vs.
+They either asked questions about the US (anchoring effects), persons related to the US (Quote attribution) or issues that are well-known to generate strong debate in the US (i.e., free speech; allowed vs.
 forbidden).
-Considering all seven effects belonged to the ML1 replication project, which collected data from labs in 10 different countries, these effects should have been expected to exhibit heterogeneity.
-[note to Jelte and Marcel: I am not sure this argumentation holds up, since ML1 did test US vs.
-non-US as a moderator and found very small effect sizes]
+Although ML1 tested US vs.
+non-US as a moderator of heterogeneity and found very small effect sizes, these are all effects for which heterogenous responses also within the US would be unsurprising (e.g., someone living close to Chicago is more likely to know the population of Chicago).
+Our results suggest little reason to believe heterogeneity is the norm in psychology, and thus imply that citing heterogeneity as a reason for non-replication of an effect is unwarranted unless predicted _a priori_.
 
@@
 There are thus both good theoretical (see introduction) and empirical reasons to expect larger effect sizes to exhibit comparatively more heterogeneity when using observed effect sizes in a meta-analysis.
-Since not all measurements (e.g., behavioral) admit adjusting for reliability as easily as questionnaires, this can be difficult to control for.
+Since not all measurements (e.g., behavioral) admit adjusting for reliability as easily as questionnaires, a potential correlation between effect size and heterogeneity could be difficult to control for.
+However, the relatively small number of effects in our sample means this association might be an artifact of the data.
 
-There are some limits to the generalizability of claims based on the data in our study.
+There are some additional limits to the generalizability of claims based on the data in our study.
 For one, the included effects are neither a representative nor random sample of effects in psychology and as such do not support making strong claims about average heterogeneity levels in psychology.
@@
 As always, absence of evidence is not evidence of absence.
-Finally, since the included studies only vary on two contextual factors, the data tell us nothing about the included effects susceptibility to changes in the other two factors (treatment and measurement variables).
+Finally, since the included studies only vary on two contextual factors (sample population and settings) , the data tell us nothing about the included effects' susceptibility to changes in the other two factors (treatment and measurement variables).
 
-Evidence does not appear to support the belief that heterogeneity is the norm in psychology.
+To conclude, evidence does not appear to support the belief that heterogeneity is the norm in psychology.
 Large-scale reviews of meta-analyses in psychology suggest considerable heterogeneity across the field of psychology [ref: Stanley; van Erp et al].
 However, in our experience psychologist tend to include widely varying studies in their meta-analyses, sometimes varying on all four contextual factors (or more).
-This is perhaps unsurprising considering the lack of delineating theory in psychology [ref: Simons et al].
-In support of this notion, [Ioannidis; uncertainty in heterogeneity] reports that, even after excluding meta-analyses of 3 or fewer studies, the median number of studies included in Cochrane meta-analyses is only 7, whereas in the dataset of [ref: van Erp et al] containing 747 meta-analyses in psychology, the median number of studies (effects) per meta-analysis is 12.].
-Our examination of heterogeneity in pre-registered multi-lab replication projects, arguably the least biased meta-analytic data currently available in psychology, indicates that there is little evidence to support the notion that heterogeneity is widespread in psychology.
+This is perhaps unsurprising considering the lack of theory delineating boundary conditions in psychology [ref: Simons et al].
+Our sample, despite consisting of the arguably best, least biased, meta-analytic data currently available in psychology, was unfortunately relatively small and not representative of the many varied effects studied in psychology.
+As such we are enthusiastic about the many multi-lab initiatives in psychology (Registered Replication Reports, Many Labs 2, ManyBabies, the Psych Science Accelerator) which in the future will provide considerable new data and enable researchers to re-evaluate the prevalence of heterogeneity in psychology.
+At current there is little evidence to support the notion that heterogeneity is widespread in psychology.
 

### 2018-06-23 code/power_simulation.r
Improved power simulation - efficiency and corrected correlation

@@ -15,132 +15,90 @@ library(metafor)
 library(dplyr)
 library(purrr) #for 'possibly'
 library(ggplot2)
+library(tidyr) #for 'spread'
 
 dat <- read_csv("../data/collated_summary_data.csv")
 
 
 #******************************************
-#Functions
+#Simulation function----
 #******************************************
-#Because we are only interested in heterogeneity, average effect size doesn't matter
-#Huedo-Medina I set it to 0.5 (using hedge's g), however, we would then be double-standardizing
-#later when running the meta-analysis since each individual's value would be measured already
-#in standard deviation units. Simpler to set it to zero.
-
-rma_simulate <- possibly(function(k, tau2, N){ #to use this across all effects I just need to add N_half as an argument
-  #I use possibly because REML does not always converge. Non-conversions then -> NA
-  N_half <- N%/%2
-  #Step 1: draw k mean effect sizes, here homogeneity
-  averages <- rnorm(n = k, mean = 0, sd = sqrt(tau2)) #we wish to loop sd = tau over a number of values
+simulate_I2 <- function(effect, reps, tau){ #this function applies to a single list object (effect)
   
-  #Step 2: draw individual results for each study, control group and treatment group
-  #I draw N/2 rounded to the closest integer for each study with equality of variances
-  #Following Huedo-Medina I use no effect in control and the full effect in treatment group
+  K <- effect$K #Number of studies
+  N <- effect$Ntotal #Sample sizes for all K studies
+  output <- vector("list", length(tau)) #empty list for output
   
-  #loop because rnorm is not vectorized for n
-  treatment <- vector("list", length(N)) #length = k
-  control <- vector("list", length(N)) #length = k
-  for(Nk in seq_along(N_half)){ 
-    treatment_i <- rnorm(n = N_half[Nk], mean = averages[Nk], sd = 1)
-    control_i <- rnorm(n = N_half[Nk], mean = 0, sd = 1)
+  if(effect$type == "r"){ #If correlation
     
[…]

### 2018-06-24 code/figures.rmd
Reorganized code files to improve clarity

@@
 
-```{r load data and packages}
+```{r load packages, data and source helper functions}
+if(!require(readr)){install.packages("readr")}
+if(!require(metafor)){install.packages("metafor")}
+if(!require(dplyr)){install.packages("dplyr")}
+if(!require(purrr)){install.packages("purrr")}
+if(!require(ggplot2)){install.packages("ggplot2")}
+if(!require(cowplot)){install.packages("cowplot")}
+
 library(readr) #To load data
 library(dplyr) #For data transformation
-library(purrr) #For data transformation
+library(purrr) #For data iteration
 library(metafor) #To run meta-analyses
@@
 dat <- read_csv("../data/collated_summary_data.csv")
-```
 
-```{r transformation_functions}
-#Formulas found in: 
-#Borenstein, M.
-(2009).
-Effect sizes for continuous data.
-In H.
-Cooper, L.
-V.
-Hedges, & J.
-C.
-Valentine (Eds.), The handbook of research synthesis and meta-analysis (2nd ed., pp.
-221-235).
-New York: Russell Sage Foundation.
-
-#For raw mean difference + SE
-transform_SE <- function(ES, SE, n1, n2){ 
-  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2)) #Borenstein, M. (2009). In Cooper & Hedges. p. 224
-  d <- ES / sdpooled
-  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes. p.234
-  r <- d / sqrt(d^2 + corr) #p.234
-  data.frame(r = r, n = n1 + n2)
-}
-
-#For mean differrence + SD
-transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
-  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #page 226. 
-  d <- (m1 - m2) / sdpooled
-  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p.234
-  r <- d / sqrt(d^2 + corr) #p. 234
-  data.frame(r = r, n = n1 + n2)
-}
-
-#For Risk difference/OR
-transform_RD <- function(ai, bi, ci, di){
-  ai <- ifelse(ai == 0, 0.5, ai)  #If value is equal to zero add one half so as to not divide by zero
-  bi <- ifelse(bi == 0, 0.5, bi)  #This affects 1 study for Allowed vs. forbidden
-  ci <- ifelse(ci == 0, 0.5, ci)  #And several studies for Low vs. high category scales
-  di <- ifelse(di == 0, 0.5, di)
-  logOR <- log((ai*di) / (bi*ci)) #p. 266
-  d = logOR * sqrt(3)/pi #p. 232
-  n1 = ai + bi
-  n2 = ci + di
-  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p. 234
-  r <- d / sqrt(d^2 + corr) #p. 234
-  data.frame(r = r, n = ai + bi + ci +di)
-}
-
-#No transformatin needed for correlation
-
-transform_MA <- function(x){
-  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
-
-    transformed <- transform_RD(ai = x$outcome_t1, bi = x$outcome_t2, ci = x$outcome_c1, di = x$outcome_c2)
-
-    #fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){
-
-     transformed <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)
-
-    #fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){
-
-     transformed <- transform_SD(x$outcome_t1, x$outcome_c1, x$outcome_t2, x$outcome_c2, x$ntreatment, x$ncontrol)
-
-    # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
-
-  } else if(any(x[, "effect_type"] == "r")){
-
-     transformed <- data.frame(r = x$effect_size, n = x$Ntotal)
-
-    # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
-
-   } else{ #For the many labs OR that were transformed to d [double check]
-
-     transformed <- transform_RD(ai = x$outcome_t1, bi = x$outcome_t2, ci = x$outcome_c1, di = x$outcome_c2)
-
-}
-
-  # data.frame(b = fit$b[[1]], I2 = fit$I2) #estimate out
-  transformed
-}
-
+source("helper_functions_tables_figures.r") #Load functions to prep data for figures
 ```
@@
 #Transform effect sizes to raw correlations
+#'transform_MA' is a sourced function
 res <- dat %>% 
@@
 
+# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61
+
 I2 <- ggplot(res2, aes(x = z, y = I2)) +
@@
 
+# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53
+
 H2 <- ggplot(res2, aes(x = z, y = H2)) + 
@@
   xlab("Fisher's z") +
-  geom_text(x = 0.14, y = 6, label = "b = 3.81, R2 = 0.53", size = 3.5) +
+  geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
   theme_classic()
@@
 
-# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61
-# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53
 ```
 
-```{r labelled_plot, fig.asp= 0.618}
-ggplot(res2, aes(x = z, y = I2, label = effect)) +
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = FALSE, color = "black") +
-  xlab("Fisher's z") +
-  coord_cartesian(ylim = c(0, 100)) +
+```{r robustness, results="hide"}
+##Excluding anchoring effects
+dropped_anchoring <- res2 %>%
+  filter(!grepl("Anchoring", effect))
+
+summary(lm(I2 ~ z, data = dropped_anchoring))
+#b = 87.87, R2 = .51
+
+```
+
+```{r Plot_tau_against_I2, fig.asp = 0.618}
+dat3 <- readRDS("temp_sim_results.RDS")
+names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
+
+dat3 <- dat3 %>% 
+  bind_rows(.id = "effect") %>% #create dataframe with identifier
+  select(I2, tau, effect) %>% 
+  group_by(tau, effect) %>% 
+  summarize(I2 = mean(I2)) %>% #Take mean of I2 at each tau-level and for each effect
+  ungroup()
+
+#combined line plot gives good overview. Point version of the same is also interesting.
+ggplot(dat3, aes(x = tau, y = I2, group = effect)) +
+  geom_line(alpha = 0.4) +
+  theme_bw() +
+  scale_x_continuous(minor_breaks = NULL) +
+  scale_y_continuous(minor_breaks = NULL) +
+  coord_cartesian(ylim = c(0, 100))
+
+```
+
+```{r Density_plot, fig.asp= 0.618}
+dens <- readRDS("temp_sim_results_2.RDS")
+names(dens) <-  sort(unique(dat$effect))
+
+#Simulated data at various heterogeneity levels, prep for plotting
+I2_dist <- dens %>% 
+  bind_rows(.id = "effect") %>% 
+  rename(heterogeneity = tau_index) %>% 
+  mutate(heterogeneity = recode(heterogeneity,
+                            '1' = "Zero",
+                            '2' = "Small",
+                            '3' = "Medium",
+                            '4' = "Large"),
+         heterogeneity = as.factor(heterogeneity))
+
+#Observed I2 estimates, i.e, results from main table, see table.rmd
+#Effects estimated with sourced function 'est_heterogeen_smd_raw'
+observed <- dat %>% 
+  split(.$effect) %>%  
+  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
+  select(effect, I2 = s_I2) %>%
+  mutate(heterogeneity = "Observed")
+
+ggplot(I2_dist, aes(x = I2, group = heterogeneity, fill = heterogeneity, linetype = heterogeneity)) +
+  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 50, alpha = 1) +
+  geom_density(alpha = 0.3) +
   theme_classic() +
-  geom_text(alpha = 0.5)
+  coord_cartesian(xlim = c(0, 100))  +
+  scale_fill_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
+  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"), breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
+  scale_color_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed"))
+
 ```

### 2018-06-24 code/tables.rmd
Reorganized code files to improve clarity

--- 2018-05-17 code/tables.rmd
@@
 
-```{r load data and packages}
-library(readr)
-library(dplyr)
-library(kableExtra)
-library(purrr)
-library(metafor)
+```{r load packages, data and source functions}
+if(!require(readr)){install.packages("readr")}
+if(!require(metafor)){install.packages("metafor")}
+if(!require(dplyr)){install.packages("dplyr")}
+if(!require(purrr)){install.packages("purrr")}
+if(!require(kableExtra)){install.packages("kableExtra")}
+
+library(readr) #To load data
+library(dplyr) #For data transformation
+library(purrr) #For data iteration
+library(metafor) #To run meta-analyses
+library(kableExtra) #For creating good-looking pdf tables
 
 dat <- read_csv("../data/collated_summary_data.csv")
+
+source("helper_functions_tables_figures.r") #Load functions to prep data for figures
 ```
@@
 
-est_heterogen_smd_raw <- function(x){
-  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
-
-    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){
-
-    fit <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)
-
-  } else if(any(x[, "effect_type"] == "Raw mean difference")){
-
-    fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){
-
-    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)
-
-  } else if(any(x[, "effect_type"] == "r")){
-
-    fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal, test = "knha", data = x)
-
-  } else{ #for all two-group count effects
-
-    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized, ML1 used 'OR2D' but that = 'OR2DL'
-               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
-
-  }
-
-  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
-             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
-}
-
-#Apply function to data
+#fit a random effects model to all empirical data
+#Each set of input datapoints is meta-analyzed as per the original replication project
+#Function 'est_heterogen_smd_raw' is sourced
 res <- dat %>% 
@@
 
-OR <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR
-
-#Add rs to the data-frame
+#Add rs and k to the data-frame and prep for table
 het <- dat %>% 
@@
                               'Raw mean difference' = "MD",
-                              'Risk difference' = "RD")) %>% 
+                              'Risk difference' = "RD"))
+
+#Load simulation results (power/type 1 error for all effects)
+dens <- readRDS("temp_sim_results_2.RDS")
+names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
+
+#Summary of simulation results, needs to be combined with main part of table
+I2_ci_lb <- dens %>% 
+  bind_rows(.id = "effect") %>% 
+  group_by(effect, tau_index) %>% 
+  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
+  ungroup() %>% 
+  tidyr::spread(key = tau_index, value = power) %>% #prep for table
+  rename(zero = '1', small = '2', medium = '3', large = '4')
+
+#Combine dataframes to create full table
+het <-  het %>% 
+  left_join(I2_ci_lb) %>% 
   select(rs, effect,k , everything()) %>% 
@@
 ```{r heterogeneity-table}
-library(kableExtra)
+#library(kableExtra)
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE,digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Size", "I2(%)", "ci.lb", "ci.ub")) %>% 
-  kable_styling("scale_down") %>%
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>%
+  add_header_above(c(" " = 8, "Heterogeneity & power/type 1" = 4)) %>% 
+  kable_styling("scale_down", font_size = 8) %>%
   footnote(threeparttable = TRUE, escape = FALSE,
-           general = "We meta-analyzed effects using the same outcome measures that were used by the original authors.
-Standardized mean difference is Hedge's g.
+           general = " Effects were estimated in metafor using REML.
 The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs.

### 2018-06-24 code/helper_functions_tables_figures.r

@@ -1,0 +1,140 @@
+#******************************************
+
+#Project: Heterogeneity in direct replications
+#Script purpose: Helper functions to prep data for tables and figures
+#Code: Anton Ohlsson Collentine
+#Additional comments: These functions are intended to be 'sourced' into the 
+#                     tables.rmd and figures.rmd files 
+
+#******************************************
+
+
+
+#******************************************
+#Function to fit a random effects model to all empirical data----
+#******************************************
+#Each set of input datapoints is meta-analyzed as per the original replication project
+
+est_heterogen_smd_raw <- function(x){
+  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
+    
+    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol,  data = x)
+    
+  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){  
+    
+    fit <-  rma(yi = effect_size, sei = outcome_c2,  data = x) 
+    
+  } else if(any(x[, "effect_type"] == "Raw mean difference")){
+    if(any(x[, "rs"] %in% c("RRR5", "RRR7"))){ #For these us the Knapp and Hartung adjustment of standard errors
+      
+      fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, test ="knha", data = x)
+    } else{
+      fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
+    }
+    
+  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){  
+    
+    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x) 
+    
+  } else if(any(x[, "effect_type"] == "r")){
[…]

### 2018-06-24 code/power_simulation.r

@@ -4,17 +4,28 @@
 #Script purpose: Simulate I2 distribution for different levels of heterogeneity given data weights
 #Code: Anton Ohlsson Collentine
 
+##TO DO----
+#Should save results as .csv maybe
+
 #******************************************
 
 
 #******************************************
 #Packages and data----
 #******************************************
-library(readr)
-library(metafor)
-library(dplyr)
-library(purrr) #for 'possibly'
-library(ggplot2)
+if(!require(readr)){install.packages("readr")}
+if(!require(metafor)){install.packages("metafor")}
+if(!require(dplyr)){install.packages("dplyr")}
+if(!require(purrr)){install.packages("purrr")}
+if(!require(ggplot2)){install.packages("ggplot2")}
+if(!require(tidyr)){install.packages("tidyr")}
+
+
+library(readr) #load data
+library(metafor) #run meta-analyses
+library(dplyr) #general data wrangling
+library(purrr) #for 'possibly' and iteration with 'map'
+library(ggplot2) #plot results from first simulation
 library(tidyr) #for 'spread'
 
 dat <- read_csv("../data/collated_summary_data.csv")
@@ -72,7 +83,7 @@ simulate_I2 <- function(effect, reps, tau){ #this function applies to a single l
 }
 
 #******************************************
-#Run simulations to estimate tau values that correspond to small/medium/large I2----
+#Simulation 1 -  estimate tau values that correspond to small/medium/large I2----
 #******************************************
 
 dat2 <- dat %>% #Extract k and effect type for each effect and N of each included study
@@ -85,7 +96,7 @@ set.seed(112)
 res <- vector("list", length(dat2)) #output of below loop
 
 system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
- res[[e]] <- simulate_I2(dat2[[e]], reps = 1, tau = tau_values)
+ res[[e]] <- simulate_I2(dat2[[e]], reps = 100, tau = tau_values) #100 reps is about 3.5 hours on my (fairly slow) machine
  cat("...RS",e, "/37") #see progress
  if (e%%5 == 0 | e == 37) saveRDS(res, "temp_sim_results.RDS") #save ocassionally and at finish
 })
@@ -110,24 +121,13 @@ dat4 <- dat3 %>%
[…]

### 2018-06-24 code/tables.rmd
Shrunk font size of main table to fit on one page

@@
 het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>%
-  add_header_above(c(" " = 8, "Heterogeneity & power/type 1" = 4)) %>% 
-  kable_styling("scale_down", font_size = 8) %>%
+  add_header_above(c(" " = 8, "Heterogeneity & error/power" = 4)) %>% 
+  kable_styling("scale_down", font_size = 7) %>%
   footnote(threeparttable = TRUE, escape = FALSE,

### 2018-06-27 writing/draft-heterogeneity.rmd
Changed tables to simple versions, addied figure captions
To arrange in word later

@@
    - \doublespacing
-output: pdf_document
+output: word_document
 ---
@@
 
-```{r load data and packages}
-library(readr)
-library(dplyr)
-library(kableExtra)
-library(metafor)
-library(purrr)
+```{r load packages, data and source functions}
+if(!require(readr)){install.packages("readr")}
+if(!require(metafor)){install.packages("metafor")}
+if(!require(dplyr)){install.packages("dplyr")}
+if(!require(purrr)){install.packages("purrr")}
+if(!require(kableExtra)){install.packages("kableExtra")}
+
+library(readr) #To load data
+library(dplyr) #For data transformation
+library(purrr) #For data iteration
+library(metafor) #To run meta-analyses
+library(kableExtra) #For creating good-looking pdf tables
 
 dat <- read_csv("../data/collated_summary_data.csv")
-```
 
-```{r prep-heterogeneity-table}
-#library(metafor)
-#library(dplyr)
-#library(purrr)
-
-est_heterogen_smd_raw <- function(x){
-  if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
-
-    fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol,  data = x)
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){
-
-    fit <-  rma(yi = effect_size, sei = outcome_c2,  data = x)
-
-  } else if(any(x[, "effect_type"] == "Raw mean difference")){
-    if(any(x[, "rs"] %in% c("RRR5", "RRR7"))){ #For these us the Knapp and Hartung adjustment of standard errors
-
-      fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, test ="knha", data = x)
-    } else{
-      fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
-    }
-
-  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){
-
-    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
-
-  } else if(any(x[, "effect_type"] == "r")){
-    if(any(x[, "rs"] == "ML1")){
-      fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal,  data = x)
-    } else{ #for ML3
-      fit <- rma(measure = "UCOR", ri = effect_size, ni = Ntotal,  data = x, vtype = "UB")
-      #Note that ML3 specifies measure = "COR" with vtype = "UB", but that this is specified as above in the latest metafor 
-    }
-
-  } else{ #for all two-group count effects
-
-    fit <- rma(measure = "OR2DL", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, 
-               n1i = ntreatment, n2i = ncontrol,  data = x)
-    #standardized, ML1 used 'OR2D' which = 'OR2DL' in latest version of metafor
-
-  }
-
-  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
-             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
-}
-
-#Apply function to data
-res <- dat %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
-
-OR <- c("Allowed vs. forbidden", "Gain vs. loss framing", "Norm of reciprocity", "Low vs. high category scales") #Effects reported as d in many labs 1 but meta-analyzed as OR
-
-#Add rs to the data-frame
-het <- dat %>% 
-  select(rs, Site, effect, effect_type) %>% 
-  group_by(rs, effect) %>% 
-  summarize(effect_type = unique(effect_type),
-            k = n_distinct(Site)) %>% 
-  left_join(res) %>% 
-  mutate(effect_type = recode(effect_type, 
-                              d = "SMD.",
-                              'Raw mean difference' = "MD",
-                              'Risk difference' = "RD")) %>% 
-  select(rs, effect,k , everything()) %>% 
-  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
+source("../code/helper_functions_tables_figures.r") #Load functions to prep data for figures
 ```
@@
 
-##Table 1.
-###Heterogeneity may increase with effect size
-```{r effect-size-heterogeneity-table}
-#library(kableExtra)
-rooted_relabilities <- matrix(rep(c(.8, .7,.6), 3), ncol = 3)
-rho <- c(0, .5, .8)
-rel <- c("R = .8", "R = .7", "R = .6")
+Table 1.
 
-rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
-diff_row <- data.frame(rel = "Diff.", X1 = 0, X2 = 0.05, X3 = 0.08)
-
-het_demo <- data.frame(rel, rooted_relabilities)
-het_demo <- rbind(het_demo, diff_row)
-
-het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "Rho = 0", "Rho = .5", "Rho = .8")) %>% 
-  kable_styling() %>% 
-  footnote(threeparttable = TRUE,
-           general = "R = square root of the multiplied reliabilities") %>% 
-  row_spec(3, hline_after = T)
-
-```
+_Heterogeneity may increase with effect size_
 
@@
 For example, the variety of countries and samples involved in some of the replication projects, not all of which are WEIRD (Western, Educated, Industrial, Rich, Democratic [ref: Weird]) might be a reason to expect heterogeneity.
-On the other hand, it may be that the less disparate collection of studies included in the these direct replication meta-analyses as compared to most psychological meta-analyses result in low heterogeneity estimates, similar to estimates in medicine.
+On the other hand, it may be that the less disparate collection of studies included in these direct replication meta-analyses as compared to most psychological meta-analyses result in low heterogeneity estimates, similar to estimates in medicine.
 Regardless of outcome, the sampled multi-lab replication projects can only inform us of susceptibility to changes in the varied contextual factors  (sample population and settings), with no information on susceptibility to changes in other contextual factors.
 
-##Table 2.
-```{r data-summary-table}
-#library(dplyr)
-#library(kableExtra)
+Table 2.
 
-#Shortened version of APA reference
-papers <- c('Klein, R.
-A., Ratliff, K.
-A., Vianello, M., Adams, R.
-B., Jr., Bahník, S., Bernstein, M.
-J., .
-.
-.
-Nosek, B.
-A.
-(2014).
-Investigating variation in replicability: A "many labs" replication project.',
-'Ebersole, C.
-R., Atherton, O.
-E., Belanger, A.
-L., Skulborstad, H.
-M., Allen, J.
-M., Banks, J.
-B., ...
-& Brown, E.
-R.
-(2016).
-Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
-'Ebersole, C.
-R., Atherton, O.
-E., Belanger, A.
-L., Skulborstad, H.
-M., Allen, J.
-M., Banks, J.
-B., ...
-& Brown, E.
-R.
-(2016).
-Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
-'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
-'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011).',
-'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
-'Cheung, I., Campbell, L., LeBel, E.
-P., Ackerman, R.
-A., Aykutoglu, B., Bahník, S., ...
-& Carcedo, R.
-J.
-(2016).
-Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).',
-'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
-'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
-"O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")
+_Pre-registered multi-lab replication studies_
 
-summary.table <- dat %>% 
-  group_by(rs) %>% 
-  summarize(k = n_distinct(Site),
-            Countries = n_distinct(country), 
-            Effects = n_distinct(effect),
-            Participants = if(Effects == 1){sum(Ntotal)}
-                           else{sum(Ntotal) / Effects}) %>% #average across effects
-  mutate(Paper = papers) %>% 
-  select(RS = rs, Paper, everything()) #change order of columns
-
-summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
-  kable_styling() %>% 
-  column_spec(2, width = "25em") %>% #specify width of paper column
-  footnote(threeparttable = TRUE,
-           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
-Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
-RS = Replication Study, k = no.
-primary studies, ML = Many Labs, RRR = Registered Replication Report.
-(OSF.io/XXXX)")
-```
-
-###Method
+##Method
 
@@
 
-We downloaded and collated summary data from 10 pre-registered multi-lab replication projects in psychology (Table 2).
-Data from all 10 projects were publicly available on the Open Science Framework (osf.io) and downloaded between 2018/02/01 and 2018/03/31.
+We downloaded and collated summary data from ten pre-registered multi-lab replication projects in psychology (Table 2).
+Data from all ten projects were publicly available on the Open Science Framework (osf.io) and downloaded between 2018/02/01 and 2018/03/31.
 Although some projects (e.g.
@@
 After estimating effects, ML3 transformed correlations into eta-squared for reporting, which we did not.
-For each effect we estimated I2 and its 95% confidence interval.
+For each effect we estimated $I^2$ and its 95% confidence interval.
 Confidence intervals were calculated in metafor which uses the Q-profile method [ref Jackson 2014].
 
-[Ignore the following paragraph - power simulation paragraph - subject to change]
-To facilitate interpreting results, we estimated power and type 1 error for each of the 37 effects under zero/small/medium/large heterogeneity (I2 = 0/25/50/75%  respectively), as well as the expected I2-distributions across effects at these heterogeneity levels (osf.io/XXXX/).
-To do so we simulated results for each effect given the number of studies, k, and the sample sizes of each study, $N_k$, for that effect.
-Our approach consisted of (i) varying the between-studies variance,  $\tau^2$, for each effect to find the values that best corresponded to I2-estimates of 25/50/75% and (ii) using the found values to estimate power and type 1 error by computing the proportion non-significant results over a large number of replications.
-In step (i), we varied $\tau^2$ between 0.000 and 0.250 in increments of 0.005,  and replicated each condition 50 times.
-We then computed the average I2 across the 50 replications, discarding non-converging models, and for each effect saved the $\tau^2$ values that best corresponded to small, medium, and large I2.
-For homogeneity we set $\tau^2$ to zero.
-In step (ii), to estimate power and type 1 error, we ran one thousand replications at each identified level of heterogeneity using the $\tau^2$-values of step (i).
-We considered a result significant when the lower bound of the 95% I2 confidence interval was above zero and save heterogeneity estimates were saved from each replication for plotting I2-distributions.
+In order to facilitate interpretation of our results, we estimated power and type 1 error for each of the 37 effects under zero/small/medium/large heterogeneity ($I^2$ = 0/25/50/75%  respectively).
+In addition, we plotted $I^2$-distributions across effects at these heterogeneity levels and compared with all observed $I^2$ estimates.
+To do so we simulated results for each effect given the number of studies, k, and the sample sizes, $N_k$, of those studies (osf.io/XXXX/).
+In the case of correlations we 1) generated a true correlation $\rho_k$ from a normal distribution with  between studies standard deviation $\tau$ and mean effect size zero, $\rho_k \sim N(0,  \tau)$, and 2) generated an observed correlation expressed as Fisher's z $rz_k$ from a normal distribution with mean $\rho_k$ and standard deviation $\sqrt{1 / N_k - 3}$, $rz_k \sim N(\rho_k, \sqrt{1 / N_k - 3})$.
+For mean differences we assumed equal within study group sizes $n_c = n_t$ ($= N_k$ rounded to closest integer) and standard deviation $\sigma_c = \sigma_t$.
+We then 1) generated study effect sizes $\mu_k$ from a normal distribution with mean zero and standard deviation $\tau$, $\mu_k \sim N(0, \tau)$, and 2) generated control and treatment means from the sampling distributions $\bar{x}_c \sim N(0, 1 / \sqrt{n_c})$ and $\bar{x}_t \sim N(\mu_k, 1 / \sqrt{n_t})$ respectively.
+Group variances were generated from their sampling distributions as well, in accordance with $s^2_c = \chi^2 (n_c - 1) / (n_c - 1)$ and  $s^2_t = \chi^2 (n_t - 1) / (n_t - 1)$.
+Due to the difficulties of data generation for odds ratios and risk differences we treated these as mean differences.
+For each effect, our simulations then proceeded in three steps: i) we varied the between studies standard deviation, $\tau$, between 0.000 and 0.50 in increments of 0.005 and replicated each condition 1000 times, each time estimating $I^2$ with a random effects model with REML, ii) we computed the average $I^2$ in each condition, discarding non-converged models, and iii) ran 10 000 replications at the $\tau$ values in step _ii_ that best corresponded to an $I^2$ estimate of 25% (small), 50% (medium) and 75% (large).
+For homogeneity we set $\tau$ to zero.
+We considered a result significant when the lower bound of the 95% $I^2$ confidence interval was above zero.
 
-[Ignore the following paragraph - power simulation paragraph - subject to change]
-In both steps of our simulation, we followed the same data generating procedure.
-For each effect, we generated k effect sizes, $\theta_k$, from a normal distribution with a mean of zero and between-studies variance $\tau^2$: $\theta_k \sim N(0,  \tau^2)$.
-For the sake of simplicity, we made the choice to set the average effect size to zero and treated each effect as consisting of a treatment and control group.
-We thus drew an effect size $\theta_k$ for each replication study of an effect, and within each study we then generated $N_k / 2$ (rounded to closest integer) sample values for a treatment and for a control group from two normal distributions with means $\mu_t = \theta_k$ and $\mu_c = 0$ and equal within-study variances ($\sigma^2 = 1$).
-This provided sample means and standard deviations for all k treatment and control groups of an effect, which we then used to estimate a random effects model for standardized mean differences in metafor using REML.
-This process was repeated the desired number of times for each condition and effect.
-
-To examine the correlation between effect size and I2 we converted all effect sizes to a common metric (osf.io/XXXX/).
-Since I2 is logically and mathematically bounded at zero, we also correlated effect sizes with the closely related heterogeneity estimate H2, which is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - I2)$ for $I2 \geq 0$.
-We first converted all effects into correlations (r) and used the R-package metafor [ref] to estimate I2 and meta-analytic effects expressed as Fisher's z.
+To examine the correlation between effect size and $I^2$ we converted all effect sizes to a common metric (osf.io/XXXX/).
+We first converted all effects into correlations (r) and used the R-package metafor [ref] to estimate $I^2$ and meta-analytic effects expressed as Fisher's z.
 In doing so, we fitted random-effects models with metafor's default REML estimator.
@@
 232) and then finally to a correlation.
-All formulas used are presented in Appendix A.
+All formulas used are presented in Appendix A (osf.io/XXXX/).
+Since $I^2$ is set to zero for the majority of cases under homogeneity (i.e., truncated), we also correlated effect size with with the closely related heterogeneity estimate H2 [ref: Higgins 2002] as a sensitivity analysis.
+The H2 index is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - $I^2$)$ for $I^2 \geq 0$.
+It ranges from zero to positive infinity, where a larger score indicates more heterogeneity, a score of one indicates homogeneity, and a score between zero and one thus indicates 'excessive' homogeneity.
 
@@
 
-Table 3 presents the meta-analytic estimates and I2 with confidence intervals for each of the 37 included effects.
+Table 3 presents the meta-analytic estimates and $I^2$ with confidence intervals for each of the 37 included effects.
 
-##Table 3.
+```{r prep-heterogeneity-table}
+# library(metafor)
+# library(dplyr)
+# library(purrr)
+
+#fit a random effects model to all empirical data
+#Each set of input datapoints is meta-analyzed as per the original replication project
+#Function 'est_heterogen_smd_raw' is sourced
+res <- dat %>% 
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
+
+#Add rs and k to the data-frame and prep for table
+het <- dat %>% 
+  select(rs, Site, effect, effect_type) %>% 
+  group_by(rs, effect) %>% 
+  summarize(effect_type = unique(effect_type),
+            k = n_distinct(Site)) %>% 
+  left_join(res) %>% 
+  mutate(effect_type = recode(effect_type, 
+                              d = "SMD.",
+                              'Raw mean difference' = "MD",
+                              'Risk difference' = "RD"))
+
+#Load simulation results (power/type 1 error for all effects)
+dens <- readRDS("../code/temp_sim_results_2.RDS")
+names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
+
+#Summary of simulation results, needs to be combined with main part of table
+I2_ci_lb <- dens %>% 
+  bind_rows(.id = "effect") %>% 
+  group_by(effect, tau_index) %>% 
+  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
+  ungroup() %>% 
+  tidyr::spread(key = tau_index, value = power) %>% #prep for table
+  rename(zero = '1', small = '2', medium = '3', large = '4')
+
+#Combine dataframes to create full table
+het <-  het %>% 
+  left_join(I2_ci_lb) %>% 
+  select(rs, effect,k , everything()) %>% 
+  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
+
+```
+
+Table 3.
+
+_Heterogeneity across primary effects in ten multi-lab replication projects._
 ```{r heterogeneity-table}
@@
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE,digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub")) %>% 
-  kable_styling("scale_down") %>%
-  footnote(threeparttable = TRUE, escape = FALSE,
-           general = " Effects were estimated in metafor using REML.
+het %>% knitr::kable(digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) 
+```
+
+**Note:**  Effects were estimated in metafor using REML.
 The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs.
@@
 high category scales'.
-RS = Replication Study, k = no.
-primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval.
+RP = Replication Project, k = no.
+primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of $I^2$ 95\\% confidence interval, ci.ub = upper bound of $I^2$ 95\\% confidence interval.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-(OSF.io/XXXX)")
+Under simulated heterogeneity, Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\%) respectively.
+(OSF.io/XXXX)"
 
+###$I^2$ estimates and confidence intervals
+
+There is limited evidence for heterogeneity across the examined effects.
+Of the 37 effects,  4/37 (11%) have $I^2$ estimates that best correspond to large heterogeneity ($I^2$ = 75%), 4/37 (11%) to medium heterogeneity ($I^2$ = 50%), 9/37 (24%)  to small heterogeneity ($I^2$ = 25%) and 17/37 (54%) to zero heterogeneity ($I^2$ = 0%).
+However, despite relatively large k and total sample size for most projects (see Table 2), Table 3 shows wide confidence intervals for many effects: 10/37 (27%) effects have confidence intervals congruent with small to large heterogeneity and 15/37 (41%) with zero to medium.
+The lower bound $I^2$ confidence interval excludes zero for only 7/37 effects (19%; Table 3), all part of the ML1 project.
+The percentage of heterogeneity estimates larger than 0 (23/37; 62%) suggests heterogeneity for at least some effects, as this percentage is higher than the expected frequency of non-zero estimates under homogeneity (46%, or about 17/37), based on the chi-square distribution and average k across projects.
+
+###$I^2$ and power
+
+We estimated $I^2$ for a large range of between studies standard deviations for each of the 37 effects (Figure 1).
+The $I^2$ index increases non-linearly with heterogeneity and is relatively more sensitive to lower between studies variances.
+This appears to be less so in the case of  mean differences than for correlations, which correspond to the more steeply inclined curves in Figure 1.
+
+```{r}
+knitr::include_graphics("../figures/tau-I2.png")
 ```
 
-We examined the evidence for heterogeneity across a set of pre-registered multi-lab replication projects.
-Few effects show evidence of heterogeneity.
-The lower bound I2 confidence interval excludes zero for only 7/37 effects (19%; Table 3), all part of the ML1 project.
-The percentage of heterogeneity estimates larger than 0 (23/37; 62%) suggests heterogeneity for at least some effects, as this percentage is higher than the expected frequency of non-zero estimates under homogeneity (46%, or about 17/37), based on the chi-square distribution and average k across projects.
-Of those effects whose lower bound confidence interval includes zero, 15/30 (50%) have confidence intervals that exceed 50% (medium heterogeneity).
+_Figure 1.
+Result of simulation relating $I^2$-values to between studies standard deviation.
+Each line represent one of 37 effects.
+The more steeply inclined lines belong to correlations and the others to mean differences._
 
-[add segment on power with figures when ready]
+Power and type 1 error estimates for zero/small/medium/large heterogeneity are shown for each effect in Table 3.
+In all cases the type 1 error is conservative, as compared to the expected 5% error rate.
+Power to detect small heterogeneity was low, ranging between 18% (Professor priming) and  45% (Flag priming), with an average of 28%.
+Power to detect medium heterogeneity was generally good, with an average of 79% power, but was only around 60% for several effects with low K.
+Power to detect strong heterogeneity was excellent across the board.
+
+Figure 2 shows the distribution of $I^2$ at different heterogeneity levels and a histogram of the observed effects.
+The shortest bars in the histogram correspond to a single effect.
+The considerable overlap of the distributions illustrates why sufficient power can be difficult to achieve, and why confidence intervals for $I^2$ are often wide.
+In particular the spread of the distribution under small heterogeneity is illustrative of the low power to be expected under such circumstances.
+Given the densities of the distributions (height of the curves) the majority of observed effects are most likely to have either zero or small heterogeneity.
+Only two effects appear to be of medium heterogeneity and three of large.
+
+```{r}
+knitr::include_graphics("../figures/density-I2.png")
+```
+
+_Figure 2.
+Simulated $I^2$ densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of [Higgins], and a histogram of the observed $I^2$ estimates for the 37 effects.
+Each simulated density consists of approximately 1,480,000 point estimates._
+
+###$I^2$ and effect sizes
 
 Larger effect sizes appear to be associated with higher heterogeneity estimates.
-In Table 3, the four effects with highest I2 estimates also have the largest effect sizes.
-As expected, heterogeneity tends to increase with (absolute) effect size, with effect size sufficient to explain 61% of variation in I2 estimates according to a simple regression model (Figure 1).
-The closely related, but unbounded, heterogeneity estimate H2 provides a similar result (R2 = .53).
-Excluding Anchoring effects as robustness check makes little difference (R2 = .51 for I2).
+In Table 3, the four effects with highest $I^2$ estimates also have the largest effect sizes.
+As expected, heterogeneity tends to increase with (absolute) effect size, with effect size sufficient to explain 61% of variation in $I^2$ estimates according to a simple regression model (Figure 3).
+The closely related, but unbounded, heterogeneity estimate $H^2$ provides a similar result ($R^2$ = .53).
+Excluding Anchoring effects as robustness check makes little difference ($R^2$ = .51 for $I^2$).
 
-##Figure 1
 ```{r}
-knitr::include_graphics("../code/effect_het.png")
+knitr::include_graphics("../figures/effect_het.png")
 ```
+
+_Figure 3. The correlation between A) $I^2$ and effect size and B) $H^2$ and effect size for 37 effects from ten pre-registered multi-lab replication projects._
 
@@
 As always, absence of evidence is not evidence of absence.
-Finally, since the included studies only vary on two contextual factors (sample population and settings) , the data tell us nothing about the included effects' susceptibility to changes in the other two factors (treatment and measurement variables).
+Finally, since the included studies only vary on two contextual factors (sample population and settings), the data tell us nothing about the included effects' susceptibility to changes in the other two factors (treatment and measurement variables).
 

### 2018-06-27 code/figures.rmd
Changed rs to rp (Replication Project)
Also added simulation data, as RDS files because .csv files were too large

@@
 
-# ggsave("I2_effect_size.png")
-
 # summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53
@@
 
-# ggsave("H2_effect_size.png")
-
 effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
 effect_het
-# save_plot("effect_het.png", effect_het,
+# save_plot("../figures/effect_het.png", effect_het,
           # nrow = 2, base_aspect_ratio = 1.3)
@@
 ```{r Plot_tau_against_I2, fig.asp = 0.618}
-dat3 <- readRDS("temp_sim_results.RDS")
+dat3 <- readRDS("../data/tau_simulation_results.RDS")
 names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
@@
 
+# ggsave("../figures/tau-I2.png")
+
 ```
@@
 ```{r Density_plot, fig.asp= 0.618}
-dens <- readRDS("temp_sim_results_2.RDS")
+dens <- readRDS("../data/power_simulation_results.RDS")
 names(dens) <-  sort(unique(dat$effect))
@@
   bind_rows(.id = "effect") %>% 
-  rename(heterogeneity = tau_index) %>% 
-  mutate(heterogeneity = recode(heterogeneity,
+  rename(Heterogeneity = tau_index) %>% 
+  mutate(Heterogeneity = recode(Heterogeneity,
                             '1' = "Zero",
@@
                             '4' = "Large"),
-         heterogeneity = as.factor(heterogeneity))
+         Heterogeneity = as.factor(Heterogeneity))
 
@@
   select(effect, I2 = s_I2) %>%
-  mutate(heterogeneity = "Observed")
+  mutate(Heterogeneity = "Observed")
 
-ggplot(I2_dist, aes(x = I2, group = heterogeneity, fill = heterogeneity, linetype = heterogeneity)) +
-  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 50, alpha = 1) +
+ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
+  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
   geom_density(alpha = 0.3) +
@@
 
+# ggsave("../figures/density-I2.png")
 ```

### 2018-06-27 code/tables.rmd
Changed rs to rp (Replication Project)
Also added simulation data, as RDS files because .csv files were too large

@@
 summary.table <- dat %>% 
-  group_by(rs) %>% 
+  group_by(rp) %>% 
   summarize(k = n_distinct(Site),
@@
   mutate(Paper = papers) %>% 
-  select(RS = rs, Paper, everything()) #change order of columns
+  select(RP = rp, Paper, everything()) #change order of columns
 
@@
 Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
-RS = Replication Study, k = no.
+RP = Replication Project, k = no.
 primary studies, ML = Many Labs, RRR = Registered Replication Report.
@@
 
-#Add rs and k to the data-frame and prep for table
+#Add rp and k to the data-frame and prep for table
 het <- dat %>% 
-  select(rs, Site, effect, effect_type) %>% 
-  group_by(rs, effect) %>% 
+  select(rp, Site, effect, effect_type) %>% 
+  group_by(rp, effect) %>% 
   summarize(effect_type = unique(effect_type),
@@
 #Load simulation results (power/type 1 error for all effects)
-dens <- readRDS("temp_sim_results_2.RDS")
+dens <- readRDS("../data/power_simulation_results.RDS")
 names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
@@
   left_join(I2_ci_lb) %>% 
-  select(rs, effect,k , everything()) %>% 
+  select(rp, effect,k , everything()) %>% 
   arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
+
 ```
@@
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>%
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>%
   add_header_above(c(" " = 8, "Heterogeneity & error/power" = 4)) %>% 
@@
 high category scales'.
-RS = Replication Study, k = no.
-primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of I2 95\\\\% confidence interval, ci.ub = upper bound of I2 95\\\\% confidence interval.
+RP = Replication Project, k = no.
+primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of $I^2$ 95\\\\% confidence interval, ci.ub = upper bound of $I^2$ 95\\\\% confidence interval.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-(OSF.io/XXXX)")
+(OSF.io/XXXX)",
+           alphabet = "These effects were simulated as standardized mean differences")
 

### 2018-06-27 code/collate_summary_data.r

@@ -18,7 +18,7 @@
 #**[2.2] t-test effects
 #**[2.3] Non-parametric tests
 #**[2.4] Interaction effects
-#**[2.5] Correlation conscientiousness and persistance
+#**[2.5] Correlation conscientiousness and persistence
 #**[2.6] Ml3 combined
 #[3] RRR1 & 2
 #[4] RRR3 
@@ -134,7 +134,7 @@ for(i in seq_along(tnames)){
     rename_at(vars(one_of(tot2)), funs(paste0("outcome_t2"))) %>%
     rename_at(vars(one_of(toc2)), funs(paste0("outcome_c2"))) %>%
     rename(effect_size = "ES (from means)")  %>%
-    mutate(rs = "ML1", #Add some descriptive information
+    mutate(rp = "ML1", #Add some descriptive information
            effect = tnames[i], 
            B_or_W = "Between", 
            design = "control vs. treatment", 
@@ -145,7 +145,7 @@ for(i in seq_along(tnames)){
            country = c("USA", "BRA", "CZE", "USA", "USA", "MYS", "USA", "USA", "TUR", "CAN", "GBR", #Country of each study site
                        "USA", "USA", "CAN", rep("USA", 8), "POL", "POL", rep("USA", 3), "NLD", "USA",
                        "ITA", rep("USA", 6))) %>% 
-    select(rs, effect, Site, country, in_lab, Ntotal, B_or_W, design, or_stat_test, effect_type, effect_size, 
+    select(rp, effect, Site, country, in_lab, Ntotal, B_or_W, design, or_stat_test, effect_type, effect_size, 
            ncontrol, ntreatment,outcomes1_2, outcome_c1, outcome_t1, outcome_c2, outcome_t2) #select only variables of interest
 }
 
@@ -197,7 +197,7 @@ chieffects[[i]] <- chieffects[[i]] %>%
     rename_at(vars(one_of(tot2)), funs(paste0("outcome_t2"))) %>%
     rename_at(vars(one_of(toc2)), funs(paste0("outcome_c2"))) %>%
     rename(effect_size = "ES (from means)")  %>%
-  mutate(rs = "ML1", #Add some descriptive information
+  mutate(rp = "ML1", #Add some descriptive information
          effect = chinames[i], 
          B_or_W = "Between", 
          design = "Choice of outcome 1 vs. 2 between groups", 
[…]

### 2018-06-27 code/helper_functions_tables_figures.r

@@ -25,7 +25,7 @@ est_heterogen_smd_raw <- function(x){
     fit <-  rma(yi = effect_size, sei = outcome_c2,  data = x) 
     
   } else if(any(x[, "effect_type"] == "Raw mean difference")){
-    if(any(x[, "rs"] %in% c("RRR5", "RRR7"))){ #For these us the Knapp and Hartung adjustment of standard errors
+    if(any(x[, "rp"] %in% c("RRR5", "RRR7"))){ #For these us the Knapp and Hartung adjustment of standard errors
       
       fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, test ="knha", data = x)
     } else{
@@ -37,7 +37,7 @@ est_heterogen_smd_raw <- function(x){
     fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x) 
     
   } else if(any(x[, "effect_type"] == "r")){
-    if(any(x[, "rs"] == "ML1")){
+    if(any(x[, "rp"] == "ML1")){
       fit <- rma(measure = "COR", ri = effect_size, ni = Ntotal,  data = x)
     } else{ #for ML3
       fit <- rma(measure = "UCOR", ri = effect_size, ni = Ntotal,  data = x, vtype = "UB")

### 2018-06-27 code/power_simulation.r

@@ -4,9 +4,6 @@
 #Script purpose: Simulate I2 distribution for different levels of heterogeneity given data weights
 #Code: Anton Ohlsson Collentine
 
-##TO DO----
-#Should save results as .csv maybe
-
 #******************************************
 
 
@@ -96,12 +93,12 @@ set.seed(112)
 res <- vector("list", length(dat2)) #output of below loop
 
 system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
- res[[e]] <- simulate_I2(dat2[[e]], reps = 100, tau = tau_values) #100 reps is about 3.5 hours on my (fairly slow) machine
+ res[[e]] <- simulate_I2(dat2[[e]], reps = 1000, tau = tau_values) #100 reps is about 3.5 hours on my (fairly slow) machine
  cat("...RS",e, "/37") #see progress
- if (e%%5 == 0 | e == 37) saveRDS(res, "temp_sim_results.RDS") #save ocassionally and at finish
+ if (e%%5 == 0 | e == 37) saveRDS(res, "../data/tau_simulation_results.RDS") #save ocassionally and at finish
 })
 
-dat3 <- readRDS("temp_sim_results.RDS")
+dat3 <- readRDS("../data/tau_simulation_results")
 names(dat3) <- names(dat2) #names are lost when looping instead of using lapply
 
 dat3 <- dat3 %>% 
@@ -143,11 +140,11 @@ res2 <- vector("list", length(dat5))
 system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progress (lapply otherwise option)
   res2[[e]] <- simulate_I2(dat5[[e]][[1]], reps = 1e4, tau = c(0, dat5[[e]][[2]]))
   cat("...RS",e, "/37") #see progress
-  if (e%%5 == 0 | e == 37) saveRDS(res2, "temp_sim_results_2.RDS") #save ocassionally and at finish
+  if (e%%5 == 0 | e == 37) saveRDS(res2, "../data/power_simulation_results.RDS") #save ocassionally and at finish
 })
 
 
-dens <- readRDS("temp_sim_results_2.RDS")
+dens <- readRDS("../data/power_simulation_results.RDS") #very large if saved as .csv
 names(dens) <-  names(dat2)
 
 #Summary of results. These are incorporated into the main table in the paper, see tables.rmd

### 2018-06-27 code/codebook_collated_summary_data.rmd
Updated codebook and created a pdf version

---
dataMaid: yes
title: Codebook for collated_summary_data.csv
subtitle: "Limited evidence for widespread heterogeneity in psychology"
output: pdf_document
documentclass: article
header-includes:
  - \newcommand{\fullline}{\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}}
  - \renewcommand\familydefault{\sfdefault}
---
```{r , echo=FALSE, include=FALSE, warning=FALSE, message=FALSE, error=FALSE}
library(ggplot2)
library(pander)
```
# Data report overview
The dataset examined has the following dimensions:

---------------------------------
Feature                    Result
------------------------ --------
Number of observations        988

Number of variables            18
---------------------------------

# Codebook summary table

-----------------------------------------------------------------------------------------------------
Label   Variable               Class         # unique  Missing  Description                          
                                               values                                                
------- ---------------------- ----------- ---------- --------- -------------------------------------
        **[rp]**               character           10  0.00 %   Replication Project

        **[effect]**           character           37  0.00 %   Studied effect

        **[Site]**             character          200  0.00 %   Lab-identifier within each           
                                                                replication project

        **[country]**          character           27  0.00 %   Country of participants {ISO         
                                                                Alpha-3 code}

        **[in\_lab]**          integer              2  0.00 %   Whether study took place in-lab {1}  
                                                                or not {0} (0 = online)

        **[Ntotal]**           integer            226  0.00 %   Total study sample size

        **[B\_or\_W]**         character            2  0.00 %   Between or within groups study

        **[design]**           character            9  0.00 %   Description of design of research

        **[or\_stat\_test]**   character           11  4.96 %   Statistical test used, if any

        **[effect\_type]**     character            4  0.00 %   Reported effect type {d, r, Risk     
                                                                difference, Raw mean difference}

        **[effect\_size]**     numeric            902  0.00 %   Size of reported effect

        **[ncontrol]**         integer            150  11.94 %  Sample size control group

        **[ntreatment]**       integer            153  11.94 %  Sample size treatment group

        **[outcomes1\_2]**     character           10  0.00 %   Describes content in outcome_1 and   
                                                                outcome_2. For chi-square            
                                                                effects(group1, group2) indicates    
                                                                'treatment' and 'control' groups

        **[outcome\_c1]**      numeric            666  14.07 %  Control group outcome 1

        **[outcome\_t1]**      numeric            675  14.07 %  Treatment group outcome 1

        **[outcome\_c2]**      numeric            652  18.22 %  Control group outcome 2

        **[outcome\_t2]**      numeric            635  20.55 %  Treatment group outcome 2            
-----------------------------------------------------------------------------------------------------

\fullline

Report generation information:

 *  Created by Anton Olsson Collentine.

 *  Report creation time: on jun 27 2018 11:39:37

 *  Based on the R-package dataMaid v1.1.2 [Pkg: 2018-05-03 from CRAN (R 3.4.4)]

 *  R version 3.4.3 (2017-11-30).

### 2018-06-27 code/codebook_collated_summary_data.r

@@ -1,0 +1,43 @@
+#************************************************
+
+##Project: MA heterogeneity project
+##Script purpose: This script creates a nice-looking pdf codebook
+##Code: Anton Ohlsson Collentine
+
+#************************************************
+#Packages and data----
+#************************************************
+if(!require(readr)){install.packages("readr")}
+if(!require(dataMaid)){install.packages("dataMaid")}
+
+library(readr) #load data
+library(dataMaid) #create rmd-file that then creates pdf-codebook
+
+dat <- read_csv("../data/collated_summary_data.csv")
+#************************************************
+#Set variable descriptions and make codebook----
+#************************************************
+
+attr(dat$rp, "shortDescription") <- "Replication Project"
+attr(dat$effect, "shortDescription") <- "Studied effect"
+attr(dat$Site, "shortDescription") <- "Lab-identifier within each replication project"
+attr(dat$country, "shortDescription") <- "Country of participants {ISO Alpha-3 code}"
+attr(dat$in_lab, "shortDescription") <- "Whether study took place in-lab {1} or not {0} (0 = online)"
+attr(dat$Ntotal, "shortDescription") <- "Total study sample size"
+attr(dat$B_or_W, "shortDescription") <- "Between or within groups study"
+attr(dat$design, "shortDescription") <- "Description of design of research"
+attr(dat$or_stat_test, "shortDescription") <- "Statistical test used, if any"
+attr(dat$effect_type, "shortDescription") <- "Reported effect type {d, r, Risk difference, Raw mean difference}"
+attr(dat$effect_size, "shortDescription") <- "Size of reported effect"
+attr(dat$ncontrol, "shortDescription") <- "Sample size control group"
+attr(dat$ntreatment, "shortDescription") <- "Sample size treatment group"
+attr(dat$outcomes1_2, "shortDescription") <- paste0("Describes content in outcome_1 and outcome_2. For chi-square effects",
+                                                     "(group1, group2) indicates 'treatment' and 'control' groups")
+attr(dat$outcome_c1, "shortDescription") <- "Control group outcome 1"
+attr(dat$outcome_t1, "shortDescription") <- "Treatment group outcome 1"
+attr(dat$outcome_c2, "shortDescription") <- "Control group outcome 2"
+attr(dat$outcome_t2, "shortDescription") <- "Treatment group outcome 2"
+
+makeCodebook(dat, file = "codebook_collated_summary_data.rmd")
+#some changes then made in the resulting .rmd file to create final pdf codebook
+

### 2018-06-27 code/figures.rmd
Cleaned up figures for publication

@@
   geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
-  theme_classic()
+  theme_classic() +
+  scale_y_continuous(name = expression(paste(I^2," index", sep = ""))) +
+  scale_x_continuous(name = "Effect size (Fisher's z)")
 
@@
   geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
-  theme_classic()
+  theme_classic() +
+  scale_y_continuous(name = expression(paste(H^2," index", sep = ""))) +
+  scale_x_continuous(name = "Effect size (Fisher's z)")
 
@@
 effect_het
-# save_plot("../figures/effect_het.png", effect_het,
-          # nrow = 2, base_aspect_ratio = 1.3)
+# save_plot("../figures/effect-het.png", effect_het,
+          # nrow = 2, base_aspect_ratio = 1.3, dpi = 600)
 
@@
 
+OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales') #effects that were transformed from OR to SMD
+
+#Categorize effects by type of simulation for graphing
+effect_type <- distinct(select(dat, effect, effect_type)) %>% 
+  mutate(effect_type = ifelse(effect %in% OR2d | effect_type == "Risk difference" | 
+                                effect_type == "Raw mean difference", "MD", effect_type),
+         effect_type = recode(effect_type, "d" = 'SMD',
+                              "r" = "Fisher's z"))
+
 dat3 <- dat3 %>% 
   bind_rows(.id = "effect") %>% #create dataframe with identifier
-  select(I2, tau, effect) %>% 
-  group_by(tau, effect) %>% 
+  left_join(., effect_type) %>% 
+  select(I2, tau, effect, effect_type) %>% 
+  group_by(tau, effect, effect_type) %>% 
   summarize(I2 = mean(I2)) %>% #Take mean of I2 at each tau-level and for each effect
@@
 #combined line plot gives good overview. Point version of the same is also interesting.
-ggplot(dat3, aes(x = tau, y = I2, group = effect)) +
-  geom_line(alpha = 0.4) +
+ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
+  geom_line(alpha = 0.6) +
   theme_bw() +
-  scale_x_continuous(minor_breaks = NULL) +
-  scale_y_continuous(minor_breaks = NULL) +
-  coord_cartesian(ylim = c(0, 100))
+  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
+                     minor_breaks = NULL) +
+  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
+                     minor_breaks = NULL) +
+  coord_cartesian(ylim = c(0, 100)) +
+  scale_color_brewer(name = "Effect type", palette = "Dark2", 
+                     breaks = c("Fisher's z", "MD", "SMD")) +
+  theme(legend.position = c(0.8, 0.4),
+        legend.background = element_rect(linetype = "solid", color = "black"))
 
-# ggsave("../figures/tau-I2.png")
+# ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)
 
@@
   coord_cartesian(xlim = c(0, 100))  +
-  scale_fill_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
-  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"), breaks = c("Zero", "Small", "Medium", "Large", "Observed")) +
-  scale_color_brewer(palette = "Dark2", breaks = c("Zero", "Small", "Medium", "Large", "Observed"))
+  scale_fill_brewer(palette = "Dark2",
+                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
+                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
+                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+  scale_color_brewer(palette = "Dark2", 
+                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+  theme(legend.position = c(0.85, 0.71),
+        legend.background = element_rect(linetype = "solid", color = "black")) +
+  scale_y_continuous(name = "Density") +
+  scale_x_continuous(name = expression(paste(I^2," index", sep = "")))
 
-# ggsave("../figures/density-I2.png")
+# ggsave("../figures/density-I2.png", dpi = 600, height =  4 , width = 6.47)
 ```

### 2018-06-27 code/codebook_collated_summary_data.r
Made project description consistent in .r-files

@@ -1,6 +1,6 @@
 #************************************************
 
-##Project: MA heterogeneity project
+##Project: Limited evidence for widespread heterogeneity in psychology
 ##Script purpose: This script creates a nice-looking pdf codebook
 ##Code: Anton Ohlsson Collentine
 

### 2018-06-27 code/collate_summary_data.r

@@ -1,6 +1,6 @@
 #*************************************************************************************************************************
 
-##Project: MA heterogeneity project
+##Project: Limited evidence for widespread heterogeneity in psychology
 ##Script purpose: This script extracts, cleans and formats summary data from Many labs 1 & 3 and Registered Replication Reports 1 - 8 
 ##Code: Anton Ohlsson Collentine
 

### 2018-06-27 code/helper_functions_tables_figures.r

@@ -1,6 +1,6 @@
 #******************************************
 
-#Project: Heterogeneity in direct replications
+#Project: Limited evidence for widespread heterogeneity in psychology
 #Script purpose: Helper functions to prep data for tables and figures
 #Code: Anton Ohlsson Collentine
 #Additional comments: These functions are intended to be 'sourced' into the 

### 2018-06-27 code/power_simulation.r

@@ -1,6 +1,6 @@
 #******************************************
 
-#Project: Heterogeneity in direct replications
+#Project: Limited evidence for widespread heterogeneity in psychology
 #Script purpose: Simulate I2 distribution for different levels of heterogeneity given data weights
 #Code: Anton Ohlsson Collentine
 

### 2018-06-27 writing/draft-heterogeneity.rmd
Added bibliography and links to OSF

@@
 ---
-title: "Limited evidence for widespread heterogeneity in psychology"
-author: "Anton Ohlsson Collentine"
-header-includes:
-   - \setlength\parindent{24pt}
-   - \usepackage{setspace}
-   - \doublespacing
-output: word_document
+title             : "Limited evidence for widespread heterogeneity in psychology"
+shorttitle        : "Limited evidence for heterogeneity"
+
+author: 
+  - name          : "Anton Ohlsson Collentine"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Warandelaan 2, 5037 AB Tilburg"
+    email         : "j.a.e.olssoncollentine@tilburguniversity.edu"
+  - name          : "Jelte Wicherts"
+    affiliation   : "1"
+    corresponding : no    # Define only one corresponding author
+  - name          : "Marcel van Assen"
+    affiliation   : "1,2"
+    corresponding : no    # Define only one corresponding author
+
+affiliation:
+  - id            : "1"
+    institution   : "Tilburg University"
+  - id            : "2"
+    institution   : "Utrecht University"
+
+abstract: |
+  Abstract to be written.
+
+keywords          : "heterogeneity, meta-analysis, replication, psychology, many labs, registered replication reports"
+wordcount         : "3"
+
+bibliography      : ../bibliography/bibliography-heterogeneity.bib
+
+figsintext        : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+lineno            : no
+
+lang              : "english"
+class             : "man"
+output            : papaja::apa6_word
 ---
@@
 if(!require(kableExtra)){install.packages("kableExtra")}
+if(!require(papaja)){install.packages("papaja")}
 
@@
 library(kableExtra) #For creating good-looking pdf tables
+library("papaja") #APA formatting of .rmd -> word
 
@@
 In the first stage, inferential statistics are used  to minimize the risk that a discovery is due to sampling error.
-In the second stage, one may ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [ref: Campbell & Stanley].
+In the second stage, one may ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [@Campbell2015].
 This extent is often explored through replications of the original study that are either as similar as possible to the original (called 'direct' or 'exact' replications) or with some deliberate variation on conceptual factors (so-called 'conceptual' or 'indirect' replications) [ref: Zwaan et al], and once sufficient studies have accumulated through meta-analysis.
@@
 Second, unaccounted for heterogeneity is an indication of incomplete theory, since it suggests that a theory is unable to predict all contextual factors of importance to its claims.
-As such, heterogeneity might imply previously unknown predictors, so called 'hidden moderators' [ref: van Bavel], the discovery of which can be seen as an opportunity for theoretical advancement [ref: Tacket et al].
-The corollary is that, unless a theory has predefined additional assumptions ('auxiliary assumptions' [ref: Earp & Trafimow]) which were not fulfilled in the replications, an absence of heterogeneity should generally preclude referral to hidden moderators.
+As such, heterogeneity might imply previously unknown predictors, so called 'hidden moderators' [@10.2139/ssrn.2820883], the discovery of which can be seen as an opportunity for theoretical advancement [@Tackett2017].
+The corollary is that, unless a theory has predefined additional assumptions ('auxiliary assumptions'; @10.3389/fpsyg.2015.00621) which were not fulfilled in the replications, an absence of heterogeneity should generally preclude referral to hidden moderators.
 
 Third,  the possibility of heterogeneity can create controversy in the interpretation of single replication results.
-The proclamation of a  'failure' to replicate an effect often seems to imply that the original find was merely a statistical fluke, due to 'p-hacking' [Ref: Simmons et al] or publication bias [ref..
-Inzlicht?].
-Unsurprisingly, some researchers take offense [e.g., ref: Baumeister].
-An alternative explanation for non-replication, often espoused by the original authors [e.g, IJzerman; Strack], is that the effect is more heterogenous than (perhaps implicitly) claimed originally.
+The proclamation of a  'failure' to replicate an effect often seems to imply that the original find was merely a statistical fluke, due to 'p-hacking' [@10.1177/0956797611417632] or publication bias [@10.2139/ssrn.2659409].
+Unsurprisingly, some researchers take offense [e.g., @10.1016/j.jesp.2016.02.003].
+An alternative explanation for non-replication, often espoused by the original authors [e.g, @10.2139/ssrn.2698810; @10.1177/1745691616674460], is that the effect is more heterogenous than (perhaps implicitly) claimed originally.
 Such explanations may be valid or not, but even if valid, an effect is typically of less general interest the more specific circumstances it requires to appear.
-A way for original authors to align researchers' expectations of heterogeneity is to preemptively specify their own, that is, the degree of heterogeneity that would make they themselves lose interest in an effect (e.g., by declaring 'constraints on generality' [ref Simons et al].
+A way for original authors to align researchers' expectations of heterogeneity is to preemptively specify their own, that is, the degree of heterogeneity that would make they themselves lose interest in an effect (e.g., by declaring 'constraints on generality' [@10.1177/1745691617708630].
 
 Fourth, meta-analytic techniques are affected by heterogeneity.
-Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [refs: Inzlicht; McShane], which is problematic considering widespread publication bias [refs] and its impact on meta-analytic estimates.
-In addition, heterogeneity alters the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity), though one may question the usefulness of interpreting the average true effect size in the presence of heterogeneity [ref: blog Simonsohn], just as it may be questionable to interpret an average main effect in the context of an interaction effect [ref Aiken and West 1993].
+Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [@@10.2139/ssrn.2659409; @10.1177/1745691616662243], which is problematic considering widespread publication bias [refs] and its impact on meta-analytic estimates.
+In addition, heterogeneity alters the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity), though one may question the usefulness of interpreting the average true effect size in the presence of heterogeneity [@Simonsohn2017], just as it may be questionable to interpret an average main effect in the context of an interaction effect [@Aiken1991].
 
 It is a commonly believed that heterogeneity is the norm in psychology.
-In support of this notion, recent large scale reviews of meta-analyses in psychology [ref: Stanley; van Erp et al] report median heterogeneity levels that can best be described as 'large' (see next paragraph).
-In comparison, the median heterogeneity estimate in medicine would be considered 'small' by the same standard [ref: Ioannidis  "uncertainty in heterogeneity"].
+In support of this notion, recent large scale reviews of meta-analyses in psychology [@Stanley2017; @10.5334/jopd.33a] report median heterogeneity levels that can best be described as 'large' (see next paragraph).
+In comparison, the median heterogeneity estimate in medicine would be considered 'small' by the same standard [@10.1136/bmj.39343.408449.80].
 It may simply be that effects in psychology are more heterogenous than those of medicine.
 However, meta-analyses in psychology also typically include more studies than those in medicine, and it could be that they tend to include studies from a much broader spectrum than meta-analyses in medicine.
-The median number of studies (effects) per meta-analysis in the psychology sample of [van Erp et al] was 12, whereas in the medicine sample of  [Ioannidis; uncertainty in heterogeneity] the median number of studies was only 7, despite exclusion of all meta-analyses of 3 or fewer studies.
+The median number of studies (effects) per meta-analysis in the psychology sample of @10.5334/jopd.33a was 12, whereas in the medicine sample of  @10.1136/bmj.39343.408449.80 the median number of studies was only 7, despite exclusion of all meta-analyses of 3 or fewer studies.
 It is difficult to separate these explanations.
 To facilitate doing so, in this paper we focus on meta-analyses of only direct replications, which are exempt from the potential problem of including too disparate studies.
-In reference to meta-analyses of direct replications, several authors [ref: McShane et al; Tacket et al] have argued that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol, and that heterogeneity has been reported even under such circumstances [e.g., ref: Many Labs 1] is an indication of widespread heterogeneity in psychology.
+In reference to meta-analyses of direct replications, several authors [@10.1177/1745691616662243; @Tackett2017] have argued that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol, and that heterogeneity has been reported even under such circumstances [e.g., @10.1027/1864-9335/a000178 is an indication of widespread heterogeneity in psychology.
 However, even in the case of multi-lab direct replication projects, studies vary on two contextual factors (sample population and settings) and if we believe an effect is sensitive to changes in these two factors we might still expect to find some heterogeneity
@@
 One problem lies in the assessment of heterogeneity and its inherent uncertainty.
-Heterogeneity is often measured by the I2 index [ref: Higgins & Higgins], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
+Heterogeneity is often measured by the $I^2$ index [@10.1002/sim.1186;  @10.1136/bmj.327.7414.557], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
 It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects (that is, sensitivity to contextual factors) rather than sampling variance, and ranges from 0-100%.
-The I2 index is a transformation of the well-known Q-test of heterogeneity in meta-analysis [ref: Cochran] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative I2 is set to zero.
-[Higgins et al] tentatively defined I2-values of 25, 50, and 75% as small/medium/large heterogeneity respectively.
-Tests of heterogeneity typically have low statistical power in many practical situations [ref: Jackson; Huedo-Medina].
-This complicates the discussion of heterogeneity, because while I2 always provides an estimate of heterogeneity, this estimate is often surrounded by wide confidence intervals [ref: Ioannidis  "uncertainty in heterogeneity"].
-For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with I2 point estimates of 0% had upper 95% confidence intervals that exceeded 33%, exceeding what [Higgins] defined as 'small' heterogeneity.
-In addition, under homogeneity I2 has a central chisquare distribution [ref: von Hippel], a distribution that is right-skewed with more than 40% of observations falling above the expected value (for all k > 4).
-In other words, even in the absence of heterogeneity, a meta-analysis of 5 or more studies will have an I2 point estimate above zero in more than 40% of cases.
+The $I^2$ index is a transformation of the well-known Q-test of heterogeneity in meta-analysis [@10.2307/3001666] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative $I^2$ is set to zero.
+@10.1136/bmj.327.7414.557 tentatively defined $I^2$-values of 25, 50, and 75% as small/medium/large heterogeneity respectively.
+Tests of heterogeneity typically have low statistical power in many practical situations [@10.1002/sim.2481; @10.1037/1082-989X.11.2.193].
+This complicates the discussion of heterogeneity, because while $I^2$ always provides an estimate of heterogeneity, this estimate is often surrounded by wide confidence intervals [@10.1136/bmj.39343.408449.80"].
+For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with $I^2$ point estimates of 0% had upper 95% confidence intervals that exceeded 33%, exceeding what @10.1136/bmj.327.7414.557 defined as 'small' heterogeneity.
+In addition, under homogeneity $I^2$ has a central chisquare distribution [@10.1186/s12874-015-0024-z], a distribution that is right-skewed with more than 40% of observations falling above the expected value (for all k > 4).
+In other words, even in the absence of heterogeneity, a meta-analysis of 5 or more studies will have an $I^2$ point estimate above zero in more than 40% of cases.
 Heterogeneity estimates may thus be congruent with a wide range of true heterogeneity levels.
-Despite exhortations to the contrary [ref: Ioannidis "uncertainty in heterogeneity"] , it remains common to omit confidence intervals in the reporting of I2.
+Despite exhortations to the contrary [@10.1136/bmj.39343.408449.80], it remains common to omit confidence intervals in the reporting of $I^2$.
 In consideration of such uncertainty and the prevalent belief that heterogeneity is the norm in psychology, we examine the existing evidence for heterogeneity in psychology using a sample of pre-registered multi-lab direct replication projects.
@@
 Intuitively, it makes sense to believe that if there is no meta-analytic effect there is nothing to moderate (i.e., no heterogeneity).
-However, a null or near null effect size estimate may arise from failure to consider contextual factors ('hidden moderators', [ref: van Bavel]) and does not by itself imply the absence of heterogeneity.
+However, a null or near null effect size estimate may arise from failure to consider contextual factors ('hidden moderators'; @10.2139/ssrn.2820883) and does not by itself imply the absence of heterogeneity.
 A large meta-analytic effect size on the other hand, can be expected to be associated with more heterogeneity.
@@
 
-We examine the evidence for widespread heterogeneity in psychology and explore the correlation between effect size and heterogeneity, using 10 pre-registered multi-lab replication projects in psychology (Table 2).
-These 10 projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
-To better interpret heterogeneity estimates we also estimate power of each project to find zero/small/medium/large heterogeneity as defined by [Higgins et al].
+We examine the evidence for widespread heterogeneity in psychology and explore the correlation between effect size and heterogeneity, using ten pre-registered multi-lab replication projects in psychology (Table 2).
+These ten projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
+To better interpret heterogeneity estimates we also estimate power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557.
 Of the four contextual factors a study might vary on (sample population, settings,  treatment variables, and measurement variables) the studies in these projects vary only on two: sample population and settings.
 Nonetheless, if we believe an effect is sensitive to changes in these two factors we may still expect to find some heterogeneity.
-For example, the variety of countries and samples involved in some of the replication projects, not all of which are WEIRD (Western, Educated, Industrial, Rich, Democratic [ref: Weird]) might be a reason to expect heterogeneity.
+For example, the variety of countries and samples involved in some of the replication projects, not all of which are WEIRD (Western, Educated, Industrial, Rich, Democratic [@10.1017/S0140525X0999152X]) might be a reason to expect heterogeneity.
 On the other hand, it may be that the less disparate collection of studies included in these direct replication meta-analyses as compared to most psychological meta-analyses result in low heterogeneity estimates, similar to estimates in medicine.
@@
 
+```{r data-summary-table}
+#library(dplyr)
+#library(kableExtra)
+
+#Shortened version of APA reference
+papers <- c('Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams, R.
+B., Jr., Bahník, S., Bernstein, M.
+J., .
+.
+.
+Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A "many labs" replication project.',
+'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
+'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
+'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
+'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011).',
+'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
+'Cheung, I., Campbell, L., LeBel, E.
+P., Ackerman, R.
+A., Aykutoglu, B., Bahník, S., ...
+& Carcedo, R.
+J.
+(2016).
+Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).',
+'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
+'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
+"O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")
+
+##Full APA reference below
+# c('Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams, R.
+B., Jr., Bahník, S., Bernstein, M.
+J., .
+.
+.
+Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A "many labs" replication project.
+Social Psychology, 45(3), 142-152.',
+# 'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.
+Journal of Experimental Social Psychology, 67, 68-82.',
+# 'Ebersole, C.
+R., Atherton, O.
+E., Belanger, A.
+L., Skulborstad, H.
+M., Allen, J.
+M., Banks, J.
+B., ...
+& Brown, E.
+R.
+(2016).
+Many Labs 3: Evaluating participant pool quality across the academic semester via replication.
+Journal of Experimental Social Psychology, 67, 68-82.',
+# 'Alogna, V.
+K., Attaya, M.
+K., Aucoin, P., Bahník, S., Birch, S., Birt, A.
+R., ...
+& Buswell, K.
+(2014).
+Registered replication report: Schooler and engstler-schooler (1990).
+Perspectives on Psychological Science, 9(5), 556-578.',
+# 'Eerland, A., Sherrill, A.
+M., Magliano, J.
+P., Zwaan, R.
+A., Arnal, J.
+D., Aucoin, P., ...
+& Crocker, C.
+(2016).
+Registered replication report: Hart & Albarracín (2011).
+Perspectives on Psychological Science, 11(1), 158-171.',
+# 'Hagger, M.
+S., Chatzisarantis, N.
+L., Alberts, H., Anggono, C.
+O., Batailler, C., Birt, A.
+R., ...
+& Calvillo, D.
+P.
+(2016).
+A multilab preregistered replication of the ego-depletion effect.
+Perspectives on Psychological Science, 11(4), 546-573.',
+# 'Cheung, I., Campbell, L., LeBel, E.
+P., Ackerman, R.
+A., Aykutoglu, B., Bahník, S., ...
+& Carcedo, R.
+J.
+(2016).
+Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).
+Perspectives on Psychological Science, 11(5), 750-764.',
+# 'Wagenmakers, E.
+J., Beek, T., Dijkhoff, L., Gronau, Q.
+F., Acosta, A., Adams Jr, R.
+B., ...
+& Bulnes, L.
+C.
+(2016).
+Registered Replication Report: Strack, Martin, & Stepper (1988).
+Perspectives on Psychological Science, 11(6), 917-928.',
+# 'Bouwmeester, S., Verkoeijen, P.
+P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ...
+& Evans, A.
+M.
+(2017).
+Registered Replication Report: Rand, Greene, and Nowak (2012).
+Perspectives on Psychological Science, 12(3), 527-542.',
+# "O'Donnell, M., Nelson, L., McLatchie, N.
+M., & Lynott, D.
+J.
+(2017).
+Registered Replication Report: Dijksterhuis & van Knippenberg (1998): Multilab direct replication of: A variant of study 4 from Dijksterhuis, A., & van Knippenberg, A.(1998).
+The relation between perception and behavior, or how to win a game of trivial pursuit.
+Journal of personality and social psychology.
+Perspectives on Psychological Science."
+
+summary.table <- dat %>% 
+  group_by(rp) %>% 
+  summarize(k = n_distinct(Site),
+            Countries = n_distinct(country), 
+            Effects = n_distinct(effect),
+            Participants = if(Effects == 1){sum(Ntotal)}
+                           else{sum(Ntotal) / Effects}) %>% #average across effects
+  mutate(Paper = papers) %>% 
+  select(RP = rp, Paper, everything()) #change order of columns
+
+summary.table %>% knitr::kable(digits = 0)
+```
+
+**Note.** For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
+Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
+RP = Replication Project, k = no.
+primary studies, ML = Many Labs, RRR = Registered Replication Report.
+(osf.io/kf6pt/)
+
 ##Method
 
-All code and data for this project are available on the Open Science Framework (OSF) at osf.io/XXXX.
+All code and data for this project are available on the Open Science Framework (OSF) at osf.io/4z3e7/.
 We refer to relevant files on OSF using brackets and links in the sections below, that is (osf.io/XXXX/).
-We ran all analyses using R version X [ref: R citation].
+We ran all analyses using R version 3.4.3 [@RCoreTeam2017].
 
@@
 RRR4) reported results from several outcome variables, we only included primary outcome variables as stated in accompanying publications, resulting in a total of 37 effects.
-For each effect we extracted (osf.io/XXXX/) summary data (e.g., means and standard deviations) at the level of the lab as specified by the original authors for their primary analysis (i.e., typically after exclusions).
-We extracted information on the country of each lab, whether participants were physically in the lab for the study, total number of participants per lab, type of effect size, and additional information related to each effect (see codebook; osf.io/XXXX/).
+For each effect we extracted (osf.io/3bmvc/) summary data (e.g., means and standard deviations) at the level of the lab as specified by the original authors for their primary analysis (i.e., typically after exclusions).
+We extracted information on the country of each lab, whether participants were physically in the lab for the study, total number of participants per lab, type of effect size, and additional information related to each effect (see codebook; osf.io/uhq4r/).
 Extracted data were in a variety of formats: Excel (Many labs 1, RRR1 & RRR2), CSV (Many labs 3, RRR3, RRR4, RRR5, RRR6) and as PDF tables (RRR7, RRR8).
@@
 Even so, we kept the original lab indicators to facilitate comparing observations in our dataset with the original datasets.
-Finally, we collated the summary data for all effects into one dataset for analysis (osf.io/XXXX/).
+Finally, we collated the summary data for all effects into one dataset for analysis (osf.io/456fz/).
 
-To examine heterogeneity across effects, we computed meta-analytic estimates for all 37 effects in our dataset (Table 3).
-We ran all analyses as specified by the replication authors (osf.io/XXXX/).
-All effects were estimated with random-effects models and the Restricted Maximum Likelihood (REML) estimator using the R-package metafor [ref], though with a variety of outcome variables: correlations, standardized mean differences, raw mean differences, odds ratios and risk differences.
-ML1 transformed odd ratios into standardized mean differences when meta-analyzing under the assumption that responses followed logistic distributions [ref: Sanchez-Meca; metafor].
-Two projects (RRR5 and RRR7) used the Knapp and Hartung adjustment of the standard errors [ref: Knapp & Hartung] and ML3 correlations were corrected for bias [ref: Hedges 1989; metafor].
+To examine heterogeneity of each of the 37 effects, we computed meta-analytic estimates for all 37 effects in our dataset (Table 3).
+We ran all analyses as specified by the replication authors (osf.io/kf6pt/).
+All effects were estimated with random-effects models and the Restricted Maximum Likelihood (REML) estimator using the R-package metafor [@10.18637/jss.v036.i03], though with a variety of outcome variables: correlations, standardized mean differences, raw mean differences, odds ratios and risk differences.
+ML1 transformed odd ratios into standardized mean differences when meta-analyzing under the assumption that responses followed logistic distributions [@10.1037/1082-989x.8.4.448; @10.18637/jss.v036.i03].
+Two projects (RRR5 and RRR7) used the Knapp and Hartung adjustment of the standard errors [@10.1002/sim.1482] and ML3 correlations were corrected for bias [@10.1037//0021-9010.74.3.469; @10.18637/jss.v036.i03].
 After estimating effects, ML3 transformed correlations into eta-squared for reporting, which we did not.
 For each effect we estimated $I^2$ and its 95% confidence interval.
-Confidence intervals were calculated in metafor which uses the Q-profile method [ref Jackson 2014].
+Confidence intervals were calculated in metafor which uses the Q-profile method [@10.1186/1471-2288-14-103].
 
-In order to facilitate interpretation of our results, we estimated power and type 1 error for each of the 37 effects under zero/small/medium/large heterogeneity ($I^2$ = 0/25/50/75%  respectively).
-In addition, we plotted $I^2$-distributions across effects at these heterogeneity levels and compared with all observed $I^2$ estimates.
-To do so we simulated results for each effect given the number of studies, k, and the sample sizes, $N_k$, of those studies (osf.io/XXXX/).
-In the case of correlations we 1) generated a true correlation $\rho_k$ from a normal distribution with  between studies standard deviation $\tau$ and mean effect size zero, $\rho_k \sim N(0,  \tau)$, and 2) generated an observed correlation expressed as Fisher's z $rz_k$ from a normal distribution with mean $\rho_k$ and standard deviation $\sqrt{1 / N_k - 3}$, $rz_k \sim N(\rho_k, \sqrt{1 / N_k - 3})$.
-For mean differences we assumed equal within study group sizes $n_c = n_t$ ($= N_k$ rounded to closest integer) and standard deviation $\sigma_c = \sigma_t$.
-We then 1) generated study effect sizes $\mu_k$ from a normal distribution with mean zero and standard deviation $\tau$, $\mu_k \sim N(0, \tau)$, and 2) generated control and treatment means from the sampling distributions $\bar{x}_c \sim N(0, 1 / \sqrt{n_c})$ and $\bar{x}_t \sim N(\mu_k, 1 / \sqrt{n_t})$ respectively.
-Group variances were generated from their sampling distributions as well, in accordance with $s^2_c = \chi^2 (n_c - 1) / (n_c - 1)$ and  $s^2_t = \chi^2 (n_t - 1) / (n_t - 1)$.
-Due to the difficulties of data generation for odds ratios and risk differences we treated these as mean differences.
-For each effect, our simulations then proceeded in three steps: i) we varied the between studies standard deviation, $\tau$, between 0.000 and 0.50 in increments of 0.005 and replicated each condition 1000 times, each time estimating $I^2$ with a random effects model with REML, ii) we computed the average $I^2$ in each condition, discarding non-converged models, and iii) ran 10 000 replications at the $\tau$ values in step _ii_ that best corresponded to an $I^2$ estimate of 25% (small), 50% (medium) and 75% (large).
-For homogeneity we set $\tau$ to zero.
-We considered a result significant when the lower bound of the 95% $I^2$ confidence interval was above zero.
+In order to facilitate interpretation of our results, we estimated type I error and power of the Q-test of heterogeneity for each of the 37 effects under zero/small/medium/large heterogeneity ($I^2$ = 0/25/50/75%  respectively).
+In addition, we plotted $I^2$-distributions across effects at these four heterogeneity levels and compared them with the distribution of the observed $I^2$ estimates of the 37 effects.
+To do so we simulated results for each effect given the number of studies, k, and the sample sizes, $N_k$, of those studies (osf.io/gbf4u/).
+We simulated the distribution of $I^2$ for correlation, standardized mean difference, and mean difference effect size measures.
+Because the standard error of the observed effect size in case of odds ratios and risk differences is strongly affected by assumptions of the probability of success in both treatment groups, we did not directly simulate the I^2 distribution for these effect size measures.
+In these cases, we used the information on study sample sizes and treated the effects as mean differences in our simulations.
 
-To examine the correlation between effect size and $I^2$ we converted all effect sizes to a common metric (osf.io/XXXX/).
-We first converted all effects into correlations (r) and used the R-package metafor [ref] to estimate $I^2$ and meta-analytic effects expressed as Fisher's z.
+As our concern was of heterogeneity, for convenience we set the true effect size to zero in our simulations.
+This does not affect the results for correlations or mean differences as estimates of effect size and heterogeneity for these measures are statistically independent, and was expected to have negligible effect on the results for standardized mean differences because while these estimates of effect size are positively correlated to their standard errors, the within study variance $\sigma^2$ was kept constant across studies.
+[Marcel/Jelte: Not sure this paragraph is correct, because my grasp of the mathematics is a bit tenuous].
+Nonetheless, as a sensitivity test we also ran the analysis with 'medium' effect sizes [@Cohen1988], see Appendix A (osf.io/XXXX/) [appendix not created yet, hence no link].
+
+In case the observed effect was a correlation, one run of a simulation proceeded as follows.
+First, we randomly sampled K Fisher-transformed true correlations $\rho_k$ from a normal distribution with mean 0 and heterogeneity (variance) $\tau^2$.
+Fisher's z-transformation is a normalizing correlation transformation that ranges from negative infinity to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [@10.2307/2331838; Fisher1921].
+Second, for each of the K true Fisher-transformed correlations we sampled one Fisher-transformed observed correlation from a normal distribution with mean $\rho_k$ and variance $1 ???
+(N_k - 3)$.
+Finally, we fitted a random-effects meta-analysis with REML and estimated $I^2$ for that run.
+In the simulations, we varied the between-studies standard deviation $\tau$ between 0.000 and 0.50 in increments of 0.005, and used 1,000 runs at each step to approximate the distribution of $I^2$ at that value for true heterogeneity.
+
+For mean differences we assumed a within-study variance of one for both treatment and control groups, $\sigma^2_c = \sigma^2_t = 1$.
+For each run we then set the population mean of the control condition to 0 and sampled K treatment population means $\mu_k$ from $N(0, \tau)$.
+Subsequently, K sample means for both control and treatment conditions were sampled, with $\bar{x}_c \sim N(0, 1 / \sqrt{n_c})$ and $\bar{x}_t \sim N(\mu_k, 1 / \sqrt{n_t})$, where $n_t$ and $n_c$ were the observed treatment and control sample sizes for each study.
+Group variances were sampled using $s^2_c \sim \chi^2 (n_c - 1) / (n_c - 1)$ and  $s^2_t \sim \chi^2 (n_t - 1) / (n_t - 1)$.
+Finally, we fitted a random-effects meta-analysis with REML and estimated $I^2$ for that run.
+For standardized mean differences we proceeded identically, except that we in the final step asked metafor to transform the effect size into a standardized mean difference in fitting the random-effects model.
+As with correlations, the distribution of $I^2$ was approximated for values of $\tau$ from 0 to .5 in steps of .005, using 1,000 runs at each step.
+
+To approximate the statistical power of all 37 effects at zero, small, medium, and true effect size we continued as follows.
+For each of the 37 effects we selected the values of $\tau$ which yielded the average value of I^2 in the simulations closest to .25 (small), .50 (medium), and .75 (large).
+For these values of $\tau$ and for $\tau = 0$ (homogeneity) we again ran 10,000 simulations, and for each run $I^2$ was calculated and the Q-test of heterogeneity was performed, yielding estimates of type I error (in case of homogeneity) and power (for heterogeneity) for each of the 37 effects.
+We considered a result significant when _p_ $\leq 0.05$ for the Q-test.
+The distributions of $I^2$ for zero, small, medium, large heterogeneity, which we compared to the observed distribution of 37 effect sizes, was generated by pooling the 37 distributions of 10,000 $I^2$ values in each category of heterogeneity.
+Hence these $I^2$ distributions can be considered a mixture distribution of 37 distributions, using equal weights across all 37 effects.
+
+To examine the correlation between effect size and $I^2$ across all 37 effects we converted all effect sizes to a common metric (osf.io/h9pft/).
+We first converted all effects into correlations (r) and used the R-package metafor to estimate $I^2$ and meta-analytic effects expressed as Fisher-transformed correlations (osf.io/zuwpg/).
 In doing so, we fitted random-effects models with metafor's default REML estimator.
-Fisher's z is a normalizing correlation transformation that ranges from negative infinity to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [ref].
-For mean differences we calculated the pooled standard deviation, [ref Borenstein in Cooper & Hedges, 2009, p.
-226), standardized the effect size and converted it to a correlation (p.
+For mean differences we calculated the pooled standard deviation, [@Borenstein2009, p.
+226], standardized the effect size and converted it to a correlation (p.
 234) with a correction factor for unequal sample sizes (p.
@@
 232) and then finally to a correlation.
-All formulas used are presented in Appendix A (osf.io/XXXX/).
-Since $I^2$ is set to zero for the majority of cases under homogeneity (i.e., truncated), we also correlated effect size with with the closely related heterogeneity estimate H2 [ref: Higgins 2002] as a sensitivity analysis.
+All formulas used are presented in Appendix B (osf.io/XXXX/) [appendix not created yet, hence no link].
+Since $I^2$ is set to zero for the majority of cases under homogeneity (i.e., truncated), we also correlated effect size with the closely related heterogeneity estimate $H^2$ [@10.1002/sim.1186] as a sensitivity analysis.
 The H2 index is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - $I^2$)$ for $I^2 \geq 0$.
@@
 
-Table 3 presents the meta-analytic estimates and $I^2$ with confidence intervals for each of the 37 included effects.
+Table 3 presents the meta-analytic effect size estimates and $I^2$ with confidence intervals for each of the 37 included effects, as well as simulated type I error and statistical power for zero, small, medium, and large true heterogeneity.
 
 ```{r prep-heterogeneity-table}
-# library(metafor)
-# library(dplyr)
-# library(purrr)
+#library(metafor)
+#library(dplyr)
+#library(purrr)
 
@@
 #Load simulation results (power/type 1 error for all effects)
-dens <- readRDS("../code/temp_sim_results_2.RDS")
+dens <- readRDS("../data/power_simulation_results.RDS")
 names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
@@
   left_join(I2_ci_lb) %>% 
-  select(rs, effect,k , everything()) %>% 
+  select(rp, effect,k , everything()) %>% 
   arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
@@
 
-het %>% knitr::kable(digits = 2, col.names = c("RS", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) 
+het %>% knitr::kable(digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) 
 ```
@@
 Under simulated heterogeneity, Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\%) respectively.
-(OSF.io/XXXX)"
+(osf.io/kf6pt/)
+
+^a^ Odds ratio or risk difference simulated as mean difference
 
@@
 
-There is limited evidence for heterogeneity across the examined effects.
+There is limited evidence for widespread heterogeneity across the examined effects.
 Of the 37 effects,  4/37 (11%) have $I^2$ estimates that best correspond to large heterogeneity ($I^2$ = 75%), 4/37 (11%) to medium heterogeneity ($I^2$ = 50%), 9/37 (24%)  to small heterogeneity ($I^2$ = 25%) and 17/37 (54%) to zero heterogeneity ($I^2$ = 0%).
-However, despite relatively large k and total sample size for most projects (see Table 2), Table 3 shows wide confidence intervals for many effects: 10/37 (27%) effects have confidence intervals congruent with small to large heterogeneity and 15/37 (41%) with zero to medium.
+However, despite a relatively large number of studies and total sample size for most projects (see Table 2), Table 3 shows very wide confidence intervals (spanning 50% or more) for many effects.
 The lower bound $I^2$ confidence interval excludes zero for only 7/37 effects (19%; Table 3), all part of the ML1 project.
@@
 
-We estimated $I^2$ for a large range of between studies standard deviations for each of the 37 effects (Figure 1).
-The $I^2$ index increases non-linearly with heterogeneity and is relatively more sensitive to lower between studies variances.
-This appears to be less so in the case of  mean differences than for correlations, which correspond to the more steeply inclined curves in Figure 1.
+Figure 1 shows how estimated $I^2$ varies across all 37 effects as a function of true heterogeneity (averaged across all simulation runs).
+Figure 1 makes clear that $I^2$ is particularly sensitive to changes in heterogeneity for small heterogeneity, and that estimates of $I^2$ may differ considerably across projects for the same value of true heterogeneity.
+This can largely be attributed to differences in number of included studies per project, but also partly to sample sizes between projects (with larger number of studies and sample sizes resulting in larger estimates of $I^2$).
+For example, the three bottom lines all belong to RRR3, the replication project with the lowest number of included studies (12; see Table 3).
+Since the between studies variance is not measured on the same scale when using different effect size measures, estimates are not directly comparable across effect size measures.
 
@@
 
-_Figure 1.
-Result of simulation relating $I^2$-values to between studies standard deviation.
-Each line represent one of 37 effects.
-The more steeply inclined lines belong to correlations and the others to mean differences._
+_Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 37 effects. Tau is not directly comparable across effect size measures._
 
-Power and type 1 error estimates for zero/small/medium/large heterogeneity are shown for each effect in Table 3.
-In all cases the type 1 error is conservative, as compared to the expected 5% error rate.
+Estimated type I error and power for zero/small/medium/large heterogeneity are shown for each effect in Table 3.
+In all cases the type I error is conservative, as compared to the expected 5% error rate.
 Power to detect small heterogeneity was low, ranging between 18% (Professor priming) and  45% (Flag priming), with an average of 28%.
@@
 Power to detect strong heterogeneity was excellent across the board.
+To conclude, even though for most projects the number of included studies (median 23) and total number of participants (median 102 per study) was relatively large, only power to detect medium or larger heterogeneity was good to excellent, whereas power to detect small heterogeneity was unacceptably low.
+Hence, even large multi-lab projects struggle to distinguish zero from small heterogeneity.
 
 Figure 2 shows the distribution of $I^2$ at different heterogeneity levels and a histogram of the observed effects.
-The shortest bars in the histogram correspond to a single effect.
+The shortest bars in the histogram correspond to the heterogeneity estimate of one effect.
 The considerable overlap of the distributions illustrates why sufficient power can be difficult to achieve, and why confidence intervals for $I^2$ are often wide.
-In particular the spread of the distribution under small heterogeneity is illustrative of the low power to be expected under such circumstances.
-Given the densities of the distributions (height of the curves) the majority of observed effects are most likely to have either zero or small heterogeneity.
+In particular, the dispersion of the distribution under small heterogeneity is illustrative of the low power to be expected under such circumstances.
+Given histogram of observed effect sizes and the densities of the distributions (height of the curves), the majority of observed effects are most likely to have zero or zero to small heterogeneity.
 Only two effects appear to be of medium heterogeneity and three of large.
@@
 _Figure 2.
-Simulated $I^2$ densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of [Higgins], and a histogram of the observed $I^2$ estimates for the 37 effects.
-Each simulated density consists of approximately 1,480,000 point estimates._
+Simulated $I^2$ densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of @10.1136/bmj.327.7414.557, and a histogram of the observed $I^2$ estimates for the 37 effects.
+Each simulated density consists of approximately 370,000 point estimates._
 
@@
 
-Larger effect sizes appear to be associated with higher heterogeneity estimates.
-In Table 3, the four effects with highest $I^2$ estimates also have the largest effect sizes.
+Larger estimated effect sizes appear to be associated with higher heterogeneity estimates.
+In Table 3, the four effects with highest $I^2$ estimates also have the largest effect size estimates.
 As expected, heterogeneity tends to increase with (absolute) effect size, with effect size sufficient to explain 61% of variation in $I^2$ estimates according to a simple regression model (Figure 3).
 The closely related, but unbounded, heterogeneity estimate $H^2$ provides a similar result ($R^2$ = .53).
-Excluding Anchoring effects as robustness check makes little difference ($R^2$ = .51 for $I^2$).
+Excluding Anchoring effects (the 1^st^, 3^rd^, 4^th^, and 6^th^ largest effect sizes) as robustness check results in only slightly less explained variance ($R^2$ = .51 for $I^2$).
 
 ```{r}
-knitr::include_graphics("../figures/effect_het.png")
+knitr::include_graphics("../figures/effect-het.png")
 ```
@@
 
-There is little evidence for heterogeneity amongst current pre-registered multi-lab replication projects in psychology.
-Across 10 projects, only 7/37 (19%) of primary outcomes had confidence intervals that excluded zero heterogeneity.
-Moreover, while each replication of an effect only varied on two contextual factors (sampling population and settings), the effects that showed evidence for heterogeneity were primarily effects that might have been expected to be sensitive to the changes in sampling population.
-Save two effects (Anchoring - Everest and IAT correlation math), all other effects that demonstrated heterogeneity were related to the US.
+There is little evidence for widespread heterogeneity amongst current pre-registered multi-lab replication projects in psychology.
+Across ten projects, only 7/37 (19%) of primary outcomes had confidence intervals that excluded zero heterogeneity.
+Moreover, while each replication of an effect only varied on two contextual factors (sampling population and settings), the effects that showed evidence for heterogeneity were primarily effects that might have been expected to be sensitive to changes in sampling population.
+That is, save two effects (Anchoring - Everest and IAT correlation math), all other effects that demonstrated heterogeneity were related to the US.
 They either asked questions about the US (anchoring effects), persons related to the US (Quote attribution) or issues that are well-known to generate strong debate in the US (i.e., free speech; allowed vs.
@@
 However, the relatively small number of effects in our sample means this association might be an artifact of the data.
+Finally, note that we only considered meta-analyses that varied two contextual factors (sample population and settings) that may cause heterogeneity, keeping constant two other ones (treatment and measurement variables), which may have resulted in both lower heterogeneity estimates as well as a stronger relationship between effect size and heterogeneity estimates in our paper.
+Other factors affecting this relationship are the number of studies and the study sample sizes, as these factors affect the precision of both estimates.
+Our strong estimated relationship between effect size and heterogeneity estimates is even more remarkable when taking the low precision of the heterogeneity estimates into account.
 
@@
 In respect to this point we look forward to the forthcoming Many Labs 2 project which should provide considerable new data on the prevalence of heterogeneity in psychology.
-In addition, while both the I2 confidence intervals and distribution of point estimates support a small number of heterogenous effects amongst those studied, most confidence intervals are congruent with anything from low to high heterogeneity as defined by [Higgins et al].
+In addition, while both the $I^2$ confidence intervals and distribution of point estimates support a small number of heterogenous effects amongst those studied, most confidence intervals are congruent with anything from low to high heterogeneity as defined by @10.1136/bmj.327.7414.557.
 As always, absence of evidence is not evidence of absence.
@@
 To conclude, evidence does not appear to support the belief that heterogeneity is the norm in psychology.
-Large-scale reviews of meta-analyses in psychology suggest considerable heterogeneity across the field of psychology [ref: Stanley; van Erp et al].
+Large-scale reviews of meta-analyses in psychology suggest considerable heterogeneity across the field of psychology [@Stanley2017; @10.5334/jopd.33a].
 However, in our experience psychologist tend to include widely varying studies in their meta-analyses, sometimes varying on all four contextual factors (or more).
-This is perhaps unsurprising considering the lack of theory delineating boundary conditions in psychology [ref: Simons et al].
+This is perhaps unsurprising considering the lack of theory delineating boundary conditions in psychology [@10.1177/1745691617708630].
 Our sample, despite consisting of the arguably best, least biased, meta-analytic data currently available in psychology, was unfortunately relatively small and not representative of the many varied effects studied in psychology.

### 2018-06-28 code/power_simulation.r
Added observed group sizes, effect size and effect types to simulations
Added mean differences. Odds ratios and risk differences are treated as mean differences.

@@ -5,7 +5,9 @@
 #Code: Anton Ohlsson Collentine
 
 #******************************************
-
+##To do:
+#1) for mean differences add sample sizes
+#2) separate between mean differences and SMD
 
 #******************************************
 #Packages and data----
@@ -31,7 +33,7 @@ dat <- read_csv("../data/collated_summary_data.csv")
 #******************************************
 #Simulation function----
 #******************************************
-simulate_I2 <- function(effect, reps, tau){ #this function applies to a single list object (effect)
+simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies to a single list object (effect), see next section
   
   K <- effect$K #Number of studies
   N <- effect$Ntotal #Sample sizes for all K studies
@@ -43,34 +45,76 @@ simulate_I2 <- function(effect, reps, tau){ #this function applies to a single l
       
       output[[t]] <- map_dfr(1:reps, possibly(function(x){ #For each tau-value repeat below "reps" times and bind into dataframe
         
-        rho <- rnorm(n = K, mean = 0, sd = tau[t]) #Draw true correlation rho for each k at the given value of tau
+        rho <- switch(effect_size, #Draw true correlation rho for each k at the given value of tau and with specified effect size
+                      zero = rnorm(n = K, mean = 0, sd = tau[t]),
+                      small = rnorm(n = K, mean = 0.1, sd = tau[t]),
+                      medium = rnorm(n = K, mean = 0.3, sd = tau[t]),
+                      large = rnorm(n = K, mean = 0.5, sd = tau[t]))
+        
         fr <- rnorm(n = K, mean = rho, sd = sqrt(1 / (N - 3))) #draw observed correlations (fisher's z) for each k
         
         fit <- rma(yi = fr, vi = 1 / (N - 3), method = "REML") #meta-analysis of fisher's z, each study weighted by its N
         
-        data.frame(I2 = fit$I2, ci.lb = confint(fit)$random[3, 2], tau = tau[t], tau_index = t)
+        data.frame(I2 = fit$I2, Qp = fit$QEp, ci.lb = confint(fit)$random[3, 2], 
+                   tau = tau[t], tau_index = t)
         
       }, otherwise = NULL)) #If rma does not converge, drop that iteration ('possibly' function)
     }
[…]

### 2018-06-28 writing/appendixA-heterogeneity.rmd
Added rough .rmd drafts of appendices

--- 2018-06-27 code/figures.rmd
@@
 ---
-title: "Figures"
-author: "Anton Ohlsson Collentine"
-output: pdf_document
+output: word_document
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.asp = 1.3)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.asp = 0.618)
 ```
@@
 if(!require(readr)){install.packages("readr")}
+if(!require(dplyr)){install.packages("dplyr")}
+if(!require(ggplot2)){install.packages("ggplot2")}
+if(!require(purrr)){install.packages("purrr")}
 if(!require(metafor)){install.packages("metafor")}
-if(!require(dplyr)){install.packages("dplyr")}
-if(!require(purrr)){install.packages("purrr")}
-if(!require(ggplot2)){install.packages("ggplot2")}
-if(!require(cowplot)){install.packages("cowplot")}
 
@@
 library(dplyr) #For data transformation
+library(ggplot2) #Plot data
 library(purrr) #For data iteration
 library(metafor) #To run meta-analyses
-library(ggplot2) #Plot data
-library(cowplot) #Combine several plots into one
 
@@
 
-source("helper_functions_tables_figures.r") #Load functions to prep data for figures
+source("../code/helper_functions_tables_figures.r") #Load functions to prep data for figures
 ```
 
-```{r transform_df}
-#Transform effect sizes to raw correlations
-#'transform_MA' is a sourced function
-res <- dat %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe
+Appendix A - Sensitivity analysis of effect size for simulations
 
+In our main results we simulated data to estimate type I error and power using an average effect size of zero.
+As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity.
+However, as a sensitivity analysis we in the Appendix analyze the same data, but generated with an average 'medium' effect size as defined by Cohen (1988).
+
+Table A1.
+
+_Type I error and power for data with an average 'medium' effect size_
+```{r table_results}
+dens <- readRDS("../data/power_simulation_results.RDS") #very large if saved as .csv
+names(dens) <-  sort(unique(dat$effect))
+
+#Summary of results. These are incorporated into the main table in the paper, see tables.rmd
+I2_ci_lb <- dens %>% 
+  bind_rows(.id = "effect") %>% 
+  group_by(effect, tau_index) %>% 
+  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
+  ungroup() %>% 
+  tidyr::spread(key = tau_index, value = power) %>% #prep for table
+  rename(zero = '1', small = '2', medium = '3', large = '4')
 ```
 
-```{r MA_df}
-summarizer <- function(x){
-  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
-  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1)) #estimates out
-}
-#Default method of metafor for calculating H2 is truncated at one.
-Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1).
-This method computes H2 as originally specified by Higgins & Thompson instead of using the more general method of metafor (see ?print.rma.uni).
-
-#Higgins, J., & Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. Statistics in medicine, 21(11), 1539-1558.
-
-res2 <- res %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(summarizer, .id = "effect") %>% 
-  mutate(z = abs(z)) #Absolute values since we are interested in effect size rather than direction
+```{r}
+knitr::kable(I2_ci_lb, digits = 2)
 ```
 
-```{r plot_res}
-
-# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61
-
-I2 <- ggplot(res2, aes(x = z, y = I2)) +
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = FALSE, color = "black") +
-  xlab("Fisher's z") +
-  coord_cartesian(ylim = c(0, 100)) +
-  geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
-  theme_classic() +
-  scale_y_continuous(name = expression(paste(I^2," index", sep = ""))) +
-  scale_x_continuous(name = "Effect size (Fisher's z)")
-
-# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53
-
-H2 <- ggplot(res2, aes(x = z, y = H2)) + 
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = FALSE, color = "black") +
-  xlab("Fisher's z") +
-  geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
-  theme_classic() +
-  scale_y_continuous(name = expression(paste(H^2," index", sep = ""))) +
-  scale_x_continuous(name = "Effect size (Fisher's z)")
-
-effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
-effect_het
-# save_plot("../figures/effect-het.png", effect_het,
-          # nrow = 2, base_aspect_ratio = 1.3, dpi = 600)
-
-```
-
-```{r robustness, results="hide"}
-##Excluding anchoring effects
-dropped_anchoring <- res2 %>%
-  filter(!grepl("Anchoring", effect))
-
-summary(lm(I2 ~ z, data = dropped_anchoring))
-#b = 87.87, R2 = .51
-
-```
+Some comments on type I errors and power in Table A1.Subsequently comments on Figure A1.
 
 ```{r Plot_tau_against_I2, fig.asp = 0.618}
-dat3 <- readRDS("../data/tau_simulation_results.RDS")
+dat3 <- readRDS("../data/appendixA_tau_simulation_results.RDS")
 names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
@@
 
-#combined line plot gives good overview. Point version of the same is also interesting.
+#combined line plot gives good overview.
 ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
@@
 
-# ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)
-
 ```
 
+_Figure A1._
+
+Here some comments on Figure A2.
 ```{r Density_plot, fig.asp= 0.618}
-dens <- readRDS("../data/power_simulation_results.RDS")
+dens <- readRDS("../data/appendixA_power_simulation_results.RDS")
 names(dens) <-  sort(unique(dat$effect))
@@
 
-# ggsave("../figures/density-I2.png", dpi = 600, height =  4 , width = 6.47)
 ```
+
+_Figure A2._
+
+Finally, conclusions from sensitivity analysis.

### 2018-06-28 writing/appendixB-heterogeneity.rmd
Added rough .rmd drafts of appendices

---
header-includes:
   - \setlength\parindent{24pt}
   - \usepackage{setspace}
   - \doublespacing

output: word_document
---
Appendix B - Formulas for effect size transformations

This appendix describes the formulas used to convert effect sizes into a common effect size measure (correlations). All formulas presented can be found in Borenstein (2009) and page numbers are cited as formulas are presented. For (standardized) mean differences, We assumed equal population standard deviations $\sigma_1 = \sigma_2$, and calculated (p. 226) the pooled standard deviation $S_p$ as follows:

$$S_p = \sqrt {\frac{(n_1 - 1) \times S_1^2 + (n_2 - 1) \times S_2^2}{n_1 + n_2 - 2}}$$

Where $n_1$/$n_2$ are group sample sizes and $S_1^2$/$S_2^2$ are the sample variances. In one case (RR8) we had to convert reported standard errors into pooled standard deviations. Standard errors are the square root of the variance of the mean:

$$SE = \sqrt{v}$$
The pooled standard deviation is then (p. 224):

$$S_p = \sqrt {\frac{v}{1 / n_1 + 1/n_2}}$$

We then standardized the mean differences (p.226):

$$d = \frac{\bar{x}_1 - \bar{x}_2}{S_p}$$

Where $d$ is the standardized mean difference and $\bar{x}_1$/$\bar{x}_2$ the sample means of the two groups. We finally converted effect sizes to correlaions $r$ (p. 234):

$$r = \frac{d}{\sqrt{d^2 + a}}$$

Where $a$ is a correction factor for unequal sample sizes $n_1 \neq n_2$. The correction factor is calculated (p. 234) as:

$$a = \frac{(n_1 + n_2)^2}{n_1 \times n_2}$$

For effects that were reported as odds ratios or risk differences, we computed log odds ratios, converted these to standardized mean differences, and proceeded as above to convert these to correlations. We first added one half to any empty cell to avoid dividing by zero. We then computed the log odds ratios as follows (p. 266):

$$OR_{log} = ln \frac{a \times d}{b \times c}$$
Where $a$, $b$, $c$, and $d$ are the four cell sizes. The log odds ratios were converted to $d$s as follows (p. 232):

$$d = \frac{OR_{log} \times \sqrt 3}{\pi}$$

### 2018-06-28 code/figures.rmd
Increase line thickness in Figure 2 legend to make it legible

@@
   theme(legend.position = c(0.8, 0.4),
-        legend.background = element_rect(linetype = "solid", color = "black"))
+        legend.background = element_rect(linetype = "solid", color = "black")) +
+  guides(color = guide_legend(override.aes = list(size = 1.4)))
 

### 2018-06-28 writing/draft-heterogeneity.rmd
Updated bibliography

@@
 It is a commonly believed that heterogeneity is the norm in psychology.
-In support of this notion, recent large scale reviews of meta-analyses in psychology [@Stanley2017; @10.5334/jopd.33a] report median heterogeneity levels that can best be described as 'large' (see next paragraph).
+In support of this notion, recent large scale reviews of meta-analyses in psychology [@Stanley2017; @10.5334/jopd.33] report median heterogeneity levels that can best be described as 'large' (see next paragraph).
 In comparison, the median heterogeneity estimate in medicine would be considered 'small' by the same standard [@10.1136/bmj.39343.408449.80].
@@
 However, meta-analyses in psychology also typically include more studies than those in medicine, and it could be that they tend to include studies from a much broader spectrum than meta-analyses in medicine.
-The median number of studies (effects) per meta-analysis in the psychology sample of @10.5334/jopd.33a was 12, whereas in the medicine sample of  @10.1136/bmj.39343.408449.80 the median number of studies was only 7, despite exclusion of all meta-analyses of 3 or fewer studies.
+The median number of studies (effects) per meta-analysis in the psychology sample of @10.5334/jopd.33 was 12, whereas in the medicine sample of  @10.1136/bmj.39343.408449.80 the median number of studies was only 7, despite exclusion of all meta-analyses of 3 or fewer studies.
 It is difficult to separate these explanations.
@@
 All effects were estimated with random-effects models and the Restricted Maximum Likelihood (REML) estimator using the R-package metafor [@10.18637/jss.v036.i03], though with a variety of outcome variables: correlations, standardized mean differences, raw mean differences, odds ratios and risk differences.
-ML1 transformed odd ratios into standardized mean differences when meta-analyzing under the assumption that responses followed logistic distributions [@10.1037/1082-989x.8.4.448; @10.18637/jss.v036.i03].
+ML1 transformed odd ratios into standardized mean differences when meta-analyzing under the assumption that responses followed logistic distributions [@10.1037/1082-989X.8.4.448; @10.18637/jss.v036.i03].
 Two projects (RRR5 and RRR7) used the Knapp and Hartung adjustment of the standard errors [@10.1002/sim.1482] and ML3 correlations were corrected for bias [@10.1037//0021-9010.74.3.469; @10.18637/jss.v036.i03].
@@
 To conclude, evidence does not appear to support the belief that heterogeneity is the norm in psychology.
-Large-scale reviews of meta-analyses in psychology suggest considerable heterogeneity across the field of psychology [@Stanley2017; @10.5334/jopd.33a].
+Large-scale reviews of meta-analyses in psychology suggest considerable heterogeneity across the field of psychology [@Stanley2017; @10.5334/jopd.33].
 However, in our experience psychologist tend to include widely varying studies in their meta-analyses, sometimes varying on all four contextual factors (or more).

### 2018-07-01 code/tables.rmd
Added bibliography and links to OSF
Updated Table 1

@@
 
-##Heterogeneity increases with effect size
+##Heterogeneity may increase with effect size
 ```{r effect-size-heterogeneity-table}
 #library(kableExtra)
-rooted_relabilities <- matrix(rep(c(.8, .7,.6), 3), ncol = 3)
-rho <- c(0, .5, .8)
-rel <- c("R = .8", "R = .7", "R = .6")
+rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
+rho <- c(0, .3, .5)
+rel <- c("R = .6", "R = .7", "R = .8")
 
 rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
-diff_row <- data.frame(rel = "Diff.", X1 = 0, X2 = 0.05, X3 = 0.08)
+rooted_relabilities <- data.frame(rel, rooted_relabilities)
 
-het_demo <- data.frame(rel, rooted_relabilities)
-het_demo <- rbind(het_demo, diff_row)
+diff_row <- data.frame(rel = "Standard deviation", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))
 
-het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "Rho = 0", "Rho = .5", "Rho = .8")) %>% 
+het_demo <- rbind(rooted_relabilities, diff_row)
+
+het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "Rho = 0", "Rho = .3", "Rho = .5"), digits = 2) %>% 
   kable_styling(position = "left") %>% 
-  footnote(threeparttable = TRUE) %>% 
+  footnote(threeparttable = TRUE,
+           general = "R = square root of the multiplied reliabilities. Rho = true effect size. Code to reproduce table: osf.io/kf6pt/") %>% 
   row_spec(3, hline_after = T)
@@
 primary studies, ML = Many Labs, RRR = Registered Replication Report.
-(OSF.io/XXXX)")
+Code to reproduce table: osf.io/kf6pt/")
 ```
@@
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-(OSF.io/XXXX)",
+Code to reproduce table: osf.io/kf6pt/",
            alphabet = "These effects were simulated as standardized mean differences")

### 2018-07-01 code/tables.rmd
Type I error and power with Q-test instead of I2 confidence interval

@@
   group_by(effect, tau_index) %>% 
-  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
+  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
   ungroup() %>% 

### 2018-07-01 code/power_simulation.r

@@ -148,7 +148,7 @@ set.seed(112)
 res <- vector("list", length(dat2)) #output of below loop
 
 system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
- res[[e]] <- simulate_I2(dat2[[e]], reps = 1e3, tau = tau_values, effect_size = "zero") #NB! 1e3 reps here is about 24 hours on my (fairly slow) machine
+ res[[e]] <- simulate_I2(dat2[[e]], reps = 1e3, tau = tau_values, effect_size = "zero") #NB! 1e3 reps here is about 36 hours on my (fairly slow) machine
  cat("...RS",e, "/37") #see progress
  if (e%%5 == 0 | e == 37) saveRDS(res, "../data/tau_simulation_results.RDS") #save ocassionally and at finish
 })
@@ -210,7 +210,7 @@ res2 <- vector("list", length(dat5))
 
 system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progress (lapply otherwise option)
   res2[[e]] <- simulate_I2(dat5[[e]][[1]], reps = 1e4,
-                           tau = c(0, dat5[[e]][[2]]), effect_size = "zero") #NB! 1e4 reps here is about 9.5 hours on my (fairly slow) machine
+                           tau = c(0, dat5[[e]][[2]]), effect_size = "zero") #NB! 1e4 reps here is about 14 hours on my (fairly slow) machine
   cat("...RS",e, "/37") #see progress
   if (e%%5 == 0 | e == 37) saveRDS(res2, "../data/power_simulation_results.RDS") #save ocassionally and at finish
 })
@@ -237,7 +237,7 @@ names(dens) <-  names(dat2)
 I2_ci_lb <- dens %>% 
   bind_rows(.id = "effect") %>% 
   group_by(effect, tau_index) %>% 
-  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
+  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
   ungroup() %>% 
   tidyr::spread(key = tau_index, value = power) %>% #prep for table
   rename(zero = '1', small = '2', medium = '3', large = '4')

### 2018-07-01 writing/draft-heterogeneity.rmd
Draft improvements

--- 2018-06-27 writing/draft-heterogeneity.rmd
@@
 author: 
-  - name          : "Anton Ohlsson Collentine"
+  - name          : "Anton Olsson-Collentine"
     affiliation   : "1"
@@
     address       : "Warandelaan 2, 5037 AB Tilburg"
-    email         : "j.a.e.olssoncollentine@tilburguniversity.edu"
-  - name          : "Jelte Wicherts"
+    email         : "j.a.e.olssoncollentine@uvt.edu"
+  - name          : "Jelte M. Wicherts"
     affiliation   : "1"
     corresponding : no    # Define only one corresponding author
-  - name          : "Marcel van Assen"
+  - name          : "Marcel A.L.M. van Assen"
     affiliation   : "1,2"
@@
 abstract: |
-  Abstract to be written.
+  We examined the evidence for heterogeneity (of effect sizes) and explored the correlation between heterogeneity and effect size in a sample of ten pre-registered multi-lab replication projects in psychology (Many Labs 1 & 3, Registered Replication Reports 1 to 8).
+Across the 37 main outcomes of these projects we found limited heterogeneity, only 4/37 (11%) effects had significant heterogeniety and the majority (32/37; 86%) were most likely to have zero to small heterogeneity.
+Power to detect small heterogeneity, as defined by @10.1136/bmj.327.7414.557, was for all projecst very low (mean 28%), but good to excellent for medium and large heterogeneity.
+We saw a strong correlation between observed effect size and heterogeneity, explaining up to 61% of variation in heterogeneity in our sample.
+Our results imply that an association between heterogeneity and effect size may need to b taken into account, and suggest that there is little cause to believe heterogeneity is the norm in psychology.
 
 keywords          : "heterogeneity, meta-analysis, replication, psychology, many labs, registered replication reports"
-wordcount         : "3"
+wordcount         : "130"
 
@@
 In the second stage, one may ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [@Campbell2015].
-This extent is often explored through replications of the original study that are either as similar as possible to the original (called 'direct' or 'exact' replications) or with some deliberate variation on conceptual factors (so-called 'conceptual' or 'indirect' replications) [ref: Zwaan et al], and once sufficient studies have accumulated through meta-analysis.
+This extent is often explored through replications of the original study that are either as similar as possible to the original (called 'direct' or 'exact' replications) or with some deliberate variation on conceptual factors (so-called 'conceptual' or 'indirect' replications) [@10.1017/S0140525X17001972], and once sufficient studies have accumulated through meta-analysis.
 In meta-analysis, the heterogeneity of an effect size (henceforth referred to as heterogeneity) is a measure of an effect's susceptibility to changes in these four factors.
 An effect strongly dependent on one or more of the four factors, unless controlled for, should exhibit high heterogeneity.
-In this paper we examine what degree of heterogeneity can be expected in replication studies in psychology and explore a proposed relationship with effect size.
-We focus in this paper on direct replications.
+In this paper we examine the heterogeneity in replication studies in psychology , focusing on direct replications, and explore a proposed relationship of effect size and heterogeneity.
 
 Heterogeneity is of concern for several reasons.
-First and foremost, unaccounted for heterogeneity can have unacceptable consequences.
-This may be most readily evident for medicine, where in the case of heterogeneity an intervention that is successful for some may have direct negative health consequences for others.
-However, the adoption of psychological research for business, law enforcement, and policymaking in general (e.g., the widespread use of 'nudges'; https://www.knowablemagazine.org/article/society/2018/nudging-grows-and-now-has-government-job) means its impact can be widespread and the consequences of heterogeneity should be no less of a concern for psychologists.
+First and foremost, unaccounted for heterogeneity can have consequences for the implementation of research that should not be ignored.
+This is readily evident for medicine, where in the case of heterogeneity an intervention, such as a medication, that is successful for some may have direct negative health consequences for others.
+The same is true of mental health interventions in psychology, but heterogeneity can also have major consequences for topics such as child development, education, and business performance, where psychological research can impact policy recommendations.
+Thus, heterogeneity should be no less of a concern for psychologists than for medical practitioners.
 
@@
 As such, heterogeneity might imply previously unknown predictors, so called 'hidden moderators' [@10.2139/ssrn.2820883], the discovery of which can be seen as an opportunity for theoretical advancement [@Tackett2017].
-The corollary is that, unless a theory has predefined additional assumptions ('auxiliary assumptions'; @10.3389/fpsyg.2015.00621) which were not fulfilled in the replications, an absence of heterogeneity should generally preclude referral to hidden moderators.
 
-Third,  the possibility of heterogeneity can create controversy in the interpretation of single replication results.
-The proclamation of a  'failure' to replicate an effect often seems to imply that the original find was merely a statistical fluke, due to 'p-hacking' [@10.1177/0956797611417632] or publication bias [@10.2139/ssrn.2659409].
+Third,  the possibility of heterogeneity can create controversy in the interpretation of replication results.
+The proclamation of a  'failure' to replicate an effect is sometimes taken to imply that the original find was merely a statistical fluke, due to 'p-hacking' [@10.1177/0956797611417632] or publication bias [@10.2139/ssrn.2659409].
 Unsurprisingly, some researchers take offense [e.g., @10.1016/j.jesp.2016.02.003].
-An alternative explanation for non-replication, often espoused by the original authors [e.g, @10.2139/ssrn.2698810; @10.1177/1745691616674460], is that the effect is more heterogenous than (perhaps implicitly) claimed originally.
+An alternative explanation for non-replication, often espoused by the original authors [e.g, @10.2139/ssrn.2698810; @10.1177/1745691616674460], is that the effect is more heterogeneous than (perhaps implicitly) claimed originally.
 Such explanations may be valid or not, but even if valid, an effect is typically of less general interest the more specific circumstances it requires to appear.
-A way for original authors to align researchers' expectations of heterogeneity is to preemptively specify their own, that is, the degree of heterogeneity that would make they themselves lose interest in an effect (e.g., by declaring 'constraints on generality' [@10.1177/1745691617708630].
+To attenuate the risk of heated discussions on the (non)existence of an effect, original authors may wish to consider pre-specifying the degree of heterogeneity that would make they themselves lose interest in the effect (e.g., by declaring 'constraints on generality' [@10.1177/1745691617708630].
+To conclude, heterogeneity or its absence provides vital information for the implementation of research in practice, the advancement of theory, and the interpretation of research outcomes.
 
-Fourth, meta-analytic techniques are affected by heterogeneity.
-Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [@@10.2139/ssrn.2659409; @10.1177/1745691616662243], which is problematic considering widespread publication bias [refs] and its impact on meta-analytic estimates.
+Heterogeneity also affects meta-analytic techniques used to statistically summarize findings on a certain topic.
+Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [@10.1177/1745691616662243; 10.1037/met0000025; 10.1177/1745691616650874], which is problematic considering widespread publication bias [@10.1007/s11192-011-0494-7] and its impact on meta-analytic estimates.
 In addition, heterogeneity alters the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity), though one may question the usefulness of interpreting the average true effect size in the presence of heterogeneity [@Simonsohn2017], just as it may be questionable to interpret an average main effect in the context of an interaction effect [@Aiken1991].
@@
 It is a commonly believed that heterogeneity is the norm in psychology.
-In support of this notion, recent large scale reviews of meta-analyses in psychology [@Stanley2017; @10.5334/jopd.33a] report median heterogeneity levels that can best be described as 'large' (see next paragraph).
-In comparison, the median heterogeneity estimate in medicine would be considered 'small' by the same standard [@10.1136/bmj.39343.408449.80].
-It may simply be that effects in psychology are more heterogenous than those of medicine.
+In support of this notion, recent large scale reviews of meta-analyses in psychology [@Stanley2017; @10.5334/jopd.33a] report median heterogeneity levels that can best be described as 'large' (@10.1136/bmj.327.7414.557; see next paragraph).
+In comparison, the median heterogeneity estimate in medicine [@10.1136/bmj.39343.408449.80] would be considered 'small' by the same standard.
+It may simply be that effects in psychology are more heterogeneous than those of medicine.
 However, meta-analyses in psychology also typically include more studies than those in medicine, and it could be that they tend to include studies from a much broader spectrum than meta-analyses in medicine.
-The median number of studies (effects) per meta-analysis in the psychology sample of @10.5334/jopd.33a was 12, whereas in the medicine sample of  @10.1136/bmj.39343.408449.80 the median number of studies was only 7, despite exclusion of all meta-analyses of 3 or fewer studies.
-It is difficult to separate these explanations.
+The median number of studies (effects) per meta-analysis in the psychology sample of @10.5334/jopd.33a was 12, whereas in the medicine it is only 3 [@10.1186/1471-2288-11-160].
+It is difficult to separate these explanations (intrinsically more heterogeneity, or psychology simply including studies from a broader spectrum).
 To facilitate doing so, in this paper we focus on meta-analyses of only direct replications, which are exempt from the potential problem of including too disparate studies.
-In reference to meta-analyses of direct replications, several authors [@10.1177/1745691616662243; @Tackett2017] have argued that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol, and that heterogeneity has been reported even under such circumstances [e.g., @10.1027/1864-9335/a000178 is an indication of widespread heterogeneity in psychology.
-However, even in the case of multi-lab direct replication projects, studies vary on two contextual factors (sample population and settings) and if we believe an effect is sensitive to changes in these two factors we might still expect to find some heterogeneity
+In reference to meta-analyses of direct replications, several authors [@10.1177/1745691616662243; @Tackettt2017] have argued that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol [such as @10.1027/1864-9335/a000178].
+They further argue that the fact that heterogeneity has been reported even under such circumstances is an indication of widespread heterogeneity in psychology.
+However, even in the case of multi-lab direct replication projects, studies still vary on two contextual factors (sample population and settings) and if we believe an effect is sensitive to changes in these two factors we might also expect to find some heterogeneity.
+
+###Quantifying heterogeneity
 
@@
 Heterogeneity is often measured by the $I^2$ index [@10.1002/sim.1186;  @10.1136/bmj.327.7414.557], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
-It can be interpreted as the percentage of variability in effect sizes that is due to heterogeneity amongst the true effects (that is, sensitivity to contextual factors) rather than sampling variance, and ranges from 0-100%.
+It can be interpreted as the percentage of variability in observed effect sizes in a meta-analysis that is due to heterogeneity amongst the true effects (that is, sensitivity to contextual factors) rather than sampling variance, and ranges from 0-100%.
 The $I^2$ index is a transformation of the well-known Q-test of heterogeneity in meta-analysis [@10.2307/3001666] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative $I^2$ is set to zero.
@@
 Tests of heterogeneity typically have low statistical power in many practical situations [@10.1002/sim.2481; @10.1037/1082-989X.11.2.193].
-This complicates the discussion of heterogeneity, because while $I^2$ always provides an estimate of heterogeneity, this estimate is often surrounded by wide confidence intervals [@10.1136/bmj.39343.408449.80"].
+This complicates the discussion of heterogeneity, because while $I^2$ always provides an estimate of heterogeneity, this estimate is often accompanied by wide confidence intervals [@10.1136/bmj.39343.408449.80"].
 For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with $I^2$ point estimates of 0% had upper 95% confidence intervals that exceeded 33%, exceeding what @10.1136/bmj.327.7414.557 defined as 'small' heterogeneity.
@@
 
-Effect size likely influences heterogeneity.
+Effect size is likely associated with heterogeneity.
 Intuitively, it makes sense to believe that if there is no meta-analytic effect there is nothing to moderate (i.e., no heterogeneity).
@@
 Each included study would need to measure the two variables somehow, possibly the same way across studies.
-However, because of individual differences, measurement is not equally exact for everyone, and between studies the measurement reliabilities may differ either due to sampling variance (that the sample happens to be more or less homogenous) or to differences in contextual factors (e.g., sampling population, method of measurement).
-This means that even if the underlying true effect size is the same, the observed correlation between the two variables will differ between studies.
+However, because of individual differences and differences in study samples, measurement reliabilities may differ across studies either due to sampling variance (that the sample happens to be more or less homogeneous) or to differences in contextual factors (e.g., sampling population, method of measurement).
+This means that even if the underlying true effect size is the same, the observed correlation between the two variables will differ between studies [see also @Schmidt2015].
 Keeping measurement reliabilities constant, differences in observed effect sizes will increase with the underlying true effect, resulting in more variability being ascribed to heterogeneity.
 More formally, an observed correlation $r_{xy}$ can be expressed as the product of the true correlation or effect size, $\rho_{xy}$, multiplied by the square root of the measurement reliabilities for X ($R_{xx'}$) and Y ($R_{yy'}$): $r_{xy} = \rho_{xy} \times \sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$.
-As such, if $\sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$ stays constant while $\rho_{xy}$ increases the observed differences between studies will also increase, thereby increasing heterogeneity of observed effect sizes (see Table 1).
-We explore the association between effect size and heterogeneity in a sample of pre-registered multi-lab replication projects.
+As such, keeping constant study differences in $\sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$ while increasing true effect size $\rho_{xy}$ increases the observed differences between studies, thereby increasing heterogeneity of observed effect sizes (see Table 1).
+We explore the association between effect size and heterogeneity in a sample of pre-registered multi-lab replication projects in psychology.
 
@@
 
+```{r effect-size-heterogeneity-table}
+#library(kableExtra)
+rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
+rho <- c(0, .3, .5)
+rel <- c("R = .6", "R = .7", "R = .8")
+
+rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
+rooted_relabilities <- data.frame(rel, rooted_relabilities)
+
+diff_row <- data.frame(rel = "Standard deviation", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))
+
+het_demo <- rbind(rooted_relabilities, diff_row)
+
+het_demo %>% knitr::kable(col.names = c("", "Rho = 0", "Rho = .3", "Rho = .5"), digits = 2)
+
+```
+**Note.** R = square root of the multiplied reliabilities. Rho = true effect size. Code to reproduce table: osf.io/kf6pt/
+
 We examine the evidence for widespread heterogeneity in psychology and explore the correlation between effect size and heterogeneity, using ten pre-registered multi-lab replication projects in psychology (Table 2).
 These ten projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
-To better interpret heterogeneity estimates we also estimate power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557.
-Of the four contextual factors a study might vary on (sample population, settings,  treatment variables, and measurement variables) the studies in these projects vary only on two: sample population and settings.
-Nonetheless, if we believe an effect is sensitive to changes in these two factors we may still expect to find some heterogeneity.
-For example, the variety of countries and samples involved in some of the replication projects, not all of which are WEIRD (Western, Educated, Industrial, Rich, Democratic [@10.1017/S0140525X0999152X]) might be a reason to expect heterogeneity.
-On the other hand, it may be that the less disparate collection of studies included in these direct replication meta-analyses as compared to most psychological meta-analyses result in low heterogeneity estimates, similar to estimates in medicine.
-Regardless of outcome, the sampled multi-lab replication projects can only inform us of susceptibility to changes in the varied contextual factors  (sample population and settings), with no information on susceptibility to changes in other contextual factors.
+To better interpret the heterogeneity estimates we also estimate power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557.
+Consequently, our analyses will provide information on how two contextual factors (sample population and settings) may affect consistency or heterogeneity of effects in psychology.
 
@@
 
-_Pre-registered multi-lab replication studies_
+_Pre-registered multi-lab replication projects_
 
@@
 primary studies, ML = Many Labs, RRR = Registered Replication Report.
-(osf.io/kf6pt/)
+Code to reproduce table: osf.io/kf6pt/
 
@@
 We refer to relevant files on OSF using brackets and links in the sections below, that is (osf.io/XXXX/).
-We ran all analyses using R version 3.4.3 [@RCoreTeam2017].
+We ran all analyses using R version 3.4.3 [@RcoreTeam2017].
 
@@
 [Marcel/Jelte: Not sure this paragraph is correct, because my grasp of the mathematics is a bit tenuous].
-Nonetheless, as a sensitivity test we also ran the analysis with 'medium' effect sizes [@Cohen1988], see Appendix A (osf.io/XXXX/) [appendix not created yet, hence no link].
+Nonetheless, as a sensitivity test we also ran the analysis with 'medium' effect sizes [@Cohen1988], see Appendix A (osf.io/bsjhu/).
 
@@
 Fisher's z-transformation is a normalizing correlation transformation that ranges from negative infinity to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [@10.2307/2331838; Fisher1921].
-Second, for each of the K true Fisher-transformed correlations we sampled one Fisher-transformed observed correlation from a normal distribution with mean $\rho_k$ and variance $1 ???
-(N_k - 3)$.
+Second, for each of the K true Fisher-transformed correlations we sampled one Fisher-transformed observed correlation from a normal distribution with mean $\rho_k$ and variance $1 /(N_k - 3)$.
 Finally, we fitted a random-effects meta-analysis with REML and estimated $I^2$ for that run.
@@
 232) and then finally to a correlation.
-All formulas used are presented in Appendix B (osf.io/XXXX/) [appendix not created yet, hence no link].
+All formulas used are presented in Appendix B (osf.io/h4vfx/) [appendix not created yet, hence no link].
 Since $I^2$ is set to zero for the majority of cases under homogeneity (i.e., truncated), we also correlated effect size with the closely related heterogeneity estimate $H^2$ [@10.1002/sim.1186] as a sensitivity analysis.
@@
 Under simulated heterogeneity, Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\%) respectively.
-(osf.io/kf6pt/)
+Code to reproduce table: osf.io/kf6pt/
 
@@
 
-_Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 37 effects. Tau is not directly comparable across effect size measures._
+_Figure 1.
+Result of simulation relating $I^2$-values to between studies standard deviation.
+Each line represent one of 37 effects.
+Tau is not directly comparable across effect size measures.
+Code to reproduce figure: osf.io/zuwpg/_
 
@@
 Simulated $I^2$ densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of @10.1136/bmj.327.7414.557, and a histogram of the observed $I^2$ estimates for the 37 effects.
-Each simulated density consists of approximately 370,000 point estimates._
+Each simulated density consists of approximately 370,000 estimates.
+Code to reproduce figure: osf.io/zuwpg/_
 
@@
 
-_Figure 3. The correlation between A) $I^2$ and effect size and B) $H^2$ and effect size for 37 effects from ten pre-registered multi-lab replication projects._
+_Figure 3. The correlation between A) $I^2$ and effect size and B) $H^2$ and effect size for 37 effects from ten pre-registered multi-lab replication projects. Code to reproduce figure: osf.io/zuwpg/_
 
@@
 
+We examined the evidence for widespread heterogeneity in psychology and the correlation between effect size and heterogeneity, in sample of ten pre-registered multi-lab replication projects in psychology.
+These ten projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
+To aid interpretation we also estimated power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557 and plotted the distributions of $I^2$ under these four heterogeneity levels.
+Our results showed that most effects in our sample likely had zero to small heterogeneity, that power to distinguish between zero and small heterogeneity was remarkably low for all projects, and that heterogeneity was strongly correlated with effect size in our sample.
+
 There is little evidence for widespread heterogeneity amongst current pre-registered multi-lab replication projects in psychology.
-Across ten projects, only 7/37 (19%) of primary outcomes had confidence intervals that excluded zero heterogeneity.
-Moreover, while each replication of an effect only varied on two contextual factors (sampling population and settings), the effects that showed evidence for heterogeneity were primarily effects that might have been expected to be sensitive to changes in sampling population.
+Across ten projects, only 7/37 (19%) of primary outcomes had confidence intervals that excluded zero heterogeneity, and given the distributions of $I^2$ under zero to large heterogeneity, most (32/37; 86%) effects appeared to have zero or small heterogeneity.
+Moreover, while each replication of an effect only varied on two contextual factors (sampling population and settings), the effects that showed significant evidence for heterogeneity were primarily effects that might have been expected to be sensitive to changes in sampling population.
 That is, save two effects (Anchoring - Everest and IAT correlation math), all other effects that demonstrated heterogeneity were related to the US.
@@
 Although ML1 tested US vs.
-non-US as a moderator of heterogeneity and found very small effect sizes, these are all effects for which heterogenous responses also within the US would be unsurprising (e.g., someone living close to Chicago is more likely to know the population of Chicago).
-Our results suggest little reason to believe heterogeneity is the norm in psychology, and thus imply that citing heterogeneity as a reason for non-replication of an effect is unwarranted unless predicted _a priori_.
+non-US as a moderator of heterogeneity and found very small effect sizes, these are all effects for which heterogeneous responses also within the US would be unsurprising (e.g., someone living close to Chicago is more likely to know the population of Chicago).
+Our finding that heterogeneity appears to be small or non-existent except where it might have been expected, is an argument against so called 'hidden moderators', or unexpected contextual sensitivity.
+Indeed, our results imply that effects cannot simply be assumed to vary extensively "across time, situations and persons" [@10.3389/fpsyg.2017.00879, p.14] and that we should not expect "minor, seemingly arbitrary and even theoretically irrelevant modifications in procedures" [@10.1186/s40359-016-0134-3, p.6] to have large impact on effect estimates.
+That is, our results imply that citing heterogeneity as a reason for non-replication of an effect is unwarranted unless predicted _a priori_.
 
-Complicating the discussion of heterogeneity is that there amongst the studied effects was a clear association between effect size and heterogeneity.
-There are thus both good theoretical (see introduction) and empirical reasons to expect larger effect sizes to exhibit comparatively more heterogeneity when using observed effect sizes in a meta-analysis.
-Since not all measurements (e.g., behavioral) admit adjusting for reliability as easily as questionnaires, a potential correlation between effect size and heterogeneity could be difficult to control for.
-However, the relatively small number of effects in our sample means this association might be an artifact of the data.
-Finally, note that we only considered meta-analyses that varied two contextual factors (sample population and settings) that may cause heterogeneity, keeping constant two other ones (treatment and measurement variables), which may have resulted in both lower heterogeneity estimates as well as a stronger relationship between effect size and heterogeneity estimates in our paper.
-Other factors affecting this relationship are the number of studies and the study sample sizes, as these factors affect the precision of both estimates.
-Our strong estimated relationship between effect size and heterogeneity estimates is even more remarkable when taking the low precision of the heterogeneity estimates into account.
+In view of the fact that most effects in our sample likely had zero to small heterogeneity, the lack of power to distinguish between these two heterogeneity levels is of concern.
+That heterogeneity is small is not the same as being negligible, as even small heterogeneity may have large consequences at the aggregated level of an intervention, or at the individual level for a few people.
+Yet, power to detect small heterogeneity was on average only 28% in our sample.
+A suggestion to double the already very impressive number of participating labs and individuals of the largest replication projects in our sample seems unrealistic even for methodologists.
+It may simply be that the $I^2$ index as a measure of heterogeneity is inadequate to examine small levels of heterogeneity.
+The good news is that sufficient power to detect large and, to a lesser degree, medium heterogeneity is realistically achievable for many meta-analyses.
 
-There are some additional limits to the generalizability of claims based on the data in our study.
+Heterogeneity amongst the studied effects was strongly associated with effect size.
+There are thus both good theoretical reasons, related to measurement reliability of estimates, and empirical reasons to expect larger effect sizes to exhibit comparatively more heterogeneity when using observed effect sizes in a meta-analysis.
+This creates challenges in disentangling the roots of heterogeneity.
+Consequently, for researchers who wish to examine heterogeneity to further theory development, it may be desirable to endeavor to account for measurement reliability in the effects that are aggregated in meta-analyses.
+We recognize that not all measurements (e.g., behavioral) admit adjusting for reliability as easily as questionnaires, meaning a correlation between effect size and heterogeneity could at times be difficult to control for.
+Nonetheless, the extensive use of scales in psychology means that for many meta-analysts there should be little reason not to control for measurement reliability when aggregating results.
+
+There are some limits to the generalizability of claims based on the data in our study.
 For one, the included effects are neither a representative nor random sample of effects in psychology and as such do not support making strong claims about average heterogeneity levels in psychology.
 In respect to this point we look forward to the forthcoming Many Labs 2 project which should provide considerable new data on the prevalence of heterogeneity in psychology.
-In addition, while both the $I^2$ confidence intervals and distribution of point estimates support a small number of heterogenous effects amongst those studied, most confidence intervals are congruent with anything from low to high heterogeneity as defined by @10.1136/bmj.327.7414.557.
-As always, absence of evidence is not evidence of absence.
-Finally, since the included studies only vary on two contextual factors (sample population and settings), the data tell us nothing about the included effects' susceptibility to changes in the other two factors (treatment and measurement variables).
+Relatedly, the relatively small number of effects in our sample means the association between heterogeneity and effect size might be an artifact of the data.
+In addition, while our results point towards most effects having zero to small heterogeneity, many confidence intervals are very wide and congruent with a large range of actual heterogeneity.
+Finally, note that we only considered meta-analyses that varied two contextual factors (sample population and settings) that may cause heterogeneity, keeping constant two other ones (treatment and measurement variables), which may have resulted in both lower heterogeneity estimates as well as a stronger relationship between effect size and heterogeneity estimates in our paper.
 
-To conclude, evidence does not appear to support the belief that heterogeneity is the norm in psychology.
-Large-scale reviews of meta-analyses in psychology suggest considerable heterogeneity across the field of psychology [@Stanley2017; @10.5334/jopd.33a].
-However, in our experience psychologist tend to include widely varying studies in their meta-analyses, sometimes varying on all four contextual factors (or more).
-This is perhaps unsurprising considering the lack of theory delineating boundary conditions in psychology [@10.1177/1745691617708630].
-Our sample, despite consisting of the arguably best, least biased, meta-analytic data currently available in psychology, was unfortunately relatively small and not representative of the many varied effects studied in psychology.
-As such we are enthusiastic about the many multi-lab initiatives in psychology (Registered Replication Reports, Many Labs 2, ManyBabies, the Psych Science Accelerator) which in the future will provide considerable new data and enable researchers to re-evaluate the prevalence of heterogeneity in psychology.
-At current there is little evidence to support the notion that heterogeneity is widespread in psychology.
+Our results and the limitations of our data provides some guidance in directions of future research.
+To fully establish whether zero to small heterogeneity is the standard for direct replications in psychology, as suggested by our results, it would be desirable to examine heterogeneity in a larger sample of meta-analyses of direct replications than the 37 examined here.
+We are enthusiastic about the possibilities to do so in the near future, thanks to the many ongoing multi-lab initiatives in psychology (Registered Replication Reports, Many Labs 2, ManyBabies, the Psych Science Accelerator).
+Relatedly, a larger sample of effects would enable testing whether the correlation between heterogeneity and effect size is generally as remarkably strong as we found in our sample, or if it was an artifact of the data.
+Moreover, it may be worthwhile to attempt to disentangle the contribution of reliability to this correlation from other aspects of measurement that are likely to contribute, such as range restrictions [@Schmidt2015].
+Finally, the poor power of $I^2$ to detect small heterogeneity means that if zero to small heterogeneity is truly the norm for direct replications in psychology, it may be time to explore new measures of heterogeneity.
+
+To conclude, in the arguably best meta-analytic data currently available in psychology, most effects had zero to small heterogeneity, and heterogeneity was strongly correlated with effect size.
+Despite a relatively large number of studies and participants in each meta-analysis, power was too low to distinguish between zero and small heterogeneity in all cases.
+Our results suggest little reason to believe heterogeneity is widespread in psychology.
 

### 2018-07-02 writing/appendixA-heterogeneity.rmd
Updated Appendix A

@@
 
+```{r results}
+##Zero effect size results
+dens <- readRDS("../data/power_simulation_results.RDS") 
+names(dens) <-  sort(unique(dat$effect))
+
+#Summary of results. These are incorporated into the main table in the paper, see tables.rmd
+zero <- dens %>% 
+  bind_rows(.id = "effect") %>% 
+  group_by(effect, tau_index) %>% 
+  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
+  ungroup() %>% 
+  tidyr::spread(key = tau_index, value = power) %>% #prep for table
+  rename(zero = '1', small = '2', medium = '3', large = '4') %>% 
+  select(-effect)
+
+##Medium effect size results
+dens2 <- readRDS("../data/appendixA_power_simulation_results.RDS") 
+names(dens2) <-  sort(unique(dat$effect))
+
+#Summary of results.
+medium <- dens2 %>% 
+  bind_rows(.id = "effect") %>% 
+  group_by(effect, tau_index) %>% 
+  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
+  ungroup() %>% 
+  tidyr::spread(key = tau_index, value = power) %>% #prep for table
+  rename(zero = '1', small = '2', medium = '3', large = '4')
+
+##combine for table
+
+comparison <- cbind(zero, medium)
+```
+
 Appendix A - Sensitivity analysis of effect size for simulations
@@
 As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity.
-However, as a sensitivity analysis we in the Appendix analyze the same data, but generated with an average 'medium' effect size as defined by Cohen (1988).
+However, as a sensitivity analysis we in this Appendix again estimate type I error and power, but generated with an average 'medium' effect size as defined by Cohen (1988).
+
+Estimated type I error and power for zero/small/medium/large heterogeneity when simulated with a true effect size of zero vs.
+medium are shown for each effect in Table A1.
+In both cases type I error is consistently conservative, as compared to the expected 5% error rate.
+With a an effect size of zero, average power was `r 100*round(mean(zero$small), digits = 2)`/`r 100*round(mean(zero$medium), digits = 2)`/`r 100*round(mean(zero$large), digits = 2)`% for small/medium/large heterogeneity respectively.
+The corresponding power with an average effect size was `r 100*round(mean(zero$small), digits = 2)`, `r 100*round(mean(zero$medium), digits = 2)`, and `r 100*round(mean(zero$large), digits = 2)`%.
+To conclude, changing true effect size in our simulations from zero to medium has little impact on estimated type I error and power.
 
@@
 
-_Type I error and power for data with an average 'medium' effect size_
-```{r table_results}
-dens <- readRDS("../data/power_simulation_results.RDS") #very large if saved as .csv
-names(dens) <-  sort(unique(dat$effect))
+_Type I error and power for data with a true effect size of zero vs. 'medium'_
 
-#Summary of results. These are incorporated into the main table in the paper, see tables.rmd
-I2_ci_lb <- dens %>% 
-  bind_rows(.id = "effect") %>% 
-  group_by(effect, tau_index) %>% 
-  summarize(power = mean(ci.lb > 0)) %>% #Estimate power/type 1 error for each tau level and effect
-  ungroup() %>% 
-  tidyr::spread(key = tau_index, value = power) %>% #prep for table
-  rename(zero = '1', small = '2', medium = '3', large = '4')
+```{r}
+knitr::kable(comparison, digits = 2)
 ```
 
-```{r}
-knitr::kable(I2_ci_lb, digits = 2)
-```
-
-Some comments on type I errors and power in Table A1.Subsequently comments on Figure A1.
-
-```{r Plot_tau_against_I2, fig.asp = 0.618}
-dat3 <- readRDS("../data/appendixA_tau_simulation_results.RDS")
-names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
-
-OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales') #effects that were transformed from OR to SMD
-
-#Categorize effects by type of simulation for graphing
-effect_type <- distinct(select(dat, effect, effect_type)) %>% 
-  mutate(effect_type = ifelse(effect %in% OR2d | effect_type == "Risk difference" | 
-                                effect_type == "Raw mean difference", "MD", effect_type),
-         effect_type = recode(effect_type, "d" = 'SMD',
-                              "r" = "Fisher's z"))
-
-dat3 <- dat3 %>% 
-  bind_rows(.id = "effect") %>% #create dataframe with identifier
-  left_join(., effect_type) %>% 
-  select(I2, tau, effect, effect_type) %>% 
-  group_by(tau, effect, effect_type) %>% 
-  summarize(I2 = mean(I2)) %>% #Take mean of I2 at each tau-level and for each effect
-  ungroup()
-
-#combined line plot gives good overview.
-ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
-  geom_line(alpha = 0.6) +
-  theme_bw() +
-  scale_x_continuous(name = expression(paste("Between studies standard deviation ", tau)),
-                     minor_breaks = NULL) +
-  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
-                     minor_breaks = NULL) +
-  coord_cartesian(ylim = c(0, 100)) +
-  scale_color_brewer(name = "Effect type", palette = "Dark2", 
-                     breaks = c("Fisher's z", "MD", "SMD")) +
-  theme(legend.position = c(0.8, 0.4),
-        legend.background = element_rect(linetype = "solid", color = "black"))
-
-```
-
-_Figure A1._
-
-Here some comments on Figure A2.
-```{r Density_plot, fig.asp= 0.618}
-dens <- readRDS("../data/appendixA_power_simulation_results.RDS")
-names(dens) <-  sort(unique(dat$effect))
-
-#Simulated data at various heterogeneity levels, prep for plotting
-I2_dist <- dens %>% 
-  bind_rows(.id = "effect") %>% 
-  rename(Heterogeneity = tau_index) %>% 
-  mutate(Heterogeneity = recode(Heterogeneity,
-                            '1' = "Zero",
-                            '2' = "Small",
-                            '3' = "Medium",
-                            '4' = "Large"),
-         Heterogeneity = as.factor(Heterogeneity))
-
-#Observed I2 estimates, i.e, results from main table, see table.rmd
-#Effects estimated with sourced function 'est_heterogeen_smd_raw'
-observed <- dat %>% 
-  split(.$effect) %>%  
-  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% 
-  select(effect, I2 = s_I2) %>%
-  mutate(Heterogeneity = "Observed")
-
-ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
-  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
-  geom_density(alpha = 0.3) +
-  theme_classic() +
-  coord_cartesian(xlim = c(0, 100))  +
-  scale_fill_brewer(palette = "Dark2",
-                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
-                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
-                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  scale_color_brewer(palette = "Dark2", 
-                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  theme(legend.position = c(0.85, 0.71),
-        legend.background = element_rect(linetype = "solid", color = "black")) +
-  scale_y_continuous(name = "Density") +
-  scale_x_continuous(name = expression(paste(I^2," index", sep = "")))
-
-```
-
-_Figure A2._
-
-Finally, conclusions from sensitivity analysis.
+**Note.** Column headers indicate the degree of simulated heterogeneity where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75%) respectively.
+Code to reproduce table: osf.io/bsjhu/

### 2018-07-02 writing/draft-heterogeneity.rmd
Updated draft, added dynamic results in text

@@
 Across the 37 main outcomes of these projects we found limited heterogeneity, only 4/37 (11%) effects had significant heterogeniety and the majority (32/37; 86%) were most likely to have zero to small heterogeneity.
-Power to detect small heterogeneity, as defined by @10.1136/bmj.327.7414.557, was for all projecst very low (mean 28%), but good to excellent for medium and large heterogeneity.
-We saw a strong correlation between observed effect size and heterogeneity, explaining up to 61% of variation in heterogeneity in our sample.
-Our results imply that an association between heterogeneity and effect size may need to b taken into account, and suggest that there is little cause to believe heterogeneity is the norm in psychology.
+Power to detect small heterogeneity, as defined by @10.1136/bmj.327.7414.557, was for all projects very low (mean 36%), but good to excellent for medium and large heterogeneity.
+We saw a strong correlation between observed effect size and heterogeneity in our sample (R^2^ = .61).
+Our results suggest that an association between heterogeneity and effect size may need to be considered when estimating heterogeneity, and a lack of evidence to indicate widespread heterogeneity in psychology.
 
 keywords          : "heterogeneity, meta-analysis, replication, psychology, many labs, registered replication reports"
-wordcount         : "130"
+wordcount         : "146"
 
@@
 First, belief in the existence of an effect is established.
-Second, its generalizability is examined by exploring its boundary conditions.
+Second, the effect's generalizability is examined by exploring its boundary conditions.
 In the first stage, inferential statistics are used  to minimize the risk that a discovery is due to sampling error.
 In the second stage, one may ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [@Campbell2015].
-This extent is often explored through replications of the original study that are either as similar as possible to the original (called 'direct' or 'exact' replications) or with some deliberate variation on conceptual factors (so-called 'conceptual' or 'indirect' replications) [@10.1017/S0140525X17001972], and once sufficient studies have accumulated through meta-analysis.
+This extent is often explored through replications of the original study that are either as similar as possible to the original (called 'direct' or 'exact' replications) or with some deliberate variation on conceptual factors [so-called 'conceptual' or 'indirect' replications; @10.1017/S0140525X17001972], and once sufficient studies have accumulated through meta-analysis.
 In meta-analysis, the heterogeneity of an effect size (henceforth referred to as heterogeneity) is a measure of an effect's susceptibility to changes in these four factors.
 An effect strongly dependent on one or more of the four factors, unless controlled for, should exhibit high heterogeneity.
-In this paper we examine the heterogeneity in replication studies in psychology , focusing on direct replications, and explore a proposed relationship of effect size and heterogeneity.
+In this paper we examine the heterogeneity in replication studies in psychology , focusing on direct replications, and explore a proposed relationship between effect size and heterogeneity.
 
 Heterogeneity is of concern for several reasons.
-First and foremost, unaccounted for heterogeneity can have consequences for the implementation of research that should not be ignored.
+First and foremost, unaccounted for heterogeneity can have practical consequences not to be ignored.
 This is readily evident for medicine, where in the case of heterogeneity an intervention, such as a medication, that is successful for some may have direct negative health consequences for others.
-The same is true of mental health interventions in psychology, but heterogeneity can also have major consequences for topics such as child development, education, and business performance, where psychological research can impact policy recommendations.
+The same is true of mental health interventions in psychology, but heterogeneity can also have major consequences for topics such as child development, education, and business performance, where psychological research often impacts policy recommendations.
 Thus, heterogeneity should be no less of a concern for psychologists than for medical practitioners.
@@
 Such explanations may be valid or not, but even if valid, an effect is typically of less general interest the more specific circumstances it requires to appear.
-To attenuate the risk of heated discussions on the (non)existence of an effect, original authors may wish to consider pre-specifying the degree of heterogeneity that would make they themselves lose interest in the effect (e.g., by declaring 'constraints on generality' [@10.1177/1745691617708630].
+To attenuate the risk of heated discussions on the (non)existence of an effect, original authors may wish to consider pre-specifying the degree of heterogeneity that would make even them lose interest in the effect (e.g., by declaring 'constraints on generality' [@10.1177/1745691617708630].
 To conclude, heterogeneity or its absence provides vital information for the implementation of research in practice, the advancement of theory, and the interpretation of research outcomes.
@@
 Heterogeneity also affects meta-analytic techniques used to statistically summarize findings on a certain topic.
-Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [@10.1177/1745691616662243; 10.1037/met0000025; 10.1177/1745691616650874], which is problematic considering widespread publication bias [@10.1007/s11192-011-0494-7] and its impact on meta-analytic estimates.
+Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [@10.1177/1745691616662243; @10.1037/met0000025; @10.1177/1745691616650874], which is problematic considering widespread publication bias [@10.1007/s11192-011-0494-7] and its impact on meta-analytic estimates.
 In addition, heterogeneity alters the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity), though one may question the usefulness of interpreting the average true effect size in the presence of heterogeneity [@Simonsohn2017], just as it may be questionable to interpret an average main effect in the context of an interaction effect [@Aiken1991].
@@
 It is a commonly believed that heterogeneity is the norm in psychology.
-In support of this notion, recent large scale reviews of meta-analyses in psychology [@Stanley2017; @10.5334/jopd.33a] report median heterogeneity levels that can best be described as 'large' (@10.1136/bmj.327.7414.557; see next paragraph).
+In support of this notion, recent large scale reviews of meta-analyses in psychology [@Stanley2017; @10.5334/jopd.33] report median heterogeneity levels that can best be described as 'large' [see next paragraph; @10.1136/bmj.327.7414.557].
 In comparison, the median heterogeneity estimate in medicine [@10.1136/bmj.39343.408449.80] would be considered 'small' by the same standard.
 It may simply be that effects in psychology are more heterogeneous than those of medicine.
-However, meta-analyses in psychology also typically include more studies than those in medicine, and it could be that they tend to include studies from a much broader spectrum than meta-analyses in medicine.
-The median number of studies (effects) per meta-analysis in the psychology sample of @10.5334/jopd.33a was 12, whereas in the medicine it is only 3 [@10.1186/1471-2288-11-160].
-It is difficult to separate these explanations (intrinsically more heterogeneity, or psychology simply including studies from a broader spectrum).
+However, meta-analyses in psychology also typically include more studies than those in medicine, and it could be that they tend to include studies from a much broader spectrum.
+The median number of studies (effects) per meta-analysis in the psychology sample of @10.5334/jopd.33 was 12, whereas in medicine it is only 3 [@10.1186/1471-2288-11-160].
+It is difficult to separate these explanations (intrinsically more heterogeneity, or psychology simply including studies from a broader spectrum?).
 To facilitate doing so, in this paper we focus on meta-analyses of only direct replications, which are exempt from the potential problem of including too disparate studies.
-In reference to meta-analyses of direct replications, several authors [@10.1177/1745691616662243; @Tackettt2017] have argued that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol [such as @10.1027/1864-9335/a000178].
+In reference to meta-analyses of direct replications, several authors [@10.1177/1745691616662243; @Tackett2017] have argued that if we were to expect heterogeneity to be absent or minimal anywhere, it would be in pre-registered multi-lab projects with a common protocol [such as @10.1027/1864-9335/a000178].
 They further argue that the fact that heterogeneity has been reported even under such circumstances is an indication of widespread heterogeneity in psychology.
-However, even in the case of multi-lab direct replication projects, studies still vary on two contextual factors (sample population and settings) and if we believe an effect is sensitive to changes in these two factors we might also expect to find some heterogeneity.
+However, even in the case of multi-lab direct replication projects, studies will still vary on two contextual factors (sample population and settings) and if we believe an effect is sensitive to changes in these two factors we might also expect to find some heterogeneity.
 
@@
 Tests of heterogeneity typically have low statistical power in many practical situations [@10.1002/sim.2481; @10.1037/1082-989X.11.2.193].
-This complicates the discussion of heterogeneity, because while $I^2$ always provides an estimate of heterogeneity, this estimate is often accompanied by wide confidence intervals [@10.1136/bmj.39343.408449.80"].
+This complicates the discussion of heterogeneity, because while $I^2$ always provides an estimate of heterogeneity, this estimate is often accompanied by wide confidence intervals [@10.1136/bmj.39343.408449.80].
 For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with $I^2$ point estimates of 0% had upper 95% confidence intervals that exceeded 33%, exceeding what @10.1136/bmj.327.7414.557 defined as 'small' heterogeneity.
@@
 ```
+
 **Note.** R = square root of the multiplied reliabilities. Rho = true effect size. Code to reproduce table: osf.io/kf6pt/
@@
 We refer to relevant files on OSF using brackets and links in the sections below, that is (osf.io/XXXX/).
-We ran all analyses using R version 3.4.3 [@RcoreTeam2017].
+We ran all analyses using R version 3.4.3 [@RCoreTeam2017].
 
@@
 We simulated the distribution of $I^2$ for correlation, standardized mean difference, and mean difference effect size measures.
-Because the standard error of the observed effect size in case of odds ratios and risk differences is strongly affected by assumptions of the probability of success in both treatment groups, we did not directly simulate the I^2 distribution for these effect size measures.
+Because the standard error of the observed effect size in case of odds ratios and risk differences is strongly affected by assumptions of the probability of success in both treatment groups, we did not directly simulate the $I^2$ distribution for these effect size measures.
 In these cases, we used the information on study sample sizes and treated the effects as mean differences in our simulations.
 
-As our concern was of heterogeneity, for convenience we set the true effect size to zero in our simulations.
-This does not affect the results for correlations or mean differences as estimates of effect size and heterogeneity for these measures are statistically independent, and was expected to have negligible effect on the results for standardized mean differences because while these estimates of effect size are positively correlated to their standard errors, the within study variance $\sigma^2$ was kept constant across studies.
-[Marcel/Jelte: Not sure this paragraph is correct, because my grasp of the mathematics is a bit tenuous].
+As our concern was heterogeneity, for convenience we set the true effect size to zero in our simulations.
+This should not affect the results for correlations or mean differences, as estimates of effect size and heterogeneity for these measures are statistically independent.
+For standardized mean differences we expect negligible effects on the results, because while these estimates of effect size are positively correlated to their standard errors, the within study variance $\sigma^2$ was kept constant across studies.
 Nonetheless, as a sensitivity test we also ran the analysis with 'medium' effect sizes [@Cohen1988], see Appendix A (osf.io/bsjhu/).
@@
 First, we randomly sampled K Fisher-transformed true correlations $\rho_k$ from a normal distribution with mean 0 and heterogeneity (variance) $\tau^2$.
-Fisher's z-transformation is a normalizing correlation transformation that ranges from negative infinity to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [@10.2307/2331838; Fisher1921].
+Fisher's z-transformation is a normalizing correlation transformation that ranges from negative infinity to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [@10.2307/2331838; @Fisher1921].
 Second, for each of the K true Fisher-transformed correlations we sampled one Fisher-transformed observed correlation from a normal distribution with mean $\rho_k$ and variance $1 /(N_k - 3)$.
@@
 
-To approximate the statistical power of all 37 effects at zero, small, medium, and true effect size we continued as follows.
-For each of the 37 effects we selected the values of $\tau$ which yielded the average value of I^2 in the simulations closest to .25 (small), .50 (medium), and .75 (large).
+To approximate the statistical power of all 37 effects at zero, small, medium, and large heterogeneity we continued as follows.
+For each of the 37 effects we selected the values of $\tau$ which yielded the average value of $I^2$ in the simulations closest to 25 (small), 50 (medium), and 75 (large).
 For these values of $\tau$ and for $\tau = 0$ (homogeneity) we again ran 10,000 simulations, and for each run $I^2$ was calculated and the Q-test of heterogeneity was performed, yielding estimates of type I error (in case of homogeneity) and power (for heterogeneity) for each of the 37 effects.
@@
 
-To examine the correlation between effect size and $I^2$ across all 37 effects we converted all effect sizes to a common metric (osf.io/h9pft/).
-We first converted all effects into correlations (r) and used the R-package metafor to estimate $I^2$ and meta-analytic effects expressed as Fisher-transformed correlations (osf.io/zuwpg/).
+To examine the correlation between effect size and $I^2$ across all 37 effects we converted all effect sizes to a common metric.
+We first converted all effects into correlations (osf.io/h9pft/) and used the R-package metafor to estimate $I^2$ and meta-analytic effects expressed as Fisher-transformed correlations (osf.io/zuwpg/).
 In doing so, we fitted random-effects models with metafor's default REML estimator.
@@
 232) and then finally to a correlation.
-All formulas used are presented in Appendix B (osf.io/h4vfx/) [appendix not created yet, hence no link].
+All formulas used are presented in Appendix B (osf.io/h4vfx/).
 Since $I^2$ is set to zero for the majority of cases under homogeneity (i.e., truncated), we also correlated effect size with the closely related heterogeneity estimate $H^2$ [@10.1002/sim.1186] as a sensitivity analysis.
-The H2 index is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - $I^2$)$ for $I^2 \geq 0$.
+The $H^2$ index is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - $I^2$)$ for $I^2 \geq 0$.
 It ranges from zero to positive infinity, where a larger score indicates more heterogeneity, a score of one indicates homogeneity, and a score between zero and one thus indicates 'excessive' homogeneity.
@@
 RP = Replication Project, k = no.
-primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of $I^2$ 95\\% confidence interval, ci.ub = upper bound of $I^2$ 95\\% confidence interval.
+primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of $I^2$ 95% confidence interval, ci.ub = upper bound of $I^2$ 95% confidence interval.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-Under simulated heterogeneity, Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\%) respectively.
+Under simulated heterogeneity, Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75%) respectively.
 Code to reproduce table: osf.io/kf6pt/
@@
 There is limited evidence for widespread heterogeneity across the examined effects.
-Of the 37 effects,  4/37 (11%) have $I^2$ estimates that best correspond to large heterogeneity ($I^2$ = 75%), 4/37 (11%) to medium heterogeneity ($I^2$ = 50%), 9/37 (24%)  to small heterogeneity ($I^2$ = 25%) and 17/37 (54%) to zero heterogeneity ($I^2$ = 0%).
+Of the 37 effects, `r sum(het$s_I2 >= 62.5)` / `r nrow(het)` (`r 100*round(sum(het$s_I2 >= 62.5) / nrow(het), digits = 2)`%) have $I^2$ estimates that best correspond to large heterogeneity ($I^2$ = 75%), `r sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5) / nrow(het), digits = 2)`%) to medium heterogeneity ($I^2$ = 50%), `r sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5) / nrow(het), digits = 2)`%)  to small heterogeneity ($I^2$ = 25%) and `r sum(het$s_I2 < 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 12.5) / nrow(het), digits = 2)`%) to zero heterogeneity ($I^2$ = 0%).
 However, despite a relatively large number of studies and total sample size for most projects (see Table 2), Table 3 shows very wide confidence intervals (spanning 50% or more) for many effects.
-The lower bound $I^2$ confidence interval excludes zero for only 7/37 effects (19%; Table 3), all part of the ML1 project.
-The percentage of heterogeneity estimates larger than 0 (23/37; 62%) suggests heterogeneity for at least some effects, as this percentage is higher than the expected frequency of non-zero estimates under homogeneity (46%, or about 17/37), based on the chi-square distribution and average k across projects.
+The lower bound $I^2$ confidence interval excludes zero for only `r sum(het$s_ci.lb > 0)`/`r nrow(het)` effects (`r 100*round(sum(het$s_ci.lb > 0) / nrow(het), digits = 2)`%; Table 3), all part of the ML1 project.
+The percentage of heterogeneity estimates larger than 0 (`r sum(het$s_I2 > 0)`/`r nrow(het)`; `r 100*round(sum(het$s_I2 > 0) / nrow(het), digits = 2)`%, two effects had $I^2$ < .005 and are rounded down in Table 3) suggests heterogeneity for at least some effects, as this percentage is higher than the expected frequency of non-zero estimates under homogeneity (46%, or about 17/37), based on the chi-square distribution and average k across projects.
 
@@
 For example, the three bottom lines all belong to RRR3, the replication project with the lowest number of included studies (12; see Table 3).
-Since the between studies variance is not measured on the same scale when using different effect size measures, estimates are not directly comparable across effect size measures.
+Since the between studies variance is not measured on the same scale when using different effect size measures, estimates are not directly comparable across effect types.
 
@@
 In all cases the type I error is conservative, as compared to the expected 5% error rate.
-Power to detect small heterogeneity was low, ranging between 18% (Professor priming) and  45% (Flag priming), with an average of 28%.
-Power to detect medium heterogeneity was generally good, with an average of 79% power, but was only around 60% for several effects with low K.
+Power to detect small heterogeneity was low, ranging between `r 100*round(min(het$small), digits = 2)`% and `r 100*round(max(het$small), digits = 2)`%, with an average of `r 100*round(mean(het$small), digits = 2)`%.
+Power to detect medium heterogeneity was generally very good, with an average of `r 100*round(mean(het$medium), digits = 2)`% power, but goes down to as low as `r 100*round(min(het$medium), digits = 2)`% for several effects with low K.
 Power to detect strong heterogeneity was excellent across the board.
-To conclude, even though for most projects the number of included studies (median 23) and total number of participants (median 102 per study) was relatively large, only power to detect medium or larger heterogeneity was good to excellent, whereas power to detect small heterogeneity was unacceptably low.
+To conclude, even though for most projects the number of included studies (median `r quantile(sort(het$k), .5)[[1]]`) and number of participants (median 102 per study) was relatively large, only power to detect medium or larger heterogeneity was good to excellent, whereas power to detect small heterogeneity was unacceptably low.
 Hence, even large multi-lab projects struggle to distinguish zero from small heterogeneity.
@@
 In particular, the dispersion of the distribution under small heterogeneity is illustrative of the low power to be expected under such circumstances.
-Given histogram of observed effect sizes and the densities of the distributions (height of the curves), the majority of observed effects are most likely to have zero or zero to small heterogeneity.
+Given the histogram of observed effect sizes and densities of the distributions (height of the curves), the majority of observed effects are most likely to have zero or zero to small heterogeneity.
 Only two effects appear to be of medium heterogeneity and three of large.
@@
 
-We examined the evidence for widespread heterogeneity in psychology and the correlation between effect size and heterogeneity, in sample of ten pre-registered multi-lab replication projects in psychology.
+We examined the evidence for widespread heterogeneity in psychology and the correlation between effect size and heterogeneity, in a sample of ten pre-registered multi-lab replication projects in psychology.
 These ten projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
 To aid interpretation we also estimated power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557 and plotted the distributions of $I^2$ under these four heterogeneity levels.
-Our results showed that most effects in our sample likely had zero to small heterogeneity, that power to distinguish between zero and small heterogeneity was remarkably low for all projects, and that heterogeneity was strongly correlated with effect size in our sample.
+Our results showed that most effects in our sample likely had zero to small heterogeneity, that power to distinguish between zero and small heterogeneity was low for all projects, and that heterogeneity was strongly correlated with effect size in our sample.
 
 There is little evidence for widespread heterogeneity amongst current pre-registered multi-lab replication projects in psychology.
-Across ten projects, only 7/37 (19%) of primary outcomes had confidence intervals that excluded zero heterogeneity, and given the distributions of $I^2$ under zero to large heterogeneity, most (32/37; 86%) effects appeared to have zero or small heterogeneity.
+Across ten projects, only `r sum(het$s_ci.lb > 0)`/`r nrow(het)` (`r 100*round(sum(het$s_ci.lb > 0) / nrow(het), digits = 2)`%) of primary outcomes had confidence intervals that excluded zero heterogeneity, and given the distributions of $I^2$ under zero to large heterogeneity, most (32/37; 86%) effects appeared to have zero or small heterogeneity.
 Moreover, while each replication of an effect only varied on two contextual factors (sampling population and settings), the effects that showed significant evidence for heterogeneity were primarily effects that might have been expected to be sensitive to changes in sampling population.
@@
 That heterogeneity is small is not the same as being negligible, as even small heterogeneity may have large consequences at the aggregated level of an intervention, or at the individual level for a few people.
-Yet, power to detect small heterogeneity was on average only 28% in our sample.
+Yet, power to detect small heterogeneity was on average only `r 100*round(mean(het$small), digits = 2)`% in our sample.
 A suggestion to double the already very impressive number of participating labs and individuals of the largest replication projects in our sample seems unrealistic even for methodologists.
 It may simply be that the $I^2$ index as a measure of heterogeneity is inadequate to examine small levels of heterogeneity.
-The good news is that sufficient power to detect large and, to a lesser degree, medium heterogeneity is realistically achievable for many meta-analyses.
+The good news is that sufficient power to detect large and medium heterogeneity is realistically achievable for many meta-analyses.
 
 Heterogeneity amongst the studied effects was strongly associated with effect size.
-There are thus both good theoretical reasons, related to measurement reliability of estimates, and empirical reasons to expect larger effect sizes to exhibit comparatively more heterogeneity when using observed effect sizes in a meta-analysis.
+There are thus both good theoretical reasons, related to the measurement reliability of estimates, and empirical reasons to expect larger effect sizes to exhibit comparatively more heterogeneity when using observed effect sizes in a meta-analysis.
 This creates challenges in disentangling the roots of heterogeneity.
@@
 We recognize that not all measurements (e.g., behavioral) admit adjusting for reliability as easily as questionnaires, meaning a correlation between effect size and heterogeneity could at times be difficult to control for.
-Nonetheless, the extensive use of scales in psychology means that for many meta-analysts there should be little reason not to control for measurement reliability when aggregating results.
+Nonetheless, the extensive use of different scales in psychology means that for many meta-analysts there should be little reason not to control for measurement reliability when aggregating results.
 
@@
 
-Our results and the limitations of our data provides some guidance in directions of future research.
+Our results and the limitations of our data provide some guidance in directions of future research.
 To fully establish whether zero to small heterogeneity is the standard for direct replications in psychology, as suggested by our results, it would be desirable to examine heterogeneity in a larger sample of meta-analyses of direct replications than the 37 examined here.
 We are enthusiastic about the possibilities to do so in the near future, thanks to the many ongoing multi-lab initiatives in psychology (Registered Replication Reports, Many Labs 2, ManyBabies, the Psych Science Accelerator).
-Relatedly, a larger sample of effects would enable testing whether the correlation between heterogeneity and effect size is generally as remarkably strong as we found in our sample, or if it was an artifact of the data.
+Relatedly, a larger sample of effects would enable testing whether the correlation between heterogeneity and effect size is generally as strong what as we found in our sample.
 Moreover, it may be worthwhile to attempt to disentangle the contribution of reliability to this correlation from other aspects of measurement that are likely to contribute, such as range restrictions [@Schmidt2015].
@@
 
-To conclude, in the arguably best meta-analytic data currently available in psychology, most effects had zero to small heterogeneity, and heterogeneity was strongly correlated with effect size.
+To conclude, in the arguably best meta-analytic data currently available in psychology, most effects likely had zero to small heterogeneity, and heterogeneity was strongly correlated with effect size.
 Despite a relatively large number of studies and participants in each meta-analysis, power was too low to distinguish between zero and small heterogeneity in all cases.

### 2018-07-08 code/power_simulation.r
Minor correction power simulation sensitivity code

@@ -162,7 +162,7 @@ system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progr
 # system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
   # res_a[[e]] <- simulate_I2(dat2[[e]], reps = 1, tau = tau_values, effect_size = "medium") #NB! 1000 reps here is about 24 hours on my (fairly slow) machine
   # cat("...RS",e, "/37") #see progress
-  # if (e%%5 == 0 | e == 37) saveRDS(res_a, "../data/AppendixA_tau_simulation_results.RDS") #save ocassionally and at finish
+  # if (e%%5 == 0 | e == 37) saveRDS(res_a, "../data/appendixA_tau_simulation_results.RDS") #save ocassionally and at finish
 # })
 #********************
 
@@ -225,7 +225,7 @@ system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progr
   # res2_a[[e]] <- simulate_I2(dat5[[e]][[1]], reps = 1e4,
                            # tau = c(0, dat5[[e]][[2]]), effect_size = "medium") #NB! 1e4 reps here is about 9.5 hours on my (fairly slow) machine
   # cat("...RS",e, "/37") #see progress
-  # if (e%%5 == 0 | e == 37) saveRDS(res2_A, "../data/AppendixA_power_simulation_results.RDS") #save ocassionally and at finish
+  # if (e%%5 == 0 | e == 37) saveRDS(res2_a, "../data/appendixA_power_simulation_results.RDS") #save ocassionally and at finish
 # })
 #********************
 

### 2018-07-08 writing/appendixA-heterogeneity.rmd
Added results for simulation sensitivity check of effect size

@@
   tidyr::spread(key = tau_index, value = power) %>% #prep for table
-  rename(zero = '1', small = '2', medium = '3', large = '4') %>% 
-  select(-effect)
+  rename(Zero = '1', Small = '2', Medium = '3', Large = '4', Effect = effect)
 
@@
   tidyr::spread(key = tau_index, value = power) %>% #prep for table
-  rename(zero = '1', small = '2', medium = '3', large = '4')
+  rename(Zero = '1', Small = '2', Medium = '3', Large = '4') %>% 
+  select(-effect)
 
@@
 medium are shown for each effect in Table A1.
-In both cases type I error is consistently conservative, as compared to the expected 5% error rate.
-With a an effect size of zero, average power was `r 100*round(mean(zero$small), digits = 2)`/`r 100*round(mean(zero$medium), digits = 2)`/`r 100*round(mean(zero$large), digits = 2)`% for small/medium/large heterogeneity respectively.
-The corresponding power with an average effect size was `r 100*round(mean(zero$small), digits = 2)`, `r 100*round(mean(zero$medium), digits = 2)`, and `r 100*round(mean(zero$large), digits = 2)`%.
-To conclude, changing true effect size in our simulations from zero to medium has little impact on estimated type I error and power.
+In both cases type I error is approximately nominal, as compared to the expected 5% error rate.
+With a an effect size of zero, average power was `r 100*round(mean(zero$Small), digits = 2)`%/`r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`% for small/medium/large heterogeneity respectively.
+The corresponding power with an average effect size was `r 100*round(mean(zero$Small), digits = 2)`%/ `r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`%.
+To conclude, changing true effect size in our simulations from zero to medium had little to no impact on estimated type I error and power.
 
@@
 
-_Type I error and power for data with a true effect size of zero vs. 'medium'_
+_Type I error and power to detect four heterogeniety levels under two true effect sizes_
 
@@
 **Note.** Column headers indicate the degree of simulated heterogeneity where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75%) respectively.
+Medium effect size is as defined by Cohen (1988).
 Code to reproduce table: osf.io/bsjhu/

### 2018-07-08 writing/draft-heterogeneity.rmd
Added results for simulation sensitivity check of effect size

@@
 footnotelist      : no
-lineno            : no
+lineno            : yes
 
@@
 For standardized mean differences we expect negligible effects on the results, because while these estimates of effect size are positively correlated to their standard errors, the within study variance $\sigma^2$ was kept constant across studies.
-Nonetheless, as a sensitivity test we also ran the analysis with 'medium' effect sizes [@Cohen1988], see Appendix A (osf.io/bsjhu/).
+As a sensitivity test we ran the analysis with 'medium' effect sizes [@Cohen1988] and found the same average power at the different heterogeneity levels, see Appendix A (osf.io/bsjhu/).
 
@@
 Estimated type I error and power for zero/small/medium/large heterogeneity are shown for each effect in Table 3.
-In all cases the type I error is conservative, as compared to the expected 5% error rate.
+In all cases the type I error is approximately nominal, as compared to the expected 5% error rate.
 Power to detect small heterogeneity was low, ranging between `r 100*round(min(het$small), digits = 2)`% and `r 100*round(max(het$small), digits = 2)`%, with an average of `r 100*round(mean(het$small), digits = 2)`%.

### 2018-07-10 code/tables.rmd
Updated draft and associated files

@@
 title: "Tables"
-author: "Anton Ohlsson Collentine"
+author: "Limited evidence for widespread heterogeneity in psychology"
 output: pdf_document
@@
 
-diff_row <- data.frame(rel = "Standard deviation", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))
+diff_row <- data.frame(rel = "Standard deviation R", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))
 
@@
 
-het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "Rho = 0", "Rho = .3", "Rho = .5"), digits = 2) %>% 
+het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("Effect size", "Rho = 0", "Rho = .3", "Rho = .5"), digits = 2) %>% 
   kable_styling(position = "left") %>% 
@@
   footnote(threeparttable = TRUE, escape = FALSE,
-           general = " Effects were estimated in metafor using REML.
+           general = "Effects were estimated in metafor using REML.
 The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs.

### 2018-07-10 writing/draft-heterogeneity.rmd
Updated draft and associated files

@@
   - id            : "1"
-    institution   : "Tilburg University"
+    institution   : "Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, the Netherlands"
   - id            : "2"
-    institution   : "Utrecht University"
+    institution   : "Department of Sociology, Faculty of Social and Behavioural Sciences, Utrecht University, the Netherlands"
 
 abstract: |
-  We examined the evidence for heterogeneity (of effect sizes) and explored the correlation between heterogeneity and effect size in a sample of ten pre-registered multi-lab replication projects in psychology (Many Labs 1 & 3, Registered Replication Reports 1 to 8).
-Across the 37 main outcomes of these projects we found limited heterogeneity, only 4/37 (11%) effects had significant heterogeniety and the majority (32/37; 86%) were most likely to have zero to small heterogeneity.
-Power to detect small heterogeneity, as defined by @10.1136/bmj.327.7414.557, was for all projects very low (mean 36%), but good to excellent for medium and large heterogeneity.
-We saw a strong correlation between observed effect size and heterogeneity in our sample (R^2^ = .61).
+  We examined the evidence for heterogeneity (of effect sizes) and explored the correlation between heterogeneity and effect size in a sample of 37 effect sizes from ten pre-registered multi-lab replication projects in psychology.
+We found limited heterogeneity; only 4/37 (11%) effects had significant heterogeneity, and most effects (32/37; 86%) were most likely to have zero to small heterogeneity.
+Power to detect small heterogeneity, was low for all projects (mean 36%), but good to excellent for medium and large heterogeneity.
+As anticipated, we found a strong correlation between observed effect size and heterogeneity in our sample (R^2^ = .61).
 Our results suggest that an association between heterogeneity and effect size may need to be considered when estimating heterogeneity, and a lack of evidence to indicate widespread heterogeneity in psychology.
@@
 keywords          : "heterogeneity, meta-analysis, replication, psychology, many labs, registered replication reports"
-wordcount         : "146"
+wordcount         : "128"
 
@@
 First, belief in the existence of an effect is established.
-Second, the effect's generalizability is examined by exploring its boundary conditions.
+Second, the effect's generalizability is examined by exploring its boundary conditions [@10.1177/1745691617708630].
 In the first stage, inferential statistics are used  to minimize the risk that a discovery is due to sampling error.
-In the second stage, one may ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [@Campbell2015].
+In the second stage, one may ask to what extent the effect depends on a particular choice of four contextual factors; the 1) sample population, 2) settings, 3) treatment variables and 4) measurement variables [e.g., @Campbell2015].
 This extent is often explored through replications of the original study that are either as similar as possible to the original (called 'direct' or 'exact' replications) or with some deliberate variation on conceptual factors [so-called 'conceptual' or 'indirect' replications; @10.1017/S0140525X17001972], and once sufficient studies have accumulated through meta-analysis.
@@
 This is readily evident for medicine, where in the case of heterogeneity an intervention, such as a medication, that is successful for some may have direct negative health consequences for others.
-The same is true of mental health interventions in psychology, but heterogeneity can also have major consequences for topics such as child development, education, and business performance, where psychological research often impacts policy recommendations.
+The same is true of mental health interventions in psychology, but heterogeneity can also have major consequences for topics such as child development, education, and business performance, where research often impacts policy recommendations.
 Thus, heterogeneity should be no less of a concern for psychologists than for medical practitioners.
@@
 Second, unaccounted for heterogeneity is an indication of incomplete theory, since it suggests that a theory is unable to predict all contextual factors of importance to its claims.
-As such, heterogeneity might imply previously unknown predictors, so called 'hidden moderators' [@10.2139/ssrn.2820883], the discovery of which can be seen as an opportunity for theoretical advancement [@Tackett2017].
+As such, heterogeneity might imply previously unknown predictors, so called 'hidden moderators' [@10.2139/ssrn.2820883], the discovery of which can be seen as an opportunity for theoretical advancement [@Tackett2017; @10.1177/1745691617708630].
 
 Third, the possibility of heterogeneity can create controversy in the interpretation of replication results.
-The proclamation of a  'failure' to replicate an effect is sometimes taken to imply that the original find was merely a statistical fluke, due to 'p-hacking' [@10.1177/0956797611417632] or publication bias [@10.2139/ssrn.2659409].
-Unsurprisingly, some researchers take offense [e.g., @10.1016/j.jesp.2016.02.003].
+The proclamation of a 'failure' to replicate an effect is sometimes taken to suggest that the original finding was merely a statistical fluke, due to 'p-hacking' [@10.1177/0956797611417632] or publication bias [@10.2139/ssrn.2659409].
+Unsurprisingly, some researchers take offense [e.g., @10.1016/j.jesp.2016.02.003], interpreting such implications as attacks on their abilities as researchers.
 An alternative explanation for non-replication, often espoused by the original authors [e.g, @10.2139/ssrn.2698810; @10.1177/1745691616674460], is that the effect is more heterogeneous than (perhaps implicitly) claimed originally.
 Such explanations may be valid or not, but even if valid, an effect is typically of less general interest the more specific circumstances it requires to appear.
-To attenuate the risk of heated discussions on the (non)existence of an effect, original authors may wish to consider pre-specifying the degree of heterogeneity that would make even them lose interest in the effect (e.g., by declaring 'constraints on generality' [@10.1177/1745691617708630].
+To attenuate the risk of heated discussions on the (non)existence of an effect, original authors are recommended to consider pre-specifying the degree of heterogeneity that would make even them lose interest in the effect (e.g., by declaring 'constraints on generality' [@10.1177/1745691617708630].
 To conclude, heterogeneity or its absence provides vital information for the implementation of research in practice, the advancement of theory, and the interpretation of research outcomes.
@@
 Heterogeneity also affects meta-analytic techniques used to statistically summarize findings on a certain topic.
-Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [@10.1177/1745691616662243; @10.1037/met0000025; @10.1177/1745691616650874], which is problematic considering widespread publication bias [@10.1007/s11192-011-0494-7] and its impact on meta-analytic estimates.
+Techniques that attempt to correct for publication bias in their estimate tend to fail in the presence of heterogeneity [@10.1177/1745691616662243; @10.1037/met0000025; @10.1177/1745691616650874], which is problematic considering the supposedly widespread publication bias [@10.1007/s11192-011-0494-7] and its impact on meta-analytic estimates.
 In addition, heterogeneity alters the interpretation of meta-analytic estimates as either _the_ true effect size (under homogeneity) or the average of the true effect sizes (under heterogeneity), though one may question the usefulness of interpreting the average true effect size in the presence of heterogeneity [@Simonsohn2017], just as it may be questionable to interpret an average main effect in the context of an interaction effect [@Aiken1991].
@@
 It may simply be that effects in psychology are more heterogeneous than those of medicine.
-However, meta-analyses in psychology also typically include more studies than those in medicine, and it could be that they tend to include studies from a much broader spectrum.
+However, meta-analyses in psychology also typically include more studies than those in medicine, and it could be that they tend to include studies from a much broader spectrum, that is, varying on more contextual factors (sample population, settings, treatment variables, measurement variables) or varying more on these four factors.
 The median number of studies (effects) per meta-analysis in the psychology sample of @10.5334/jopd.33 was 12, whereas in medicine it is only 3 [@10.1186/1471-2288-11-160].
-It is difficult to separate these explanations (intrinsically more heterogeneity, or psychology simply including studies from a broader spectrum?).
+It is difficult to separate these explanations (intrinsically more heterogeneity, or psychology including studies from a broader spectrum?).
 To facilitate doing so, in this paper we focus on meta-analyses of only direct replications, which are exempt from the potential problem of including too disparate studies.
@@
 One problem lies in the assessment of heterogeneity and its inherent uncertainty.
-Heterogeneity is often measured by the $I^2$ index [@10.1002/sim.1186;  @10.1136/bmj.327.7414.557], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
+Heterogeneity is often measured by the _I^2^_ index [@10.1002/sim.1186;  @10.1136/bmj.327.7414.557], which allows comparison of estimates across meta-analyses and has an intuitive interpretation.
 It can be interpreted as the percentage of variability in observed effect sizes in a meta-analysis that is due to heterogeneity amongst the true effects (that is, sensitivity to contextual factors) rather than sampling variance, and ranges from 0-100%.
-The $I^2$ index is a transformation of the well-known Q-test of heterogeneity in meta-analysis [@10.2307/3001666] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative $I^2$ is set to zero.
-@10.1136/bmj.327.7414.557 tentatively defined $I^2$-values of 25, 50, and 75% as small/medium/large heterogeneity respectively.
+The _I^2^_ index is a transformation of the well-known Q-test of heterogeneity in meta-analysis [@10.2307/3001666] by taking $[Q - (k - 1)] / Q \times 100$%, where k is the number of studies included in the meta-analysis and a negative _I^2^_ is set to zero.
+@10.1136/bmj.327.7414.557 tentatively defined _I^2^_-values of 25, 50, and 75% as small/medium/large heterogeneity respectively, labels we also use un this paper.
+
 Tests of heterogeneity typically have low statistical power in many practical situations [@10.1002/sim.2481; @10.1037/1082-989X.11.2.193].
-This complicates the discussion of heterogeneity, because while $I^2$ always provides an estimate of heterogeneity, this estimate is often accompanied by wide confidence intervals [@10.1136/bmj.39343.408449.80].
-For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with $I^2$ point estimates of 0% had upper 95% confidence intervals that exceeded 33%, exceeding what @10.1136/bmj.327.7414.557 defined as 'small' heterogeneity.
-In addition, under homogeneity $I^2$ has a central chisquare distribution [@10.1186/s12874-015-0024-z], a distribution that is right-skewed with more than 40% of observations falling above the expected value (for all k > 4).
-In other words, even in the absence of heterogeneity, a meta-analysis of 5 or more studies will have an $I^2$ point estimate above zero in more than 40% of cases.
+This complicates the discussion of heterogeneity, because while _I^2^_ always provides an estimate of heterogeneity, this estimate is often accompanied by wide confidence intervals [@10.1136/bmj.39343.408449.80].
+For example, Ioannidis reports that in a large set of Cochrane meta-analyses, all meta-analyses with _I^2^_ point estimates of 0% had upper 95% confidence intervals that exceeded _I^2^_ estimates of 33%, exceeding what @10.1136/bmj.327.7414.557 defined as 'small' heterogeneity.
+In addition, under homogeneity _I^2^_ has a central chisquare distribution [@10.1186/s12874-015-0024-z], a distribution that is right-skewed with more than 40% of observations falling above the expected value (for all k > 4).
+In other words, even in the absence of true heterogeneity, a meta-analysis of 5 or more studies will have an _I^2^_ point estimate above zero in more than 40% of cases.
 Heterogeneity estimates may thus be congruent with a wide range of true heterogeneity levels.
-Despite exhortations to the contrary [@10.1136/bmj.39343.408449.80], it remains common to omit confidence intervals in the reporting of $I^2$.
+Despite exhortations to the contrary [@10.1136/bmj.39343.408449.80], it remains common to omit confidence intervals in the reporting of _I^2^_.
 In consideration of such uncertainty and the prevalent belief that heterogeneity is the norm in psychology, we examine the existing evidence for heterogeneity in psychology using a sample of pre-registered multi-lab direct replication projects.
+
+###Association between effect size and heterogeneity
 
@@
 To illustrate, consider a meta-analysis of say, the correlation between neuroticism and procrastination.
-Each included study would need to measure the two variables somehow, possibly the same way across studies.
-However, because of individual differences and differences in study samples, measurement reliabilities may differ across studies either due to sampling variance (that the sample happens to be more or less homogeneous) or to differences in contextual factors (e.g., sampling population, method of measurement).
+Each included study would need to measure the two variables somehow, possibly the same way across studies in the meta-analysis.
+However, because of individual differences and differences in study samples, measurement reliabilities may differ across studies either due to sampling variance (that the sample happens to be more or less homogeneous) or to differences in contextual factors (e.g., sampling population, measurement variables).
 This means that even if the underlying true effect size is the same, the observed correlation between the two variables will differ between studies [see also @Schmidt2015].
@@
 As such, keeping constant study differences in $\sqrt{R_{xx'}} \times \sqrt{R_{yy'}}$ while increasing true effect size $\rho_{xy}$ increases the observed differences between studies, thereby increasing heterogeneity of observed effect sizes (see Table 1).
-We explore the association between effect size and heterogeneity in a sample of pre-registered multi-lab replication projects in psychology.
+We therefore explore with a meta-meta-analysis if a positive association exists between effect size and heterogeneity in the sample of pre-registered multi-lab replication projects in psychology.
 
@@
 
-het_demo %>% knitr::kable(col.names = c("", "Rho = 0", "Rho = .3", "Rho = .5"), digits = 2)
+het_demo %>% knitr::kable(col.names = c("Effect size", "Rho = 0", "Rho = .3", "Rho = .5"), digits = 2)
 
@@
 
-We examine the evidence for widespread heterogeneity in psychology and explore the correlation between effect size and heterogeneity, using ten pre-registered multi-lab replication projects in psychology (Table 2).
-These ten projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
-To better interpret the heterogeneity estimates we also estimate power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557.
-Consequently, our analyses will provide information on how two contextual factors (sample population and settings) may affect consistency or heterogeneity of effects in psychology.
+Table 2 lists the ten replication projects, with a total of 37 primary outcome variables, we used to examine heterogeneity and the correlation between effect size and heterogeneity in psychology.
+As all ten projects were (relatively) large-scale and pre-registered, our dataset arguably represents the best, least biased, meta-analytic data currently available in psychology.
+To better interpret the heterogeneity estimates we also estimate power of each project to find zero/small/medium/large heterogeneity.
+Consequently, our analyses will provide information on how two contextual factors (sample population and settings) may affect consistency or heterogeneity of effects in psychology, and on the precision of its estimate.
 
@@
 All code and data for this project are available on the Open Science Framework (OSF) at osf.io/4z3e7/.
-We refer to relevant files on OSF using brackets and links in the sections below, that is (osf.io/XXXX/).
+We refer directly to relevant files on the OSF using brackets and links in the sections below.
 We ran all analyses using R version 3.4.3 [@RCoreTeam2017].
 
-We downloaded and collated summary data from ten pre-registered multi-lab replication projects in psychology (Table 2).
+We downloaded and collated summary data from the ten pre-registered multi-lab replication projects in psychology (Table 2).
 Data from all ten projects were publicly available on the Open Science Framework (osf.io) and downloaded between 2018/02/01 and 2018/03/31.
@@
 We ran all analyses as specified by the replication authors (osf.io/kf6pt/).
-All effects were estimated with random-effects models and the Restricted Maximum Likelihood (REML) estimator using the R-package metafor [@10.18637/jss.v036.i03], though with a variety of outcome variables: correlations, standardized mean differences, raw mean differences, odds ratios and risk differences.
-ML1 transformed odd ratios into standardized mean differences when meta-analyzing under the assumption that responses followed logistic distributions [@10.1037/1082-989X.8.4.448; @10.18637/jss.v036.i03].
+All effects were estimated with random-effects models and the Restricted Maximum Likelihood (REML) estimator using the R-package metafor [@10.18637/jss.v036.i03], though with a variety of outcome variables: correlations (r), standardized mean differences (SMD), raw mean differences (MD), and risk differences (RD).
+ML1 transformed effects measured as odd ratios into standardized mean differences when meta-analyzing under the assumption that responses followed logistic distributions [@10.1037/1082-989X.8.4.448; @10.18637/jss.v036.i03].
 Two projects (RRR5 and RRR7) used the Knapp and Hartung adjustment of the standard errors [@10.1002/sim.1482] and ML3 correlations were corrected for bias [@10.1037//0021-9010.74.3.469; @10.18637/jss.v036.i03].
 After estimating effects, ML3 transformed correlations into eta-squared for reporting, which we did not.
-For each effect we estimated $I^2$ and its 95% confidence interval.
+For each effect we estimated _I^2^_ and its 95% confidence interval.
 Confidence intervals were calculated in metafor which uses the Q-profile method [@10.1186/1471-2288-14-103].
 
-In order to facilitate interpretation of our results, we estimated type I error and power of the Q-test of heterogeneity for each of the 37 effects under zero/small/medium/large heterogeneity ($I^2$ = 0/25/50/75%  respectively).
-In addition, we plotted $I^2$-distributions across effects at these four heterogeneity levels and compared them with the distribution of the observed $I^2$ estimates of the 37 effects.
-To do so we simulated results for each effect given the number of studies, k, and the sample sizes, $N_k$, of those studies (osf.io/gbf4u/).
-We simulated the distribution of $I^2$ for correlation, standardized mean difference, and mean difference effect size measures.
-Because the standard error of the observed effect size in case of odds ratios and risk differences is strongly affected by assumptions of the probability of success in both treatment groups, we did not directly simulate the $I^2$ distribution for these effect size measures.
-In these cases, we used the information on study sample sizes and treated the effects as mean differences in our simulations.
+In order to facilitate interpretation of our results, we estimated type I error and power of the Q-test of heterogeneity for each of the 37 effects under zero/small/medium/large heterogeneity (_I^2^_ = 0/25/50/75%  respectively).
+In addition, we approximated the probability density function of _I^2^_ across effects at each of these four heterogeneity levels and compared them with the observed frequency distribution of the observed _I^2^_ estimates of the 37 effects.
+Hence, five distributions of _I^2^_ were obtained; four simulated and one observed.
+To do so we simulated results of _I^2^_ for each effect given its number of studies (K), sample sizes of those studies (vector $N_k$), and each of the four heterogeneity levels (osf.io/gbf4u/).
+We directly simulated the distribution of _I^2^_ for correlation, standardized mean difference, and mean difference effect size measures, but not for risk ratios.
+We treated risk ratios as mean differences using the study sample sizes to compute study precision, because treating them as risk ratios would require strong assumptions on the probability of success in both treatment groups, assumptions which would greatly affect the outcomes of the simulation.
+For the same reason we treated the four effects of ML1 which were measured as odds ratios (and then transformed into standardized mean differences) as standardized mean differences.
 
-As our concern was heterogeneity, for convenience we set the true effect size to zero in our simulations.
+As our concern was heterogeneity, for convenience we set the true effect size to zero in our simulations of heterogeneity.
 This should not affect the results for correlations or mean differences, as estimates of effect size and heterogeneity for these measures are statistically independent.
 For standardized mean differences we expect negligible effects on the results, because while these estimates of effect size are positively correlated to their standard errors, the within study variance $\sigma^2$ was kept constant across studies.
-As a sensitivity test we ran the analysis with 'medium' effect sizes [@Cohen1988] and found the same average power at the different heterogeneity levels, see Appendix A (osf.io/bsjhu/).
+As a sensitivity analysis we also ran all analyses assuming 'medium' effect sizes [@Cohen1988] and found the same average power at the different heterogeneity levels, see Appendix A (osf.io/bsjhu/).
 
@@
 First, we randomly sampled K Fisher-transformed true correlations $\rho_k$ from a normal distribution with mean 0 and heterogeneity (variance) $\tau^2$.
-Fisher's z-transformation is a normalizing correlation transformation that ranges from negative infinity to positive infinity, though except for extreme correlations it stays close to the -1 to 1 range [@10.2307/2331838; @Fisher1921].
+Fisher's z-transformation is a normalizing correlation transformation that ranges from negative infinity to positive infinity, though except for extreme correlations it stays within the -1 to 1 range [@10.2307/2331838; @Fisher1921].
 Second, for each of the K true Fisher-transformed correlations we sampled one Fisher-transformed observed correlation from a normal distribution with mean $\rho_k$ and variance $1 /(N_k - 3)$.
-Finally, we fitted a random-effects meta-analysis with REML and estimated $I^2$ for that run.
-In the simulations, we varied the between-studies standard deviation $\tau$ between 0.000 and 0.50 in increments of 0.005, and used 1,000 runs at each step to approximate the distribution of $I^2$ at that value for true heterogeneity.
+Finally, we fitted a random-effects meta-analysis with REML and estimated _I^2^_ for that run.
+In the simulations, we varied the between-studies standard deviation $\tau$ between 0.000 and 0.50 in increments of 0.005, and used 1,000 runs at each step to approximate the distribution of _I^2^_ at that value for true heterogeneity.
 
-For mean differences we assumed a within-study variance of one for both treatment and control groups, $\sigma^2_c = \sigma^2_t = 1$.
+For mean differences (and hence also for risk ratios) we assumed a within-study variance of one for both treatment and control groups, $\sigma^2_c = \sigma^2_t = 1$.
 For each run we then set the population mean of the control condition to 0 and sampled K treatment population means $\mu_k$ from $N(0, \tau)$.
@@
 Group variances were sampled using $s^2_c \sim \chi^2 (n_c - 1) / (n_c - 1)$ and  $s^2_t \sim \chi^2 (n_t - 1) / (n_t - 1)$.
-Finally, we fitted a random-effects meta-analysis with REML and estimated $I^2$ for that run.
-For standardized mean differences we proceeded identically, except that we in the final step asked metafor to transform the effect size into a standardized mean difference in fitting the random-effects model.
-As with correlations, the distribution of $I^2$ was approximated for values of $\tau$ from 0 to .5 in steps of .005, using 1,000 runs at each step.
+Finally, we fitted a random-effects meta-analysis with REML and estimated _I^2^_ for that run.
+For standardized mean differences (and odds ratios) we proceeded identically, except that in the final step we asked metafor to transform the effect size into a standardized mean difference in fitting the random-effects model.
+As with correlations, the distribution of _I^2^_ was approximated for values of $\tau$ from 0 to .5 in steps of .005, using 1,000 runs at each step.
 
 To approximate the statistical power of all 37 effects at zero, small, medium, and large heterogeneity we continued as follows.
-For each of the 37 effects we selected the values of $\tau$ which yielded the average value of $I^2$ in the simulations closest to 25 (small), 50 (medium), and 75 (large).
-For these values of $\tau$ and for $\tau = 0$ (homogeneity) we again ran 10,000 simulations, and for each run $I^2$ was calculated and the Q-test of heterogeneity was performed, yielding estimates of type I error (in case of homogeneity) and power (for heterogeneity) for each of the 37 effects.
+For each of the 37 effects we selected the values of $\tau$ which yielded the average value of _I^2^_ in the simulations closest to 25 (small), 50 (medium), and 75 (large).
+For these values of $\tau$ and for $\tau = 0$ (homogeneity) we again ran 10,000 simulations, and for each run _I^2^_ was calculated and the Q-test of heterogeneity was performed, yielding estimates of type I error (in case of homogeneity) and power (for heterogeneity) for each of the 37 effects.
 We considered a result significant when _p_ $\leq 0.05$ for the Q-test.
-The distributions of $I^2$ for zero, small, medium, large heterogeneity, which we compared to the observed distribution of 37 effect sizes, was generated by pooling the 37 distributions of 10,000 $I^2$ values in each category of heterogeneity.
-Hence these $I^2$ distributions can be considered a mixture distribution of 37 distributions, using equal weights across all 37 effects.
+The distributions of _I^2^_ for zero, small, medium, large heterogeneity, which we compared to the observed distribution of 37 effect sizes, was generated by pooling the 37 distributions of 10,000 _I^2^_ values in each category of heterogeneity.
+Hence these _I^2^_ distributions can be considered a mixture distribution of 37 distributions, using equal weights across all 37 effects.
 
-To examine the correlation between effect size and $I^2$ across all 37 effects we converted all effect sizes to a common metric.
-We first converted all effects into correlations (osf.io/h9pft/) and used the R-package metafor to estimate $I^2$ and meta-analytic effects expressed as Fisher-transformed correlations (osf.io/zuwpg/).
+To examine the correlation between effect size and _I^2^_ across all 37 effects we converted all effect sizes to a common metric.
+We first converted all effects into correlations (osf.io/h9pft/) and used the R-package metafor to estimate _I^2^_ and meta-analytic effects expressed as Fisher-transformed correlations (osf.io/zuwpg/).
 In doing so, we fitted random-effects models with metafor's default REML estimator.
@@
 234).
-In one case (RRR8), we first had to convert reported standard errors into pooled standard deviation (p.224).
+In one case (RRR8), we first had to convert reported standard errors into pooled standard deviations (p.224).
 For risk differences and odds ratios we first added 1/2 to a cell if it was empty to avoid dividing by zero, next calculated the logarithmic odds ratio (p.
@@
 All formulas used are presented in Appendix B (osf.io/h4vfx/).
-Since $I^2$ is set to zero for the majority of cases under homogeneity (i.e., truncated), we also correlated effect size with the closely related heterogeneity estimate $H^2$ [@10.1002/sim.1186] as a sensitivity analysis.
-The $H^2$ index is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - $I^2$)$ for $I^2 \geq 0$.
+Since _I^2^_ is set to zero for the majority of cases under homogeneity (i.e., truncated), we also correlated effect size with the closely related heterogeneity estimate _H^2^_ [@10.1002/sim.1186] as a sensitivity analysis.
+The _H^2^_ index is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - _I^2^_)$ for $I^2 \geq 0$.
 It ranges from zero to positive infinity, where a larger score indicates more heterogeneity, a score of one indicates homogeneity, and a score between zero and one thus indicates 'excessive' homogeneity.
@@
 
-Table 3 presents the meta-analytic effect size estimates and $I^2$ with confidence intervals for each of the 37 included effects, as well as simulated type I error and statistical power for zero, small, medium, and large true heterogeneity.
+Table 3 presents the meta-analytic effect size estimates and _I^2^_ with confidence intervals for each of the 37 included effects, as well as simulated type I error and statistical power for zero, small, medium, and large true heterogeneity.
 
@@
   select(rp, effect,k , everything()) %>% 
-  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
+  arrange(desc(s_I2),  desc(s_ci.ub)) %>% 
+  ungroup()#sort by I2 and upper CI bound
 
@@
 
-_Heterogeneity across primary effects in ten multi-lab replication projects._
+_Heterogeneity across primary effects in ten multi-lab replication projects, ordered with respect to estimated heterogeneity_
 ```{r heterogeneity-table}
@@
 RP = Replication Project, k = no.
-primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of $I^2$ 95% confidence interval, ci.ub = upper bound of $I^2$ 95% confidence interval.
+primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of _I^2^_ 95% confidence interval, ci.ub = upper bound of _I^2^_ 95% confidence interval.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-Under simulated heterogeneity, Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75%) respectively.
+Under simulated heterogeneity, Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity (_I^2^_ = 25/50/75%) respectively.
 Code to reproduce table: osf.io/kf6pt/
 
-^a^ Odds ratio or risk difference simulated as mean difference
+^a^ Odds ratio or risk difference simulated as (standardized) mean difference
 
-###$I^2$ estimates and confidence intervals
+###_I^2^_ estimates and confidence intervals
 
 There is limited evidence for widespread heterogeneity across the examined effects.
-Of the 37 effects, `r sum(het$s_I2 >= 62.5)` / `r nrow(het)` (`r 100*round(sum(het$s_I2 >= 62.5) / nrow(het), digits = 2)`%) have $I^2$ estimates that best correspond to large heterogeneity ($I^2$ = 75%), `r sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5) / nrow(het), digits = 2)`%) to medium heterogeneity ($I^2$ = 50%), `r sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5) / nrow(het), digits = 2)`%)  to small heterogeneity ($I^2$ = 25%) and `r sum(het$s_I2 < 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 12.5) / nrow(het), digits = 2)`%) to zero heterogeneity ($I^2$ = 0%).
+Of the 37 effects, `r sum(het$s_I2 >= 62.5)` / `r nrow(het)` (`r 100*round(sum(het$s_I2 >= 62.5) / nrow(het), digits = 2)`%) have _I^2^_ estimates that best correspond to large heterogeneity (_I^2^_ = 75%), `r sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5) / nrow(het), digits = 2)`%) to medium heterogeneity (_I^2^_ = 50%), `r sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5) / nrow(het), digits = 2)`%)  to small heterogeneity (_I^2^_ = 25%) and `r sum(het$s_I2 < 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 12.5) / nrow(het), digits = 2)`%) to zero heterogeneity (_I^2^_ = 0%).
 However, despite a relatively large number of studies and total sample size for most projects (see Table 2), Table 3 shows very wide confidence intervals (spanning 50% or more) for many effects.
-The lower bound $I^2$ confidence interval excludes zero for only `r sum(het$s_ci.lb > 0)`/`r nrow(het)` effects (`r 100*round(sum(het$s_ci.lb > 0) / nrow(het), digits = 2)`%; Table 3), all part of the ML1 project.
-The percentage of heterogeneity estimates larger than 0 (`r sum(het$s_I2 > 0)`/`r nrow(het)`; `r 100*round(sum(het$s_I2 > 0) / nrow(het), digits = 2)`%, two effects had $I^2$ < .005 and are rounded down in Table 3) suggests heterogeneity for at least some effects, as this percentage is higher than the expected frequency of non-zero estimates under homogeneity (46%, or about 17/37), based on the chi-square distribution and average k across projects.
+The lower bound _I^2^_ confidence interval excludes zero for only `r sum(het$s_ci.lb > 0)`/`r nrow(het)` effects (`r 100*round(sum(het$s_ci.lb > 0) / nrow(het), digits = 2)`%; Table 3), all part of the ML1 project.
+The percentage of heterogeneity estimates larger than 0 (`r sum(het$s_I2 > 0)`/`r nrow(het)`; `r 100*round(sum(het$s_I2 > 0) / nrow(het), digits = 2)`%, two effects had _I^2^_ < .005 and are rounded down in Table 3) suggests heterogeneity for at least some effects, as this percentage is higher than the expected frequency of non-zero estimates under homogeneity (46%, or about 17/37), based on the chi-square distribution and average k across projects.
 
-###$I^2$ and power
+###_I^2^_ and power
 
-Figure 1 shows how estimated $I^2$ varies across all 37 effects as a function of true heterogeneity (averaged across all simulation runs).
-Figure 1 makes clear that $I^2$ is particularly sensitive to changes in heterogeneity for small heterogeneity, and that estimates of $I^2$ may differ considerably across projects for the same value of true heterogeneity.
-This can largely be attributed to differences in number of included studies per project, but also partly to sample sizes between projects (with larger number of studies and sample sizes resulting in larger estimates of $I^2$).
-For example, the three bottom lines all belong to RRR3, the replication project with the lowest number of included studies (12; see Table 3).
+Figure 1 shows how estimated _I^2^_ varies across all 37 effects as a function of true heterogeneity (averaged across all simulation runs).
+Figure 1 makes clear that _I^2^_ is particularly sensitive to changes in heterogeneity for small heterogeneity, and that estimates of _I^2^_ may differ considerably across projects for the same value of true heterogeneity.
+This can largely be attributed to differences in the sample sizes of the studies incorporated in a meta-analyses (with larger sample sizes resulting in larger estimates of _I^2^_).
+For example, the three bottom lines all belong to RRR3, the replication project with the lowest average sample size per study (`r round(min(summary.table$Participants) / min(summary.table$k), digits = 0)`; see Table 2).
 Since the between studies variance is not measured on the same scale when using different effect size measures, estimates are not directly comparable across effect types.
@@
 _Figure 1.
-Result of simulation relating $I^2$-values to between studies standard deviation.
+Result of simulation relating _I^2^_-values to between studies standard deviation.
 Each line represent one of 37 effects.
@@
 In all cases the type I error is approximately nominal, as compared to the expected 5% error rate.
-Power to detect small heterogeneity was low, ranging between `r 100*round(min(het$small), digits = 2)`% and `r 100*round(max(het$small), digits = 2)`%, with an average of `r 100*round(mean(het$small), digits = 2)`%.
-Power to detect medium heterogeneity was generally very good, with an average of `r 100*round(mean(het$medium), digits = 2)`% power, but goes down to as low as `r 100*round(min(het$medium), digits = 2)`% for several effects with low K.
+Power to detect small heterogeneity was low, ranging from `r 100*round(min(het$small), digits = 2)`% to `r 100*round(max(het$small), digits = 2)`%, with an average of `r 100*round(mean(het$small), digits = 2)`%.
+Power to detect medium heterogeneity was generally very good, with an average of `r 100*round(mean(het$medium), digits = 2)`% power, but goes down to as low as `r 100*round(min(het$medium), digits = 2)`% - `r 100*round(sort(het$medium)[2], digits = 2)` for several effects with low K (i.e., effects from RRR3).
 Power to detect strong heterogeneity was excellent across the board.
@@
 
-Figure 2 shows the distribution of $I^2$ at different heterogeneity levels and a histogram of the observed effects.
+Figure 2 shows the distribution of _I^2^_ at different heterogeneity levels and a histogram of the observed effects.
 The shortest bars in the histogram correspond to the heterogeneity estimate of one effect.
-The considerable overlap of the distributions illustrates why sufficient power can be difficult to achieve, and why confidence intervals for $I^2$ are often wide.
+The considerable overlap of the distributions illustrates why sufficient power can be difficult to achieve, and why confidence intervals for _I^2^_ are often wide.
 In particular, the dispersion of the distribution under small heterogeneity is illustrative of the low power to be expected under such circumstances.
 Given the histogram of observed effect sizes and densities of the distributions (height of the curves), the majority of observed effects are most likely to have zero or zero to small heterogeneity.
-Only two effects appear to be of medium heterogeneity and three of large.
+Only for five effects there seems to be substantial evidence that they originate from medium (two) or large true effects, as they fall outside the dominant densities of lower true effects.
 
@@
 _Figure 2.
-Simulated $I^2$ densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of @10.1136/bmj.327.7414.557, and a histogram of the observed $I^2$ estimates for the 37 effects.
+Simulated _I^2^_ densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of @10.1136/bmj.327.7414.557, and a histogram of the observed _I^2^_ estimates for the 37 effects.
 Each simulated density consists of approximately 370,000 estimates.
@@
 
-###$I^2$ and effect sizes
+###_I^2^_ and effect sizes
 
 Larger estimated effect sizes appear to be associated with higher heterogeneity estimates.
-In Table 3, the four effects with highest $I^2$ estimates also have the largest effect size estimates.
-As expected, heterogeneity tends to increase with (absolute) effect size, with effect size sufficient to explain 61% of variation in $I^2$ estimates according to a simple regression model (Figure 3).
-The closely related, but unbounded, heterogeneity estimate $H^2$ provides a similar result ($R^2$ = .53).
-Excluding Anchoring effects (the 1^st^, 3^rd^, 4^th^, and 6^th^ largest effect sizes) as robustness check results in only slightly less explained variance ($R^2$ = .51 for $I^2$).
+In Table 3, the four effects with highest _I^2^_ estimates also have the largest effect size estimates.
+As expected, heterogeneity tends to increase with (absolute) effect size, with effect size sufficient to explain 61% of variation in _I^2^_ estimates (_p_ < .001) according to a simple regression model (Figure 3).
+The closely related, but unbounded, heterogeneity estimate _H^2^_ provides a similar result (_R^2^_ = .53, _p_ < .001).
+Excluding Anchoring effects (the 1^st^, 3^rd^, 4^th^, and 6^th^ largest effect sizes) as robustness check results in only slightly less explained variance (_R^2^_ = .51, _p_ < .001 for _I^2^_).
 
@@
 
-_Figure 3. The correlation between A) $I^2$ and effect size and B) $H^2$ and effect size for 37 effects from ten pre-registered multi-lab replication projects. Code to reproduce figure: osf.io/zuwpg/_
+_Figure 3.
+The correlation between A) _I^2^_ and effect size and B) _H^2^_ and effect size for 37 effects from ten pre-registered multi-lab replication projects.
+Code to reproduce figure: osf.io/zuwpg/_
 
@@
 These ten projects examined a total of 37 primary outcome variables and arguably represent the best, least biased, meta-analytic data currently available in psychology.
-To aid interpretation we also estimated power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557 and plotted the distributions of $I^2$ under these four heterogeneity levels.
-Our results showed that most effects in our sample likely had zero to small heterogeneity, that power to distinguish between zero and small heterogeneity was low for all projects, and that heterogeneity was strongly correlated with effect size in our sample.
+To aid interpretation we also estimated power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557 and approximated the distributions of _I^2^_ under these four heterogeneity levels.
+Our results showed that by far most effects in our sample likely had zero (`r 1 - 100*round(sum(het$s_ci.lb > 0) / nrow(het), digits = 2)`% of confidence intervals included zero heterogeneity) to small heterogeneity, that power to distinguish between zero and small heterogeneity was low for all projects, and that heterogeneity was strongly correlated with effect size in our sample.
 
-There is little evidence for widespread heterogeneity amongst current pre-registered multi-lab replication projects in psychology.
-Across ten projects, only `r sum(het$s_ci.lb > 0)`/`r nrow(het)` (`r 100*round(sum(het$s_ci.lb > 0) / nrow(het), digits = 2)`%) of primary outcomes had confidence intervals that excluded zero heterogeneity, and given the distributions of $I^2$ under zero to large heterogeneity, most (32/37; 86%) effects appeared to have zero or small heterogeneity.
-Moreover, while each replication of an effect only varied on two contextual factors (sampling population and settings), the effects that showed significant evidence for heterogeneity were primarily effects that might have been expected to be sensitive to changes in sampling population.
+In addition to most effects showing no or small heterogeneity, the effects that showed significant evidence for heterogeneity were primarily effects that might have been expected to be sensitive to changes in sampling population.
 That is, save two effects (Anchoring - Everest and IAT correlation math), all other effects that demonstrated heterogeneity were related to the US.
@@
 Indeed, our results imply that effects cannot simply be assumed to vary extensively "across time, situations and persons" [@10.3389/fpsyg.2017.00879, p.14] and that we should not expect "minor, seemingly arbitrary and even theoretically irrelevant modifications in procedures" [@10.1186/s40359-016-0134-3, p.6] to have large impact on effect estimates.
-That is, our results imply that citing heterogeneity as a reason for non-replication of an effect is unwarranted unless predicted _a priori_.
+That is, our results imply that citing heterogeneity as a reason for non-replication of an effect is unwarranted unless predicted _a priori_ [@10.1177/1745691617708630].
 
 In view of the fact that most effects in our sample likely had zero to small heterogeneity, the lack of power to distinguish between these two heterogeneity levels is of concern.
-That heterogeneity is small is not the same as being negligible, as even small heterogeneity may have large consequences at the aggregated level of an intervention, or at the individual level for a few people.
-Yet, power to detect small heterogeneity was on average only `r 100*round(mean(het$small), digits = 2)`% in our sample.
-A suggestion to double the already very impressive number of participating labs and individuals of the largest replication projects in our sample seems unrealistic even for methodologists.
-It may simply be that the $I^2$ index as a measure of heterogeneity is inadequate to examine small levels of heterogeneity.
+That heterogeneity is small is not the same as being negligible, as even small heterogeneity may have consequences for implementing interventions, the advancement of theory, and the the interpretation of research outcomes including replication studies.
+A suggestion to double the already very impressive number of participating labs and individuals of the largest replication projects in our sample seems unrealistic.
 The good news is that sufficient power to detect large and medium heterogeneity is realistically achievable for many meta-analyses.
+We therefore conclude that large (preferably preregistered) multi-lab studies are very valuable for increasing understanding of psychological phenomena.
 
@@
 Nonetheless, the extensive use of different scales in psychology means that for many meta-analysts there should be little reason not to control for measurement reliability when aggregating results.
+Controlling for measurement error, however, introduces the problem into the analysis that estimates of measurement reliability are themselves imprecise, which will affect the study effect size estimates and thereby the estimated overall effect size and heterogeneity.
 
@@
 For one, the included effects are neither a representative nor random sample of effects in psychology and as such do not support making strong claims about average heterogeneity levels in psychology.
-In respect to this point we look forward to the forthcoming Many Labs 2 project which should provide considerable new data on the prevalence of heterogeneity in psychology.
-Relatedly, the relatively small number of effects in our sample means the association between heterogeneity and effect size might be an artifact of the data.
-In addition, while our results point towards most effects having zero to small heterogeneity, many confidence intervals are very wide and congruent with a large range of actual heterogeneity.
-Finally, note that we only considered meta-analyses that varied two contextual factors (sample population and settings) that may cause heterogeneity, keeping constant two other ones (treatment and measurement variables), which may have resulted in both lower heterogeneity estimates as well as a stronger relationship between effect size and heterogeneity estimates in our paper.
+More particularly, we only considered meta-analyses that varied two contextual factors (sample population and settings) that may cause heterogeneity, keeping constant two other ones (treatment and measurement variables), which may have resulted in both lower heterogeneity estimates as well as a stronger relationship between effect size and heterogeneity estimates in our paper.
+Relatedly, the relatively small number of effects in our sample means the association between heterogeneity and effect size might be an artifact of the data, although exclusion of the rather extreme anchoring effects from our analysis only slightly reduced the correlation between effect size and heterogeneity.
+Finally, we should stress that while our results point towards most effects having zero to small heterogeneity, many confidence intervals are very wide and congruent with a large range of actual heterogeneity.
 
@@
 Moreover, it may be worthwhile to attempt to disentangle the contribution of reliability to this correlation from other aspects of measurement that are likely to contribute, such as range restrictions [@Schmidt2015].
-Finally, the poor power of $I^2$ to detect small heterogeneity means that if zero to small heterogeneity is truly the norm for direct replications in psychology, it may be time to explore new measures of heterogeneity.
 

### 2018-07-10 code/power_simulation.r
Fixed mistakes in simulation code
MD was simulated as SMD and effects measured as OR should be simulated as SMD rather than MD

@@ -61,7 +61,7 @@ simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies 
       }, otherwise = NULL)) #If rma does not converge, drop that iteration ('possibly' function)
     }
     
-  }else if(effect$type == "d"){
+  }else if(effect$type == "d"){ #That is, for SMD and odds ratios
     
     n_c <- effect$ncontrol #observed control group sizes
     n_t <- effect$ntreatment #observed treatment group sizes
@@ -110,7 +110,7 @@ simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies 
         var_c <- rchisq(n = K, df = n_c - 1) / (n_c - 1) #draw variances from sampling distribution control group
         var_t <- rchisq(n = K, df = n_t - 1) / (n_t - 1) #draw variances from sampling distribution treatment group
         
-        fit <- rma(measure = "SMD",  m1i = avg_t, m2i = avg_c, sd1i = sqrt(var_t),
+        fit <- rma(measure = "MD",  m1i = avg_t, m2i = avg_c, sd1i = sqrt(var_t),
                    sd2i = sqrt(var_c), n1i = n_t, n2i = n_c, method = "REML") #fit meta-analysis for mean difference
         
         data.frame(I2 = fit$I2, Qp = fit$QEp, ci.lb = confint(fit)$random[3, 2], 
@@ -128,12 +128,14 @@ simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies 
 #******************************************
 
 ##Prep data for simulation function
-OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #effects that were transformed from OR to SMD
-          'Norm of reciprocity', 'Low vs. high category scales') 
+
+# OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #effects that were transformed from OR to SMD
+#           'Norm of reciprocity', 'Low vs. high category scales') #Not used after all
 
 dat2 <- dat %>% #Extract k, effect type and sample sizes for each effect
-  mutate(effect_type = ifelse(effect %in% OR2d | effect_type == "Risk difference" | #treat all these effects.. 
-                                effect_type == "Raw mean difference", "MD", effect_type)) %>% #..as mean differences in simulation
+  mutate(effect_type = recode(effect_type, 
[…]

### 2018-10-08 writing/draft-heterogeneity.rmd
Minor corrections, commas etc

@@
   We examined the evidence for heterogeneity (of effect sizes) and explored the correlation between heterogeneity and effect size in a sample of 37 effect sizes from ten pre-registered multi-lab replication projects in psychology.
-We found limited heterogeneity; only 4/37 (11%) effects had significant heterogeneity, and most effects (32/37; 86%) were most likely to have zero to small heterogeneity.
-Power to detect small heterogeneity, was low for all projects (mean 36%), but good to excellent for medium and large heterogeneity.
+We found limited heterogeneity; only 7/37 (19%) effects had significant heterogeneity, and most effects (32/37; 86%) were most likely to have zero to small heterogeneity.
+Power to detect small heterogeneity was low for all projects (mean 36%), but good to excellent for medium and large heterogeneity.
 As anticipated, we found a strong correlation between observed effect size and heterogeneity in our sample (R^2^ = .61).
@@
 Intuitively, it makes sense to believe that if there is no meta-analytic effect there is nothing to moderate (i.e., no heterogeneity).
-However, a null or near null effect size estimate may arise from failure to consider contextual factors ('hidden moderators'; @10.2139/ssrn.2820883) and does not by itself imply the absence of heterogeneity.
+However, a null or near null effect size estimate may arise from failure to consider contextual factors ['hidden moderators'; @10.2139/ssrn.2820883] and does not by itself imply the absence of heterogeneity.
 A large meta-analytic effect size on the other hand, can be expected to be associated with more heterogeneity.
@@
 Since _I^2^_ is set to zero for the majority of cases under homogeneity (i.e., truncated), we also correlated effect size with the closely related heterogeneity estimate _H^2^_ [@10.1002/sim.1186] as a sensitivity analysis.
-The _H^2^_ index is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - _I^2^_)$ for $I^2 \geq 0$.
+The _H^2^_ index is calculated as $H2 = Q  / (k - 1)$ and equals $1 / (1 - I^2)$ for $I^2 \geq 0$.
 It ranges from zero to positive infinity, where a larger score indicates more heterogeneity, a score of one indicates homogeneity, and a score between zero and one thus indicates 'excessive' homogeneity.
@@
 There is limited evidence for widespread heterogeneity across the examined effects.
-Of the 37 effects, `r sum(het$s_I2 >= 62.5)` / `r nrow(het)` (`r 100*round(sum(het$s_I2 >= 62.5) / nrow(het), digits = 2)`%) have _I^2^_ estimates that best correspond to large heterogeneity (_I^2^_ = 75%), `r sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5) / nrow(het), digits = 2)`%) to medium heterogeneity (_I^2^_ = 50%), `r sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5) / nrow(het), digits = 2)`%)  to small heterogeneity (_I^2^_ = 25%) and `r sum(het$s_I2 < 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 12.5) / nrow(het), digits = 2)`%) to zero heterogeneity (_I^2^_ = 0%).
+Of the 37 effects, `r sum(het$s_I2 >= 62.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 >= 62.5) / nrow(het), digits = 2)`%) have _I^2^_ estimates that best correspond to large heterogeneity (_I^2^_ = 75%), `r sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 62.5 & het$s_I2 >= 37.5) / nrow(het), digits = 2)`%) to medium heterogeneity (_I^2^_ = 50%), `r sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 37.5 & het$s_I2 >= 12.5) / nrow(het), digits = 2)`%)  to small heterogeneity (_I^2^_ = 25%) and `r sum(het$s_I2 < 12.5)`/`r nrow(het)` (`r 100*round(sum(het$s_I2 < 12.5) / nrow(het), digits = 2)`%) to zero heterogeneity (_I^2^_ = 0%).
 However, despite a relatively large number of studies and total sample size for most projects (see Table 2), Table 3 shows very wide confidence intervals (spanning 50% or more) for many effects.
@@
 Power to detect small heterogeneity was low, ranging from `r 100*round(min(het$small), digits = 2)`% to `r 100*round(max(het$small), digits = 2)`%, with an average of `r 100*round(mean(het$small), digits = 2)`%.
-Power to detect medium heterogeneity was generally very good, with an average of `r 100*round(mean(het$medium), digits = 2)`% power, but goes down to as low as `r 100*round(min(het$medium), digits = 2)`% - `r 100*round(sort(het$medium)[2], digits = 2)` for several effects with low K (i.e., effects from RRR3).
+Power to detect medium heterogeneity was generally very good, with an average of `r 100*round(mean(het$medium), digits = 2)`% power, but goes down to as low as `r 100*round(min(het$medium), digits = 2)` - `r 100*round(sort(het$medium)[2], digits = 2)`% for several effects with low K (i.e., effects from RRR3).
 Power to detect strong heterogeneity was excellent across the board.
@@
 To aid interpretation we also estimated power of each project to find zero/small/medium/large heterogeneity as defined by @10.1136/bmj.327.7414.557 and approximated the distributions of _I^2^_ under these four heterogeneity levels.
-Our results showed that by far most effects in our sample likely had zero (`r 1 - 100*round(sum(het$s_ci.lb > 0) / nrow(het), digits = 2)`% of confidence intervals included zero heterogeneity) to small heterogeneity, that power to distinguish between zero and small heterogeneity was low for all projects, and that heterogeneity was strongly correlated with effect size in our sample.
+Our results showed that by far most effects in our sample likely had zero (`r 100*round(1 - sum(het$s_ci.lb > 0) / nrow(het), digits = 2)`% of confidence intervals included zero heterogeneity) to small heterogeneity, that power to distinguish between zero and small heterogeneity was low for all projects, and that heterogeneity was strongly correlated with effect size in our sample.
 
@@
 In view of the fact that most effects in our sample likely had zero to small heterogeneity, the lack of power to distinguish between these two heterogeneity levels is of concern.
-That heterogeneity is small is not the same as being negligible, as even small heterogeneity may have consequences for implementing interventions, the advancement of theory, and the the interpretation of research outcomes including replication studies.
+That heterogeneity is small is not the same as being negligible, as even small heterogeneity may have consequences for implementing interventions, the advancement of theory, and the interpretation of research outcomes including replication studies.
 A suggestion to double the already very impressive number of participating labs and individuals of the largest replication projects in our sample seems unrealistic.

### 2018-10-31 code/power_simulation.r
Minor cleaning of script

@@ -5,9 +5,6 @@
 #Code: Anton Ohlsson Collentine
 
 #******************************************
-##To do:
-#1) for mean differences add sample sizes
-#2) separate between mean differences and SMD
 
 #******************************************
 #Packages and data----
@@ -169,7 +166,7 @@ system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progr
 #********************
 
 ##Simulation results
-dat3 <- readRDS("../data/AppendixA_tau_simulation_results.RDS")
+dat3 <- readRDS("../data/tau_simulation_results.RDS")
 names(dat3) <- names(dat2) #names are lost when looping instead of using lapply
 
 dat3 <- dat3 %>% #create dataframe with identifier
@@ -220,15 +217,15 @@ system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progr
 #*********************
 #Effect size sensitivity simulation for Appendix A
 
-set.seed(50)
- res2_a <- vector("list", length(dat2)) #output of below loop
-
- system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progress (lapply otherwise option)
-   res2_a[[e]] <- simulate_I2(dat5[[e]][[1]], reps = 1e4,
-                            tau = c(0, dat5[[e]][[2]]), effect_size = "medium") #NB! 1e4 reps here is about 9.5 hours on my (fairly slow) machine
-  cat("...RS",e, "/37") #see progress
-   if (e%%5 == 0 | e == 37) saveRDS(res2_a, "../data/AppendixA_power_simulation_results.RDS") #save ocassionally and at finish
- })
+# set.seed(50)
+#  res2_a <- vector("list", length(dat2)) #output of below loop
+# 
+#  system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progress (lapply otherwise option)
+#    res2_a[[e]] <- simulate_I2(dat5[[e]][[1]], reps = 1e4,
+#                             tau = c(0, dat5[[e]][[2]]), effect_size = "medium") #NB! 1e4 reps here is about 9.5 hours on my (fairly slow) machine
+#   cat("...RS",e, "/37") #see progress
+#    if (e%%5 == 0 | e == 37) saveRDS(res2_a, "../data/AppendixA_power_simulation_results.RDS") #save ocassionally and at finish
+#  })
 #********************
 
 ##Simulation results

### 2018-10-31 code/collate_summary_data.r
Fixed incorrect link

@@ -563,7 +563,7 @@ ml3 <- rbind(ml3_stroop, ml3t, nonp, inter, cons_cor) %>%
 #******************************************
 #[3] RRR1 & 2 ----
 #******************************************
-##summary data from Registered Replication Report 1 & 2 https://osf.io/jymhe/
+##summary data from Registered Replication Report 1 & 2 https://osf.io/ybeur/ 
 ##Data RRR1 https://osf.io/dv5ei/
 ##Data RRR2 https://osf.io/dy6at/
 

### 2018-11-02 code/figures.rmd
Updated draft and associated files
Corrected legend alpha figure 3

@@
 
-# summary(lm(H2alt ~ z, data = res2)) #b = 3.81, R2 = 0.53
+# summary(lm(H2 ~ z, data = res2)) #b = 3.81, R2 = 0.53
 
@@
   scale_y_continuous(name = "Density") +
-  scale_x_continuous(name = expression(paste(I^2," index", sep = "")))
+  scale_x_continuous(name = expression(paste(I^2," index", sep = ""))) +
+  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
 
-# ggsave("../figures/density-I2.png", dpi = 600, height =  4 , width = 6.47)
+ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
 ```

### 2018-11-02 code/tables.rmd
Improvements to Table 1 and 3, correction of reference in Table 2

@@
 rho <- c(0, .3, .5)
-rel <- c("R = .6", "R = .7", "R = .8")
+rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
 
@@
 
-diff_row <- data.frame(rel = "Standard deviation R", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))
+diff_row <- data.frame(rel = "SD observed effect sizes", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))
 
@@
 
-het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("Effect size", "Rho = 0", "Rho = .3", "Rho = .5"), digits = 2) %>% 
+het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho$ = 0", "$\\rho$ = .3", "$\\rho$ = .5"), escape = FALSE, digits = 2) %>% 
   kable_styling(position = "left") %>% 
-  footnote(threeparttable = TRUE,
-           general = "R = square root of the multiplied reliabilities. Rho = true effect size. Code to reproduce table: osf.io/kf6pt/") %>% 
+  footnote(threeparttable = TRUE, escape = FALSE,
+           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$.
+SD = standard deviation.
+Code to reproduce table: osf.io/kf6pt/") %>%
   row_spec(3, hline_after = T)
@@
 Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
-'Ebersole, C.
-R., Atherton, O.
-E., Belanger, A.
-L., Skulborstad, H.
-M., Allen, J.
-M., Banks, J.
-B., ...
-& Brown, E.
-R.
-(2016).
-Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
+'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
 'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
@@
 Journal of Experimental Social Psychology, 67, 68-82.',
-# 'Ebersole, C.
-R., Atherton, O.
-E., Belanger, A.
-L., Skulborstad, H.
-M., Allen, J.
-M., Banks, J.
-B., ...
-& Brown, E.
-R.
-(2016).
-Many Labs 3: Evaluating participant pool quality across the academic semester via replication.
-Journal of Experimental Social Psychology, 67, 68-82.',
+# 'Alogna, V.
+K., Attaya, M.
+K., Aucoin, P., Bahník, S., Birch, S., Birt, A.
+R., ...
+& Buswell, K.
+(2014).
+Registered replication report: Schooler and engstler-schooler (1990).
+Perspectives on Psychological Science, 9(5), 556-578.',
 # 'Alogna, V.
@@
   left_join(I2_ci_lb) %>% 
-  select(rp, effect,k , everything()) %>% 
-  arrange(desc(s_I2),  desc(s_ci.ub)) #sort by I2 and upper CI bound
+  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by I2 and upper CI bound
+  mutate(ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]")) %>% 
+  select(rp, effect, k, effect_type, eff_size, s_I2, ci, zero, small, medium, large)
 
@@
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE,  digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Estimate", "I2(%)", "ci.lb", "ci.ub", "Zero", "Small", "Medium", "Large")) %>%
-  add_header_above(c(" " = 8, "Heterogeneity & error/power" = 4)) %>% 
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Effect size estimate", "$I^2$(\\%)", "$I^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+  add_header_above(c(" " = 7, "Level of heterogeneity" = 4)) %>% 
+  add_header_above(c(" " = 7, "Statistical power" = 4)) %>% 
   kable_styling("scale_down", font_size = 7) %>%
@@
 RP = Replication Project, k = no.
-primary studies, Estimate = Point estimates of effect sizes, ci.lb = lower bound of $I^2$ 95\\\\% confidence interval, ci.ub = upper bound of $I^2$ 95\\\\% confidence interval.
+primary studies, Estimate = Point estimates of effect sizes, $I^2$ 95\\\\% CI = $I^2$ 95\\\\% confidence interval.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.

### 2018-11-02 code/figures.rmd
Minor clarification of comment on H2 computation

@@
 Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1).
-This method computes H2 as originally specified by Higgins & Thompson instead of using the more general method of metafor (see ?print.rma.uni).
+This method approximates H2 as if we were using the Dersimonian and Laird estimate of tau2, although we use REML.
+See Higgins & Thompson, 2002 and ?print.rma.uni.
 

### 2018-11-02 code/codebook_collated_summary_data.rmd
Updated project name in header in code files

@@
 title: Codebook for collated_summary_data.csv
-subtitle: "Limited evidence for widespread heterogeneity in psychology"
+subtitle: "Heterogeneity in direct replications in psychology and its association with effect size"
 output: pdf_document

### 2018-11-02 code/tables.rmd
Corrected footnote of Table 3
Updated project name in header in code files

@@
 title: "Tables"
-author: "Limited evidence for widespread heterogeneity in psychology"
+author: "Heterogeneity in direct replications in psychology and its association with effect size"
 output: pdf_document
@@
 primary studies, Estimate = Point estimates of effect sizes, $I^2$ 95\\\\% CI = $I^2$ 95\\\\% confidence interval.
+Statistical power was simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.

### 2018-11-02 code/codebook_collated_summary_data.r

@@ -1,6 +1,6 @@
 #************************************************
 
-##Project: Limited evidence for widespread heterogeneity in psychology
+##Project: Heterogeneity in direct replications in psychology and its association with effect size
 ##Script purpose: This script creates a nice-looking pdf codebook
 ##Code: Anton Ohlsson Collentine
 

### 2018-11-02 code/collate_summary_data.r

@@ -1,6 +1,6 @@
 #*************************************************************************************************************************
 
-##Project: Limited evidence for widespread heterogeneity in psychology
+##Project: Heterogeneity in direct replications in psychology and its association with effect size
 ##Script purpose: This script extracts, cleans and formats summary data from Many labs 1 & 3 and Registered Replication Reports 1 - 8 
 ##Code: Anton Ohlsson Collentine
 

### 2018-11-02 code/helper_functions_tables_figures.r

@@ -1,6 +1,6 @@
 #******************************************
 
-#Project: Limited evidence for widespread heterogeneity in psychology
+#Project: Heterogeneity in direct replications in psychology and its association with effect size
 #Script purpose: Helper functions to prep data for tables and figures
 #Code: Anton Ohlsson Collentine
 #Additional comments: These functions are intended to be 'sourced' into the 

### 2018-11-02 code/power_simulation.r

@@ -1,6 +1,6 @@
 #******************************************
 
-#Project: Limited evidence for widespread heterogeneity in psychology
+#Project: Heterogeneity in direct replications in psychology and its association with effect size
 #Script purpose: Simulate I2 distribution for different levels of heterogeneity given data weights
 #Code: Anton Ohlsson Collentine
 

### 2018-11-02 code/figures.rmd
Updated project name in header in code files
Changed R2 to r and added bootstrap CI

@@
 title: "Figures"
-author: "Anton Ohlsson Collentine"
+author: "Heterogeneity in direct replications in psychology and its association with effect size"
 output: pdf_document
@@
 if(!require(cowplot)){install.packages("cowplot")}
+if(!require(boot)){install.packages("boot")}
 
@@
 library(cowplot) #Combine several plots into one
+library(boot) #Bootstrap confidence intervals for correlations
 
@@
 
-```{r plot_res}
+```{r cor_het_z}
+#Basic correlations
+cor.test(res2$I2, res2$z) #pearson
 
-# summary(lm(I2 ~ z, data = res2)) #b = 69.40, R2 = 0.61
+I2_fit <- summary(lm(I2 ~ z, data = res2))
 
-I2 <- ggplot(res2, aes(x = z, y = I2)) +
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = FALSE, color = "black") +
-  xlab("Fisher's z") +
-  coord_cartesian(ylim = c(0, 100)) +
-  geom_text(x = 0.15, y = 80, label = "b = 69.40, R2 = 0.61", size = 3.5) +
-  theme_classic() +
-  scale_y_continuous(name = expression(paste(I^2," index", sep = ""))) +
-  scale_x_continuous(name = "Effect size (Fisher's z)")
+cor.test(res2$H2, res2$z) #pearson
 
-# summary(lm(H2 ~ z, data = res2)) #b = 3.81, R2 = 0.53
+H2_fit <- summary(lm(H2 ~ z, data = res2))
 
-H2 <- ggplot(res2, aes(x = z, y = H2)) + 
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = FALSE, color = "black") +
-  xlab("Fisher's z") +
-  geom_text(x = 0.14, y = 5.9, label = "b = 3.81, R2 = 0.53", size = 3.5) +
-  theme_classic() +
-  scale_y_continuous(name = expression(paste(H^2," index", sep = ""))) +
-  scale_x_continuous(name = "Effect size (Fisher's z)")
+cor.test(res2$I2, res2$z, method = "spearman") #spearman
 
-effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
-effect_het
-# save_plot("../figures/effect-het.png", effect_het,
-          # nrow = 2, base_aspect_ratio = 1.3, dpi = 600)
-
-```
-
-```{r robustness, results="hide"}
 ##Excluding anchoring effects
@@
 
-summary(lm(I2 ~ z, data = dropped_anchoring))
-#b = 87.87, R2 = .51
+cor.test(dropped_anchoring$I2, dropped_anchoring$z) #pearson
+
+#bootstrap confidence intervals
+#code by Amir Abdol
+
+#I2
+pear <- function(formula, data, indices){ #pearson
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ I2 + z, data=d)
+     return(fit$estimate)
+}
+
+bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ z + I2)
+
+I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+spear <- function(formula, data, indices){ #spearman
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ I2 + z, data=d, method = "spearman")
+     return(fit$estimate)
+}
+
+options(warn=-1)
+bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ z + I2)
+options(warn=0)
+
+I2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
+
+#Excluding anchoring effects
+bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ z + I2)
+
+I2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+#H2
+pear <- function(formula, data, indices){
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ H2 + z, data=d)
+     return(fit$estimate)
+}
+
+bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ z + H2)
+
+H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
+
+```
+
+```{r plot_res}
+
+I2 <- ggplot(res2, aes(x = z, y = I2)) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") +
+  xlab("Fisher's z") +
+  coord_cartesian(ylim = c(0, 100)) +
+  geom_text(x = 0.15, y = 80, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
+  theme_classic() +
+  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
+  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z), ")")))
+
+H2 <- ggplot(res2, aes(x = z, y = H2)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") +
+  xlab("Fisher's z") +
+  geom_text(x = 0.14, y = 5.9, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
+  theme_classic() +
+  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
+  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z),")")))
+
+effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
+effect_het
+save_plot("../figures/effect-het.png", effect_het,
+          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
 

### 2018-11-05 code/tables.rmd
Cleaned up Table 1

@@
 
-##Heterogeneity may increase with effect size
+##Table 1
+###Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
 ```{r effect-size-heterogeneity-table}
@@
 
-diff_row <- data.frame(rel = "SD observed effect sizes", X1 = sd(rooted_relabilities$X1), X2 = sd(rooted_relabilities$X2), X3 = sd(rooted_relabilities$X3))
-
-het_demo <- rbind(rooted_relabilities, diff_row)
-
-het_demo %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho$ = 0", "$\\rho$ = .3", "$\\rho$ = .5"), escape = FALSE, digits = 2) %>% 
+rooted_relabilities %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
   kable_styling(position = "left") %>% 
   footnote(threeparttable = TRUE, escape = FALSE,
-           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$.
-SD = standard deviation.
+           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$.
 Code to reproduce table: osf.io/kf6pt/") %>%
@@
 
-##Summary table
+##Table 2
+###Pre-registered multi-lab replication projects
 ```{r data-summary-table}
@@
 
-##Heterogeneity in preregistered multi-lab psychology studies
+##Table 3
+###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity
 ```{r heterogeneity-table}

### 2018-11-05 code/figures.rmd
Changed labels in Figure 3 to lowercase

@@
 
-effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("A", "B"), align = "v") #combine plots
+effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
 effect_het

### 2018-11-13 code/codebook_collated_summary_data.r
"Anonymized" for submission (removed author of code)

@@ -2,7 +2,7 @@
 
 ##Project: Heterogeneity in direct replications in psychology and its association with effect size
 ##Script purpose: This script creates a nice-looking pdf codebook
-##Code: Anton Ohlsson Collentine
+##Code: 
 
 #************************************************
 #Packages and data----

### 2018-11-13 code/collate_summary_data.r

@@ -2,7 +2,7 @@
 
 ##Project: Heterogeneity in direct replications in psychology and its association with effect size
 ##Script purpose: This script extracts, cleans and formats summary data from Many labs 1 & 3 and Registered Replication Reports 1 - 8 
-##Code: Anton Ohlsson Collentine
+##Code: 
 
 ##Script content:----
 

### 2018-11-13 code/helper_functions_tables_figures.r

@@ -2,7 +2,7 @@
 
 #Project: Heterogeneity in direct replications in psychology and its association with effect size
 #Script purpose: Helper functions to prep data for tables and figures
-#Code: Anton Ohlsson Collentine
+#Code: 
 #Additional comments: These functions are intended to be 'sourced' into the 
 #                     tables.rmd and figures.rmd files 
 

### 2018-11-13 code/power_simulation.r

@@ -2,7 +2,7 @@
 
 #Project: Heterogeneity in direct replications in psychology and its association with effect size
 #Script purpose: Simulate I2 distribution for different levels of heterogeneity given data weights
-#Code: Anton Ohlsson Collentine
+#Code: 
 
 #******************************************
 

### 2018-11-14 writing/appendixA-heterogeneity.rmd
Re-added appendices since one of them includes a table

@@
 
-Appendix A - Sensitivity analysis of effect size for simulations
+Appendix A - Sensitivity analysis assuming a medium true effect size rather than zero true effect size
 
-In our main results we simulated data to estimate type I error and power using an average effect size of zero.
+In our main results we simulated data to estimate type I error and power using an average true effect size equal to zero.
 As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity.
-However, as a sensitivity analysis we in this Appendix again estimate type I error and power, but generated with an average 'medium' effect size as defined by Cohen (1988).
+However, as a sensitivity analysis, in this appendix we also estimated type I error and power, but generated with an average 'medium' true effect size as defined by Cohen (1988).
 
@@
 In both cases type I error is approximately nominal, as compared to the expected 5% error rate.
-With a an effect size of zero, average power was `r 100*round(mean(zero$Small), digits = 2)`%/`r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`% for small/medium/large heterogeneity respectively.
-The corresponding power with an average effect size was `r 100*round(mean(zero$Small), digits = 2)`%/ `r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`%.
+With a true effect size of zero, average power was `r 100*round(mean(zero$Small), digits = 2)`%/`r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`% for small/medium/large heterogeneity, respectively.
+The corresponding power with a true medium effect size was also `r 100*round(mean(zero$Small), digits = 2)`%/ `r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`%, respectively.
 To conclude, changing true effect size in our simulations from zero to medium had little to no impact on estimated type I error and power.
@@
 
-_Type I error and power to detect four heterogeniety levels under two true effect sizes_
+_Type I error and power to detect four heterogeneity levels under two true effect sizes_
 

### 2018-11-14 writing/appendixB-heterogeneity.rmd
Re-added appendices since one of them includes a table

@@
 This appendix describes the formulas used to convert effect sizes into a common effect size measure (correlations).
-All formulas presented can be found in Borenstein (2009) and page numbers are cited as formulas are presented.
-For (standardized) mean differences, We assumed equal population standard deviations $\sigma_1 = \sigma_2$, and calculated (p.
+All formulas presented can be found in Borenstein (2009).
+For (standardized) mean differences, we assumed equal population standard deviations $\sigma_1 = \sigma_2$, and calculated (p.
 226) the pooled standard deviation $S_p$ as follows:
@@
 
-Where $n_1$/$n_2$ are group sample sizes and $S_1^2$/$S_2^2$ are the sample variances.
+where $n_1$/$n_2$ are group sample sizes and $S_1^2$/$S_2^2$ are the sample variances.
 In one case (RR8) we had to convert reported standard errors into pooled standard deviations.
@@
 
-Where $d$ is the standardized mean difference and $\bar{x}_1$/$\bar{x}_2$ the sample means of the two groups. We finally converted effect sizes to correlaions $r$ (p. 234):
+where $d$ is the standardized mean difference and $\bar{x}_1$/$\bar{x}_2$ the sample means of the two groups. We finally converted effect sizes to correlations (p. 234):
 
@@
 
-For effects that were reported as odds ratios or risk differences, we computed log odds ratios, converted these to standardized mean differences, and proceeded as above to convert these to correlations.
-We first added one half to any empty cell to avoid dividing by zero.
-We then computed the log odds ratios as follows (p.
+For effects that were measured as odds ratios (transformed by ML1 into standardized mean difference) or risk differences, we computed log odds ratios, converted these to standardized mean differences, and proceeded as above to convert these to correlations.
+We first added one half to any empty cell to avoid dividing by zero and then computed the log odds ratios as follows (p.
 266):
@@
 $$OR_{log} = ln \frac{a \times d}{b \times c}$$
-Where $a$, $b$, $c$, and $d$ are the four cell sizes. The log odds ratios were converted to $d$s as follows (p. 232):
+where $a$, $b$, $c$, and $d$ are the four cell sizes. The log odds ratios were converted to $d$s as follows (p. 232):
 

### 2019-04-02 code/tables.rmd
Added tau2 with confidence intervals to table 3

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, miktex.verbose = TRUE)
 ```
@@
 A., Vianello, M., Adams, R.
-B., Jr., Bahník, S., Bernstein, M.
+B., Jr., Bahn?k, S., Bernstein, M.
 J., .
@@
 Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
-'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
-'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahník, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
-'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarracín (2011).',
+'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
+'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
+'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarrac?n (2011).',
 'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
@@
 P., Ackerman, R.
-A., Aykutoglu, B., Bahník, S., ...
+A., Aykutoglu, B., Bahn?k, S., ...
 & Carcedo, R.
@@
 'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
-'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
+'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., B?gue, L., Bra?as-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
 "O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")
@@
 K., Attaya, M.
-K., Aucoin, P., Bahník, S., Birch, S., Birt, A.
+K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A.
 R., ...
@@
 (2016).
-Registered replication report: Hart & Albarracín (2011).
+Registered replication report: Hart & Albarrac?n (2011).
 Perspectives on Psychological Science, 11(1), 158-171.',
@@
 # 'Bouwmeester, S., Verkoeijen, P.
-P., Aczel, B., Barbosa, F., Bègue, L., Brañas-Garza, P., ...
+P., Aczel, B., Barbosa, F., B?gue, L., Bra?as-Garza, P., ...
 & Evans, A.
@@
                               'Raw mean difference' = "MD",
-                              'Risk difference' = "RD"))
+                              'Risk difference' = "RD")) %>% 
+  ungroup()
 
@@
   left_join(I2_ci_lb) %>% 
-  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by I2 and upper CI bound
-  mutate(ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]")) %>% 
-  select(rp, effect, k, effect_type, eff_size, s_I2, ci, zero, small, medium, large)
+  arrange(desc(tau2),  desc(tau2_ci.ub)) %>% #sort by tau2 and upper CI bound
+  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
+         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(tau2_ci.ub, 2), nsmall = 2)), "]")) %>% 
+  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau2, tau2_ci, zero, small, medium, large)
 
@@
 ##Table 3
-###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity
+###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
 ```{r heterogeneity-table}
@@
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Effect size estimate", "$I^2$(\\%)", "$I^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
-  add_header_above(c(" " = 7, "Level of heterogeneity" = 4)) %>% 
-  add_header_above(c(" " = 7, "Statistical power" = 4)) %>% 
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Effect size estimate", "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau^2$", "$\\tau^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+  add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>% 
+  add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>% 
   kable_styling("scale_down", font_size = 7) %>%
+  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
   footnote(threeparttable = TRUE, escape = FALSE,
@@
 RP = Replication Project, k = no.
-primary studies, Estimate = Point estimates of effect sizes, $I^2$ 95\\\\% CI = $I^2$ 95\\\\% confidence interval.
-Statistical power was simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.
+primary studies, CI = confidence intervals.
+Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
 Code to reproduce table: osf.io/kf6pt/",
-           alphabet = "These effects were simulated as standardized mean differences")
+           alphabet = "These effects were simulated as standardized mean differences") %>% 
+  landscape()
 

### 2019-04-02 code/helper_functions_tables_figures.r

@@ -52,9 +52,10 @@ est_heterogen_smd_raw <- function(x){
     
   }
   
-  I2_1 <- confint(fit)$random[3, ] #Gives us the I2 estimate and its confidence interval
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate)
-             s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3]) #I2 + CI
+  hetero <- confint(fit)$random[c(1, 3), ] #Gives us the tau2 and I2 estimates with confidence intervals
+  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3]) #I2 + CI
 }
 
 

### 2019-04-08 code/helper_functions_tables_figures.r
Changed code for point-biserial  transformations to exact formula

@@ -67,22 +67,26 @@ est_heterogen_smd_raw <- function(x){
 #Borenstein, M. (2009). Effect sizes for continuous data. In H. Cooper, L. V. Hedges, & J. C. Valentine (Eds.), 
 #The handbook of research synthesis and meta-analysis (2nd ed., pp. 221-235). New York: Russell Sage Foundation.
 
+#Jacobs, P., & Viechtbauer, W. (2017). Estimation of the biserial correlation and its sampling variance for use
+#in meta-analysis. Research Synthesis Methods, 8(2), 161-180.
+#(provide an exact computation of the point-biserial correlation rather than the approximate in Borenstein)
+
+#Note that Jacobs and Viechtbauer (2017) recommend transforming the point-biserial correlation to a 
+#biserial correlation. However, doing so results in impossible values (r > 1) for 37 of the studies; 
+#those with very large effect sizes (> ~2.5 SD)
+
 #For raw mean difference + SE
 transform_SE <- function(ES, SE, n1, n2){ 
   sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2)) #Borenstein, M. (2009). In Cooper & Hedges. p. 224
   d <- ES / sdpooled
-  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes. p.234
-  r <- d / sqrt(d^2 + corr) #p.234
-  data.frame(r = r, n = n1 + n2)
+  data.frame(d = d, n1 = n1, n2 = n2)
 }
 
 #For mean differrence + SD
 transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
-  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #page 226. 
+  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #Borenstein, M. (2009), p. 226. 
   d <- (m1 - m2) / sdpooled
-  corr <- (n1 + n2)^2 / (n1*n2) #correction factor if unequal sample sizes, p.234
-  r <- d / sqrt(d^2 + corr) #p. 234
-  data.frame(r = r, n = n1 + n2)
+  data.frame(d = d, n1 = n1, n2 = n2)
 }
 
 #For Risk difference/OR
[…]

### 2019-04-08 code/figures.rmd
Added r (point-biserial) tau2 figure and caching options

@@
   fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
-  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1)) #estimates out
+  fitr <- rma(measure = "COR", ri = x$r, ni = x$n, data = x)
+  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1),
+             r = fitr$b[[1]], tau2r = fitr$I2) #estimates out
 }
@@
   map_dfr(summarizer, .id = "effect") %>% 
-  mutate(z = abs(z)) #Absolute values since we are interested in effect size rather than direction
+  mutate(z = abs(z), r = abs(r)) #Absolute values since we are interested in effect size rather than direction
 ```
 
-```{r cor_het_z}
+```{r cor_het_effect_size, results = "hide", cache=TRUE}
 #Basic correlations
-cor.test(res2$I2, res2$z) #pearson
+cor.test(res2$I2, res2$z) #pearson I2
 
-I2_fit <- summary(lm(I2 ~ z, data = res2))
+I2_fit <- summary(lm(I2 ~ z, data = res2)) #for annotating figures
 
-cor.test(res2$H2, res2$z) #pearson
+cor.test(res2$tau2r, res2$r) #pearson tau2
+
+tau2_fit <- summary(lm(tau2r ~ r, data = res2))
+
+cor.test(res2$H2, res2$z) #pearson H2
 
@@
 
-```{r plot_res}
+```{r plot_res, cache = TRUE}
 
@@
   geom_smooth(method = "lm", se = TRUE, color = "black") +
-  xlab("Fisher's z") +
   coord_cartesian(ylim = c(0, 100)) +
@@
   geom_smooth(method = "lm", se = TRUE, color = "black") +
-  xlab("Fisher's z") +
   geom_text(x = 0.14, y = 5.9, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
@@
 effect_het
-save_plot("../figures/effect-het.png", effect_het,
-          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
+#save_plot("../figures/effect-het.png", effect_het,
+#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
 
@@
 
-```{r Plot_tau_against_I2, fig.asp = 0.618}
+```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
+r_tau2 <- ggplot(res2, aes(x = r, y = tau2r)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") +
+  geom_text(x = 0.14, y = 75, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
+  theme_classic() +
+  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
+  scale_x_continuous(name = expression(paste("Point-biserial correlation ", italic(r))))
+
+r_tau2
+# ggsave("../figures/r_tau2.png", dpi = 600, height =  4 , width = 6.47)
+
+```
+
+```{r Plot_tau_against_I2, fig.asp = 0.618, cache = TRUE}
 dat3 <- readRDS("../data/tau_simulation_results.RDS")
@@
 
-```{r Density_plot, fig.asp= 0.618}
+```{r Density_plot, fig.asp= 0.618, cache = TRUE}
 dens <- readRDS("../data/power_simulation_results.RDS")

### 2019-04-08 code/helper_functions_tables_figures.r

@@ -60,7 +60,7 @@ est_heterogen_smd_raw <- function(x){
 
 
 #******************************************
-#Functions to transform all effect sizes to the same unit of measurement (Fisher's z)----
+#Functions to transform all effect sizes to the same unit of measurement----
 #******************************************
 
 #Formulas found in: 

### 2019-04-09 code/figures.rmd
Added .gitignore for caching folders
Added tau2 vs. effect size faceted by effect type (NB! OR = SMD)

@@
 
+#Plots of H2 and I2 vs. fisher's z for all effects together
+
 I2 <- ggplot(res2, aes(x = z, y = I2)) +
@@
 # ggsave("../figures/r_tau2.png", dpi = 600, height =  4 , width = 6.47)
+
+```
+
+```{r corr_per_effect_type, cache = TRUE}
+#Each set of input datapoints is meta-analyzed as per the original replication project
+#Then correlated with tau2 per effect type
+#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
+tau2_per_type <- dat %>% 
+  split(.$effect) %>%  
+  map_dfr(est_heterogen_smd_raw, .id = "effect")
+
+tau2_per_type <- dat %>% #This is to add the effect_type names
+  select(effect, effect_type) %>% 
+  distinct() %>% 
+  mutate(effect_type = recode(effect_type, 
+                              d = "Standardized Mean Difference",
+                              'Raw mean difference' = "Mean Difference",
+                              'Risk difference' = "Risk Difference",
+                              'r' = "Correlation")) %>% 
+  left_join(tau2_per_type) %>% 
+  mutate(eff_size = abs(eff_size)) #need the absolute values for plotting
+
+fitter <- function(df){ #function to fit correlations for annotating facet plots
+ fit <- summary(lm(tau2 ~ eff_size, data = df))
+ data.frame(b = format(round(fit$coefficients[2, 1], digits = 2), nsmall = 2), #because map_dfr requires dataframe
+            r = format(round(sqrt(fit$r.squared), digits = 2), nsmall = 2)) #output, the output is kept as two vars
+}
+
+labels <- tau2_per_type %>% 
+  split(.$effect_type) %>% 
+  map_dfr(fitter, .id = "effect_type") %>% 
+  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting
+
+tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
+  geom_point(alpha = 0.5) +
+  geom_line(stat = "smooth", method = "lm", se = FALSE, color = "black", alpha = .5, linetype = "dashed") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
+  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
+  scale_x_continuous(name = "Effect size") +
+  theme_classic() +
+  theme(strip.background = element_blank(), #remove box around titles
+        strip.text = element_text(size = 12),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid")) + 
+  facet_wrap(~effect_type, scales = "free") #use free scales since scales are different
+
+tau2_facet
+# ggsave("../figures/tau2_facet.png", dpi = 600, height =  7, width = 7)
 
@@
 
-ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
+#ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
 ```

### 2019-04-09 code/figures.rmd
Transform point-biserial to truncated biserial corr. per Jacobs & Viecht

@@
   fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
-  fitr <- rma(measure = "COR", ri = x$r, ni = x$n, data = x)
+  fitr <- rma(yi = x$r, vi = x$vi, data = x)
   data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1),

### 2019-04-09 code/helper_functions_tables_figures.r

@@ -106,7 +106,14 @@ transform_d_to_r <- function(d, n1, n2){
   m <- n1 + n2 - 2 #Jacobs and Viechtbauer (2017), p.164
   h <- m/n1 + m/n2 #p. 164
   rpb <- d / sqrt(d^2 + h) #point-biserial correlation, Jacobs and Viechtbauer (2017), equation 5
-  data.frame(r = rpb, n = n1 + n2)
+  p <- n1 / (n1 + n2)
+  q <- n2 / (n1 + n2)
+  zp <- qnorm(p)
+  fzp <- dnorm(zp)
+  rb <- sqrt(p*q) / fzp * rpb #biserial correlation, Jacobs and Viechtbauer (2017), equation 8
+  rb_trunc <- ifelse(rb > 1, 1, rb) #truncate if > 1 to avoid neg. variance. p. 166-167
+  var_rb <- 1/(n1 + n2 -1) * (sqrt(p*q) / fzp - rb_trunc^2)^2 #variance biserial r, approximate formula, eq. 13 (only different from exact formula under extreme conditions p. 172
+  data.frame(r = rb_trunc, vi = var_rb) #I use the approximate formula above to decrease the risk of coding error (due to simplicity)
 }
 
 
@@ -136,7 +143,8 @@ transform_MA <- function(x){
     
   } else if(any(x[, "effect_type"] == "r")){
     
-    out <- data.frame(r = x$effect_size, n = x$Ntotal)
+    out <- metafor::escalc(measure = "COR", ri = x$effect_size, ni =x$Ntotal)
+    out <- data.frame(r = out$yi, vi = out$vi)
     
     # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
     

### 2019-04-09 code/figures.rmd
Dropped z-transformation of biserial correlation. Now r only effect size
Z-transformation not recommended by Jacobs and Viechtbauer (2017) for biserial correlations, p. 176

@@
 ```{r MA_df}
-summarizer <- function(x){
-  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
-  fitr <- rma(yi = x$r, vi = x$vi, data = x)
-  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1),
-             r = fitr$b[[1]], tau2r = fitr$I2) #estimates out
+summarizer <- function(x){#Z-transformation not recommended by Jacobs and Viechtbauer (2017) for biserial correlations, p. 176
+  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
+  data.frame(r = fitr$b[[1]], tau2r = fitr$tau2, I2 = fitr$I2, H2trunc = fitr$H2, H2 = fitr$QE / (fitr$k - 1)) 
 }
@@
   map_dfr(summarizer, .id = "effect") %>% 
-  mutate(z = abs(z), r = abs(r)) #Absolute values since we are interested in effect size rather than direction
+  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
 ```
@@
 #Basic correlations
-cor.test(res2$I2, res2$z) #pearson I2
+cor.test(res2$I2, res2$r) #pearson I2
 
-I2_fit <- summary(lm(I2 ~ z, data = res2)) #for annotating figures
+I2_fit <- summary(lm(I2 ~ r, data = res2)) #for annotating figures
 
@@
 
-cor.test(res2$H2, res2$z) #pearson H2
+cor.test(res2$H2, res2$r) #pearson H2
 
-H2_fit <- summary(lm(H2 ~ z, data = res2))
+H2_fit <- summary(lm(H2 ~ r, data = res2))
 
-cor.test(res2$I2, res2$z, method = "spearman") #spearman
+cor.test(res2$I2, res2$r, method = "spearman") #spearman
 
@@
 
-cor.test(dropped_anchoring$I2, dropped_anchoring$z) #pearson
+cor.test(dropped_anchoring$I2, dropped_anchoring$r) #pearson
 
@@
      d <- data[indices,]
-     fit <- cor.test(formula = ~ I2 + z, data=d)
+     fit <- cor.test(formula = ~ I2 + r, data=d)
      return(fit$estimate)
@@
 
-bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ z + I2)
+bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + I2)
 
@@
      d <- data[indices,]
-     fit <- cor.test(formula = ~ I2 + z, data=d, method = "spearman")
+     fit <- cor.test(formula = ~ I2 + r, data=d, method = "spearman")
      return(fit$estimate)
@@
 options(warn=-1)
-bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ z + I2)
+bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ r + I2)
 options(warn=0)
@@
 #Excluding anchoring effects
-bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ z + I2)
+bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ r + I2)
 
@@
      d <- data[indices,]
-     fit <- cor.test(formula = ~ H2 + z, data=d)
+     fit <- cor.test(formula = ~ H2 + r, data=d)
      return(fit$estimate)
@@
 
-bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ z + H2)
+bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + H2)
 
@@
 
-#Plots of H2 and I2 vs. fisher's z for all effects together
+#Plots of H2 and I2 vs. biserial correlation r for all effects together
 
-I2 <- ggplot(res2, aes(x = z, y = I2)) +
+I2 <- ggplot(res2, aes(x = r, y = I2)) +
   geom_point(alpha = 0.5) +
@@
   coord_cartesian(ylim = c(0, 100)) +
-  geom_text(x = 0.15, y = 80, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
+  geom_text(x = 0.14, y = Inf, vjust = 7, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
   theme_classic() +
   scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
-  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z), ")")))
+  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))
 
-H2 <- ggplot(res2, aes(x = z, y = H2)) + 
+H2 <- ggplot(res2, aes(x = r, y = H2)) + 
   geom_point(alpha = 0.5) +
   geom_smooth(method = "lm", se = TRUE, color = "black") +
-  geom_text(x = 0.14, y = 5.9, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
+  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
   theme_classic() +
   scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
-  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z),")")))
+  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))
 
@@
   geom_smooth(method = "lm", se = TRUE, color = "black") +
-  geom_text(x = 0.14, y = 75, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
+  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
   theme_classic() +
   scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
-  scale_x_continuous(name = expression(paste("Point-biserial correlation ", italic(r))))
+  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))
 

### 2019-04-09 code/helper_functions_tables_figures.r

@@ -113,7 +113,7 @@ transform_d_to_r <- function(d, n1, n2){
   rb <- sqrt(p*q) / fzp * rpb #biserial correlation, Jacobs and Viechtbauer (2017), equation 8
   rb_trunc <- ifelse(rb > 1, 1, rb) #truncate if > 1 to avoid neg. variance. p. 166-167
   var_rb <- 1/(n1 + n2 -1) * (sqrt(p*q) / fzp - rb_trunc^2)^2 #variance biserial r, approximate formula, eq. 13 (only different from exact formula under extreme conditions p. 172
-  data.frame(r = rb_trunc, vi = var_rb) #I use the approximate formula above to decrease the risk of coding error (due to simplicity)
+  data.frame(r = rb_trunc, vi = var_rb, n = n1 + n2) #I use the approximate formula above to decrease the risk of coding error (due to simplicity)
 }
 
 

### 2019-04-10 code/tables.rmd
Added effect description to table 2 + gitignore for table cache

@@
 ###Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
-```{r effect-size-heterogeneity-table}
+```{r effect-size-heterogeneity-table, cache = TRUE}
 #library(kableExtra)
@@
 #Shortened version of APA reference
-papers <- c('Klein, R.
-A., Ratliff, K.
-A., Vianello, M., Adams, R.
-B., Jr., Bahn?k, S., Bernstein, M.
-J., .
-.
-.
-Nosek, B.
-A.
-(2014).
-Investigating variation in replicability: A "many labs" replication project.',
-'Ebersole, C.
-R., Atherton, O.
-E., Belanger, A.
-L., Skulborstad, H.
-M., Allen, J.
-M., Banks, J.
-B., ...
-& Brown, E.
-R.
-(2016).
-Many Labs 3: Evaluating participant pool quality across the academic semester via replication.',
-'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
-'Alogna, V. K., Attaya, M. K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A. R., ... & Buswell, K. (2014). Registered replication report: Schooler and engstler-schooler (1990).',
-'Eerland, A., Sherrill, A. M., Magliano, J. P., Zwaan, R. A., Arnal, J. D., Aucoin, P., ... & Crocker, C. (2016). Registered replication report: Hart & Albarrac?n (2011).',
-'Hagger, M. S., Chatzisarantis, N. L., Alberts, H., Anggono, C. O., Batailler, C., Birt, A. R., ... & Calvillo, D. P. (2016). A multilab preregistered replication of the ego-depletion effect.',
-'Cheung, I., Campbell, L., LeBel, E.
-P., Ackerman, R.
-A., Aykutoglu, B., Bahn?k, S., ...
-& Carcedo, R.
-J.
-(2016).
-Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).',
-'Wagenmakers, E. J., Beek, T., Dijkhoff, L., Gronau, Q. F., Acosta, A., Adams Jr, R. B., ... & Bulnes, L. C. (2016). Registered Replication Report: Strack, Martin, & Stepper (1988).',
-'Bouwmeester, S., Verkoeijen, P. P., Aczel, B., Barbosa, F., B?gue, L., Bra?as-Garza, P., ... & Evans, A. M. (2017). Registered Replication Report: Rand, Greene, and Nowak (2012).',
-"O'Donnell, M., Nelson, L., McLatchie, N. M., & Lynott, D. J. (2017). Registered Replication Report: Dijksterhuis & van Knippenberg (1998)")
+papers <- c('Klein et al. (2014)', 
+'Ebersole et al. (2016)',
+'Alogna et al. (2014)',
+'Alogna et al. (2014)',
+'Eerland et al. (2016)',
+'Hagger et al. (2016)',
+'Cheung et al. (2016)',
+'Wagenmakers et al. (2016)',
+'Bouwmeester et al. (2017)',
+"O'Donnell et al. (2017)")
 
@@
 
+description <- c("Two correlational effects: 'Gender math attitude' compared implicit attitudes (IAT) towards math between genders and 'IAT correlation math' correlated implicit attitudes with self-reported measures.
+The remainder were experiments with two independent groups.
+The groups were primed in some way (Anchoring 1-4; low vs.
+high category scales; norm of reciprocity; flag priming; currency priming), asked to imagine slightly different situations (Sunk costs; gain vs.
+loss framing; gambler's fallacy; imagined contact) or asked their agreement with statements presented differently (Allowed vs.
+forbidden; quote attribution).
+", #ML1
+            "Several effects were experiments with two independent groups.
+The groups were either primed in some way (Power and perspective; warmth perceptions; subjective distance interaction), saw slightly different statements (Elaboration likelihood interaction; credentials interaction) or experienced different situations (weight embodiment).
+Examined interactions were between treatment conditions and participant characteristics.
+One priming effect (metaphor) compared two treatment groups with a control.
+One effect was correlational: 'persistence and conscientiousness' was measured by an unsolvable anagram task and self-report respectively.
+The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML2
+                 "Verbal overshadowing 1; Independent groups experiment.
+Participants either described a robber after watching a video or listed countries/capitals.
+DV = correctly identifying the robber in a lineup.", #RRR1
+            "Verbal overshadowing 2; Different from 1 only in that the filler task took place before the descriptive task instead of after.", #RRR2
+                 "Grammar on intentionality/intention attribution/detailed processing; Independent groups experiment with three outcome variables.
+Actions either described in imperfect or perfect.", #RRR3
+            "Ego depletion; Independent groups experiment. Participants either assigned to a cognitively demanding task or a neutral and performance was then measured in a subsequent task.", #RRR4
+            "Commitment on neglect/exit; Independent groups experiment with two outcome variables. Participants either primed to think about commitment or independence from partner.", #RRR5
+            "Facial feedback hypothesis; Independent groups experiment. Participants either induced to 'smile' or 'pouth' with a pen and then rated funniness of cartoons. ", #RRR6
+            "Intuitive cooperation; Independent groups experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
+                 "Professor priming; Participants were assigned to groups and primed with either a 'professor' or 'hooligan' stimuli. DV = Percentage correct trivia answers.") #RRR8
+
+sample_settings <- c("9 online, 28 in lab, 25 US, Only 3/36 labs did not recruit explicitly from student populations.
+25/36>94% from university students, 7 unclear, 2 non-students", #https://osf.io/g3udn/, ML1
+                     "1 mturk sample, rest students, 2 Canadian samples, remainder US. Only mturk sample was online" #ML2, need to add the rest later
+                     )
+
 summary.table <- dat %>% 
@@
                            else{sum(Ntotal) / Effects}) %>% #average across effects
-  mutate(Paper = papers) %>% 
+  mutate(Paper = papers,
+         'Description of Effects' = description) %>% 
   select(RP = rp, Paper, everything()) #change order of columns
@@
 summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
-  kable_styling() %>% 
-  column_spec(2, width = "25em") %>% #specify width of paper column
+  kable_styling("scale_down", font_size = 7) %>% 
+  column_spec(2, width = "8em") %>% #specify width of paper column
+  column_spec(7, width = "25em") %>% 
   footnote(threeparttable = TRUE,
@@
 
-```{r prep-heterogeneity-table}
+```{r prep-heterogeneity-table, cache = TRUE}
 #library(metafor)
@@
 ###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
-```{r heterogeneity-table}
+```{r heterogeneity-table, cache = TRUE}
 #library(kableExtra)

### 2019-04-11 code/tables.rmd
Added table 2 remaining descriptions + column with sample/settings
Also added number of US countries in parenthesis to K

@@
 The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML2
-                 "Verbal overshadowing 1; Independent groups experiment.
-Participants either described a robber after watching a video or listed countries/capitals.
-DV = correctly identifying the robber in a lineup.", #RRR1
+                 "Verbal overshadowing 1; Independent two-group experiment.
+Participants either described a robber after watching a video or listed countries/capitals and after a filler task attempted to identify the robber in a lineup.", #RRR1
             "Verbal overshadowing 2; Different from 1 only in that the filler task took place before the descriptive task instead of after.", #RRR2
-                 "Grammar on intentionality/intention attribution/detailed processing; Independent groups experiment with three outcome variables.
+                 "Grammar on intentionality/intention attribution/detailed processing; Independent two-group experiment with three outcome variables.
 Actions either described in imperfect or perfect.", #RRR3
-            "Ego depletion; Independent groups experiment. Participants either assigned to a cognitively demanding task or a neutral and performance was then measured in a subsequent task.", #RRR4
-            "Commitment on neglect/exit; Independent groups experiment with two outcome variables. Participants either primed to think about commitment or independence from partner.", #RRR5
-            "Facial feedback hypothesis; Independent groups experiment. Participants either induced to 'smile' or 'pouth' with a pen and then rated funniness of cartoons. ", #RRR6
-            "Intuitive cooperation; Independent groups experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
-                 "Professor priming; Participants were assigned to groups and primed with either a 'professor' or 'hooligan' stimuli. DV = Percentage correct trivia answers.") #RRR8
+            "Ego depletion; Independent two-group experiment.
+Participants either assigned to a cognitively demanding task or a neutral, and performance was then measured in a subsequent cognitive task.", #RRR4
+            "Commitment on neglect/exit; Independent two-group experiment with two outcome variables. Participants either primed to think about commitment to or independence from partner.", #RRR5
+            "Facial feedback hypothesis; Independent two-group experiment. Participants either induced to 'smile' or 'pouth' with a pen and then rated funniness of cartoons. ", #RRR6
+            "Intuitive cooperation; Independent two-group experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
+                 "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.") #RRR8
 
-sample_settings <- c("9 online, 28 in lab, 25 US, Only 3/36 labs did not recruit explicitly from student populations.
-25/36>94% from university students, 7 unclear, 2 non-students", #https://osf.io/g3udn/, ML1
-                     "1 mturk sample, rest students, 2 Canadian samples, remainder US. Only mturk sample was online" #ML2, need to add the rest later
-                     )
+US_online <- dat %>% #Extract the (max when multiple effects) number of US/online labs per RP
+  group_by(rp, effect) %>% 
+  summarize(US = sum(country == "USA"),
+            online = sum(in_lab == 0)) %>% 
+  group_by(rp) %>% 
+  summarize(US = max(US),
+            online = max(online)) %>% 
+  ungroup() %>% select(US, online)
+
+sample_settings <- c("26/36 samples were primarily university students, 3 general population and 7 undescribed.
+9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
+                     "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
+                     "31/32 samples were undergraduate students between 18-25, 1 general population which was also the only online sample.", #RRR1
+                     "22/23 samples were undergraduate students between 18-25, 1 general population which was also the only online sample.", #RRR2
+                     "11/12 samples were undergraduate students mostly between 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
+                     "All samples consisted of in-lab undergraduate students", #RRR4
+                     "All samples consisted of in-lab undergraduate students between 18-25", #RRR5
+               "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
+               'All samples consisted of in-lab undergraduate students between 18-34.', #RRR7
+                     "All samples consisted of in-lab undergraduate students betweeb 18-25") #RRR8
+
+#1) what kind of samples
 
@@
   group_by(rp) %>% 
-  summarize(k = n_distinct(Site),
-            Countries = n_distinct(country), 
+  summarize(Countries = n_distinct(country),
+            k = n_distinct(Site), 
             Effects = n_distinct(effect),
@@
   mutate(Paper = papers,
-         'Description of Effects' = description) %>% 
-  select(RP = rp, Paper, everything()) #change order of columns
+         'Sample and Settings' = sample_settings,
+         'Description of Effects' = description,
+         'K (US)' = paste0(k, " (", US_online$US, ")")) %>% 
+  select(RP = rp, Paper, Countries,'K (US)', everything(), -k) #change order of columns
 
-summary.table %>% knitr::kable("latex", booktabs = T, digits = 0) %>% 
-  kable_styling("scale_down", font_size = 7) %>% 
-  column_spec(2, width = "8em") %>% #specify width of paper column
-  column_spec(7, width = "25em") %>% 
+summary.table %>% knitr::kable("latex", 
+                               booktabs = TRUE,
+                               digits = 0) %>% 
+  kable_styling("repeat_header", font_size = 7) %>% 
+  column_spec(2, width = "7em") %>% #specify width of paper column 
+  column_spec(7, width = "16em") %>% 
+  column_spec(8, width = "30em") %>% 
   footnote(threeparttable = TRUE,
@@
 Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
-RP = Replication Project, k = no.
-primary studies, ML = Many Labs, RRR = Registered Replication Report.
-Code to reproduce table: osf.io/kf6pt/")
+RP = Replication Project, K (US) = no.
+primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report.
+Code to reproduce table: osf.io/kf6pt/") %>%
+  landscape()
 ```

### 2019-04-11 code/helper_functions_tables_figures.r

@@ -112,7 +112,7 @@ transform_d_to_r <- function(d, n1, n2){
   fzp <- dnorm(zp)
   rb <- sqrt(p*q) / fzp * rpb #biserial correlation, Jacobs and Viechtbauer (2017), equation 8
   rb_trunc <- ifelse(rb > 1, 1, rb) #truncate if > 1 to avoid neg. variance. p. 166-167
-  var_rb <- 1/(n1 + n2 -1) * (sqrt(p*q) / fzp - rb_trunc^2)^2 #variance biserial r, approximate formula, eq. 13 (only different from exact formula under extreme conditions p. 172
+  var_rb <- 1/(n1 + n2 -1) * (sqrt(p*q) / fzp - rb_trunc^2)^2 #variance biserial r, approximate formula, eq. 13 
   data.frame(r = rb_trunc, vi = var_rb, n = n1 + n2) #I use the approximate formula above to decrease the risk of coding error (due to simplicity)
 }
 

### 2019-04-15 code/power_simulation.r
Add function to simulate tau2 for correlations/biserial correaltions

@@ -26,9 +26,9 @@ library(tidyr) #for 'spread'
 
 dat <- read_csv("../data/collated_summary_data.csv")
 
-
+source("./helper_functions_tables_figures.r") #for function to transform d to biserial correlation
 #******************************************
-#Simulation function----
+#Simulation functions----
 #******************************************
 simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies to a single list object (effect), see next section
   
@@ -120,6 +120,74 @@ simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies 
   bind_rows(output) #Combine output across tau-values into one dataframe
 }
 
+
+#*************************
+simulate_biserial <- function(effect, reps, tau){ #similar to above, but only for biserial correlations, effect size -> 0
+  
+  K <- effect$K #Number of studies
+  N <- effect$Ntotal #Sample sizes for all K studies
+  output <- vector("list", length(tau)) #empty list for output
+  
+  if(effect$type == "r"){ #If 'correlation'
+    
+    for(t in seq_along(tau)){ #loop over each tau-value
+      
+      output[[t]] <- map_dfr(1:reps, possibly(function(x){ #For each tau-value repeat below "reps" times and bind into dataframe
+        
+        rho <- rnorm(n = K, mean = 0, sd = tau[t]) #draw effect sizes for each K at given tau
+        
+        fr <- rnorm(n = K, mean = rho, sd = sqrt(1 / (N - 3))) #draw observed correlations (fisher's z) for each k
+        
+        fit <- rma(yi = fr, vi = 1 / (N - 3), method = "REML") #meta-analysis of fisher's z, each study weighted by its N
+        
+        data.frame(tau2_hat = fit$tau2, I2 = fit$I2, Qp = fit$QEp, 
+                   tau = tau[t], tau_index = t)
+        
+      }, otherwise = NULL)) #If rma does not converge, drop that iteration ('possibly' function)
+    }
+    
+  }else{ #for all non-'correlations' transform into biserial correlations
+    
+    n_c <- effect$ncontrol #observed control group sizes
+    n_t <- effect$ntreatment #observed treatment group sizes
+    
+    for(t in seq_along(tau)){
+      
+      output[[t]] <- map_dfr(1:reps, possibly(function(x){
+        
[…]

### 2019-04-16 code/power_simulation.r
Prepped code to run biserial simulation

@@ -178,16 +178,7 @@ simulate_biserial <- function(effect, reps, tau){ #similar to above, but only fo
   bind_rows(output)
 }
 
-#******************************
-#apply biserial simulation function (first run data prep)
-tau2 <- c(1/321, 1/107, 3/107)
-aa <- lapply(dat2, simulate_biserial, reps = 10, tau = sqrt(tau2))
-#There are some effects in ML3 which don't have ntreatment or ncontrol, see str(aa, max.level = 1)
-#these thus need to be treated as correlations in the simulations. [actually, we decided that this
-#is what we'll do with all these correlations anyway]
-# -> fixed
 
-fit <- rma(measure = "UCOR", ri = effect_size, ni = Ntotal,  data = x, vtype = "UB") #model used by ML3
 #******************************************
 #Simulation 1 -  estimate tau values that correspond to small/medium/large I2----
 #******************************************
@@ -280,6 +271,21 @@ system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progr
                            tau = c(0, dat5[[e]][[2]]), effect_size = "zero") #NB! 1e4 reps here is about 14 hours on my (fairly slow) machine
   cat("...RS",e, "/37") #see progress
   if (e%%5 == 0 | e == 37) saveRDS(res2, "../data/power_simulation_results.RDS") #save ocassionally and at finish
+})
+
+#******************************
+#apply biserial simulation function (first run data prep)
+tau <- sqrt(c(1/321, 1/107, 3/107)) #tau2 values for Fisher's z corresponding to small/medium/large I2 with N = 108
+
+##Simulation
+set.seed(60)
+res_biserial <- vector("list", length(dat2)) 
+
+system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
+  res_biserial[[e]] <- simulate_biserial(dat2[[e]], reps = 10,
+                           tau = c(0, tau)) #NB! 1e4 reps here is about 14 hours on my (fairly slow) machine
+  cat("...RS",e, "/37") #see progress
+  if (e%%5 == 0 | e == 37) saveRDS(res_biserial, "../data/biserial_simulation_results.RDS") #save ocassionally and at finish
 })
 
 #*********************

### 2019-04-16 code/tables.rmd
Added tau2 from correlations to table 3

@@
 
+#Transform effect sizes to raw correlations
+#'transform_MA' is a sourced function
+dat2 <- dat %>% 
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe
+
+summarizer <- function(x){ #function to run rma on transformed biserial and correlations
+  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
+  ci <- confint(fitr)$random[c(1, 3), ]
+  data.frame(r = fitr$b[[1]], tau2 = fitr$tau2, tau2.lb = ci[1, 2], tau2.ub = ci[1, 3],
+             I2 = fitr$I2, I2.lb = ci[2, 2], I2.ub = ci[2, 3]) 
+}
+
+#estimate tau2 for tranformed biserial and pearson's correlations
+res2 <- dat2 %>% 
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map_dfr(summarizer, .id = "effect")
+
+#NB! note that for low vs. high category scales, the I2 lower bound is zero, but after transformation
+#the tau2 lower bound is *not* zero. This is an indication of the problems with effect size tranformations.
+
+res <- res %>%
+  mutate(tau2 = res2$tau2, #For table 3, report tau2 and transformed effect sizes (biserial correlations)
+         tau2_ci.lb = res2$tau2.lb,
+         tau2_ci.ub = res2$tau2.ub,
+         r = res2$r)
+
 #Add rp and k to the data-frame and prep for table
@@
 #Summary of simulation results, needs to be combined with main part of table
-I2_ci_lb <- dens %>% 
+I2_power <- dens %>% 
   bind_rows(.id = "effect") %>% 
@@
 het <-  het %>% 
-  left_join(I2_ci_lb) %>% 
-  arrange(desc(tau2),  desc(tau2_ci.ub)) %>% #sort by tau2 and upper CI bound
+  left_join(I2_power) %>% 
+  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
   mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
          tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(tau2_ci.ub, 2), nsmall = 2)), "]")) %>% 
-  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau2, tau2_ci, zero, small, medium, large)
+  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau2, tau2_ci, zero, small, medium, large)
 
@@
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "k", "Effect type", "Effect size estimate", "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau^2$", "$\\tau^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
-  add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>% 
-  add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>% 
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "r*" , "$\\tau^2$", "$\\tau^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+  add_header_above(c(" " = 10, "Level of heterogeneity" = 4)) %>% 
+  add_header_above(c(" " = 10, "Type I Error Rate & Statistical Power" = 4)) %>% 
   kable_styling("scale_down", font_size = 7) %>%
@@
 RP = Replication Project, k = no.
-primary studies, CI = confidence intervals.
+primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations.
 Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.

### 2019-04-16 code/figures.rmd
Added plot code for tau2 densitites +  'summarizer' function as sourced

@@
 
-```{r transform_df}
+```{r transform_effect_and_compute_rma}
 #Transform effect sizes to raw correlations
@@
 
-```
-
-```{r MA_df}
-summarizer <- function(x){#Z-transformation not recommended by Jacobs and Viechtbauer (2017) for biserial correlations, p. 176
-  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
-  data.frame(r = fitr$b[[1]], tau2r = fitr$tau2, I2 = fitr$I2, H2trunc = fitr$H2, H2 = fitr$QE / (fitr$k - 1)) 
-}
-#Default method of metafor for calculating H2 is truncated at one.
-Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1).
-This method approximates H2 as if we were using the Dersimonian and Laird estimate of tau2, although we use REML.
-See Higgins & Thompson, 2002 and ?print.rma.uni.
-
-#Higgins, J., & Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. Statistics in medicine, 21(11), 1539-1558.
-
+#compute random effect meta-analysis of transformed effects
+#'summarizer' is a sourced function
 res2 <- res %>% 
@@
 
-cor.test(res2$tau2r, res2$r) #pearson tau2
+cor.test(res2$tau2, res2$r) #pearson tau2
 
-tau2_fit <- summary(lm(tau2r ~ r, data = res2))
+tau2_fit <- summary(lm(tau2 ~ r, data = res2))
 
@@
 ```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
-r_tau2 <- ggplot(res2, aes(x = r, y = tau2r)) + 
+r_tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
   geom_point(alpha = 0.5) +
@@
 ```{r Density_plot, fig.asp= 0.618, cache = TRUE}
+
+#1) I2 plot----
 dens <- readRDS("../data/power_simulation_results.RDS")
@@
 
-ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
+I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
   geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
@@
 #ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
+
+#2) tau2 plot----
+
+dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
+names(dens_tau2) <-  sort(unique(dat$effect))
+
+#Simulated data at various heterogeneity levels, prep for plotting
+tau2_dist <- dens_tau2 %>% 
+  bind_rows(.id = "effect") %>% 
+  rename(Heterogeneity = tau_index) %>% 
+  mutate(Heterogeneity = recode(Heterogeneity,
+                            '1' = "Zero",
+                            '2' = "Small",
+                            '3' = "Medium",
+                            '4' = "Large"),
+         Heterogeneity = as.factor(Heterogeneity))
+
+#Observed tau22 estimates, i.e, results from main table, see table.rmd
+#Effects estimated with sourced function 'summarizer'
+observed <- dat %>% 
+  split(.$effect) %>%  
+  map_dfr(summarizer, .id = "effect") %>% 
+  select(effect, tau2 = tau2) %>%
+  mutate(Heterogeneity = "Observed")
+
+tau2_plot <- ggplot(tau2_dist, aes(x = tau2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
+  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
+  geom_density(alpha = 0.3) +
+  theme_classic() +
+  coord_cartesian(xlim = c(0, 100))  +
+  scale_fill_brewer(palette = "Dark2",
+                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
+                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
+                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+  scale_color_brewer(palette = "Dark2", 
+                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+  theme(legend.position = c(0.85, 0.71),
+        legend.background = element_rect(linetype = "solid", color = "black")) +
+  scale_y_continuous(name = "Density") +
+  scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
+  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
+
+#ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
+
+#3) combine I2-tau2-density-plots----
+
+densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
+densities
+#save_plot("../figures/densities_het.png", densities,
+#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
+
 ```

### 2019-04-16 code/tables.rmd
Added plot code for tau2 densitites +  'summarizer' function as sourced

@@
 
-summarizer <- function(x){ #function to run rma on transformed biserial and correlations
-  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
-  ci <- confint(fitr)$random[c(1, 3), ]
-  data.frame(r = fitr$b[[1]], tau2 = fitr$tau2, tau2.lb = ci[1, 2], tau2.ub = ci[1, 3],
-             I2 = fitr$I2, I2.lb = ci[2, 2], I2.ub = ci[2, 3]) 
-}
-
 #estimate tau2 for tranformed biserial and pearson's correlations
+#'summarizer' is a sourced function
 res2 <- dat2 %>% 

### 2019-04-16 code/power_simulation.r
Ran biserial simulation and saved results

@@ -274,7 +274,7 @@ system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progr
 })
 
 #******************************
-#apply biserial simulation function (first run data prep)
+#**apply biserial simulation function----
 tau <- sqrt(c(1/321, 1/107, 3/107)) #tau2 values for Fisher's z corresponding to small/medium/large I2 with N = 108
 
 ##Simulation
@@ -282,7 +282,7 @@ set.seed(60)
 res_biserial <- vector("list", length(dat2)) 
 
 system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
-  res_biserial[[e]] <- simulate_biserial(dat2[[e]], reps = 10,
+  res_biserial[[e]] <- simulate_biserial(dat2[[e]], reps = 1e4,
                            tau = c(0, tau)) #NB! 1e4 reps here is about 14 hours on my (fairly slow) machine
   cat("...RS",e, "/37") #see progress
   if (e%%5 == 0 | e == 37) saveRDS(res_biserial, "../data/biserial_simulation_results.RDS") #save ocassionally and at finish

### 2019-04-16 code/figures.rmd

@@
   scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
-  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))
+  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
 
@@
   scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
-  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))
+  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
 
@@
   scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
-  scale_x_continuous(name = expression(paste("Biserial correlation ", italic(r))))
+  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
 
@@
 
+#effects that were transformed from OR to SMD
+OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
+           'Norm of reciprocity', 'Low vs. high category scales') #refit as OR
+
+OR_fit <- function(x){ #fit rma to odds raios
+  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
+  hetero <- confint(fit)$random[c(1, 3), ] 
+  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}
+
+fit_OR <- dat %>% 
+  filter(effect %in% OR2d) %>% 
+  split(.$effect) %>% 
+  map_dfr(OR_fit, .id = "effect")
+
 tau2_per_type <- dat %>% #This is to add the effect_type names
@@
   left_join(tau2_per_type) %>% 
-  mutate(eff_size = abs(eff_size)) #need the absolute values for plotting
+  filter(!effect %in% OR2d) %>% #drop old SMD converted OR
+  bind_rows(fit_OR) %>% #and instead add OR meta-analyzed as OR
+  mutate(effect_type = ifelse(is.na(effect_type), "Odds Ratio", effect_type),
+         eff_size = abs(eff_size)) #need the absolute values for plotting
 
@@
 
-dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
-names(dens_tau2) <-  sort(unique(dat$effect))
-
-#Simulated data at various heterogeneity levels, prep for plotting
-tau2_dist <- dens_tau2 %>% 
-  bind_rows(.id = "effect") %>% 
-  rename(Heterogeneity = tau_index) %>% 
-  mutate(Heterogeneity = recode(Heterogeneity,
-                            '1' = "Zero",
-                            '2' = "Small",
-                            '3' = "Medium",
-                            '4' = "Large"),
-         Heterogeneity = as.factor(Heterogeneity))
-
-#Observed tau22 estimates, i.e, results from main table, see table.rmd
-#Effects estimated with sourced function 'summarizer'
-observed <- dat %>% 
-  split(.$effect) %>%  
-  map_dfr(summarizer, .id = "effect") %>% 
-  select(effect, tau2 = tau2) %>%
-  mutate(Heterogeneity = "Observed")
-
-tau2_plot <- ggplot(tau2_dist, aes(x = tau2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
-  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
-  geom_density(alpha = 0.3) +
-  theme_classic() +
-  coord_cartesian(xlim = c(0, 100))  +
-  scale_fill_brewer(palette = "Dark2",
-                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
-                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
-                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  scale_color_brewer(palette = "Dark2", 
-                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  theme(legend.position = c(0.85, 0.71),
-        legend.background = element_rect(linetype = "solid", color = "black")) +
-  scale_y_continuous(name = "Density") +
-  scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
-  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
-
-#ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
-
-#3) combine I2-tau2-density-plots----
-
-densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
-densities
-#save_plot("../figures/densities_het.png", densities,
-#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
+# dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
+# names(dens_tau2) <-  sort(unique(dat$effect))
+# 
+# #Simulated data at various heterogeneity levels, prep for plotting
+# tau2_dist <- dens_tau2 %>% 
+#   bind_rows(.id = "effect") %>% 
+#   rename(Heterogeneity = tau_index) %>% 
+#   mutate(Heterogeneity = recode(Heterogeneity,
+#                             '1' = "Zero",
+#                             '2' = "Small",
+#                             '3' = "Medium",
+#                             '4' = "Large"),
+#          Heterogeneity = as.factor(Heterogeneity))
+# 
+# #Observed tau22 estimates, i.e, results from main table, see table.rmd
+# #Effects estimated with sourced function 'summarizer'
+# observed <- dat %>% 
+#   split(.$effect) %>%  
+#   map_dfr(summarizer, .id = "effect") %>% 
+#   select(effect, tau2 = tau2) %>%
+#   mutate(Heterogeneity = "Observed")
+# 
+# tau2_plot <- ggplot(tau2_dist, aes(x = tau2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
+#   geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
+#   geom_density(alpha = 0.3) +
+#   theme_classic() +
+#   coord_cartesian(xlim = c(0, 100))  +
+#   scale_fill_brewer(palette = "Dark2",
+#                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+#                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+#   scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
+#                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
+#                         labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+#   scale_color_brewer(palette = "Dark2", 
+#                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+#                      labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
+#   theme(legend.position = c(0.85, 0.71),
+#         legend.background = element_rect(linetype = "solid", color = "black")) +
+#   scale_y_continuous(name = "Density") +
+#   scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
+#   guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
+# 
+# #ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
+# 
+# #3) combine I2-tau2-density-plots----
+# 
+# densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
+# densities
+# #save_plot("../figures/densities_het.png", densities,
+# #          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
 

### 2019-04-16 code/figures.rmd
Fixed code for tau2 density plot

@@
 
-```{r Density_plot, fig.asp= 0.618, cache = TRUE}
+```{r Density_plot, cache = TRUE}
 
@@
 
-# dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
-# names(dens_tau2) <-  sort(unique(dat$effect))
-# 
-# #Simulated data at various heterogeneity levels, prep for plotting
-# tau2_dist <- dens_tau2 %>% 
-#   bind_rows(.id = "effect") %>% 
-#   rename(Heterogeneity = tau_index) %>% 
-#   mutate(Heterogeneity = recode(Heterogeneity,
-#                             '1' = "Zero",
-#                             '2' = "Small",
-#                             '3' = "Medium",
-#                             '4' = "Large"),
-#          Heterogeneity = as.factor(Heterogeneity))
-# 
-# #Observed tau22 estimates, i.e, results from main table, see table.rmd
-# #Effects estimated with sourced function 'summarizer'
-# observed <- dat %>% 
-#   split(.$effect) %>%  
-#   map_dfr(summarizer, .id = "effect") %>% 
-#   select(effect, tau2 = tau2) %>%
-#   mutate(Heterogeneity = "Observed")
-# 
-# tau2_plot <- ggplot(tau2_dist, aes(x = tau2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
-#   geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
-#   geom_density(alpha = 0.3) +
-#   theme_classic() +
-#   coord_cartesian(xlim = c(0, 100))  +
-#   scale_fill_brewer(palette = "Dark2",
-#                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-#                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-#   scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
-#                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
-#                         labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-#   scale_color_brewer(palette = "Dark2", 
-#                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-#                      labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-#   theme(legend.position = c(0.85, 0.71),
-#         legend.background = element_rect(linetype = "solid", color = "black")) +
-#   scale_y_continuous(name = "Density") +
-#   scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
-#   guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
-# 
-# #ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
-# 
-# #3) combine I2-tau2-density-plots----
-# 
-# densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
-# densities
-# #save_plot("../figures/densities_het.png", densities,
-# #          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
+dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
+names(dens_tau2) <-  sort(unique(dat$effect))
 
+# Simulated data at various heterogeneity levels, prep for plotting
+tau2_dist <- dens_tau2 %>%
+ bind_rows(.id = "effect") %>%
+ rename(Heterogeneity = tau_index) %>%
+ mutate(Heterogeneity = recode(Heterogeneity,
+                             '1' = "Zero",
+                             '2' = "Small",
+                             '3' = "Medium",
+                             '4' = "Large"),
+          Heterogeneity = as.factor(Heterogeneity))
+
+# Observed tau22 estimates, i.e, results from main table, see table.rmd
+# Effects transformed and estimated with sourced functions 'transform_MA' and 'summarizer'
+observed_tau2 <- dat %>%
+   split(.$effect) %>%
+   map(transform_MA) %>% 
+   map_dfr(summarizer, .id = "effect") %>%
+   select(effect, tau2) %>%
+   mutate(Heterogeneity = "Observed")
+
+tau2_plot <- ggplot(tau2_dist, aes(x = tau2_hat, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
+  geom_histogram(data = observed_tau2, aes(y = ..density.., x = tau2), bins = 200, alpha = 1) +
+  geom_density(alpha = 0.3) +
+  theme_classic() +
+  coord_cartesian(xlim = c(0, 0.05)) +
+  scale_fill_brewer(palette = "Dark2",
+                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+                     labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
+  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
+                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+                         labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
+  scale_color_brewer(palette = "Dark2",
+                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
+                      labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
+  theme(legend.position = c(0.85, 0.71),
+       legend.background = element_rect(linetype = "solid", color = "black")) +
+  scale_y_continuous(name = "Density") +
+  scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
+  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
+
+#ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
+
+#3) combine I2-tau2-density-plots----
+densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
+densities
+
+# save_plot("../figures/densities_het.png", densities,
+     #      nrow = 2, base_height = 5, base_width = 5, dpi = 600)
 ```

### 2019-04-16 code/tables.rmd
Added linespace to table 2

@@
                                booktabs = TRUE,
-                               digits = 0) %>% 
-  kable_styling("repeat_header", font_size = 7) %>% 
+                               digits = 0,
+                               linesep = "\\addlinespace",
+                               longtable = TRUE) %>% 
+  kable_styling(c("hold_position", "repeat_header"), font_size = 7) %>% 
   column_spec(2, width = "7em") %>% #specify width of paper column 
@@
   column_spec(8, width = "30em") %>% 
-  footnote(threeparttable = TRUE,
-           general = "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
+  landscape()
+```
+Note: "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
 Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
@@
 primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report.
-Code to reproduce table: osf.io/kf6pt/") %>%
-  landscape()
-```
+Code to reproduce table: osf.io/kf6pt/"
 

### 2019-04-16 code/figures.rmd
Changed order of plots in output to match paper

@@
 
-```{r transform_effect_and_compute_rma}
-#Transform effect sizes to raw correlations
-#'transform_MA' is a sourced function
-res <- dat %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe
-
-#compute random effect meta-analysis of transformed effects
-#'summarizer' is a sourced function
-res2 <- res %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(summarizer, .id = "effect") %>% 
-  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
-```
-
-```{r cor_het_effect_size, results = "hide", cache=TRUE}
-#Basic correlations
-cor.test(res2$I2, res2$r) #pearson I2
-
-I2_fit <- summary(lm(I2 ~ r, data = res2)) #for annotating figures
-
-cor.test(res2$tau2, res2$r) #pearson tau2
-
-tau2_fit <- summary(lm(tau2 ~ r, data = res2))
-
-cor.test(res2$H2, res2$r) #pearson H2
-
-H2_fit <- summary(lm(H2 ~ r, data = res2))
-
-cor.test(res2$I2, res2$r, method = "spearman") #spearman
-
-##Excluding anchoring effects
-dropped_anchoring <- res2 %>%
-  filter(!grepl("Anchoring", effect))
-
-cor.test(dropped_anchoring$I2, dropped_anchoring$r) #pearson
-
-#bootstrap confidence intervals
-#code by Amir Abdol
-
-#I2
-pear <- function(formula, data, indices){ #pearson
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ I2 + r, data=d)
-     return(fit$estimate)
-}
-
-bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + I2)
-
-I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
-
-spear <- function(formula, data, indices){ #spearman
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ I2 + r, data=d, method = "spearman")
-     return(fit$estimate)
-}
-
-options(warn=-1)
-bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ r + I2)
-options(warn=0)
-
-I2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
-
-#Excluding anchoring effects
-bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ r + I2)
-
-I2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
-
-#H2
-pear <- function(formula, data, indices){
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ H2 + r, data=d)
-     return(fit$estimate)
-}
-
-bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + H2)
-
-H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
-
-```
-
-```{r plot_res, cache = TRUE}
-
-#Plots of H2 and I2 vs. biserial correlation r for all effects together
-
-I2 <- ggplot(res2, aes(x = r, y = I2)) +
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") +
-  coord_cartesian(ylim = c(0, 100)) +
-  geom_text(x = 0.14, y = Inf, vjust = 7, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
-  theme_classic() +
-  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
-  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
-
-H2 <- ggplot(res2, aes(x = r, y = H2)) + 
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") +
-  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
-  theme_classic() +
-  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
-  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
-
-effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
-effect_het
-#save_plot("../figures/effect-het.png", effect_het,
-#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
-
-```
-
-```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
-r_tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") +
-  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
-  theme_classic() +
-  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
-  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
-
-r_tau2 
-# ggsave("../figures/r_tau2.png", dpi = 600, height =  4 , width = 6.47)
-
-```
-
-```{r corr_per_effect_type, cache = TRUE}
-#Each set of input datapoints is meta-analyzed as per the original replication project
-#Then correlated with tau2 per effect type
-#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
-tau2_per_type <- dat %>% 
-  split(.$effect) %>%  
-  map_dfr(est_heterogen_smd_raw, .id = "effect")
-
-#effects that were transformed from OR to SMD
-OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
-           'Norm of reciprocity', 'Low vs. high category scales') #refit as OR
-
-OR_fit <- function(x){ #fit rma to odds raios
-  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
-  hetero <- confint(fit)$random[c(1, 3), ] 
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
-             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
-             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}
-
-fit_OR <- dat %>% 
-  filter(effect %in% OR2d) %>% 
-  split(.$effect) %>% 
-  map_dfr(OR_fit, .id = "effect")
-
-tau2_per_type <- dat %>% #This is to add the effect_type names
-  select(effect, effect_type) %>% 
-  distinct() %>% 
-  mutate(effect_type = recode(effect_type, 
-                              d = "Standardized Mean Difference",
-                              'Raw mean difference' = "Mean Difference",
-                              'Risk difference' = "Risk Difference",
-                              'r' = "Correlation")) %>% 
-  left_join(tau2_per_type) %>% 
-  filter(!effect %in% OR2d) %>% #drop old SMD converted OR
-  bind_rows(fit_OR) %>% #and instead add OR meta-analyzed as OR
-  mutate(effect_type = ifelse(is.na(effect_type), "Odds Ratio", effect_type),
-         eff_size = abs(eff_size)) #need the absolute values for plotting
-
-fitter <- function(df){ #function to fit correlations for annotating facet plots
- fit <- summary(lm(tau2 ~ eff_size, data = df))
- data.frame(b = format(round(fit$coefficients[2, 1], digits = 2), nsmall = 2), #because map_dfr requires dataframe
-            r = format(round(sqrt(fit$r.squared), digits = 2), nsmall = 2)) #output, the output is kept as two vars
-}
-
-labels <- tau2_per_type %>% 
-  split(.$effect_type) %>% 
-  map_dfr(fitter, .id = "effect_type") %>% 
-  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting
-
-tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
-  geom_point(alpha = 0.5) +
-  geom_line(stat = "smooth", method = "lm", se = FALSE, color = "black", alpha = .5, linetype = "dashed") + #to set alpha for the line geom_line must be used rather than geom_smooth
-  geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
-  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
-  scale_x_continuous(name = "Effect size") +
-  theme_classic() +
-  theme(strip.background = element_blank(), #remove box around titles
-        strip.text = element_text(size = 12),
-        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
-                                    size = 0.5, linetype = "solid")) + 
-  facet_wrap(~effect_type, scales = "free") #use free scales since scales are different
-
-tau2_facet
-# ggsave("../figures/tau2_facet.png", dpi = 600, height =  7, width = 7)
-
-```
-
+##Figure 1
 ```{r Plot_tau_against_I2, fig.asp = 0.618, cache = TRUE}
@@
 
+##Figure 2
 ```{r Density_plot, cache = TRUE}
@@
 ```
+
+```{r transform_effect_and_compute_rma}
+#Transform effect sizes to raw correlations
+#'transform_MA' is a sourced function
+res <- dat %>% 
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe
+
+#compute random effect meta-analysis of transformed effects
+#'summarizer' is a sourced function
+res2 <- res %>% 
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map_dfr(summarizer, .id = "effect") %>% 
+  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
+```
+
+```{r cor_het_effect_size, results = "hide", cache=TRUE}
+#Basic correlations
+cor.test(res2$I2, res2$r) #pearson I2
+
+I2_fit <- summary(lm(I2 ~ r, data = res2)) #for annotating figures
+
+cor.test(res2$tau2, res2$r) #pearson tau2
+
+tau2_fit <- summary(lm(tau2 ~ r, data = res2))
+
+cor.test(res2$H2, res2$r) #pearson H2
+
+H2_fit <- summary(lm(H2 ~ r, data = res2))
+
+cor.test(res2$I2, res2$r, method = "spearman") #spearman
+
+##Excluding anchoring effects
+dropped_anchoring <- res2 %>%
+  filter(!grepl("Anchoring", effect))
+
+cor.test(dropped_anchoring$I2, dropped_anchoring$r) #pearson
+
+#bootstrap confidence intervals
+#code by Amir Abdol
+
+#I2
+pear <- function(formula, data, indices){ #pearson
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ I2 + r, data=d)
+     return(fit$estimate)
+}
+
+bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + I2)
+
+I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+spear <- function(formula, data, indices){ #spearman
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ I2 + r, data=d, method = "spearman")
+     return(fit$estimate)
+}
+
+options(warn=-1)
+bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ r + I2)
+options(warn=0)
+
+I2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
+
+#Excluding anchoring effects
+bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ r + I2)
+
+I2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+#H2
+pear <- function(formula, data, indices){
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ H2 + r, data=d)
+     return(fit$estimate)
+}
+
+bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + H2)
+
+H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
+
+```
+
+##Figure 3
+```{r plot_res, cache = TRUE}
+
+#Plots of H2 and I2 vs. biserial correlation r for all effects together
+
+I2 <- ggplot(res2, aes(x = r, y = I2)) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") +
+  coord_cartesian(ylim = c(0, 100)) +
+  geom_text(x = 0.14, y = Inf, vjust = 7, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
+  theme_classic() +
+  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
+  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
+
+H2 <- ggplot(res2, aes(x = r, y = H2)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") +
+  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
+  theme_classic() +
+  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
+  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
+
+effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
+effect_het
+#save_plot("../figures/effect-het.png", effect_het,
+#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
+
+```
+
+##Alternative/additional Figure 3
+```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
+r_tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") +
+  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
+  theme_classic() +
+  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
+  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
+
+r_tau2 
+# ggsave("../figures/r_tau2.png", dpi = 600, height =  4 , width = 6.47)
+
+```
+
+##Correlations per effect type (alternative figure 3, probably drop)
+```{r corr_per_effect_type, cache = TRUE}
+#Each set of input datapoints is meta-analyzed as per the original replication project
+#Then correlated with tau2 per effect type
+#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
+tau2_per_type <- dat %>% 
+  split(.$effect) %>%  
+  map_dfr(est_heterogen_smd_raw, .id = "effect")
+
+#effects that were transformed from OR to SMD
+OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
+           'Norm of reciprocity', 'Low vs. high category scales') #refit as OR
+
+OR_fit <- function(x){ #fit rma to odds raios
+  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
+  hetero <- confint(fit)$random[c(1, 3), ] 
+  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}
+
+fit_OR <- dat %>% 
+  filter(effect %in% OR2d) %>% 
+  split(.$effect) %>% 
+  map_dfr(OR_fit, .id = "effect")
+
+tau2_per_type <- dat %>% #This is to add the effect_type names
+  select(effect, effect_type) %>% 
+  distinct() %>% 
+  mutate(effect_type = recode(effect_type, 
+                              d = "Standardized Mean Difference",
+                              'Raw mean difference' = "Mean Difference",
+                              'Risk difference' = "Risk Difference",
+                              'r' = "Correlation")) %>% 
+  left_join(tau2_per_type) %>% 
+  filter(!effect %in% OR2d) %>% #drop old SMD converted OR
+  bind_rows(fit_OR) %>% #and instead add OR meta-analyzed as OR
+  mutate(effect_type = ifelse(is.na(effect_type), "Odds Ratio", effect_type),
+         eff_size = abs(eff_size)) #need the absolute values for plotting
+
+fitter <- function(df){ #function to fit correlations for annotating facet plots
+ fit <- summary(lm(tau2 ~ eff_size, data = df))
+ data.frame(b = format(round(fit$coefficients[2, 1], digits = 2), nsmall = 2), #because map_dfr requires dataframe
+            r = format(round(sqrt(fit$r.squared), digits = 2), nsmall = 2)) #output, the output is kept as two vars
+}
+
+labels <- tau2_per_type %>% 
+  split(.$effect_type) %>% 
+  map_dfr(fitter, .id = "effect_type") %>% 
+  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting
+
+tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
+  geom_point(alpha = 0.5) +
+  geom_line(stat = "smooth", method = "lm", se = FALSE, color = "black", alpha = .5, linetype = "dashed") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
+  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
+  scale_x_continuous(name = "Effect size") +
+  theme_classic() +
+  theme(strip.background = element_blank(), #remove box around titles
+        strip.text = element_text(size = 12),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid")) + 
+  facet_wrap(~effect_type, scales = "free") #use free scales since scales are different
+
+tau2_facet
+# ggsave("../figures/tau2_facet.png", dpi = 600, height =  7, width = 7)
+
+```

### 2019-04-18 code/figures.rmd
Combined all Figure 3 versions into one figure using cowplot

@@
 
-#Plots of H2 and I2 vs. biserial correlation r for all effects together
+#Plots of H2 and I2 vs. biserial correlation r for all effects together, two above chunks need to be run first
 
@@
   coord_cartesian(ylim = c(0, 100)) +
-  geom_text(x = 0.14, y = Inf, vjust = 7, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
+  annotate("text", x = 0.14, y = Inf, vjust = 5, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
   theme_classic() +
+  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
+        axis.ticks.x = element_blank(),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid")) +
   scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
-  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
+  scale_x_continuous(name = NULL)
 
@@
   geom_smooth(method = "lm", se = TRUE, color = "black") +
-  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
+  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
   theme_classic() +
+  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
+        axis.ticks.x = element_blank(),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid")) +
   scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
-  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
+  scale_x_continuous(name = NULL)
 
-effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
+tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") +
+  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
+  theme_classic() +
+  theme(panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid")) +
+  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
+  scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))
+
+effect_het <- plot_grid(I2, H2, tau2, ncol = 1, align = "v", rel_heights = c(0.86, 0.86, 1)) #combine plots
 effect_het
 #save_plot("../figures/effect-het.png", effect_het,
-#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)
-
-```
-
-##Alternative/additional Figure 3
-```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
-r_tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") +
-  geom_text(x = 0.14, y = Inf, vjust = 7, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
-  theme_classic() +
-  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
-  scale_x_continuous(name = expression(paste("Biserial and pearson correlations ")))
-
-r_tau2 
-# ggsave("../figures/r_tau2.png", dpi = 600, height =  4 , width = 6.47)
+#          ncol = 1, base_height = 7, base_width = 5, dpi = 600)
 

### 2019-04-23 code/tables.rmd
Minor addition to note on table 1

@@
   footnote(threeparttable = TRUE, escape = FALSE,
-           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$.
+           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ when sample size is infinite.
+Increasing differences between observed effect sizes in the columns illustrate the association between effect size, reliability of measurement and heterogeneity.
 Code to reproduce table: osf.io/kf6pt/") %>%

### 2019-04-24 code/tables.rmd
Minor cleaning of tables, added pub. bias reference to bibliography

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, miktex.verbose = TRUE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
 ```
@@
            general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ when sample size is infinite.
-Increasing differences between observed effect sizes in the columns illustrate the association between effect size, reliability of measurement and heterogeneity.
-Code to reproduce table: osf.io/kf6pt/") %>%
+Increasing column-wise variance in observed effect sizes illustrates the association between effect size, reliability of measurement and heterogeneity  Code to reproduce table: osf.io/kf6pt/") %>%
   row_spec(3, hline_after = T)
@@
             Effects = n_distinct(effect),
-            Participants = if(Effects == 1){sum(Ntotal)}
+            N = if(Effects == 1){sum(Ntotal)}
                            else{sum(Ntotal) / Effects}) %>% #average across effects
@@
 Note: "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
-Participant numbers are those used for primary analyses by original authors (i.e., after exclusions).
+N = Participants used for primary analyses by original authors (i.e., after exclusions).
 RP = Replication Project, K (US) = no.
@@
 high category scales'.
-RP = Replication Project, k = no.
+RP = Replication Project, K = no.
 primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations.
+$I^2$ and its confidence intervals are for original effect size specifications whereas $/tau^2$ and its confidence intervals are for transformed r* effect sizes.
 Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.

### 2019-04-24 code/figures.rmd
End-polishing of figures

@@
 ```
+Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 37 effects. Tau is not directly comparable across effect size measures.
 
@@
 # save_plot("../figures/densities_het.png", densities,
-     #      nrow = 2, base_height = 5, base_width = 5, dpi = 600)
+           # nrow = 2,  base_width = 7, base_aspect_ratio = 0.618, dpi = 600)
 ```
+Figure 2.
+Simulated $I^2$ (a) and $/tau^2$ (b) densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed I2 estimates for the 37 effects.
+For panel b) effects consist of correlations and biserial correlation and heterogeneity levels were approximated by Fisher’s z values corresponding to Higgins’ definitions for the median sample size of 108.
+Each simulated density consists of approximately 370,000 estimates.
 
@@
                                     size = 0.5, linetype = "solid")) +
-  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
+  scale_y_continuous(name = expression(paste(italic(tau)^2, " estimate"))) +
   scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))
 
-effect_het <- plot_grid(I2, H2, tau2, ncol = 1, align = "v", rel_heights = c(0.86, 0.86, 1)) #combine plots
+effect_het <- plot_grid(I2, H2, tau2, ncol = 1, align = "v", rel_heights = c(0.86, 0.86, 1), labels = c("a", "b", "c")) #combine plots
 effect_het
-#save_plot("../figures/effect-het.png", effect_het,
+# save_plot("../figures/effect-het.png", effect_het,
          # ncol = 1, base_height = 7, base_width = 5, dpi = 600)
@@
 ```
+Figure 3.
+The correlation between a) I2 ,and effect size and b) H2 and c)  τ ̂^2and effect size for 37 effects from ten pre-registered multi-lab replication projects.
+Shaded bands represent 95% confidence intervals
 

### 2019-04-25 code/figures.rmd
Took the square root of tau2 to make figure 2 more informative

@@
                              '4' = "Large"),
-          Heterogeneity = as.factor(Heterogeneity))
+          Heterogeneity = as.factor(Heterogeneity),
+        tau = sqrt(tau2_hat))
 
-# Observed tau22 estimates, i.e, results from main table, see table.rmd
+# Observed tau2 estimates, i.e, results from main table, see table.rmd
 # Effects transformed and estimated with sourced functions 'transform_MA' and 'summarizer'
-observed_tau2 <- dat %>%
+observed_tau <- dat %>%
    split(.$effect) %>%
@@
    select(effect, tau2) %>%
-   mutate(Heterogeneity = "Observed")
+   mutate(Heterogeneity = "Observed",
+          tau = sqrt(tau2))
 
-tau2_plot <- ggplot(tau2_dist, aes(x = tau2_hat, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
-  geom_histogram(data = observed_tau2, aes(y = ..density.., x = tau2), bins = 200, alpha = 1) +
+tau_plot <- ggplot(tau2_dist, aes(x = tau, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
+  geom_histogram(data = observed_tau, aes(y = ..density.., x = tau), bins = 130, alpha = 1) +
   geom_density(alpha = 0.3) +
   theme_classic() +
-  coord_cartesian(xlim = c(0, 0.05)) +
+  coord_cartesian(xlim = c(0, 0.25)) + #truncate plot for better visualization
   scale_fill_brewer(palette = "Dark2",
@@
   scale_y_continuous(name = "Density") +
-  scale_x_continuous(name = expression(paste(italic(tau)^2," index", sep = ""))) +
+  scale_x_continuous(name = expression(paste(italic(tau)," estimate", sep = ""))) +
   guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
@@
 #3) combine I2-tau2-density-plots----
-densities <- plot_grid(I2_plot, tau2_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
+densities <- plot_grid(I2_plot, tau_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
 densities

### 2019-04-25 code/tables.rmd
Cleaned up helper function R-file and tables.rmd a little

@@
 
-#Transform effect sizes to raw correlations
-#'transform_MA' is a sourced function
-dat2 <- dat %>% 
+#Transform effect sizes to biserial correlations (pearson's correlations left as is)
+#estimate tau2 for correlations
+#'transform_MA' and 'summarizer' are sourced functions
+res2 <- dat %>% 
   split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe
-
-#estimate tau2 for tranformed biserial and pearson's correlations
-#'summarizer' is a sourced function
-res2 <- dat2 %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map(transform_MA) %>% #
   map_dfr(summarizer, .id = "effect")

### 2019-04-25 code/helper_functions_tables_figures.r

@@ -117,7 +117,6 @@ transform_d_to_r <- function(d, n1, n2){
 }
 
 
-
 #Function to apply the transformation functions to the data
 transform_MA <- function(x){
   if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
@@ -125,37 +124,27 @@ transform_MA <- function(x){
     d_conversion <- transform_RD(ai = x$outcome_t1, bi = x$outcome_t2, ci = x$outcome_c1, di = x$outcome_c2)
     out <- transform_d_to_r(d_conversion$d, d_conversion$n1, d_conversion$n2)
     
-    #fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
-    
   } else if(any(x[, "outcomes1_2"] == "mean _ SE")){  
     
     d_conversion <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)
     out <- transform_d_to_r(d_conversion$d, d_conversion$n1, d_conversion$n2)
-    
-    #fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
     
   } else if(any(x[, "outcomes1_2"] == "mean _ SD")){  
     
     d_conversion <- transform_SD(x$outcome_t1, x$outcome_c1, x$outcome_t2, x$outcome_c2, x$ntreatment, x$ncontrol)
     out <- transform_d_to_r(d_conversion$d, d_conversion$n1, d_conversion$n2)
     
-    # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
-    
   } else if(any(x[, "effect_type"] == "r")){
     
     out <- metafor::escalc(measure = "COR", ri = x$effect_size, ni =x$Ntotal)
     out <- data.frame(r = out$yi, vi = out$vi)
     
-    # fit <- rma(measure = "ZCOR", ri = zcor, ni = n, test = "knha", data = transformed)
-    
-  } else{ #For the many labs OR that were transformed to d [double check]
+  } else{ #For the many labs OR that were transformed to d
     
     d_conversion <- transform_RD(ai = x$outcome_t1, bi = x$outcome_t2, ci = x$outcome_c1, di = x$outcome_c2)
     out <- transform_d_to_r(d_conversion$d, d_conversion$n1, d_conversion$n2)
     
   }
-  
[…]

### 2019-04-25 code/figures.rmd
Simplified figures.rmd code and re-added comment to helper file..

@@
 ```{r transform_effect_and_compute_rma}
-#Transform effect sizes to raw correlations
-#'transform_MA' is a sourced function
+#Transform effect sizes to biserial correlations (pearson's correlations as is)
+#then compute random effects meta-analyses per effect
+#'transform_MA' and 'summarizer' are sourced functions
 res <- dat %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(transform_MA, .id = "effect") #apply function and transform back from list to dataframe
-
-#compute random effect meta-analysis of transformed effects
-#'summarizer' is a sourced function
-res2 <- res %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(summarizer, .id = "effect") %>% 
+  split(.$effect) %>%  #necessary step otherwise the function is applied overall
+  map(transform_MA) %>% #apply function each effect in the list
+  map_dfr(summarizer, .id = "effect") %>%  #apply function and transform to dataframe
   mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction

### 2019-04-25 code/helper_functions_tables_figures.r

@@ -159,3 +159,7 @@ summarizer <- function(x){#Z-transformation not recommended by Jacobs and Viecht
              I2 = fitr$I2, I2.lb = ci[2, 2], I2.ub = ci[2, 3], H2trunc = fitr$H2, H2 = fitr$QE / (fitr$k - 1)) 
 }
 
+#Default method of metafor for calculating H2 is truncated at one. Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1). This method approximates H2 as if we were using the Dersimonian and Laird estimate of tau2, although we use REML. See Higgins & Thompson, 2002 and ?print.rma.uni.
+
+#Higgins, J., & Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. Statistics in medicine, 21(11), 1539-1558.
+

### 2019-04-25 code/helper_functions_tables_figures.r
Fixed error in biserial truncation: only for computing variance
Previously the truncated values were used also as effect sizes when computing the meta-analyses

@@ -111,9 +111,9 @@ transform_d_to_r <- function(d, n1, n2){
   zp <- qnorm(p)
   fzp <- dnorm(zp)
   rb <- sqrt(p*q) / fzp * rpb #biserial correlation, Jacobs and Viechtbauer (2017), equation 8
-  rb_trunc <- ifelse(rb > 1, 1, rb) #truncate if > 1 to avoid neg. variance. p. 166-167
+  rb_trunc <- ifelse(rb > 1, 1, rb) #truncate for > 1 when computing variance to avoid neg. variance. p. 166-167
   var_rb <- 1/(n1 + n2 -1) * (sqrt(p*q) / fzp - rb_trunc^2)^2 #variance biserial r, approximate formula, eq. 13 
-  data.frame(r = rb_trunc, vi = var_rb, n = n1 + n2) #I use the approximate formula above to decrease the risk of coding error (due to simplicity)
+  data.frame(r = rb, vi = var_rb, n = n1 + n2) #I use the approximate formula (eq 13) above to decrease the risk of coding error
 }
 
 

### 2019-04-25 code/helper_functions_tables_figures.r
Comment clarification helper file

@@ -71,9 +71,8 @@ est_heterogen_smd_raw <- function(x){
 #in meta-analysis. Research Synthesis Methods, 8(2), 161-180.
 #(provide an exact computation of the point-biserial correlation rather than the approximate in Borenstein)
 
-#Note that Jacobs and Viechtbauer (2017) recommend transforming the point-biserial correlation to a 
-#biserial correlation. However, doing so results in impossible values (r > 1) for 37 of the studies; 
-#those with very large effect sizes (> ~2.5 SD)
+#Jacobs and Viechtbauer (2017) recommend transforming the point-biserial correlation to a 
+#biserial correlation. 
 
 #For raw mean difference + SE
 transform_SE <- function(ES, SE, n1, n2){ 

### 2019-04-26 code/tetrachoric.r
temporary file with formulas for computing tetrachoric correlatiions

@@ -1,0 +1,40 @@
+#Code to compute tetrachoric correlations for odds ratios and risk differences
+#ie.e, anything where we have 2x2 tables
+
+q <- matrix(c(61661,1610,85,20),2,2)
+
+
+
+a <- 61661
+b <- 85
+c <- 1610
+d <- 20
+r <- 0.3481
+N <- a+b+c+d
+z1 <- (a + c) / N
+z2 <- (b + d) / N
+
+#bivariate normal density formula (below) from http://mathworld.wolfram.com/BivariateNormalDistribution.html
+
+bdnorm <- function(z1, z2, r){ #standardized, i.e, mu1 = mu2 = 0 and sigma1 = sigma2 = 1
+  z <- z1^2 - 2*r*z1*z2 - z2^2
+  1 / (2*pi*sqrt(1-r^2)) * exp(-z / (2*(1-r^2)))
+}
+#correctness of dbnorm function checked with online calculator: https://www.easycalculation.com/statistics/bivariate-distribution-calculator.php
+
+#For computing standard errors of the tetrachoric correlations Hamdan 1970 proposed a relatively simple
+#formula, which is recommended by Brown and Benedetti 1977, as well as Olsson 1979
+#[these all cited by Jacobs and Viechtbauer]
+
+var_tetra <- function(a, b, c, d, r){ 
+  N <- a+b+c+d
+  z1 <- (a + c) / N
+  z2 <- (b + d) / N
+  SE <- 1 / (N*bdnorm(z1, z2, r)) * (1/a + 1/b + 1/c + 1/d)^-0.5
+  SE^2
+}
+
+#we use polycor::polychor(q, ML = TRUE) to compute the tetrachoric correlation (where q is a 2x2 matrix)
+#this uses, I believe, Olsson's ML approach
+
+

### 2019-04-29 code/helper_functions_tables_figures.r
Added code to manually transform into tetrachoric correlations
Problem with some variance being zero, which doesn't work for meta-analysis. Will next try metafor's computations instead.

@@ -69,37 +69,33 @@ est_heterogen_smd_raw <- function(x){
 
 #Jacobs, P., & Viechtbauer, W. (2017). Estimation of the biserial correlation and its sampling variance for use
 #in meta-analysis. Research Synthesis Methods, 8(2), 161-180.
-#(provide an exact computation of the point-biserial correlation rather than the approximate in Borenstein)
+#(provide an exact computation of the point-biserial correlation rather than the approximate [Hunter & Schmitd] in Borenstein)
 
 #Jacobs and Viechtbauer (2017) recommend transforming the point-biserial correlation to a 
 #biserial correlation. 
 
-#For raw mean difference + SE
+#Brown, M. B., & Benedetti, J. K. (1977). On the mean and variance of the tetrachoric correlation coefficient. 
+#Psychometrika, 42(3), 347-355.
+#(Equation 9 used to compute the tetrachoric correlation variance)
+
+#Olsson, U. (1979) Maximum likelihood estimation of the polychoric correlation coefficient. 
+#Psychometrika 44, 443-460.
+#ML approach used by polycor::polychoric to compute the tetrachoric correlations
+
+##For raw mean difference + SE
 transform_SE <- function(ES, SE, n1, n2){ 
   sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2)) #Borenstein, M. (2009). In Cooper & Hedges. p. 224
   d <- ES / sdpooled
   data.frame(d = d, n1 = n1, n2 = n2)
 }
 
-#For mean differrence + SD
+##For mean differrence + SD
 transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
   sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #Borenstein, M. (2009), p. 226. 
   d <- (m1 - m2) / sdpooled
   data.frame(d = d, n1 = n1, n2 = n2)
 }
 
-#For Risk difference/OR
-transform_RD <- function(ai, bi, ci, di){
-  ai <- ifelse(ai == 0, 0.5, ai)  #If value is equal to zero add one half so as to not divide by zero
-  bi <- ifelse(bi == 0, 0.5, bi)  #This affects 1 study for Allowed vs. forbidden
[…]

### 2019-04-29 code/tetrachoric.r

@@ -37,4 +37,14 @@ var_tetra <- function(a, b, c, d, r){
 #we use polycor::polychor(q, ML = TRUE) to compute the tetrachoric correlation (where q is a 2x2 matrix)
 #this uses, I believe, Olsson's ML approach
 
+dat %>% filter(
+
+ri <- a %>% 
+  split(.$Site) %>% 
+  map(~matrix(c(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2), 2, 2)) %>% 
+  map(polycor::polychor, ML = TRUE) %>% 
+  map_dfr(~data.frame(r = .[[1]]))
+
+vi <- var_tetra(a$outcome_t1, a$outcome_c1, a$outcome_t2, a$outcome_c2, r = ri$r)
+
 

### 2019-04-29 code/helper_functions_tables_figures.r
Transform everything  except SE effect using metafor::escalc instead

@@ -70,17 +70,11 @@ est_heterogen_smd_raw <- function(x){
 #Jacobs, P., & Viechtbauer, W. (2017). Estimation of the biserial correlation and its sampling variance for use
 #in meta-analysis. Research Synthesis Methods, 8(2), 161-180.
 #(provide an exact computation of the point-biserial correlation rather than the approximate [Hunter & Schmitd] in Borenstein)
+#Jacobs and Viechbauers version has the advantage that it can compute variance even if r = 1
 
 #Jacobs and Viechtbauer (2017) recommend transforming the point-biserial correlation to a 
 #biserial correlation. 
 
-#Brown, M. B., & Benedetti, J. K. (1977). On the mean and variance of the tetrachoric correlation coefficient. 
-#Psychometrika, 42(3), 347-355.
-#(Equation 9 used to compute the tetrachoric correlation variance)
-
-#Olsson, U. (1979) Maximum likelihood estimation of the polychoric correlation coefficient. 
-#Psychometrika 44, 443-460.
-#ML approach used by polycor::polychoric to compute the tetrachoric correlations
 
 ##For raw mean difference + SE
 transform_SE <- function(ES, SE, n1, n2){ 
@@ -88,14 +82,6 @@ transform_SE <- function(ES, SE, n1, n2){
   d <- ES / sdpooled
   data.frame(d = d, n1 = n1, n2 = n2)
 }
-
-##For mean differrence + SD
-transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
-  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #Borenstein, M. (2009), p. 226. 
-  d <- (m1 - m2) / sdpooled
-  data.frame(d = d, n1 = n1, n2 = n2)
-}
-
 
 transform_d_to_r <- function(d, n1, n2){ 
   m <- n1 + n2 - 2 #Jacobs and Viechtbauer (2017), p.164
@@ -111,85 +97,40 @@ transform_d_to_r <- function(d, n1, n2){
   data.frame(r = rb, vi = var_rb, n = n1 + n2) #I use the approximate formula (eq 13) above to decrease the risk of coding error
 }
 
-
-##For Risk difference/OR [first function no longer used. Instead compute tetrachoric correlations]
-
[…]

### 2019-04-29 code/figures.rmd
Updated figures/tables after the switch to tetrachoric cors. for OR/RD

@@
 author: "Heterogeneity in direct replications in psychology and its association with effect size"
-output: pdf_document
+output: 
+  pdf_document: 
+    latex_engine: xelatex
 ---
@@
 ```
+
 Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 37 effects. Tau is not directly comparable across effect size measures.
@@
 ```
+
 Figure 2.
@@
 #Basic correlations
-cor.test(res2$I2, res2$r) #pearson I2
+cor.test(res$I2, res$r) #pearson I2
 
-I2_fit <- summary(lm(I2 ~ r, data = res2)) #for annotating figures
+I2_fit <- summary(lm(I2 ~ r, data = res)) #for annotating figures
 
-cor.test(res2$tau2, res2$r) #pearson tau2
+cor.test(res$tau2, res$r) #pearson tau2
 
-tau2_fit <- summary(lm(tau2 ~ r, data = res2))
+tau2_fit <- summary(lm(tau2 ~ r, data = res))
 
-cor.test(res2$H2, res2$r) #pearson H2
+cor.test(res$H2, res$r) #pearson H2
 
-H2_fit <- summary(lm(H2 ~ r, data = res2))
+H2_fit <- summary(lm(H2 ~ r, data = res))
 
-cor.test(res2$I2, res2$r, method = "spearman") #spearman
+cor.test(res$I2, res$r, method = "spearman") #spearman
 
 ##Excluding anchoring effects
-dropped_anchoring <- res2 %>%
+dropped_anchoring <- res %>%
   filter(!grepl("Anchoring", effect))
@@
 
-bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + I2)
+bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + I2)
 
@@
 options(warn=-1)
-bootfit <- boot(data=res2, statistic=spear, R=1000, formula= ~ r + I2)
+bootfit <- boot(data=res, statistic=spear, R=1000, formula= ~ r + I2)
 options(warn=0)
@@
 
-bootfit <- boot(data=res2, statistic=pear, R=1000, formula= ~ r + H2)
+bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + H2)
 
@@
 
-I2 <- ggplot(res2, aes(x = r, y = I2)) +
+I2 <- ggplot(res, aes(x = r, y = I2)) +
   geom_point(alpha = 0.5) +
@@
 
-H2 <- ggplot(res2, aes(x = r, y = H2)) + 
+H2 <- ggplot(res, aes(x = r, y = H2)) + 
   geom_point(alpha = 0.5) +
@@
 
-tau2 <- ggplot(res2, aes(x = r, y = tau2)) + 
+tau2 <- ggplot(res, aes(x = r, y = tau2)) + 
   geom_point(alpha = 0.5) +
@@
 ```
+
 Figure 3.

### 2019-04-29 code/helper_functions_tables_figures.r

@@ -100,6 +100,7 @@ transform_d_to_r <- function(d, n1, n2){
 #Note that above function gives the same result as
 #metafor::escalc(measure = "RBIS", ml1, ml2, sd1, sd2, n1, n2, data = x)
 #The only reason I wrote the above function is because of the effect that has SE rather than SD
+#For convenience I also use it on line 168 in 'power_simulation.r'
 
 #Function to apply the transformation functions to the data
 transform_MA <- function(x){

### 2019-04-29 code/tetrachoric.r

@@ -1,50 +1,0 @@
-#Code to compute tetrachoric correlations for odds ratios and risk differences
-#ie.e, anything where we have 2x2 tables
-
-q <- matrix(c(61661,1610,85,20),2,2)
-
-
-
-a <- 61661
-b <- 85
-c <- 1610
-d <- 20
-r <- 0.3481
-N <- a+b+c+d
-z1 <- (a + c) / N
-z2 <- (b + d) / N
-
-#bivariate normal density formula (below) from http://mathworld.wolfram.com/BivariateNormalDistribution.html
-
-bdnorm <- function(z1, z2, r){ #standardized, i.e, mu1 = mu2 = 0 and sigma1 = sigma2 = 1
-  z <- z1^2 - 2*r*z1*z2 - z2^2
-  1 / (2*pi*sqrt(1-r^2)) * exp(-z / (2*(1-r^2)))
-}
-#correctness of dbnorm function checked with online calculator: https://www.easycalculation.com/statistics/bivariate-distribution-calculator.php
-
-#For computing standard errors of the tetrachoric correlations Hamdan 1970 proposed a relatively simple
-#formula, which is recommended by Brown and Benedetti 1977, as well as Olsson 1979
-#[these all cited by Jacobs and Viechtbauer]
-
-var_tetra <- function(a, b, c, d, r){ 
-  N <- a+b+c+d
-  z1 <- (a + c) / N
-  z2 <- (b + d) / N
-  SE <- 1 / (N*bdnorm(z1, z2, r)) * (1/a + 1/b + 1/c + 1/d)^-0.5
-  SE^2
-}
-
-#we use polycor::polychor(q, ML = TRUE) to compute the tetrachoric correlation (where q is a 2x2 matrix)
-#this uses, I believe, Olsson's ML approach
-
-dat %>% filter(
-
-ri <- a %>% 
-  split(.$Site) %>% 
-  map(~matrix(c(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2), 2, 2)) %>% 
-  map(polycor::polychor, ML = TRUE) %>% 
-  map_dfr(~data.frame(r = .[[1]]))
-
-vi <- var_tetra(a$outcome_t1, a$outcome_c1, a$outcome_t2, a$outcome_c2, r = ri$r)
-
-

### 2019-04-30 code/figures.rmd
Added tau2 correlation CIs

@@
 
+##Figure 3
 ```{r transform_effect_and_compute_rma}
@@
 
+#Tau2
+pear <- function(formula, data, indices){
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ tau2 + r, data=d)
+     return(fit$estimate)
+}
+
+bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + tau2)
+
+tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
+
 ```
 
-##Figure 3
 ```{r plot_res, cache = TRUE}

### 2019-05-01 code/tables.rmd
Added code to manually transform into tetrachoric correlations
Problem with some variance being zero, which doesn't work for meta-analysis. Will next try metafor's computations instead.
Transform everything  except SE effect using metafor::escalc instead
Change tau2 and CI in table 3 to have 4 digits after decimal

@@
 
+##Table 3
+###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
 ```{r prep-heterogeneity-table, cache = TRUE}
@@
   mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
-         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(tau2_ci.ub, 2), nsmall = 2)), "]")) %>% 
+         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 4), nsmall = 4)), ", ", trimws(format(round(tau2_ci.ub, 4), nsmall = 4)), "]"),
+         tau2 = format(round(tau2, 4), nsmall = 4)) %>% #rounded here instead of in table function because should have 4 digits
   select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau2, tau2_ci, zero, small, medium, large)
@@
 
-##Table 3
-###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
 ```{r heterogeneity-table, cache = TRUE}

### 2019-05-09 code/troubleshooting_tau2.rmd
Exploring tau2 - I2 relationship after transformation

---
title: "Troubleshooting tau2"
author: "Anton Olsson Collentine"
date: "7 mei 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r load packages, data and source functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}
if(!require(kableExtra)){install.packages("kableExtra")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(kableExtra) #For creating good-looking pdf tables
library(ggplot2)
library(cowplot)

dat <- read_csv("../data/collated_summary_data.csv")

source("helper_functions_tables_figures.r") #Load functions to prep data for figures
```

TO DO:
* First figure: replicate panel 2 but with untruncated
* Hopefully the last 3 points will move up
* Also compare mu for truncated and untruncated versions
* Maybe see if can figure out contribution of each lab to overall effect size mu

```{r, cache = TRUE}
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date

het <- dat %>% 
  select(rp, Site, effect, effect_type) %>% 
  group_by(rp, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>% 
  ungroup()

a <- het %>% filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "SMD.")

a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2), label = effect)) + geom_point() + ggtitle("ML1 SMD - untransformed effect sizes") + geom_text()

```

```{r prepping, cache = TRUE}

#Transform effect sizes to biserial correlations (pearson's correlations left as is)
#estimate tau2 for correlations
#'transform_MA' and 'summarizer' are sourced functions
res2 <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA) %>% #
  map_dfr(summarizer, .id = "effect")

#Add rp and k to the data-frame and prep for table
het <- dat %>% 
  select(rp, Site, effect, effect_type) %>% 
  group_by(rp, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res2) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>% 
  ungroup()

b <- het %>% filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "SMD.")

b_plot <- ggplot(b, aes(x = I2, y = sqrt(tau2), label = effect)) + geom_point() + ggtitle("ML1 biserial r - transformed SMD effect sizes") + geom_text()

```

```{r}
cowplot::plot_grid(a_plot, b_plot, ncol = 1)
```

**The four effects at the end are Anchoring 1,2,3,4**

```{r, }
het %>% filter(rp == "ML3") %>% ggplot(aes(x = I2, y = sqrt(tau2))) + geom_point() + facet_wrap(~effect_type) + ggtitle("ML3 (SMD transformed to biserial correlations)")
```

**The one non-increasing effect in the left plot above is 'Credentials interaction'. **
However, note that all the ML3 'correlations' are either transformed partial eta-squared of 2x2 tables in the first table (we can't fix this, would have to get into the raw data which seems liek too much work, I mentioned this in the revised draft)

**Check which effects get truncated:**

```{r, echo = TRUE, cache = TRUE}
dat %>% 
  split(.$effect) %>% 
  map_dfr(transform_MA, .id = "effect") %>% 
  filter(r > 1)
```

Basically the anchoring effects.

```{r}
het %>% ggplot(aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("All effects - tetrachoric, biserial & product-moment r")
```
The effect that is close to one of the anchoring effects (I2 ~75, tau ~.05) is Allowed vs. forbidden which also has r = .90.

### 2019-05-16 code/troubleshooting_tau2.rmd
Continued exploration

@@
 TO DO:
+
 * First figure: replicate panel 2 but with untruncated
@@
 
-a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2), label = effect)) + geom_point() + ggtitle("ML1 SMD - untransformed effect sizes") + geom_text()
+a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("ML1 SMD - untransformed effect sizes")
 
@@
 
-#Add rp and k to the data-frame and prep for table
+#Add rp and k to the data-frame 
 het <- dat %>% 
@@
 
-b_plot <- ggplot(b, aes(x = I2, y = sqrt(tau2), label = effect)) + geom_point() + ggtitle("ML1 biserial r - transformed SMD effect sizes") + geom_text()
+b_plot <- ggplot(b, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("ML1 biserial r - transformed SMD effect sizes")
+
+```
+
+```{r untruncated-biserial, cache = TRUE}
+
+res3 <- dat %>%
+  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & outcomes1_2 == "mean _ SD") %>% 
+  split(.$effect) %>% 
+  map(~transform_SD(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2, .$ntreatment, .$ncontrol)) %>% 
+  map(~untruncated_d_to_r(.$d, .$n1, .$n2)) %>% 
+  map_dfr(summarizer, .id = "effect")
+
+c_plot <- b_plot + geom_point(data = res3, shape = 4, aes(x = I2, y = sqrt(tau2)))
 
@@
 ```{r}
-cowplot::plot_grid(a_plot, b_plot, ncol = 1)
+cowplot::plot_grid(a_plot, c_plot, ncol = 1)
 ```
 
-**The four effects at the end are Anchoring 1,2,3,4**
+**The four effects at the end are Anchoring 1,2,3,4. X corresponds to untruncated and circles are truncated**
 
-```{r, }
-het %>% filter(rp == "ML3") %>% ggplot(aes(x = I2, y = sqrt(tau2))) + geom_point() + facet_wrap(~effect_type) + ggtitle("ML3 (SMD transformed to biserial correlations)")
+**Compare the actual values**
+```{r, cache = TRUE, echo = TRUE}
+b %>% select(effect, r, tau2, I2) %>% left_join(res3 %>% select(effect, r, tau2, I2), by = "effect") %>% 
+  rename(trunc_ES = r.x, trunc_tau2 = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau2 = tau2.y, nontrunc_I2 = I2.y)
+
 ```
 
-**The one non-increasing effect in the left plot above is 'Credentials interaction'. **
-However, note that all the ML3 'correlations' are either transformed partial eta-squared of 2x2 tables in the first table (we can't fix this, would have to get into the raw data which seems liek too much work, I mentioned this in the revised draft)
+It is strange that there are (very slightly) different outcomes for non-truncated effects, this is probably due to metafor (which I use for truncation) uses the exact variance formula whereas I use the approximate.
+Compare truncated vs.
+non-truncated manual formulas to check:
+```{r}
+res4 <- dat %>%
+  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & outcomes1_2 == "mean _ SD") %>% 
+  split(.$effect) %>% 
+  map(~transform_SD(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2, .$ntreatment, .$ncontrol)) %>% 
+  map(~transform_d_to_r(.$d, .$n1, .$n2)) %>% 
+  map_dfr(summarizer, .id = "effect")
+
+res4 %>% select(effect, r, tau2, I2) %>% left_join(res3 %>% select(effect, r, tau2, I2), by = "effect") %>% 
+  rename(trunc_ES = r.x, trunc_tau2 = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau2 = tau2.y, nontrunc_I2 = I2.y)
+```
+**Exactly the same result for non-truncated effects, so that seems to be the case**
 
@@
 
+```{r, }
+het %>% filter(rp == "ML3") %>% ggplot(aes(x = I2, y = sqrt(tau2))) + geom_point() + facet_wrap(~effect_type) + ggtitle("ML3 (SMD transformed to biserial correlations)")
+```
+
+**The one non-increasing effect in the left plot above is 'Credentials interaction'. **
+However, note that all the ML3 'correlations' are either transformed partial eta-squared of 2x2 tables in the first table (we can't fix this, would have to get into the raw data which seems liek too much work, I mentioned this in the revised draft)
+
 ```{r}

### 2019-05-16 code/helper_functions_tables_figures.r

@@ -99,7 +99,8 @@ transform_d_to_r <- function(d, n1, n2){
 
 #Note that above function gives the same result as
 #metafor::escalc(measure = "RBIS", ml1, ml2, sd1, sd2, n1, n2, data = x)
-#The only reason I wrote the above function is because of the effect that has SE rather than SD
+#With the difference that metafor used the exact variance equation (eq 12, Jacobs and Viechtbauer, 2017)
+#and I use the approximate (eq. 13).
 #For convenience I also use it on line 168 in 'power_simulation.r'
 
 #Function to apply the transformation functions to the data
@@ -152,3 +153,29 @@ summarizer <- function(x){#Z-transformation not recommended by Jacobs and Viecht
 
 #Higgins, J., & Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. Statistics in medicine, 21(11), 1539-1558.
 
+
+
+##****************
+#Function to compute biserial correlations without truncation 
+#identical to function on line 86 but with the truncation removed when computing the variance
+untruncated_d_to_r <- function(d, n1, n2){ 
+  m <- n1 + n2 - 2 #Jacobs and Viechtbauer (2017), p.164
+  h <- m/n1 + m/n2 #p. 164
+  rpb <- d / sqrt(d^2 + h) #point-biserial correlation, Jacobs and Viechtbauer (2017), equation 5
+  p <- n1 / (n1 + n2)
+  q <- n2 / (n1 + n2)
+  zp <- qnorm(p)
+  fzp <- dnorm(zp)
+  rb <- sqrt(p*q) / fzp * rpb #biserial correlation, Jacobs and Viechtbauer (2017), equation 8
+  var_rb <- 1/(n1 + n2 -1) * (sqrt(p*q) / fzp - rb^2)^2 #variance biserial r, approximate formula, eq. 13 
+  data.frame(r = rb, vi = var_rb, n = n1 + n2) #I use the approximate formula (eq 13) above to decrease the risk of coding error
+}
+
+
+
+#Helper to compute SMD (hedge's g)
+transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
+  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #Borenstein, M. (2009), p. 226. 
+  d <- (m1 - m2) / sdpooled
+  data.frame(d = d, n1 = n1, n2 = n2)
+}

### 2019-05-16 code/tables.rmd
Changed tau2 to tau in table 3

--- 2019-04-25 code/tables.rmd
@@
 res <- res %>%
-  mutate(tau2 = res2$tau2, #For table 3, report tau2 and transformed effect sizes (biserial correlations)
-         tau2_ci.lb = res2$tau2.lb,
-         tau2_ci.ub = res2$tau2.ub,
+  mutate(tau = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
+         tau_ci.lb = sqrt(res2$tau2.lb),
+         tau_ci.ub = sqrt(res2$tau2.ub),
          r = res2$r)
@@
   mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
-         tau2_ci = paste0("[", trimws(format(round(tau2_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(tau2_ci.ub, 2), nsmall = 2)), "]")) %>% 
-  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau2, tau2_ci, zero, small, medium, large)
+         tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 4), nsmall = 4)), ", ", trimws(format(round(tau_ci.ub, 4), nsmall = 4)), "]"),
+         tau = format(round(tau, 4), nsmall = 4)) %>% #rounded here instead of in table function because should have 4 digits
+  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau, tau_ci, zero, small, medium, large)
 
@@
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "r*" , "$\\tau^2$", "$\\tau^2$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "r*" , "$\\tau$", "$\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
   add_header_above(c(" " = 10, "Level of heterogeneity" = 4)) %>% 

### 2019-05-16 code/tables.rmd
Table 3 adjusted number of significant digits I2 and tau with CIs

@@
   arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
-  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
-         tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 4), nsmall = 4)), ", ", trimws(format(round(tau_ci.ub, 4), nsmall = 4)), "]"),
-         tau = format(round(tau, 4), nsmall = 4)) %>% #rounded here instead of in table function because should have 4 digits
+  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 1), nsmall = 1)), ", ", trimws(format(round(s_ci.ub, 1), nsmall = 1)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
+         s_I2 = format(round(s_I2, 1), nsmall = 1),
+         tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),
+         tau = format(round(tau, 3), nsmall = 3)) %>% #rounded here instead of in table function because should have 4 digits
   select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau, tau_ci, zero, small, medium, large)
@@
 
-```{r heterogeneity-table, cache = TRUE}
+```{r heterogeneity-table, cache = FALSE}
 #library(kableExtra)

### 2019-05-16 code/troubleshooting_tau2.rmd
in explore. took the sqrt in the tables to make comparable to figure 1

@@
 author: "Anton Olsson Collentine"
-date: "7 mei 2019"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output: pdf_document
@@
 
-* First figure: replicate panel 2 but with untruncated
-* Hopefully the last 3 points will move up
-* Also compare mu for truncated and untruncated versions
-* Maybe see if can figure out contribution of each lab to overall effect size mu
+* First figure: replicate panel 2 but with untruncated [done]
+* Hopefully the last 3 points will move up [nope :(]
+* Also compare mu for truncated and untruncated versions [done]
+* Maybe see if can figure out contribution of each lab to overall effect size mu [dunno]
 
@@
 **Compare the actual values**
-```{r, cache = TRUE, echo = TRUE}
+```{r, cache = TRUE}
 b %>% select(effect, r, tau2, I2) %>% left_join(res3 %>% select(effect, r, tau2, I2), by = "effect") %>% 
-  rename(trunc_ES = r.x, trunc_tau2 = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau2 = tau2.y, nontrunc_I2 = I2.y)
+  rename(trunc_ES = r.x, trunc_tau = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau = tau2.y, nontrunc_I2 = I2.y) %>% 
+  mutate(trunc_tau = sqrt(trunc_tau), nontrunc_tau = sqrt(nontrunc_tau)) %>% 
+  knitr::kable(booktabs = TRUE)
 
@@
 res4 %>% select(effect, r, tau2, I2) %>% left_join(res3 %>% select(effect, r, tau2, I2), by = "effect") %>% 
-  rename(trunc_ES = r.x, trunc_tau2 = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau2 = tau2.y, nontrunc_I2 = I2.y)
+  rename(trunc_ES = r.x, trunc_tau = tau2.x, trunc_I2 = I2.x, nontrunc_ES  = r.y, nontrunc_tau = tau2.y, nontrunc_I2 = I2.y) %>% 
+  mutate(trunc_tau = sqrt(trunc_tau), nontrunc_tau = sqrt(nontrunc_tau)) %>% 
+  knitr::kable(booktabs = TRUE) 
 ```
-**Exactly the same result for non-truncated effects, so that seems to be the case**
+Exactly the same result for non-truncated effects, so that seems to be the case
 
-**Check which effects get truncated:**
+Let's take a closer look at the truncated vs. untruncated variance estimates for Anchoring 4 which has the largest change in I2.
+
+```{r, cache = TRUE}
+anch4 <- dat %>%
+  filter(effect == "Anchoring 4 - Babies") %>% 
+  rowwise() %>% 
+  do(transform_SD(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2, .$ntreatment, .$ncontrol)) 
+#See this stackoverflow question to understand the usage of rowwise and 'do'
+#https://stackoverflow.com/questions/22240816/dplyr-summarise-with-multiple-return-values-from-a-single-function
+
+anch4_trunc <- anch4 %>% 
+  do(transform_d_to_r(.$d, .$n1, .$n2))
+
+anch4_nontrunc <- anch4 %>% 
+  do(untruncated_d_to_r(.$d, .$n1, .$n2))
+
+bind_cols(anch4_trunc, anch4_nontrunc) %>% 
+  rename(trunc_vi = vi, nontrunc_vi = vi1) %>% 
+  select(r, trunc_vi, nontrunc_vi, n) %>% 
+  arrange(desc(r)) %>% 
+  knitr::kable(booktabs = TRUE)
+
+```
+Note that the (biserial) r itself is not truncated and so the same between the two. It is clear truncation leads to a larger estimate of the variance for an effect.
+
+**To summarize: Truncation leads to an increase in estimated study variance, but a (small) decrease in meta-analytic effect size estimate.
+In other words, truncation (as seen in the first figure) leads to a lower I2 but does not affect the $\tau$ particularly**
+
+##Old stuff
+
+Check which effects get truncated:
 

### 2019-05-22 code/troubleshooting_tau2.rmd
Exploring tau2 transformation effect, getting closer

@@
 if(!require(kableExtra)){install.packages("kableExtra")}
+if(!require(writexl)){install.packages("writexl")}
 
@@
 library(cowplot)
+library(writexl)
 
@@
 ```
-
-TO DO:
-
-* First figure: replicate panel 2 but with untruncated [done]
-* Hopefully the last 3 points will move up [nope :(]
-* Also compare mu for truncated and untruncated versions [done]
-* Maybe see if can figure out contribution of each lab to overall effect size mu [dunno]
 
@@
 
+Figure 1.
 ```{r}
@@
 
+We see that the non-monotonicity after transformation is not explained by truncation.
+Rather (especially in view of the 4th to last effect which wasn't truncated) there seems like there might be a relation with effect size.
+
+##Effect size?
+```{r, cache = TRUE}
+
+both <- dat %>%
+  filter(effect %in% c("Quote Attribution", "Anchoring 1 - NYC")) %>% 
+  split(.$effect) %>% 
+  map(function(x){
+    metafor::escalc(measure = "SMD", m1i = x$outcome_t1, m2i = x$outcome_c1, sd1i = x$outcome_t2, sd2i = x$outcome_c2, n1i = x$ntreatment, n2i = x$ncontrol, data = x)
+    })
+
+both_trunc <- both %>% 
+  map(~transform_d_to_r(.$yi, .$ntreatment, .$ncontrol))
+
+both_nontrunc <- both %>% 
+  map(~untruncated_d_to_r(.$yi, .$ntreatment, .$ncontrol))
+
+#For excel
+out <- bind_cols(both[[1]][, c("yi", "vi")], both[[2]][, c("yi", "vi")],
+          both_trunc[[1]][, c("r", "vi")], both_trunc[[2]][, c("r", "vi")],
+          both_nontrunc[[1]][, c("r", "vi")], both_nontrunc[[2]][, c("r", "vi")],
+          both[[1]][, c("ntreatment", "ncontrol")], both[[2]][,c("ntreatment", "ncontrol")]) %>% 
+  mutate_at(vars(contains("vi")), sqrt) %>% 
+  select(yi, vi, yi1, vi1, r, r1, everything(), -r2, -r3) %>% 
+  rename("Anch_d" = yi, "Anch_d_SE" = vi, "Quote_d" = yi1, "Quote_d_SE" = vi1,
+         "Anch_r" = r, "Anch_trunc_SE" = vi2, "Quote_r" = r1, "Quote_trunc_SE" = vi3,
+         "Anch_nontrunc_SE" = vi4, "Quote_nontrunc_SE" = vi5,
+         "Anch_n1" = ntreatment, "Anch_n2" = ncontrol, "Quote_n1" = ntreatment1, "Quote_n2" = ncontrol1)
+
+write_xlsx(out, "effect_sizes_with_SE.xlsx")
+```
+
+```{r}
+eff <- out %>% 
+  mutate(ratio_SE_d = Anch_d_SE / Quote_d_SE,
+         ratio_SE_biserial = Anch_trunc_SE / Quote_trunc_SE,
+         Quote_ratio = Quote_d_SE / Quote_trunc_SE,
+         Anch_ratio = Anch_d_SE / Anch_trunc_SE,
+         diff = ratio_SE_d - ratio_SE_biserial) %>%
+  arrange(desc(Anch_d)) %>%
+  select(Anch_d, Quote_d, Quote_ratio, Anch_ratio, ratio_SE_d, ratio_SE_biserial, diff)
+
+```
+
+- The transformation is not monotonic for large values and this is not explained by the truncation (see next section) which almost only affects the I2
+
+- Let's take a closer look at two effects with very different effect sizes (mean SMD `r round(mean(eff$Quote_d), 2)` vs.
+`r round(mean(eff$Anch_d), 2)`): Quote attribution [fifth effect from the right Figure 1] vs.
+Anchoring 1.
+[4th effect from the right Figure 1].
+
+**Consider the following:**
+
+a) higher variance for large effect sizes -> less weight for these effects -> higher tau2 estimate
+
+b) The formulas for variance for hedge's g and for variance for biserial correlations both include effect size
+
+c) For hedge's g larger effect size -> more variance (see Borenstein for formula) and not clear for biserial
+
+d) If the impact of effect size on variance is larger for hedge's g than for biserial it makes sense to expect some differences in the variance (and tau2) estimates after transformation
+
+e) If the weight of large effect sizes (inverse variance) is relatively higher after transformation (i.e., their relative variance decreases) then we would expect lower tau2 estimates after transformation.
+This effect should be larger for larger effect sizes.
+
+f) This is exactly what we see below and in figure 1.
+In the table below, note the large difference in SE ratios before vs.
+after transformation to biserial correlations.
+The relative variance of the larger effect sizes (anchoring) decreases considerably after transformation.
+The same is true of larger effect sizes _within_ the Anchoring effect: the correlation between the Anchoring effect sizes and the difference in ratios is _r_ = `r cor(eff$Anch_d, eff$diff)`.
+
+```{r}
+
+knitr::kable(eff, booktabs = TRUE) 
+```
+Note: Anch_d = SMD Anchoring, Quote_d = SMD Quote attribution, ratio_SE_d = Ratio SMD SEs: Anchoring / Quote attribution, ratio_SE_biserial = Ratio biserial SEs: Anchoring / Quote attribution, diff = Ratio SMD - Ratio biserial.
+
+Correlation Anch_d and Anch_ratio _r_ = `r cor(eff$Anch_ratio, eff$Anch_d)`
+
+##Truncation problems?
 **Compare the actual values**

### 2019-06-06 code/troubleshooting_tau2.rmd
Added tau2 REML and DL estimates to the excel troubleshooting file

@@
 
+both_tau2_d <- lapply(both, function(x){
+  d_DL <-  rma(yi = x$yi, vi = x$vi, data = x, method = "DL")$tau2
+  d_REML <-  rma(yi = x$yi, vi = x$vi, data = x)$tau2
+  data.frame(d_DL = rep(d_DL, 36), d_REML = rep(d_REML, 36))})
+
+both_tau2_trunc <- lapply(both_trunc, function(x){
+  trunc_DL = rma(yi = x$r, vi = x$vi, data = x, method = "DL")$tau2
+  trunc_REML = rma(yi = x$r, vi = x$vi, data = x)$tau2
+  data.frame(trunc_DL = rep(trunc_DL, 36), trunc_REML = rep(trunc_REML, 36))})
+
 #For excel
@@
           both_nontrunc[[1]][, c("r", "vi")], both_nontrunc[[2]][, c("r", "vi")],
-          both[[1]][, c("ntreatment", "ncontrol")], both[[2]][,c("ntreatment", "ncontrol")]) %>% 
+          both[[1]][, c("ntreatment", "ncontrol")], both[[2]][,c("ntreatment", "ncontrol")],
+          both_tau2_d[[1]], both_tau2_d[[2]],
+          both_tau2_trunc[[1]], both_tau2_trunc[[2]]) %>% 
   mutate_at(vars(contains("vi")), sqrt) %>% 
@@
          "Anch_nontrunc_SE" = vi4, "Quote_nontrunc_SE" = vi5,
-         "Anch_n1" = ntreatment, "Anch_n2" = ncontrol, "Quote_n1" = ntreatment1, "Quote_n2" = ncontrol1)
+         "Anch_n1" = ntreatment, "Anch_n2" = ncontrol, "Quote_n1" = ntreatment1, "Quote_n2" = ncontrol1,
+         "Anch_d_tau2_DL" = d_DL, "Anch_d_tau2_REML" = d_REML, "Quote_d_tau2_DL" = d_DL1, "Quote_d_tau2_REML" = d_REML1,
+         "Anch_trunc_tau2_DL" = trunc_DL, "Anch_trunc_tau2_REML" = trunc_REML, "Quote_trunc_tau2_DL" = trunc_DL1, "Quote_trunc_tau2_REML" = trunc_REML1)
 
-write_xlsx(out, "effect_sizes_with_SE.xlsx")
+# write_xlsx(out, "effect_sizes_with_SE.xlsx")
 ```
@@
 
-**Consider the following:**
+**Facts so far:**
 
-a) higher variance for large effect sizes -> less weight for these effects -> higher tau2 estimate
+a) After transformation we see an unexpected pattern in heterogeneity estimates amongst the four largest effect sizes; tau2 seems too low compared to I2
 
-b) The formulas for variance for hedge's g and for variance for biserial correlations both include effect size
+b) The transformation affects sampling variance estimates differently depending on effect size; the relative decrease in sampling variance is larger the larger the effect size.
+In other words, after transformation the larger effect sizes have relatively more weight than before the transformation (see table below).
 
-c) For hedge's g larger effect size -> more variance (see Borenstein for formula) and not clear for biserial
+c) This is true both across effects and within effects.
+E.g., for the Anchoring effect size d = 1.94 the ratio of the  pre-transformation variance to post-transformation variance is 4.92 whereas for the effect size d = .78 it is 1.98.
+This correlation is almost perfect (_r_ = `r cor(eff$Anch_ratio, eff$Anch_d)`)
 
-d) If the impact of effect size on variance is larger for hedge's g than for biserial it makes sense to expect some differences in the variance (and tau2) estimates after transformation
-
-e) If the weight of large effect sizes (inverse variance) is relatively higher after transformation (i.e., their relative variance decreases) then we would expect lower tau2 estimates after transformation.
-This effect should be larger for larger effect sizes.
-
-f) This is exactly what we see below and in figure 1.
-In the table below, note the large difference in SE ratios before vs.
-after transformation to biserial correlations.
-The relative variance of the larger effect sizes (anchoring) decreases considerably after transformation.
-The same is true of larger effect sizes _within_ the Anchoring effect: the correlation between the Anchoring effect sizes and the difference in ratios is _r_ = `r cor(eff$Anch_d, eff$diff)`.
+d) For anchoring 1, 15/36 effect sizes are above the mean
 
@@
 ```
-Note: Anch_d = SMD Anchoring, Quote_d = SMD Quote attribution, ratio_SE_d = Ratio SMD SEs: Anchoring / Quote attribution, ratio_SE_biserial = Ratio biserial SEs: Anchoring / Quote attribution, diff = Ratio SMD - Ratio biserial.
+Note: Anch_d = SMD Anchoring, Quote_d = SMD Quote attribution, Quote_ratio = pre-transformation SE / post-transformation SE for Quote attribution, Anch_ratio = pre-transformation SE / post-transformation SE for Anchoring 1, ratio_SE_d = Ratio SMD SEs: Anchoring / Quote attribution, ratio_SE_biserial = Ratio biserial SEs: Anchoring / Quote attribution, diff = Ratio SMD - Ratio biserial.
 
-Correlation Anch_d and Anch_ratio _r_ = `r cor(eff$Anch_ratio, eff$Anch_d)`
+```{r above_average_anchoring}
+dat %>% filter(grepl("Anchoring", effect)) %>% 
+  group_by(effect) %>% 
+  summarize(above_average = sum(effect_size - mean(effect_size) > 0))
+```
 

### 2019-06-24 code/tables.rmd
Added original tau estimates to table 3 + changed RBIS to manual for SMD

@@
   split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
+  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
+  mutate(tau = sqrt(tau2),
+         tau_ci.lb = sqrt(tau2_ci.lb),
+         tau_ci.ub = sqrt(tau2_ci.ub)) %>% 
+  select(-tau2, - tau2_ci.lb, -tau2_ci.ub) #drop redundant variables
 
@@
 
-#NB! note that for low vs. high category scales, the I2 lower bound is zero, but after transformation
-#the tau2 lower bound is *not* zero. This is an indication of the problems with effect size tranformations.
-
 res <- res %>%
-  mutate(tau = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
-         tau_ci.lb = sqrt(res2$tau2.lb),
-         tau_ci.ub = sqrt(res2$tau2.ub),
-         r = res2$r)
+  mutate(r = res2$r,
+         tau_r = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
+         tau_r_ci.lb = sqrt(res2$tau2.lb),
+         tau_r_ci.ub = sqrt(res2$tau2.ub))
 
@@
   mutate(effect_type = recode(effect_type, 
-                              d = "SMD.",
+                              d = "SMD",
                               'Raw mean difference' = "MD",
@@
   left_join(I2_power) %>% 
-  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by tau2 and upper CI bound
+  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by I2 and upper CI bound
   mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 1), nsmall = 1)), ", ", trimws(format(round(s_ci.ub, 1), nsmall = 1)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
@@
          tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),
-         tau = format(round(tau, 3), nsmall = 3)) %>% #rounded here instead of in table function because should have 4 digits
-  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, r, tau, tau_ci, zero, small, medium, large)
+         tau = format(round(tau, 3), nsmall = 3),
+         tau_r = format(round(tau_r, 3), nsmall = 3),
+         tau_r_ci = paste0("[", trimws(format(round(tau_r_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_r_ci.ub, 3), nsmall = 3)), "]")) %>% #rounded here instead of in table function because should have 4 digits
+  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau, tau_ci, r, tau_r, tau_r_ci, zero, small, medium, large)
 
@@
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "r*" , "$\\tau$", "$\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
-  add_header_above(c(" " = 10, "Level of heterogeneity" = 4)) %>% 
-  add_header_above(c(" " = 10, "Type I Error Rate & Statistical Power" = 4)) %>% 
+het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "r*" , "r* $\\tau$", "r* $\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+  add_header_above(c(" " = 12, "Level of heterogeneity" = 4)) %>% 
+  add_header_above(c(" " = 12, "Type I Error Rate & Statistical Power" = 4)) %>% 
   kable_styling("scale_down", font_size = 7) %>%
@@
 primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations.
-$I^2$ and its confidence intervals are for original effect size specifications whereas $/tau^2$ and its confidence intervals are for transformed r* effect sizes.
+$I^2$ and its confidence intervals are for original effect size specifications whereas $\tau$ and its confidence intervals are for transformed r* effect sizes.
 Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.

### 2019-06-24 code/helper_functions_tables_figures.r

@@ -76,10 +76,17 @@ est_heterogen_smd_raw <- function(x){
 #biserial correlation. 
 
 
-##For raw mean difference + SE
+##For raw mean difference + SE -> Hedge's g
 transform_SE <- function(ES, SE, n1, n2){ 
   sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2)) #Borenstein, M. (2009). In Cooper & Hedges. p. 224
   d <- ES / sdpooled
+  data.frame(d = d, n1 = n1, n2 = n2)
+}
+
+#For raw mean difference + SD -> Hedge's g
+transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean difference
+  sdpooled <- sqrt(((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2)) #Borenstein, M. (2009), p. 226. 
+  d <- (m1 - m2) / sdpooled
   data.frame(d = d, n1 = n1, n2 = n2)
 }
 
@@ -99,9 +106,9 @@ transform_d_to_r <- function(d, n1, n2){
 
 #Note that above function gives the same result as
 #metafor::escalc(measure = "RBIS", ml1, ml2, sd1, sd2, n1, n2, data = x)
-#With the difference that metafor used the exact variance equation (eq 12, Jacobs and Viechtbauer, 2017)
-#and I use the approximate (eq. 13).
-#For convenience I also use it on line 168 in 'power_simulation.r'
+#With the difference that metafor uses the exact variance equation (eq 12, Jacobs and Viechtbauer, 2017)
+#and we use the approximate (eq. 13). For consistency we only apply the approximate method
+#We chose this version because the escalc approach cannot handle the effect where SE are reported rather than SD
 
 #Function to apply the transformation functions to the data
 transform_MA <- function(x){
@@ -118,10 +125,8 @@ transform_MA <- function(x){
     
   } else if(any(x[, "outcomes1_2"] == "mean _ SD")){  
     
-    converted <- metafor::escalc("RBIS", m1i = x$outcome_t1, m2i  = x$outcome_c1, #convert to biserial correlations
-                         sd1i = x$outcome_t2, sd2i = x$outcome_c2,
-                         n1i = x$ntreatment, n2i = x$ncontrol)
[…]

### 2019-06-24 code/tables.rmd
Minor change in table code to make them less latex specific

@@
 
-rooted_relabilities %>% knitr::kable("latex", booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
+rooted_relabilities %>% knitr::kable(booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
   kable_styling(position = "left") %>% 
@@
 
-summary.table %>% knitr::kable("latex", 
-                               booktabs = TRUE,
+summary.table %>% knitr::kable(booktabs = TRUE,
                                digits = 0,
@@
 
-het %>% knitr::kable("latex", align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "r*" , "r* $\\tau$", "r* $\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "r*" , "r* $\\tau$", "r* $\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
   add_header_above(c(" " = 12, "Level of heterogeneity" = 4)) %>% 
   add_header_above(c(" " = 12, "Type I Error Rate & Statistical Power" = 4)) %>% 
-  kable_styling("scale_down", font_size = 7) %>%
+  kable_styling("scale_down", font_size = 7) %>% #comment out if outputting html file
   column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 

### 2019-06-26 code/figures.rmd
Added tau vs. effect size correlation per effect type (SMD, fisher's z)

@@
 
+MD_fit <- function(x){
+    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
+    hetero <- confint(fit)$random[c(1, 3), ] 
+    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])
+}
+
+fisher_fit <- function(x){
+    fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, data = x)
+    hetero <- confint(fit)$random[c(1, 3), ] 
+    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])
+    }
+
+#Raw mean differences to SMD
+MD_standardized <- dat %>% 
+  filter(effect_type == "Raw mean difference" & !outcomes1_2 == "mean _ SE") %>% #No method in metafor to compute SMD when standard deviations not given, so skip this study 
+  split(.$effect) %>% 
+  map_dfr(MD_fit, .id = "effect")
+
+fisher <- dat %>% 
+  filter(effect_type == "r") %>% 
+  split(.$effect) %>% 
+  map_dfr(fisher_fit, .id = "effect")
+
 #effects that were transformed from OR to SMD
@@
 
-OR_fit <- function(x){ #fit rma to odds raios
-  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
-  hetero <- confint(fit)$random[c(1, 3), ] 
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
-             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
-             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}
-
-fit_OR <- dat %>% 
-  filter(effect %in% OR2d) %>% 
-  split(.$effect) %>% 
-  map_dfr(OR_fit, .id = "effect")
+#If we don't use the Odds ratios we don't need the below
+# OR_fit <- function(x){ #fit rma to odds raios
+#   fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
+#   hetero <- confint(fit)$random[c(1, 3), ] 
+#   data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+#              s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+#              tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}
+# 
+# fit_OR <- dat %>% 
+#   filter(effect %in% OR2d) %>% 
+#   split(.$effect) %>% 
+#   map_dfr(OR_fit, .id = "effect")
 
@@
   mutate(effect_type = recode(effect_type, 
-                              d = "Standardized Mean Difference",
-                              'Raw mean difference' = "Mean Difference",
-                              'Risk difference' = "Risk Difference",
-                              'r' = "Correlation")) %>% 
+                              d = "Standardized Mean Difference")) %>% 
   left_join(tau2_per_type) %>% 
-  filter(!effect %in% OR2d) %>% #drop old SMD converted OR
-  bind_rows(fit_OR) %>% #and instead add OR meta-analyzed as OR
-  mutate(effect_type = ifelse(is.na(effect_type), "Odds Ratio", effect_type),
-         eff_size = abs(eff_size)) #need the absolute values for plotting
+  filter(!effect %in% c(OR2d, MD_standardized$effect, fisher$effect)) %>% #drop old SMD converted OR, unstandardized MD and raw correlations
+  bind_rows(MD_standardized) %>% 
+  bind_rows(fisher) %>% 
+  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
+         effect_type = ifelse(effect %in% fisher$effect, "Fisher's z", effect_type),
+         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
+  filter(effect_type %in% c("Standardized Mean Difference", "Fisher's z"))
 
@@
   geom_point(alpha = 0.5) +
-  geom_line(stat = "smooth", method = "lm", se = FALSE, color = "black", alpha = .5, linetype = "dashed") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
   geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
@@
                                     size = 0.5, linetype = "solid")) + 
-  facet_wrap(~effect_type, scales = "free") #use free scales since scales are different
+  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different
 

### 2019-07-11 code/Supplement-biserial-correlations.Rmd
Converted troubleshooting into supplement

---
title: "Supplement - Biserial correlation transformations"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
Sys.setlocale("LC_TIME", "English" ) #to print date in YAML in English
```

```{r load packages, data and source functions}
if(!require(readr)){install.packages("readr")}
if(!require(metafor)){install.packages("metafor")}
if(!require(dplyr)){install.packages("dplyr")}
if(!require(purrr)){install.packages("purrr")}

library(readr) #To load data
library(dplyr) #For data transformation
library(purrr) #For data iteration
library(metafor) #To run meta-analyses
library(ggplot2) #plotting figures
library(cowplot) #combine plots

dat <- read_csv("../data/collated_summary_data.csv")

source("helper_functions_tables_figures.r") #Load functions to prep data for figures
```

```{r a-plot-prep, cache = TRUE}
res <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date

het <- dat %>% 
  select(rp, Site, effect, effect_type) %>% 
  group_by(rp, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>% 
  ungroup()

a <- het %>% filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "SMD.")
```

```{r, cache = FALSE}
a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("SMD (untransformed)") +
  scale_x_continuous(name = expression(paste(italic(I)^2, "Index"))) +
  scale_y_continuous(name = "Tau")

```

```{r trunc-biserial, cache = TRUE}
#Transform effect sizes to biserial correlations (pearson's correlations left as is)
#estimate tau2 for correlations
#'transform_MA' and 'summarizer' are sourced functions
res2 <- dat %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map(transform_MA) %>% #
  map_dfr(summarizer, .id = "effect")

#Add rp and k to the data-frame 
het <- dat %>% 
  select(rp, Site, effect, effect_type) %>% 
  group_by(rp, effect) %>% 
  summarize(effect_type = unique(effect_type),
            k = n_distinct(Site)) %>% 
  left_join(res2) %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "SMD.",
                              'Raw mean difference' = "MD",
                              'Risk difference' = "RD")) %>% 
  ungroup()

b <- het %>% filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "SMD.")
```

```{r b-plot-1, cache = FALSE}
b_plot_1 <- ggplot(b, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("Biserial r (transformed SMD)")

```

```{r untruncated-biserial, cache = TRUE}
res3 <- dat %>%
  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & outcomes1_2 == "mean _ SD") %>% 
  split(.$effect) %>% 
  map(~transform_SD(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2, .$ntreatment, .$ncontrol)) %>% 
  map(~untruncated_d_to_r(.$d, .$n1, .$n2)) %>% 
  map_dfr(summarizer, .id = "effect")
```

```{r b-plot, cache = FALSE}
b_plot <- b_plot_1 + geom_point(data = res3, shape = 4, aes(x = I2, y = sqrt(tau2))) +
  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_y_continuous(name = "Tau")

```

```{r tau-vs-tau}
d <- select(a, effect, tau2) %>% 
  left_join(select(b, effect, tau2), by = "effect")
```

```{r d-plot}
d_plot <- ggplot(d, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) + 
  geom_point() + 
  ggtitle("SMD vs. biserial") +
  scale_x_continuous(name = "Tau (SMD)") +
  scale_y_continuous(name = "Tau (biserial r)")

```

```{r, fig.width = 6, fig.asp = 1.3}
cowplot::plot_grid(a_plot, b_plot, d_plot, ncol = 1, labels = "AUTO")
```

_Figure S.1_ Association between $\tau$ and $I^2$ after and before standardized mean difference (SMD) effects were transformed into biserial correlations for all effects reported as SMDs in ManyLabs 1. Panel A shows the association between $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text). Panel B shows the same associations for the same effects after transformation to biserial correlations, either with truncation of correlations over 1 (circles) or without (crosses). Panel C shows the association between $\tau$ for the same effects before and after transformation.

### 2019-07-12 code/figures.rmd
Changed Figure 3 into correlations per effect-type

--- 2019-04-29 code/figures.rmd
@@
 
-```{r transform_effect_and_compute_rma}
-#Transform effect sizes to biserial correlations (pearson's correlations as is)
-#then compute random effects meta-analyses per effect
-#'transform_MA' and 'summarizer' are sourced functions
-res <- dat %>% 
-  split(.$effect) %>%  #necessary step otherwise the function is applied overall
-  map(transform_MA) %>% #apply function each effect in the list
-  map_dfr(summarizer, .id = "effect") %>%  #apply function and transform to dataframe
-  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
-```
-
-```{r cor_het_effect_size, results = "hide", cache=TRUE}
-#Basic correlations
-cor.test(res$I2, res$r) #pearson I2
-
-I2_fit <- summary(lm(I2 ~ r, data = res)) #for annotating figures
-
-cor.test(res$tau2, res$r) #pearson tau2
-
-tau2_fit <- summary(lm(tau2 ~ r, data = res))
-
-cor.test(res$H2, res$r) #pearson H2
-
-H2_fit <- summary(lm(H2 ~ r, data = res))
-
-cor.test(res$I2, res$r, method = "spearman") #spearman
-
-##Excluding anchoring effects
-dropped_anchoring <- res %>%
-  filter(!grepl("Anchoring", effect))
-
-cor.test(dropped_anchoring$I2, dropped_anchoring$r) #pearson
-
-#bootstrap confidence intervals
-#code by Amir Abdol
-
-#I2
-pear <- function(formula, data, indices){ #pearson
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ I2 + r, data=d)
-     return(fit$estimate)
-}
-
-bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + I2)
-
-I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
-
-spear <- function(formula, data, indices){ #spearman
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ I2 + r, data=d, method = "spearman")
-     return(fit$estimate)
-}
-
-options(warn=-1)
-bootfit <- boot(data=res, statistic=spear, R=1000, formula= ~ r + I2)
-options(warn=0)
-
-I2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
-
-#Excluding anchoring effects
-bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ r + I2)
-
-I2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
-
-#H2
-pear <- function(formula, data, indices){
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ H2 + r, data=d)
-     return(fit$estimate)
-}
-
-bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + H2)
-
-H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
-
-```
-
-##Figure 3
-```{r plot_res, cache = TRUE}
-
-#Plots of H2 and I2 vs. biserial correlation r for all effects together, two above chunks need to be run first
-
-I2 <- ggplot(res, aes(x = r, y = I2)) +
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") +
-  coord_cartesian(ylim = c(0, 100)) +
-  annotate("text", x = 0.14, y = Inf, vjust = 5, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
-  theme_classic() +
-  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
-        axis.ticks.x = element_blank(),
-        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
-                                    size = 0.5, linetype = "solid")) +
-  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
-  scale_x_continuous(name = NULL)
-
-H2 <- ggplot(res, aes(x = r, y = H2)) + 
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") +
-  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
-  theme_classic() +
-  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
-        axis.ticks.x = element_blank(),
-        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
-                                    size = 0.5, linetype = "solid")) +
-  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
-  scale_x_continuous(name = NULL)
-
-tau2 <- ggplot(res, aes(x = r, y = tau2)) + 
-  geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") +
-  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
-  theme_classic() +
-  theme(panel.border = element_rect(fill = NA, colour = "black", #add box around plots
-                                    size = 0.5, linetype = "solid")) +
-  scale_y_continuous(name = expression(paste(italic(tau)^2, " estimate"))) +
-  scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))
-
-effect_het <- plot_grid(I2, H2, tau2, ncol = 1, align = "v", rel_heights = c(0.86, 0.86, 1), labels = c("a", "b", "c")) #combine plots
-effect_het
-# save_plot("../figures/effect-het.png", effect_het,
-         # ncol = 1, base_height = 7, base_width = 5, dpi = 600)
-
-```
-
-Figure 3.
-The correlation between a) I2 ,and effect size and b) H2 and c)  τ ̂^2and effect size for 37 effects from ten pre-registered multi-lab replication projects.
-Shaded bands represent 95% confidence intervals
-
-##Correlations per effect type (alternative figure 3, probably drop)
-```{r corr_per_effect_type, cache = TRUE}
+##Figure 3, correlations per effect type
+```{r corr_per_effect_type, cache = FALSE}
 #Each set of input datapoints is meta-analyzed as per the original replication project
@@
 
-#effects that were transformed from OR to SMD
+MD_fit <- function(x){
+    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
+    hetero <- confint(fit)$random[c(1, 3), ] 
+    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
+             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
+}
+
+fisher_fit <- function(x){
+    fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, data = x)
+    hetero <- confint(fit)$random[c(1, 3), ] 
+    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
+             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
+    }
+
+#Raw mean differences to SMD
+MD_standardized <- dat %>% 
+  filter(effect_type == "Raw mean difference" & !outcomes1_2 == "mean _ SE") %>% #No method in metafor to compute SMD when standard deviations not given, so skip this study 
+  split(.$effect) %>% 
+  map_dfr(MD_fit, .id = "effect")
+
+fisher <- dat %>% 
+  filter(effect_type == "r") %>% 
+  split(.$effect) %>% 
+  map_dfr(fisher_fit, .id = "effect")
+
+#effects that were transformed from OR to SMD by ML1 which we will drop
 OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
@@
 
-OR_fit <- function(x){ #fit rma to odds raios
-  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
-  hetero <- confint(fit)$random[c(1, 3), ] 
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
-             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
-             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}
-
-fit_OR <- dat %>% 
-  filter(effect %in% OR2d) %>% 
-  split(.$effect) %>% 
-  map_dfr(OR_fit, .id = "effect")
-
 tau2_per_type <- dat %>% #This is to add the effect_type names
   select(effect, effect_type) %>% 
-  distinct() %>% 
+  distinct() %>% #get unique rows
   mutate(effect_type = recode(effect_type, 
-                              d = "Standardized Mean Difference",
-                              'Raw mean difference' = "Mean Difference",
-                              'Risk difference' = "Risk Difference",
-                              'r' = "Correlation")) %>% 
-  left_join(tau2_per_type) %>% 
-  filter(!effect %in% OR2d) %>% #drop old SMD converted OR
-  bind_rows(fit_OR) %>% #and instead add OR meta-analyzed as OR
-  mutate(effect_type = ifelse(is.na(effect_type), "Odds Ratio", effect_type),
-         eff_size = abs(eff_size)) #need the absolute values for plotting
+                              d = "Standardized Mean Difference")) %>% 
+  left_join(tau2_per_type) %>% #Add the meta-analytic results
+  filter(!effect %in% c(OR2d, MD_standardized$effect, fisher$effect)) %>% #drop old SMD converted OR, unstandardized MD and raw correlations
+  bind_rows(MD_standardized) %>% #add MD after standardization
+  bind_rows(fisher) %>% #add correlations as fisher's z
+  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
+         effect_type = ifelse(effect %in% fisher$effect, "Fisher's z", effect_type),
+         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
+  filter(effect_type %in% c("Standardized Mean Difference", "Fisher's z"))
 
 fitter <- function(df){  #function to fit correlations for annotating facet plots
- fit <- summary(lm(tau2 ~ eff_size, data = df))
- data.frame(b = format(round(fit$coefficients[2, 1], digits = 2), nsmall = 2), #because map_dfr requires dataframe
-            r = format(round(sqrt(fit$r.squared), digits = 2), nsmall = 2)) #output, the output is kept as two vars
+ fit_tau2 <- summary(lm(tau2 ~ eff_size, data = df))
+ fit_I2 <- summary(lm(s_I2 ~ eff_size, data = df))
+ fit_H2 <- summary(lm(H2 ~ eff_size, data = df))
+ b <- c(fit_tau2$coefficients[2, 1], fit_I2$coefficients[2, 1], fit_H2$coefficients[2, 1])
+ r <- c(sqrt(fit_tau2$r.squared), sqrt(fit_I2$r.squared), sqrt(fit_H2$r.squared))
+ data.frame(b = format(round(b, digits = 2), nsmall = 2), #because map_dfr requires dataframe
+            r = format(round(r, digits = 2), nsmall = 2),
+            index = c("tau2", "I2", "H2")) #output, the output is kept as two vars
 }
 
-labels <- tau2_per_type %>% 
+labels <- tau2_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
   split(.$effect_type) %>% 
@@
 
+#tau2plot----
 tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
   geom_point(alpha = 0.5) +
-  geom_line(stat = "smooth", method = "lm", se = FALSE, color = "black", alpha = .5, linetype = "dashed") + #to set alpha for the line geom_line must be used rather than geom_smooth
-  geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
+  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
   scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
@@
                                     size = 0.5, linetype = "solid")) + 
-  facet_wrap(~effect_type, scales = "free") #use free scales since scales are different
+  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different
 
-tau2_facet
-# ggsave("../figures/tau2_facet.png", dpi = 600, height =  7, width = 7)
+#I2plot----
+I2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = s_I2)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
+  scale_x_continuous(name = "Effect size") +
+  coord_cartesian(ylim = c(0, 100)) +
+  theme_classic() +
+  theme(strip.background = element_blank(), #remove box around titles
+        strip.text = element_text(size = 12),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid")) + 
+  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different
+
+#H2plot----
+H2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = H2)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
+  scale_x_continuous(name = "Effect size") +
+  theme_classic() +
+  theme(strip.background = element_blank(), #remove box around titles
+        strip.text = element_text(size = 12),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid")) + 
+  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different
+
+#combined----
+combo <- cowplot::plot_grid(tau2_facet, I2_facet, H2_facet, labels = "AUTO")
+#ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
+combo
+```
+
+Figure 3.
+The correlation between effect size and A) tau2, b) I2 and c) H2 respectively  22 effects that were measured as mean or standardized mean differences and 6 effects measured as correlations from ten pre-registered multi-lab replication projects.
+Effects reported as mean differences were standardized and correlations were transformed into Fisher’s z.
+Shaded bands represent 95% confidence intervals
+
+```{r cor_het_effect_size, results = "hide", cache=TRUE}
+
+#1. Standardized mean differences----
+SMDs <- tau2_per_type %>% filter(effect_type == "Standardized Mean Difference")
+
+cor.test(SMDs$tau2, SMDs$eff_size) #pearson tau2
+cor.test(SMDs$s_I2, SMDs$eff_size) #pearson I2
+cor.test(SMDs$H2, SMDs$eff_size) #pearson H2
+
+cor.test(SMDs$tau2, SMDs$eff_size, method = "spearman") #spearman
+cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
+cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman
+
+##Excluding anchoring effects
+dropped_anchoring <- SMDs %>%
+  filter(!grepl("Anchoring", effect))
+
+cor.test(dropped_anchoring$s_I2, dropped_anchoring$eff_size) #pearson
+
+#bootstrap confidence intervals
+#code by Amir Abdol
+
+#1.1 I2 confidence intervals----
+pear <- function(formula, data, indices){ #pearson
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d)
+     return(fit$estimate)
+}
+
+bootfit <- boot(data=SMDs, statistic=pear, R=1000, formula= ~ eff_size + s_I2)
+I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+#Excluding anchoring effects
+bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + s_I2)
+
+I2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+#1.2 Tau2 confidence intervals----
+pear <- function(formula, data, indices){
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ tau2 + eff_size, data=d)
+     return(fit$estimate)
+}
+
+bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + tau2)
+
+tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
+
+#Excluding anchoring effects
+cor.test(dropped_anchoring$tau2, dropped_anchoring$eff_size)
+
+bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + tau2)
+
+tau2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+#1.3 H2 confidence intervals----
+pear <- function(formula, data, indices){
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ H2 + eff_size, data=d)
+     return(fit$estimate)
+}
+
+bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + H2)
+
+H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
+
+#1.4 spearman bootstrap CIs----
+#First for I2
+spear <- function(formula, data, indices){ #spearman
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d, method = "spearman")
+     return(fit$estimate)
+}
+
+options(warn=-1)
+bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + s_I2)
+options(warn=0)
+
+I2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
+
+#Second for tau2
+spear <- function(formula, data, indices){ #spearman
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ tau2 + eff_size, data=d, method = "spearman")
+     return(fit$estimate)
+}
+
+options(warn=-1)
+bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + tau2)
+options(warn=0)
+
+tau2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
+
+#2. Fisher's z----
+fish <- tau2_per_type %>% filter(effect_type == "Fisher's z" )
+cor.test(fish$tau2, fish$eff_size) #pearson tau2
+cor.test(fish$s_I2, fish$eff_size) #pearson I2
+cor.test(fish$H2, fish$eff_size)
 

### 2019-07-12 code/helper_functions_tables_figures.r

@@ -55,7 +55,8 @@ est_heterogen_smd_raw <- function(x){
   hetero <- confint(fit)$random[c(1, 3), ] #Gives us the tau2 and I2 estimates with confidence intervals
   data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
              s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
-             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3]) #I2 + CI
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
+             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
 }
 
 

### 2019-07-15 code/tables.rmd
Clarifications of some effect descriptions Table 2

@@
             "Verbal overshadowing 2; Different from 1 only in that the filler task took place before the descriptive task instead of after.", #RRR2
-                 "Grammar on intentionality/intention attribution/detailed processing; Independent two-group experiment with three outcome variables.
-Actions either described in imperfect or perfect.", #RRR3
+                 "Grammar's effect on interpretation; Independent two-group vignette experiment with three outcome variables.
+Participants read about actions either described in imperfect or perfect tense and then rated protagonist's intentions (intentionality/intention attribution/detailed processing).", #RRR3
             "Ego depletion; Independent two-group experiment.
@@
             "Commitment on neglect/exit; Independent two-group experiment with two outcome variables. Participants either primed to think about commitment to or independence from partner.", #RRR5
-            "Facial feedback hypothesis; Independent two-group experiment. Participants either induced to 'smile' or 'pouth' with a pen and then rated funniness of cartoons. ", #RRR6
+            "Facial feedback hypothesis; Independent two-group experiment.
+Participants either induced to 'smile' or 'pouth' by holding a pen in their mouth differently and simultaneously rated funniness of cartoons.
+", #RRR6
             "Intuitive cooperation; Independent two-group experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
@@
                      "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
-                     "31/32 samples were undergraduate students between 18-25, 1 general population which was also the only online sample.", #RRR1
-                     "22/23 samples were undergraduate students between 18-25, 1 general population which was also the only online sample.", #RRR2
-                     "11/12 samples were undergraduate students mostly between 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
+                     "31/32 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR1
+                     "22/23 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR2
+                     "11/12 samples were undergraduate students mostly aged 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
                      "All samples consisted of in-lab undergraduate students", #RRR4
-                     "All samples consisted of in-lab undergraduate students between 18-25", #RRR5
+                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR5
                "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
-               'All samples consisted of in-lab undergraduate students between 18-34.', #RRR7
-                     "All samples consisted of in-lab undergraduate students betweeb 18-25") #RRR8
+               'All samples consisted of in-lab undergraduate students aged 18-34.', #RRR7
+                     "All samples consisted of in-lab undergraduate students aged 18-25") #RRR8
 

### 2019-07-15 code/Supplement-figures-tables.Rmd
Updated code file for supplement tables and figures

--- 2019-06-24 code/tables.rmd
@@
 ---
-title: "Tables"
-author: "Heterogeneity in direct replications in psychology and its association with effect size"
+title: "Supplement - Biserial correlation transformations"
+date: "`r format(Sys.time(), '%d %B, %Y')`"
 output: pdf_document
@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+Sys.setlocale("LC_TIME", "English" ) #to print date in YAML in English
 ```
@@
 if(!require(purrr)){install.packages("purrr")}
-if(!require(kableExtra)){install.packages("kableExtra")}
+if(!require(kableExtra)){install.packages("kablExxtra")}
 
@@
 library(metafor) #To run meta-analyses
-library(kableExtra) #For creating good-looking pdf tables
+library(ggplot2) #plotting figures
+library(cowplot) #combine plots
+library(kableExtra) #create fancy pdf tables
 
@@
 
-##Table 1
-###Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
-```{r effect-size-heterogeneity-table, cache = TRUE}
-#library(kableExtra)
-rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
-rho <- c(0, .3, .5)
-rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
+```{r a-plot-prep, cache = TRUE}
+res <- dat %>% 
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map_dfr(est_heterogen_smd_raw, .id = "effect") #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
 
-rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
-rooted_relabilities <- data.frame(rel, rooted_relabilities)
+het <- dat %>% 
+  select(rp, Site, effect, effect_type) %>% 
+  group_by(rp, effect) %>% 
+  summarize(effect_type = unique(effect_type),
+            k = n_distinct(Site)) %>% 
+  left_join(res) %>% 
+  mutate(effect_type = recode(effect_type, 
+                              d = "SMD.",
+                              'Raw mean difference' = "MD",
+                              'Risk difference' = "RD")) %>% 
+  ungroup()
 
-rooted_relabilities %>% knitr::kable(booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
-  kable_styling(position = "left") %>% 
-  footnote(threeparttable = TRUE, escape = FALSE,
-           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ when sample size is infinite.
-Increasing column-wise variance in observed effect sizes illustrates the association between effect size, reliability of measurement and heterogeneity  Code to reproduce table: osf.io/kf6pt/") %>%
-  row_spec(3, hline_after = T)
+a <- het %>% filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "SMD.")
+```
+
+```{r, cache = FALSE}
+a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("SMD (untransformed)") +
+  scale_x_continuous(name = expression(paste(italic(I)^2, "Index"))) +
+  scale_y_continuous(name = "Tau")
 
@@
 
-##Table 2
-###Pre-registered multi-lab replication projects
-```{r data-summary-table}
-#library(dplyr)
-#library(kableExtra)
+```{r trunc-biserial, cache = TRUE}
+#Transform effect sizes to biserial correlations (pearson's correlations left as is)
+#estimate tau2 for correlations
+#'transform_MA' and 'summarizer' are sourced functions
+res2 <- dat %>% 
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map(transform_MA) %>% #
+  map_dfr(summarizer, .id = "effect")
 
-#Shortened version of APA reference
-papers <- c('Klein et al. (2014)', 
-'Ebersole et al. (2016)',
-'Alogna et al. (2014)',
-'Alogna et al. (2014)',
-'Eerland et al. (2016)',
-'Hagger et al. (2016)',
-'Cheung et al. (2016)',
-'Wagenmakers et al. (2016)',
-'Bouwmeester et al. (2017)',
-"O'Donnell et al. (2017)")
+#Add rp and k to the data-frame 
+het <- dat %>% 
+  select(rp, Site, effect, effect_type) %>% 
+  group_by(rp, effect) %>% 
+  summarize(effect_type = unique(effect_type),
+            k = n_distinct(Site)) %>% 
+  left_join(res2) %>% 
+  mutate(effect_type = recode(effect_type, 
+                              d = "SMD.",
+                              'Raw mean difference' = "MD",
+                              'Risk difference' = "RD")) %>% 
+  ungroup()
 
-##Full APA reference below
-# c('Klein, R.
-A., Ratliff, K.
-A., Vianello, M., Adams, R.
-B., Jr., Bahn?k, S., Bernstein, M.
-J., .
-.
-.
-Nosek, B.
-A.
-(2014).
-Investigating variation in replicability: A "many labs" replication project.
-Social Psychology, 45(3), 142-152.',
-# 'Ebersole, C.
-R., Atherton, O.
-E., Belanger, A.
-L., Skulborstad, H.
-M., Allen, J.
-M., Banks, J.
-B., ...
-& Brown, E.
-R.
-(2016).
-Many Labs 3: Evaluating participant pool quality across the academic semester via replication.
-Journal of Experimental Social Psychology, 67, 68-82.',
-# 'Alogna, V.
-K., Attaya, M.
-K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A.
-R., ...
-& Buswell, K.
-(2014).
-Registered replication report: Schooler and engstler-schooler (1990).
-Perspectives on Psychological Science, 9(5), 556-578.',
-# 'Alogna, V.
-K., Attaya, M.
-K., Aucoin, P., Bahn?k, S., Birch, S., Birt, A.
-R., ...
-& Buswell, K.
-(2014).
-Registered replication report: Schooler and engstler-schooler (1990).
-Perspectives on Psychological Science, 9(5), 556-578.',
-# 'Eerland, A., Sherrill, A.
-M., Magliano, J.
-P., Zwaan, R.
-A., Arnal, J.
-D., Aucoin, P., ...
-& Crocker, C.
-(2016).
-Registered replication report: Hart & Albarrac?n (2011).
-Perspectives on Psychological Science, 11(1), 158-171.',
-# 'Hagger, M.
-S., Chatzisarantis, N.
-L., Alberts, H., Anggono, C.
-O., Batailler, C., Birt, A.
-R., ...
-& Calvillo, D.
-P.
-(2016).
-A multilab preregistered replication of the ego-depletion effect.
-Perspectives on Psychological Science, 11(4), 546-573.',
-# 'Cheung, I., Campbell, L., LeBel, E.
-P., Ackerman, R.
-A., Aykutoglu, B., Bahn?k, S., ...
-& Carcedo, R.
-J.
-(2016).
-Registered Replication Report: Study 1 from Finkel, Rusbult, Kumashiro, & Hannon (2002).
-Perspectives on Psychological Science, 11(5), 750-764.',
-# 'Wagenmakers, E.
-J., Beek, T., Dijkhoff, L., Gronau, Q.
-F., Acosta, A., Adams Jr, R.
-B., ...
-& Bulnes, L.
-C.
-(2016).
-Registered Replication Report: Strack, Martin, & Stepper (1988).
-Perspectives on Psychological Science, 11(6), 917-928.',
-# 'Bouwmeester, S., Verkoeijen, P.
-P., Aczel, B., Barbosa, F., B?gue, L., Bra?as-Garza, P., ...
-& Evans, A.
-M.
-(2017).
-Registered Replication Report: Rand, Greene, and Nowak (2012).
-Perspectives on Psychological Science, 12(3), 527-542.',
-# "O'Donnell, M., Nelson, L., McLatchie, N.
-M., & Lynott, D.
-J.
-(2017).
-Registered Replication Report: Dijksterhuis & van Knippenberg (1998): Multilab direct replication of: A variant of study 4 from Dijksterhuis, A., & van Knippenberg, A.(1998).
-The relation between perception and behavior, or how to win a game of trivial pursuit.
-Journal of personality and social psychology.
-Perspectives on Psychological Science."
+d <- het %>% filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "SMD.") %>% 
+  mutate(sigma2 = tau2/(I2/100) - tau2) #add 'typical within study variance' per project
 
-description <- c("Two correlational effects: 'Gender math attitude' compared implicit attitudes (IAT) towards math between genders and 'IAT correlation math' correlated implicit attitudes with self-reported measures.
-The remainder were experiments with two independent groups.
-The groups were primed in some way (Anchoring 1-4; low vs.
-high category scales; norm of reciprocity; flag priming; currency priming), asked to imagine slightly different situations (Sunk costs; gain vs.
-loss framing; gambler's fallacy; imagined contact) or asked their agreement with statements presented differently (Allowed vs.
-forbidden; quote attribution).
-", #ML1
-            "Several effects were experiments with two independent groups.
-The groups were either primed in some way (Power and perspective; warmth perceptions; subjective distance interaction), saw slightly different statements (Elaboration likelihood interaction; credentials interaction) or experienced different situations (weight embodiment).
-Examined interactions were between treatment conditions and participant characteristics.
-One priming effect (metaphor) compared two treatment groups with a control.
-One effect was correlational: 'persistence and conscientiousness' was measured by an unsolvable anagram task and self-report respectively.
-The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML2
-                 "Verbal overshadowing 1; Independent two-group experiment.
-Participants either described a robber after watching a video or listed countries/capitals and after a filler task attempted to identify the robber in a lineup.", #RRR1
-            "Verbal overshadowing 2; Different from 1 only in that the filler task took place before the descriptive task instead of after.", #RRR2
-                 "Grammar on intentionality/intention attribution/detailed processing; Independent two-group experiment with three outcome variables.
-Actions either described in imperfect or perfect.", #RRR3
-            "Ego depletion; Independent two-group experiment.
-Participants either assigned to a cognitively demanding task or a neutral, and performance was then measured in a subsequent cognitive task.", #RRR4
-            "Commitment on neglect/exit; Independent two-group experiment with two outcome variables. Participants either primed to think about commitment to or independence from partner.", #RRR5
-            "Facial feedback hypothesis; Independent two-group experiment. Participants either induced to 'smile' or 'pouth' with a pen and then rated funniness of cartoons. ", #RRR6
-            "Intuitive cooperation; Independent two-group experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
-                 "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.") #RRR8
+```
 
-US_online <- dat %>% #Extract the (max when multiple effects) number of US/online labs per RP
-  group_by(rp, effect) %>% 
-  summarize(US = sum(country == "USA"),
-            online = sum(in_lab == 0)) %>% 
-  group_by(rp) %>% 
-  summarize(US = max(US),
-            online = max(online)) %>% 
-  ungroup() %>% select(US, online)
+```{r c-plot-1, cache = FALSE}
+c_plot_1 <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("Biserial r (transformed SMD)")
 
-sample_settings <- c("26/36 samples were primarily university students, 3 general population and 7 undescribed.
-9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
-                     "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
-                     "31/32 samples were undergraduate students between 18-25, 1 general population which was also the only online sample.", #RRR1
-                     "22/23 samples were undergraduate students between 18-25, 1 general population which was also the only online sample.", #RRR2
-                     "11/12 samples were undergraduate students mostly between 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
-                     "All samples consisted of in-lab undergraduate students", #RRR4
-                     "All samples consisted of in-lab undergraduate students between 18-25", #RRR5
-               "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
-               'All samples consisted of in-lab undergraduate students between 18-34.', #RRR7
-                     "All samples consisted of in-lab undergraduate students betweeb 18-25") #RRR8
+```
 
-#1) what kind of samples
+```{r untruncated-biserial, cache = TRUE}
+res3 <- dat %>%
+  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & outcomes1_2 == "mean _ SD") %>% 
+  split(.$effect) %>% 
+  map(~transform_SD(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2, .$ntreatment, .$ncontrol)) %>% 
+  map(~untruncated_d_to_r(.$d, .$n1, .$n2)) %>% 
+  map_dfr(summarizer, .id = "effect")
+```
 
-summary.table <- dat %>% 
-  group_by(rp) %>% 
-  summarize(Countries = n_distinct(country),
-            k = n_distinct(Site), 
-            Effects = n_distinct(effect),
-            N = if(Effects == 1){sum(Ntotal)}
-                           else{sum(Ntotal) / Effects}) %>% #average across effects
-  mutate(Paper = papers,
-         'Sample and Settings' = sample_settings,
-         'Description of Effects' = description,
-         'K (US)' = paste0(k, " (", US_online$US, ")")) %>% 
-  select(RP = rp, Paper, Countries,'K (US)', everything(), -k) #change order of columns
+```{r c-plot, cache = FALSE}
+c_plot <- c_plot_1 + geom_point(data = res3, shape = 4, aes(x = I2, y = sqrt(tau2))) +
+  scale_x_continuous(name = expression(paste(italic(I)^2, " Index (biserial)"))) +
+  scale_y_continuous(name = "Tau (biserial)")
 
-summary.table %>% knitr::kable(booktabs = TRUE,
-                               digits = 0,
-                               linesep = "\\addlinespace",
-                               longtable = TRUE) %>% 
-  kable_styling(c("hold_position", "repeat_header"), font_size = 7) %>% 
-  column_spec(2, width = "7em") %>% #specify width of paper column 
-  column_spec(7, width = "16em") %>% 
-  column_spec(8, width = "30em") %>% 
-  landscape()
 ```
-Note: "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
-N = Participants used for primary analyses by original authors (i.e., after exclusions).
-RP = Replication Project, K (US) = no.
-primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report.
-Code to reproduce table: osf.io/kf6pt/"
 
-##Table 3
-###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
+```{r tau-vs-tau}
+b <- select(a, effect, tau2) %>% 
+  left_join(select(d, effect, tau2), by = "effect") %>% #add truncated transformation tau2
+  left_join(select(res3, effect, tau2), by = "effect") #add untruncated transformation tau2
+```
+
+```{r b-plot-1}
+b_plot_1 <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) + 
+  geom_point()
+
+```
+
+```{r b-plot}
+b_plot <- b_plot_1 + geom_point(data = b, shape = 4, aes(x = sqrt(tau2.x), y = sqrt(tau2))) +
+  ggtitle("SMD vs. biserial") +
+  scale_x_continuous(name = "Tau (SMD)") +
+  scale_y_continuous(name = "Tau (biserial)")
+```
+
+```{r, fig.width = 6, fig.asp = 1.3}
+cowplot::plot_grid(a_plot, b_plot, c_plot, ncol = 1, labels = "AUTO")
+
+# ggsave("../figures/Figure-S1.png", dpi = 600, width = 6, height = 7.8)
+```
+
+_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into biserial correlations for all effects reported as SMDs in ManyLabs 1.
+Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text).
+Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to biserial correlations, either with truncation of correlations over 1 (circles) or without (crosses) when estimating variance.
+Panel C  shows the associations between estimates of $I^2$ on the SMD metric and estimates of $\tau$ after transformation, either with truncation or not.
+
+#Table S1.
+###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
 ```{r prep-heterogeneity-table, cache = TRUE}

### 2019-07-15 code/figures.rmd
Only include panel a) of Figure 3 in the main manuscript
Cleaned up figures file

@@
 ---
-title: "Figures"
+title: "Figures main manuscript"
 author: "Heterogeneity in direct replications in psychology and its association with effect size"
@@
 ##Figure 1
+
 ```{r Plot_tau_against_I2, fig.asp = 0.618, cache = TRUE}
@@
 ##Figure 2
-```{r Density_plot, cache = TRUE}
 
+```{r Density-plot-prep, cache = TRUE}
 #1) I2 plot----
@@
   mutate(Heterogeneity = "Observed")
+```
 
+```{r Density-plot, fig.height=4, fig.width=6.47}
 I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
@@
 
-#ggsave("../figures/density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
+I2_plot
+# ggsave("../figures/density-I2.png", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
 
-#2) tau2 plot----
-
-dens_tau2 <- readRDS("../data/biserial_simulation_results.RDS")
-names(dens_tau2) <-  sort(unique(dat$effect))
-
-# Simulated data at various heterogeneity levels, prep for plotting
-tau2_dist <- dens_tau2 %>%
- bind_rows(.id = "effect") %>%
- rename(Heterogeneity = tau_index) %>%
- mutate(Heterogeneity = recode(Heterogeneity,
-                             '1' = "Zero",
-                             '2' = "Small",
-                             '3' = "Medium",
-                             '4' = "Large"),
-          Heterogeneity = as.factor(Heterogeneity),
-        tau = sqrt(tau2_hat))
-
-# Observed tau2 estimates, i.e, results from main table, see table.rmd
-# Effects transformed and estimated with sourced functions 'transform_MA' and 'summarizer'
-observed_tau <- dat %>%
-   split(.$effect) %>%
-   map(transform_MA) %>% 
-   map_dfr(summarizer, .id = "effect") %>%
-   select(effect, tau2) %>%
-   mutate(Heterogeneity = "Observed",
-          tau = sqrt(tau2))
-
-tau_plot <- ggplot(tau2_dist, aes(x = tau, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
-  geom_histogram(data = observed_tau, aes(y = ..density.., x = tau), bins = 130, alpha = 1) +
-  geom_density(alpha = 0.3) +
-  theme_classic() +
-  coord_cartesian(xlim = c(0, 0.25)) + #truncate plot for better visualization
-  scale_fill_brewer(palette = "Dark2",
-                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                     labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
-  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
-                         breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                         labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
-  scale_color_brewer(palette = "Dark2",
-                      breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                      labels = c("Zero (0)", "Small (1/321)", "Medium (1/107)", "Large (3/107)", "Observed")) +
-  theme(legend.position = c(0.85, 0.71),
-       legend.background = element_rect(linetype = "solid", color = "black")) +
-  scale_y_continuous(name = "Density") +
-  scale_x_continuous(name = expression(paste(italic(tau)," estimate", sep = ""))) +
-  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
-
-#ggsave("../figures/density-tau2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
-
-#3) combine I2-tau2-density-plots----
-densities <- plot_grid(I2_plot, tau_plot, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
-densities
-
-# save_plot("../figures/densities_het.png", densities,
-#            nrow = 2,  base_width = 7, base_aspect_ratio = 0.618, dpi = 600)
 ```
@@
 Figure 2.
-Simulated $I^2$ (a) and $/tau^2$ (b) densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed I2 estimates for the 37 effects.
-For panel b) effects consist of correlations and biserial correlation and heterogeneity levels were approximated by Fisher’s z values corresponding to Higgins’ definitions for the median sample size of 108.
+Simulated $I^2$  densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed $I^2$ estimates for the 37 effects.
 Each simulated density consists of approximately 370,000 estimates.
@@
 ##Figure 3, correlations per effect type
-```{r corr_per_effect_type, cache = FALSE}
+
+```{r corr_per_effect_type-prep, cache = TRUE}
 #Each set of input datapoints is meta-analyzed as per the original replication project
@@
   mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting
+```
 
+```{r corr_per_effect_type-plot, cache = FALSE}
 #tau2plot----
@@
 ```{r cor_het_effect_size, results = "hide", cache=TRUE}
+
+#This section gives the correlations reported in the section 'Heterogeneity and effect sizes' in the main manuscript
 

### 2019-07-15 code/tables.rmd
Cleaned up tables file

@@
 
+```{r, include=FALSE}
+options(tinytex.verbose = TRUE)
+```
 ##Table 1
@@
            general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ when sample size is infinite.
-Increasing column-wise variance in observed effect sizes illustrates the association between effect size, reliability of measurement and heterogeneity  Code to reproduce table: osf.io/kf6pt/") %>%
+Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06") %>%
   row_spec(3, hline_after = T)
@@
 ```
-Note: "For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
+Note: For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
 N = Participants used for primary analyses by original authors (i.e., after exclusions).
@@
 primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report.
-Code to reproduce table: osf.io/kf6pt/"
+Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06"
 
 ##Table 3
-###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated between studies variance ($\tau^2$).
+###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
 ```{r prep-heterogeneity-table, cache = TRUE}
@@
   select(-tau2, - tau2_ci.lb, -tau2_ci.ub) #drop redundant variables
-
-#Transform effect sizes to biserial correlations (pearson's correlations left as is)
-#estimate tau2 for correlations
-#'transform_MA' and 'summarizer' are sourced functions
-res2 <- dat %>% 
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map(transform_MA) %>% #
-  map_dfr(summarizer, .id = "effect")
-
-res <- res %>%
-  mutate(r = res2$r,
-         tau_r = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
-         tau_r_ci.lb = sqrt(res2$tau2.lb),
-         tau_r_ci.ub = sqrt(res2$tau2.ub))
 
@@
          tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),
-         tau = format(round(tau, 3), nsmall = 3),
-         tau_r = format(round(tau_r, 3), nsmall = 3),
-         tau_r_ci = paste0("[", trimws(format(round(tau_r_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_r_ci.ub, 3), nsmall = 3)), "]")) %>% #rounded here instead of in table function because should have 4 digits
-  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau, tau_ci, r, tau_r, tau_r_ci, zero, small, medium, large)
+         tau = format(round(tau, 3), nsmall = 3)) %>% #rounded here instead of in table function because should have 4 digits
+  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau, tau_ci, zero, small, medium, large)
 
@@
 
-het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "r*" , "r* $\\tau$", "r* $\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
   add_header_above(c(" " = 12, "Level of heterogeneity" = 4)) %>% 
@@
 RP = Replication Project, K = no.
-primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations.
-$I^2$ and its confidence intervals are for original effect size specifications whereas $\tau$ and its confidence intervals are for transformed r* effect sizes.
+primary studies, tau = between studies standard deviation, CI = confidence intervals.
 Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-Code to reproduce table: osf.io/kf6pt/",
+Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06",
            alphabet = "These effects were simulated as standardized mean differences") %>% 

### 2019-07-16 code/figures.rmd
Added confidence intervals to annotations of Figure 3

@@
 
+#labels for figure 3----
 fitter <- function(df){  #function to fit correlations for annotating facet plots
@@
  r <- c(sqrt(fit_tau2$r.squared), sqrt(fit_I2$r.squared), sqrt(fit_H2$r.squared))
- data.frame(b = format(round(b, digits = 2), nsmall = 2), #because map_dfr requires dataframe
+ data.frame(b = format(round(b, digits = 2), nsmall = 2), 
             r = format(round(r, digits = 2), nsmall = 2),
-            index = c("tau2", "I2", "H2")) #output, the output is kept as two vars
+            index = c("tau2", "I2", "H2")) 
 }
+
+#functions to estimate bootstrapped confidence intervals to add to plot correlations
+pear_tau2 <- function(formula, data, indices){ #pearson
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ tau2 + eff_size, data=d)
+     return(fit$estimate)
+}
+pear_I2 <- function(formula, data, indices){ #pearson
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d)
+     return(fit$estimate)
+}
+pear_H2 <- function(formula, data, indices){ #pearson
+     d <- data[indices,]
+     fit <- cor.test(formula = ~ H2 + eff_size, data=d)
+     return(fit$estimate)
+}
+
+bootfitter <- function(x){ #function that computes the bootstrapped confidence intervals using above functions to annotate plots
+  bootfit <- boot(data=x, statistic=pear_tau2, R=1000, formula= ~ eff_size + tau2)
+  tau2_ci_pears <- boot.ci(bootfit, type="perc")
+  bootfit <- boot(data=x, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2)
+  I2_ci_pears <- boot.ci(bootfit, type="perc")
+  bootfit <- boot(data=x, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
+  H2_ci_pears <- boot.ci(bootfit, type="perc")
+
+  ci.lb <- c(tau2_ci_pears$percent[4], I2_ci_pears$percent[4], H2_ci_pears$percent[4])
+  ci.ub <- c(tau2_ci_pears$percent[5], I2_ci_pears$percent[5], H2_ci_pears$percent[5])
+
+  ci <- paste0("[", format(round(ci.lb, 2), nsmall = 2), ", ",
+       format(round(ci.ub, 2), nsmall = 2), "]")#percentile 
+  data.frame(ci, index = c("tau2", "I2", "H2"))
+}
+
+set.seed(435) #for the bootstrapping
+fig3_ci <- tau2_per_type %>% 
+  split(.$effect_type) %>% 
+  map_dfr(bootfitter, .id = "effect_type")
 
@@
   map_dfr(fitter, .id = "effect_type") %>%
-  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting
+  mutate(r = ifelse(r == 0.15, -0.15, r), #should be negative, but I took squared root of R^2 to get correlations so needs correction
+         lab = paste0("b = ", b, ", r = ", r, " ", fig3_ci$ci)) #put output into one variable for improved plotting
+
 ```

### 2019-07-16 code/figures.rmd
Removed visual confidence bands from Figure 3

@@
   geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
   geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
@@
   geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
   geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
@@
   geom_point(alpha = 0.5) +
-  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
   geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different

### 2019-07-19 code/Supplement-figures-tables.Rmd
Formatting of table .rmd output to make it equivalent to paper tables

@@
 ---
-title: "Supplement - Biserial correlation transformations"
+title: "Tables and Figures - Supplement A and B"
 date: "`r format(Sys.time(), '%d %B, %Y')`"
@@
 ---
+
+This document contains the code to reproduce tables and figures from Supplement A and Supplement B for the project "Heterogeneity in direct replications in psychology and its association with effect size".
 
@@
 ```
+
+##Supplement A
 
@@
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-Code to reproduce table: osf.io/kf6pt/",
+Code to reproduce table: https://osf.io/j9zyd/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06",
            alphabet = "These effects were simulated as standardized mean differences") %>% 
@@
 ```
+
+##Supplement B
+
+```{r Supplement-B-table}
+
+#Summary of results. These are incorporated into the main table in the paper, see tables.rmd
+zero <- dens %>% 
+  bind_rows(.id = "effect") %>% 
+  group_by(effect, tau_index) %>% 
+  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
+  ungroup() %>% 
+  tidyr::spread(key = tau_index, value = power) %>% #prep for table
+  rename(Zero = '1', Small = '2', Medium = '3', Large = '4', Effect = effect)
+
+##Medium effect size results
+dens2 <- readRDS("../data/appendixA_power_simulation_results.RDS") 
+names(dens2) <-  sort(unique(dat$effect))
+
+#Summary of results.
+medium <- dens2 %>% 
+  bind_rows(.id = "effect") %>% 
+  group_by(effect, tau_index) %>% 
+  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
+  ungroup() %>% 
+  tidyr::spread(key = tau_index, value = power) %>% #prep for table
+  rename(Zero = '1', Small = '2', Medium = '3', Large = '4') %>% 
+  select(-effect)
+
+##combine for table
+
+comparison <- cbind(zero, medium)
+```
+
+Sensitivity analysis assuming a medium true effect size rather than zero true effect size
+
+In our main results we simulated data to estimate type I error and power using an average true effect size equal to zero.
+As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity.
+However, as a sensitivity analysis, in Supplement B we also estimated type I error and power, but generated with an average 'medium' true effect size as defined by Cohen (1988).
+
+Estimated type I error and power for zero/small/medium/large heterogeneity when simulated with a true effect size of zero vs.
+medium are shown for each effect in Table A1.
+In both cases type I error is approximately nominal, as compared to the expected 5% error rate.
+With a true effect size of zero, average power was `r 100*round(mean(zero$Small), digits = 2)`%/`r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`% for small/medium/large heterogeneity, respectively.
+The corresponding power with a true medium effect size was also `r 100*round(mean(zero$Small), digits = 2)`%/ `r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`%, respectively.
+To conclude, changing true effect size in our simulations from zero to medium had little to no impact on estimated type I error and power.
+
+_Type I error and power to detect four heterogeneity levels under two true effect sizes_
+
+```{r}
+knitr::kable(comparison, digits = 2)
+```
+
+**Note.** Column headers indicate the degree of simulated heterogeneity where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75%) respectively.
+Medium effect size is as defined by Cohen (1988).
+Code to reproduce table: https://osf.io/j9zyd/?view_only=e6639d8d4f924739a7310782fbbb4e06

### 2019-07-19 code/tables.rmd
Formatting of table .rmd output to make it equivalent to paper tables

@@
 
-```{r, include=FALSE}
-options(tinytex.verbose = TRUE)
-```
 ##Table 1
@@
   kable_styling(position = "left") %>% 
-  footnote(threeparttable = TRUE, escape = FALSE,
-           general = "Values in cells are observed effect sizes arising from the true effect size $\\\\rho_{xy}$ and measurement reliabilites $\\\\sqrt{R_{xx'}}\\\\times\\\\sqrt{R_{yy'}}$ when sample size is infinite.
-Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06") %>%
   row_spec(3, hline_after = T)
@@
 ```
+*Note:* Values in cells are observed effect sizes arising from the true effect size $\rho_{xy}$ and measurement reliabilites $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ when sample size is infinite.
+Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06
 
@@
 One priming effect (metaphor) compared two treatment groups with a control.
-One effect was correlational: 'persistence and conscientiousness' was measured by an unsolvable anagram task and self-report respectively.
+One effect was correlational: 'Conscientiousness and persistence' was measured by an unsolvable anagram task and self-report respectively.
 The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML2
@@
          tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),
-         tau = format(round(tau, 3), nsmall = 3)) %>% #rounded here instead of in table function because should have 4 digits
+         tau = format(round(tau, 3), nsmall = 3)) %>% #rounded here instead of in table function because should have 3 digits
+  mutate_at(vars(zero, small, medium, large), ~format(round(., 2), nsmall = 2)) %>% #round here because of superscripts added later
   select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau, tau_ci, zero, small, medium, large)
+
+#Add superscripts
+het <- het %>% 
+  mutate(s_I2 = ifelse(effect %in% c("Grammar on intention attribution", "Conscientiousness and persistence"), paste0(s_I2, "\\textsuperscript{a}"), s_I2), #add a superscript
+         tau = ifelse(effect == "Conscientiousness and persistence", paste0(tau, "\\textsuperscript{a}"), tau)) %>% 
+  mutate_at(vars(zero, small, medium, large), ~ifelse(effect %in% c('Allowed vs.
+forbidden', 'Gain vs.
+loss framing', 'Norm of reciprocity', 'Low vs.
+high category scales', 'Verbal overshadowing 1', 'Verbal overshadowing 2'), paste0(., "\\textsuperscript{b}"), .)) #add b superscript
 
@@
 
-het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
-  add_header_above(c(" " = 12, "Level of heterogeneity" = 4)) %>% 
-  add_header_above(c(" " = 12, "Type I Error Rate & Statistical Power" = 4)) %>% 
+het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+  add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>% 
+  add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>% 
   kable_styling("scale_down", font_size = 7) %>% #comment out if outputting html file
@@
 RP = Replication Project, K = no.
-primary studies, tau = between studies standard deviation, CI = confidence intervals.
-Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.
+primary studies, $\\\\hat\\\\tau$ = between studies standard deviation, CI = confidence intervals.
+Statistical power was simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large
+heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06",
-           alphabet = "These effects were simulated as standardized mean differences") %>% 
+Code to reproduce table: osf.io/kf6pt/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06" ,
+           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences")) %>% 
   landscape()

### 2019-07-19 code/power_simulation.r
Clean up repository

@@ -26,9 +26,8 @@ library(tidyr) #for 'spread'
 
 dat <- read_csv("../data/collated_summary_data.csv")
 
-source("./helper_functions_tables_figures.r") #for function to transform d to biserial correlation
 #******************************************
-#Simulation functions----
+#Simulation function----
 #******************************************
 simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies to a single list object (effect), see next section
   
@@ -121,63 +120,6 @@ simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies 
 }
 
 
-#*************************
-simulate_biserial <- function(effect, reps, tau){ #similar to above, but only for biserial correlations, effect size -> 0
-  
-  K <- effect$K #Number of studies
-  N <- effect$Ntotal #Sample sizes for all K studies
-  output <- vector("list", length(tau)) #empty list for output
-  
-  if(effect$type == "r"){ #If 'correlation'
-    
-    for(t in seq_along(tau)){ #loop over each tau-value
-      
-      output[[t]] <- map_dfr(1:reps, possibly(function(x){ #For each tau-value repeat below "reps" times and bind into dataframe
-        
-        rho <- rnorm(n = K, mean = 0, sd = tau[t]) #draw effect sizes for each K at given tau
-        
-        fr <- rnorm(n = K, mean = rho, sd = sqrt(1 / (N - 3))) #draw observed correlations (fisher's z) for each k
-        
-        fit <- rma(yi = fr, vi = 1 / (N - 3), method = "REML") #meta-analysis of fisher's z, each study weighted by its N
-        
-        data.frame(tau2_hat = fit$tau2, I2 = fit$I2, Qp = fit$QEp, 
-                   tau = tau[t], tau_index = t)
-        
-      }, otherwise = NULL)) #If rma does not converge, drop that iteration ('possibly' function)
-    }
-    
-  }else{ #for all non-'correlations' transform into biserial correlations
-    
-    n_c <- effect$ncontrol #observed control group sizes
-    n_t <- effect$ntreatment #observed treatment group sizes
-    
-    for(t in seq_along(tau)){
-      
-      output[[t]] <- map_dfr(1:reps, possibly(function(x){
-        
[…]

### 2019-11-05 code/collate_summary_data.r
Added ncp variance to ML2 to compute rmd exactly the same

@@ -152,11 +152,12 @@ for(i in seq_along(tnames)){
            effect_type = "d",
            outcomes1_2 = "mean _ SD", #Describes the content of outcome1 and outcome2 variables
            Ntotal = ntreatment + ncontrol,
+           ml2_ncp_variance = NA, #only for ml2
            country = c("USA", "BRA", "CZE", "USA", "USA", "MYS", "USA", "USA", "TUR", "CAN", "GBR", #Country of each study site
                        "USA", "USA", "CAN", rep("USA", 8), "POL", "POL", rep("USA", 3), "NLD", "USA",
                        "ITA", rep("USA", 6))) %>% 
     select(rp, effect, Site, country, in_lab, Ntotal, B_or_W, design, or_stat_test, effect_type, effect_size, 
-           ntreatment, ncontrol, outcomes1_2, outcome_t1, outcome_c1, outcome_t2, outcome_c2) #select only variables of interest
+           ntreatment, ncontrol, outcomes1_2, outcome_t1, outcome_c1, outcome_t2, outcome_c2, ml2_ncp_variance) #select only variables of interest
 }
 
 teffects <- do.call("rbind", teffects) #bind into one dataframe
@@ -217,11 +218,12 @@ chieffects[[i]] <- chieffects[[i]] %>%
          ntreatment = outcome_t1 + outcome_t2,
          ncontrol = outcome_c1 + outcome_c2,
          Ntotal = ntreatment + ncontrol,
+         ml2_ncp_variance = NA, #only for ml2
          country = c("USA", "BRA", "CZE", "USA", "USA", "MYS", "USA", "USA", "TUR", "CAN", "GBR",
                      "USA", "USA", "CAN", rep("USA", 8), "POL", "POL", rep("USA", 3), "NLD", "USA",
                      "ITA", rep("USA", 6))) %>% 
   select(rp, effect, Site, country, in_lab, Ntotal, B_or_W, design, or_stat_test, effect_type, effect_size, 
-         ntreatment, ncontrol, outcomes1_2, outcome_t1, outcome_c1, outcome_t2, outcome_c2) #select only variables of interest
+         ntreatment, ncontrol, outcomes1_2, outcome_t1, outcome_c1, outcome_t2, outcome_c2, ml2_ncp_variance) #select only variables of interest
 }
 
 chieffects <- do.call("rbind", chieffects) #combine into one dataframe
@@ -254,11 +256,12 @@ math_art <- math_art %>%
[…]

### 2019-11-05 code/power_simulation.r
updated simulation code to handle cohen's q

@@ -57,6 +57,31 @@ simulate_I2 <- function(effect, reps, tau, effect_size){ #this function applies 
       }, otherwise = NULL)) #If rma does not converge, drop that iteration ('possibly' function)
     }
     
+  }else if(effect$type == "q"){ #If difference between correlations (cohen's q)
+    n_c <- effect$ncontrol #observed control group sizes
+    n_t <- effect$ntreatment #observed treatment group sizes
+    
+    for(t in seq_along(tau)){ #loop over each tau-value
+      
+      output[[t]] <- map_dfr(1:reps, possibly(function(x){ #For each tau-value repeat below "reps" times and bind into dataframe
+        
+        rho <- switch(effect_size, #Draw true difference in correlation rho for each k at the given value of tau and with specified effect size
+                      zero = rnorm(n = K, mean = 0, sd = tau[t]),
+                      small = rnorm(n = K, mean = 0.1, sd = tau[t]),
+                      medium = rnorm(n = K, mean = 0.3, sd = tau[t]),
+                      large = rnorm(n = K, mean = 0.5, sd = tau[t]))
+        
+        var_fr <- 1/(n_t - 3) + 1/(n_c -3) #variances of observed difference in correlations q for each K
+        fr <- rnorm(n = K, mean = rho, sd = sqrt(var_fr)) #draw observed difference in correlations (fisher's z) for each k
+        
+        fit <- rma(yi = fr, vi = var_fr, method = "REML") #meta-analysis of difference in fisher's z, each study weighted by its N
+        
+        data.frame(I2 = fit$I2, Qp = fit$QEp, ci.lb = confint(fit)$random[3, 2], 
+                   tau = tau[t], tau_index = t)
+        
+      }, otherwise = NULL)) #If rma does not converge, drop that iteration ('possibly' function)
+    }
+    
   }else if(effect$type == "d"){ #That is, for SMD and odds ratios
     
     n_c <- effect$ncontrol #observed control group sizes
@@ -148,7 +173,7 @@ set.seed(112)
 res <- vector("list", length(dat2)) #output of below loop
 
 system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
- res[[e]] <- simulate_I2(dat2[[e]], reps = 1e3, tau = tau_values, effect_size = "zero") #NB! 1e3 reps here is about 36 hours on my (fairly slow) machine
[…]

### 2019-11-05 code/collate_summary_data.r
corrected coding error for ML2 trolley 2 collation

@@ -482,7 +482,7 @@ ml2_or <- ml2_or %>%
            effect == "Affect & Risk" ~ "count moviestar (low, certain) _ count money (low, certain)", #I use the parentheses to clarify here because there is no clear treatment/control division
            effect == "Trolley Dilemma 1" ~ "count yes (side effect, greater good) _ count no (side effect, greater good)",
            effect == "Framing" ~ "count yes (cheap, costly) _ count no (cheap, costly)",
-           effect == "Trolley Dilemma  2" ~  "count yes (side effect, greater good) _ count no (side effect, greater good)"),
+           effect == "Trolley Dilemma 2" ~  "count yes (side effect, greater good) _ count no (side effect, greater good)"),
          country = recode(country, #Recode country names to official three letter acronyms for consistency
                           Hungary = "HUN", #
                           'United Arab Emirates' = "ARE", #

### 2019-11-05 code/collate_summary_data.r
corrected data extraction ML2 Tversky & Gati

@@ -353,11 +353,10 @@ ml2$online[ml2$source.Setting%in%c("Online (at home)")] <- "online" #from line 3
 # [11] "Moral Typecasting (Gray & Wegner, 2009)"        
 # [12] "Moral Cleansing (Zhong & Liljenquist, 2006)"    
 # [13] "Intentional Side-Effects (Knobe, 2003)"         
-# [14] "Direction & Similarity (Tversky & Gati, 1978)"  
-# [15] "Direction & SES (Huang et al., 2014)"           
-# [16] "Incidental Disfluency (Alter et al., 2007)"     
-# [17] "Tempting Fate (Risen & Gilovich, 2008)"         
-# [18] "Priming Warmth (Zaval et al., 2014)"   
+# [14] "Direction & SES (Huang et al., 2014)"           
+# [15] "Incidental Disfluency (Alter et al., 2007)"     
+# [16] "Tempting Fate (Risen & Gilovich, 2008)"         
+# [17] "Priming Warmth (Zaval et al., 2014)"   
 #**************
 
 
@@ -370,6 +369,7 @@ ml2_smd <- ml2_smd %>% #Drop remaining non-standard SMD effects
                                "Inbar.1a", #difference between correlations q
                                "vanLange.1", #correlation r
                                "Shafir.1", #strange effect 
+                               "Gati.2", #Within subjects difference between conditions (similarity scores)
                                "Schwarz.1a")) #difference between correlations q
 
 
@@ -669,22 +669,32 @@ ml2_q <- ml2_q %>%
          ntreatment, ncontrol, outcomes1_2, outcome_t1, outcome_c1, outcome_t2, outcome_c2, ml2_ncp_variance) #select only variables of interest
 
 #*****************************************
-#**[2.4] Actions are Choices (Savani et al., 2010)----
+#**[2.4] Other effects ----
 #*****************************************
 #Effects extracted in this section
-# [1] "Actions are Choices (Savani et al., 2010)" 
+# [1] "Choosing or Rejecting (Shafir, 1993)"         
+# [2] "Direction & Similarity (Tversky & Gati, 1978)"
+# [3] "Actions are Choices (Savani et al., 2010)" 
 #**************
 
-ml2_savani <- ml2 %>% filter(analysis.name == "Savani.3a")
+ml2_other <- ml2 %>% filter(analysis.name %in% c("Savani.3a", "Shafir.1", "Gati.2"))
+
[…]

### 2019-11-05 code/figures.rmd
Updated figure text to match
updated main rma function for ML2 + figure 3

@@
 
-fisher_fit <- function(x){
-    fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, data = x)
+OR_fit <- function(x){
+    fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
     hetero <- confint(fit)$random[c(1, 3), ] 
@@
 MD_standardized <- dat %>% 
-  filter(effect_type == "Raw mean difference" & !outcomes1_2 == "mean _ SE") %>% #No method in metafor to compute SMD when standard deviations not given, so skip this study 
+  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE study since no method in metafor to convert into standardized mean differences
   split(.$effect) %>% 
@@
 
-fisher <- dat %>% 
-  filter(effect_type == "r") %>% 
+#effects that were originally transformed from OR to SMD by ML1 which we refit as OR
+OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', 
+           'Norm of reciprocity', 'Low vs. high category scales')
+
+ml2_or <- c("Affect & Risk", "Trolley Dilemma 1", "Framing", "Trolley Dilemma 2") #odds ratio effects in ML2 we will fit as OR
+
+odds_ratios <- dat %>% 
+  filter(effect %in% c(OR2d, ml2_or)) %>% 
   split(.$effect) %>% 
-  map_dfr(fisher_fit, .id = "effect")
-
-#effects that were transformed from OR to SMD by ML1 which we will drop
-OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
-           'Norm of reciprocity', 'Low vs. high category scales') #refit as OR
+  map_dfr(OR_fit, .id = "effect")
 
@@
   left_join(tau2_per_type) %>% #Add the meta-analytic results
-  filter(!effect %in% c(OR2d, MD_standardized$effect, fisher$effect)) %>% #drop old SMD converted OR, unstandardized MD and raw correlations
+  filter(!effect %in% c(odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
   bind_rows(MD_standardized) %>% #add MD after standardization
-  bind_rows(fisher) %>% #add correlations as fisher's z
+  bind_rows(odds_ratios) %>% #add odds ratios
   mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
-         effect_type = ifelse(effect %in% fisher$effect, "Fisher's z", effect_type),
+         effect_type = ifelse(effect %in% odds_ratios$effect, "Odds Ratio", effect_type),
          eff_size = abs(eff_size)) %>% #need the absolute values for plotting
-  filter(effect_type %in% c("Standardized Mean Difference", "Fisher's z"))
+  filter(effect_type %in% c("Standardized Mean Difference", "Odds Ratio"))
 
@@
 Figure 3.
-The correlation between effect size and A) tau2, b) I2 and c) H2 respectively  22 effects that were measured as mean or standardized mean differences and 6 effects measured as correlations from ten pre-registered multi-lab replication projects.
-Effects reported as mean differences were standardized and correlations were transformed into Fisher’s z.
-Shaded bands represent 95% confidence intervals
+The correlation between effect size and A) tau2, B) I2 and C) H2 respectively  40 effects that were measured as mean or standardized mean differences and 8 effects measured as odds ratios from 13 pre-registered multi-lab replication projects.
+Effects reported as mean differences were standardized.
+Square brackets contain 95% bootstrapped percentile confidence intervals.
 

### 2019-11-05 code/tables.rmd
updated main rma function for ML2 + figure 3

@@
 papers <- c('Klein et al. (2014)', 
+            'Klein et al. (2018)',
 'Ebersole et al. (2016)',
@@
 Social Psychology, 45(3), 142-152.',
+# Add full APA ref for ML2
 # 'Ebersole, C.
@@
 ", #ML1
+                 "'Summary about ML2 effects': 17/28 effects were experiments with two independent groups.
+Two correlational effects.
+Two difference between correlations.
+4 odds ratio effects.
+One hierarchical regression effect.
+One strange effect.", #ML2
             "Several effects were experiments with two independent groups.
@@
 One effect was correlational: 'Conscientiousness and persistence' was measured by an unsolvable anagram task and self-report respectively.
-The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML2
+The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML3
                  "Verbal overshadowing 1; Independent two-group experiment.
@@
 9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
+                     "'ML2 sample information'", #ML2
                      "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3

### 2019-11-05 code/helper_functions_tables_figures.r

@@ -32,7 +32,14 @@ est_heterogen_smd_raw <- function(x){
       fit <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
     }
     
-  } else if(any(x[, "outcomes1_2"] == "mean _ SD")){  
+  } else if(any(x[, "rp"] == "ML2")){  
+    if(any(x[, "effect_type"] == "r")){
+      fit <- rma(yi = effect_size, vi = ml2_ncp_variance,  data = x)
+    }else{ #for ML2 cohen's q
+      fit <- rma(yi = effect_size, vi = outcome_t1,  data = x) 
+    }
+    
+  }else if(any(x[, "outcomes1_2"] == "mean _ SD")){  
     
     fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x) 
     

### 2019-11-06 code/collate_summary_data.r
corrected ML2 in_lab variable to be {0,1} instead of a string

@@ -333,8 +333,8 @@ ml1 <- rbind(teffects, chieffects, math_art, math_cor)
 ml2 <- read.csv("../data/source/Ml2/Data_Figure_NOweird.csv", stringsAsFactors = FALSE)
 
 #Initial clean and format data
-ml2$online[ml2$source.Setting%in%c("In a classroom","In a lab")] <- "lab" #from line 35 in ML2_meta_analyses_simple.R https://osf.io/4akjw/
-ml2$online[ml2$source.Setting%in%c("Online (at home)")] <- "online" #from line 36 in ML2_meta_analyses_simple.R https://osf.io/4akjw/
+ml2$online[ml2$source.Setting%in%c("In a classroom","In a lab")] <- 1 #adapted from line 35 in ML2_meta_analyses_simple.R https://osf.io/4akjw/
+ml2$online[ml2$source.Setting%in%c("Online (at home)")] <- 0 #adapted from line 36 in ML2_meta_analyses_simple.R https://osf.io/4akjw/
 #******************************************
 
 #**[2.1] t-test effects----

### 2019-11-06 code/tables.rmd
Updated Table 2 (descriptives) with ML2/RRR9/RRR10 info

--- 2019-07-19 code/tables.rmd
@@
 'Bouwmeester et al. (2017)',
-"O'Donnell et al. (2017)")
+"O'Donnell et al. (2017)",
+"McCarthy et al. (2018)",
+"Verschuere et al. (2018)")
 
@@
 Social Psychology, 45(3), 142-152.',
+# Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams, R.
+B., Alper, S., … Nosek, B.
+A.
+(2018).
+Many Labs 2: Investigating Variation in Replicability Across Samples and Settings.
+Advances in Methods and Practices in Psychological Science, 1(4), 443–490.
+https://doi.org/10.1177/2515245918810225
 # 'Ebersole, C.
@@
 Perspectives on Psychological Science."
+#McCarthy, R.
+J., Skowronski, J.
+J., Verschuere, B., Meijer, E.
+H., Jim, A., Hoogesteyn, K., ...
+& Barbosa, F.
+(2018).
+Registered replication report on Srull and Wyer (1979).
+Advances in Methods and Practices in Psychological Science, 1(3), 321-336.
+#Verschuere, B., Meijer, E.
+H., Jim, A., Hoogesteyn, K., Orthey, R., McCarthy, R.
+J., ...
+& Barbosa, F.
+(2018).
+Registered replication report on Mazar, Amir, and Ariely (2008).
+Advances in Methods and Practices in Psychological Science, 1(3), 299-317.
 
@@
 ", #ML1
+                 "Most effects were experiments with two independent groups.
+Often participants were primed in some way (Structure & Goal Pursuit, Priming Consumerism, Incidental Anchors, Position & Power, Moral Cleansing, Priming Warmth) or asked to imagine slightly different situations (SMS & Well-Being, Less is Better, Moral Typecasting, Intentional Side-Effects, Tempting Fate, Affect & Risk, Trolley Dilemma 1, Framing, Trolley Dilemma 2, Disgust & Homophobia, Choosing or Rejecting).
+Some groups saw slightly different statements (Correspondence Bias, Intuitive Reasoning), were asked to perform slightly different tasks (Direction & SES, Actions are Choices), or had to read a text with a clear vs.
+unclear font (Incidental Disfluency).
+Two correlational effects measured the correlations of Moral Foundations with political leaning, and Social Value Orientation with family size.
+Two effects examined order effects (Assimilation & Contrasts, Direction & Similarity).
+Finally, in False Consensus 1 and 2, participants made a binary choice and estimated how many people had made the same choice.", #ML2
             "Several effects were experiments with two independent groups.
@@
             "Intuitive cooperation; Independent two-group experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
-                 "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.") #RRR8
+                 "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.", #RRR8
+            "Hostility priming; Independent two-group experiment. Participants descrambled sentences, either 20% or 80% were hostile, then rated ambiguos behavior.", #RRR9
+            "Moral reminder; Independent two-group experiment. Participants either recalled the Ten Commandments or books they'd read. Outcome was degree of cheating when reporting results. ") #RRR10
 
@@
   summarize(US = sum(country == "USA"),
-            online = sum(in_lab == 0)) %>% 
+            online = sum(in_lab == 0, na.rm = TRUE)) %>% 
   group_by(rp) %>% 
@@
 9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
+                     "79/125 samples were collected in person (typically in labs), remainder online. Mean age in two rounds of data collection were 22.37 and 23.34 years.", #ML2
                      "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
@@
                'All samples consisted of in-lab undergraduate students aged 18-34.', #RRR7
-                     "All samples consisted of in-lab undergraduate students aged 18-25") #RRR8
+                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR8
+               "All samples consisted of in-lab students aged 18-25",
+               "All samples consisted of in-lab students aged 18-25")
 
@@
   select(RP = rp, Paper, Countries,'K (US)', everything(), -k) #change order of columns
+
+summary.table <- summary.table[c(1:4, 6:13, 5),] #reorder so RRR10 is last instead of after RRR1
 

### 2019-11-11 code/collate_summary_data.r
corrected osf page link for RRR9/10

@@ -1526,7 +1526,7 @@ rrr8 <- rrr8 %>%
 #******************************************
 #[10] RRR9 ----
 #******************************************
-##summary data from Registered Replication Report 10 https://osf.io/k27hm/
+##summary data from Registered Replication Report 9 https://osf.io/vxz7q/
 ##Direct link to .zip file with raw data: https://osf.io/qegfd/
 ##To extract summary data we ran the RRR9 code in the file above on their raw data
 
@@ -1582,7 +1582,7 @@ rrr9 <- rrr9 %>%
 #******************************************
 #[11] RRR10 ----
 #******************************************
-##summary data from Registered Replication Report 9 https://osf.io/k27hm/
+##summary data from Registered Replication Report 10 https://osf.io/vxz7q/
 ##Direct link to .zip file with data: https://osf.io/fwnc2/
 ##Summary data located at Meta-Analysis_2018-07-09.zip\Meta-Analysis\Results_perMAA\Main\Tables\10 commandments effect_table_data.csv
 #Additional comments:  standard error of difference, no SD per group

### 2019-11-11 code/figures.rmd
updated tables and figures with ML2 & RRR9/10

@@
          effect_type = recode(effect_type, "d" = 'SMD',
-                              "r" = "Fisher's z"))
+                              "r" = "Fisher's z",
+                              "q" = "Cohen's q"))
 
@@
   scale_color_brewer(name = "Effect type", palette = "Dark2", 
-                     breaks = c("Fisher's z", "MD", "SMD")) +
+                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) +
   theme(legend.position = c(0.8, 0.4),
@@
 Figure 2.
-Simulated $I^2$  densities across 37 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed $I^2$ estimates for the 37 effects.
-Each simulated density consists of approximately 370,000 estimates.
+Simulated $I^2$  densities across 67 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed $I^2$ estimates for the 67 effects.
+Each simulated density consists of approximately 670,000 estimates.
 
@@
 combo <- cowplot::plot_grid(tau2_facet, I2_facet, H2_facet, labels = "AUTO")
-#ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
+# ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
 combo

### 2019-11-11 code/tables.rmd
updated tables and figures with ML2 & RRR9/10

@@
 
-##Table 1
-###Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
+## Table 1
+### Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
 ```{r effect-size-heterogeneity-table, cache = TRUE}
@@
 
-##Table 2
-###Pre-registered multi-lab replication projects
+## Table 2
+### Pre-registered multi-lab replication projects
 ```{r data-summary-table}
@@
                                longtable = TRUE) %>% 
-  kable_styling(c("hold_position", "repeat_header"), font_size = 7) %>%
+  kable_styling(latex_options = c("hold_position", "repeat_header"), font_size = 7) %>%
   column_spec(2, width = "7em") %>% #specify width of paper column 
@@
 
-##Table 3
-###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
+## Table 3
+### Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
 ```{r prep-heterogeneity-table, cache = TRUE}
@@
 
+het$effect <- gsub("&", "\\\\&", het$effect)
 ```
@@
 
-het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+het %>% knitr::kable(align = "c", longtable = TRUE, booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
   add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>% 
   add_header_above(c(" " = 9, "Type I Error Rate & Statistical Power" = 4)) %>% 
-  kable_styling("scale_down", font_size = 7) %>% #comment out if outputting html file
+  kable_styling(latex_options = c("scale_down", "repeat_header"), font_size = 7) %>% #comment out if outputting html file
   column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped 
@@
 Code to reproduce table: osf.io/kf6pt/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06" ,
-           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences")) %>% 
-  landscape()
-
+           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences")) %>% landscape()
 ```

### 2019-11-12 code/tables.rmd
Updated Table 1 for clarity

@@
 rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
+ma <- c("I: $\\mu = 0$", "II: $\\mu = .3$", "III: $\\mu = .5$")
 
 rooted_relabilities <- sweep(rooted_relabilities, 2, rho, "*")
-rooted_relabilities <- data.frame(rel, rooted_relabilities)
+devs <- apply(rooted_relabilities, 2, sd)
+table1 <- data.frame(ma, t(rooted_relabilities), devs)
 
-rooted_relabilities %>% knitr::kable(booktabs = T, col.names = c("", "$\\rho_{xy}$ = 0", "$\\rho_{xy}$ = .3", "$\\rho_{xy}$ = .5"), escape = FALSE, digits = 2) %>% 
+table1 %>% knitr::kable(booktabs = T, col.names = c("Meta-Analysis", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)"), escape = FALSE, digits = 2) %>%
   kable_styling(position = "left") %>% 
-  row_spec(3, hline_after = T)
+  add_header_above(c(" " = 1, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>% 
+  add_header_above(c(" " = 1, "Observed effect sizes" = 3))
 
+#alternative inversed table 1
+# table1b <- t(table1)[2:5,]
+# studies <- c("Study 1: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "Study 2: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "Study 3: $\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)")
+# table1b <- cbind(studies, table1b)
+# rownames(table1b) <- NULL
+# 
+# table1b %>% knitr::kable(booktabs = T, col.names = c("Study and Measurement Error", "I: $\\mu = 0$", "II: $\\mu = .3$", "III: $\\mu = .5$"), escape = FALSE, digits = 2) %>% 
+#   add_header_above(c(" " = 1, "Meta-Analysis" = 3)) %>% 
+#   add_header_above(c(" " = 1, "Observed effect sizes" = 3)) %>% 
+#   row_spec(3, hline_after = TRUE)
 ```
-*Note:* Values in cells are observed effect sizes arising from the true effect size $\rho_{xy}$ and measurement reliabilites $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ when sample size is infinite.
+*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\rho_{xy}$  when sample size is infinite.
+SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite sample sizes.
 Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06

### 2019-11-26 code/figures.rmd
Added Risk differences to Fig 3 and plot clarifications

@@
 
-```{r Plot_tau_against_I2, fig.asp = 0.618, cache = TRUE}
+```{r Plot_tau_against_I2, fig.asp = 0.618}
 dat3 <- readRDS("../data/tau_simulation_results.RDS")
@@
 
-```{r Density-plot-prep, cache = TRUE}
+```{r Density-plot-prep}
 #1) I2 plot----
@@
 
-##Figure 3, correlations per effect type
+## Figure 3, correlations per effect type
 
-```{r corr_per_effect_type-prep, cache = TRUE}
+```{r corr_per_effect_type-prep}
 #Each set of input datapoints is meta-analyzed as per the original replication project
@@
 
-OR_fit <- function(x){
+log_or_fit <- function(x){ #NB! if a cell is 0, 1/2 will be added to it
     fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
@@
 
-ml2_or <- c("Affect & Risk", "Trolley Dilemma 1", "Framing", "Trolley Dilemma 2") #odds ratio effects in ML2 we will fit as OR
+#odds ratio effects in ML2 we will fit as OR
+ml2_or <- c("Affect & Risk", "Trolley Dilemma 1", "Framing", "Trolley Dilemma 2")
 
-odds_ratios <- dat %>% 
-  filter(effect %in% c(OR2d, ml2_or)) %>% 
+#Risk differences from RRR1 that can be fit as odds ratios as well
+rd_effects <- c("Verbal overshadowing 1", "Verbal overshadowing 2")
+
+log_odds_ratios <- dat %>% 
+  filter(effect %in% c(OR2d, ml2_or, rd_effects)) %>% 
   split(.$effect) %>% 
-  map_dfr(OR_fit, .id = "effect")
+  map_dfr(log_or_fit, .id = "effect")
+
+#One with NA values: ML2; Trolley dilemma 1; Site = 'cas'
 
@@
   left_join(tau2_per_type) %>% #Add the meta-analytic results
-  filter(!effect %in% c(odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
+  filter(!effect %in% c(log_odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
   bind_rows(MD_standardized) %>% #add MD after standardization
-  bind_rows(odds_ratios) %>% #add odds ratios
+  bind_rows(log_odds_ratios) %>% #add odds ratios
   mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
-         effect_type = ifelse(effect %in% odds_ratios$effect, "Odds Ratio", effect_type),
+         effect_type = ifelse(effect %in% log_odds_ratios$effect, "Log Odds Ratio", effect_type),
          eff_size = abs(eff_size)) %>% #need the absolute values for plotting
-  filter(effect_type %in% c("Standardized Mean Difference", "Odds Ratio"))
+  filter(effect_type %in% c("Standardized Mean Difference", "Log Odds Ratio"))
 
@@
   geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
-  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
-  scale_x_continuous(name = "Effect size") +
+  scale_y_continuous(name = expression(paste("Between Studies Variance ", italic(tau)^2))) +
+  scale_x_continuous(name = "Absolute Effect Size") +
   theme_classic() +
@@
   scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
-  scale_x_continuous(name = "Effect size") +
+  scale_x_continuous(name = "Absolute Effect Size") +
   coord_cartesian(ylim = c(0, 100)) +
@@
   scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
-  scale_x_continuous(name = "Effect size") +
+  scale_x_continuous(name = "Absolute Effect Size") +
   theme_classic() +
@@
 Figure 3.
-The correlation between effect size and A) tau2, B) I2 and C) H2 respectively 40 effects that were measured as mean or standardized mean differences and 8 effects measured as odds ratios from 13 pre-registered multi-lab replication projects.
-Effects reported as mean differences were standardized.
+The correlation between absolute effect size and A) tau2, B) I2 and C) H2 respectively for 40 effects that were measured as mean or standardized mean differences and 8 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects.
+Effects reported as mean differences were standardized and risk differences computed as log odds ratios.
 Square brackets contain 95% bootstrapped percentile confidence intervals.

### 2019-11-26 code/collate_summary_data.r
Dropped one study from ML2 trolley 1 with NA on one value, does not affect results since it was automatically dropped by metafor before

@@ -521,6 +521,8 @@ ml2_or <- ml2_or %>%
   select(rp, effect, Site, country, in_lab, Ntotal, B_or_W, design, or_stat_test, effect_type, effect_size, 
          ntreatment, ncontrol, outcomes1_2, outcome_t1, outcome_c1, outcome_t2, outcome_c2, ml2_ncp_variance) #select only variables of interest
 
+#One lab ("cas") does not have any stat.cond4 values for the trolley dilemma, so we drop this study
+ml2_or <- ml2_or %>% filter(!(effect == "Trolley Dilemma 1" & Site == "cas"))
 
 #*****************************************
 #**[2.3] Correlations----

### 2019-11-27 code/tables.rmd
Table 2 error due to sorting RRR10 after RRR1 (corrected)

@@
             online = max(online)) %>% 
-  ungroup() %>% select(US, online)
+  ungroup() %>% select(rp, US, online)
 
@@
                            else{sum(Ntotal) / Effects}) %>% #average across effects
-  mutate(Paper = papers,
-         'Sample and Settings' = sample_settings,
-         'Description of Effects' = description,
-         'K (US)' = paste0(k, " (", US_online$US, ")")) %>% 
-  select(RP = rp, Paper, Countries,'K (US)', everything(), -k) #change order of columns
+  mutate('K (US)' = paste0(k, " (", US_online$US, ")"))
 
 summary.table <- summary.table[c(1:4, 6:13, 5),] #reorder so RRR10 is last instead of after RRR1
+
+summary.table <- summary.table %>% 
+  mutate(Paper = papers, #In these vectors RRR1-10 are sorted in descending order since they were manually created
+         'Sample and Settings' = sample_settings,
+         'Description of Effects' = description) %>% 
+  select(RP = rp, Paper, Countries,'K (US)', everything(), -k) #change order of columns
 
@@
 ## Table 3
-### Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
+### Heterogeneity across primary effects and statistical power of thirteen multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
 ```{r prep-heterogeneity-table, cache = TRUE}

### 2019-11-27 code/figures.rmd
Clarified y-axis of Figure 1

@@
 
-##Figure 1
+## Figure 1
 
@@
                      minor_breaks = NULL) +
-  scale_y_continuous(name = expression(paste(I^2," index", sep = "")),
+  scale_y_continuous(name = expression(paste("Average ", italic(I)^2," index", sep = "")),
                      minor_breaks = NULL) +
@@
 
-# ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)
+ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)
 
@@
 
-Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 37 effects. Tau is not directly comparable across effect size measures.
+Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 67 effects. Tau is not directly comparable across effect size measures.
 
-##Figure 2
+## Figure 2
 
@@
 Figure 3.
-The correlation between absolute effect size and A) tau2, B) I2 and C) H2 respectively for 40 effects that were measured as mean or standardized mean differences and 8 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects.
+The correlation between absolute effect size and A) tau2, B) I2 and C) H2 respectively for 40 effects that were measured as mean or standardized mean differences and 10 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects.
 Effects reported as mean differences were standardized and risk differences computed as log odds ratios.

### 2019-11-29 code/tables.rmd
Clarified y-axis of Figure 1
Checked and updated headers and footnotes of all tables

@@
 ## Table 1
-### Effect size $\rho_{xy}$ and its heterogeneity as a function of true effect size and measurement reliability.  
+### Variation in observed effect sizes as a function of true effect size and measurement reliability.  
 ```{r effect-size-heterogeneity-table, cache = TRUE}
@@
 rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
-ma <- c("I: $\\mu = 0$", "II: $\\mu = .3$", "III: $\\mu = .5$")
+ma <- c("I: $\\mu = 0.0$", "II: $\\mu = 0.3$", "III: $\\mu = 0.5$")
 
@@
   add_header_above(c(" " = 1, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>% 
-  add_header_above(c(" " = 1, "Observed effect sizes" = 3))
+  add_header_above(c(" " = 1, "Observed Effect Sizes" = 3))
 
@@
 ```
-*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\rho_{xy}$  when sample size is infinite.
-SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite sample sizes.
+*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\mu$ when within study sample size is infinite.
+SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite within study sample sizes.
 Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06
@@
                  "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.", #RRR8
-            "Hostility priming; Independent two-group experiment. Participants descrambled sentences, either 20% or 80% were hostile, then rated ambiguos behavior.", #RRR9
+            "Hostility priming; Independent two-group experiment. Participants descrambled sentences, either 20% or 80% were hostile, then rated ambiguous behavior.", #RRR9
             "Moral reminder; Independent two-group experiment. Participants either recalled the Ten Commandments or books they'd read. Outcome was degree of cheating when reporting results. ") #RRR10
@@
 high category scales'.
+All ML2 meta-analyses with effect type 'r' except 'Moral foundations' and 'Social Value Orientation' were transformed to correlations from a variety of effect sizes.
 RP = Replication Project, K = no.

### 2019-11-29 code/figures.rmd
checked and updated figures and figure notes

@@
 
-ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)
+# ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)
 
@@
 Figure 2.
-Simulated $I^2$  densities across 67 effects for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and a histogram of the observed $I^2$ estimates for the 67 effects.
+Simulated $I^2$  densities across 67 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 67 meta-analyses.
 Each simulated density consists of approximately 670,000 estimates.
 
-## Figure 3, correlations per effect type
+## Figure 3: correlations per effect type
 
@@
  fit_H2 <- summary(lm(H2 ~ eff_size, data = df))
- b <- c(fit_tau2$coefficients[2, 1], fit_I2$coefficients[2, 1], fit_H2$coefficients[2, 1])
  r <- c(sqrt(fit_tau2$r.squared), sqrt(fit_I2$r.squared), sqrt(fit_H2$r.squared))
- data.frame(b = format(round(b, digits = 2), nsmall = 2), 
-            r = format(round(r, digits = 2), nsmall = 2),
+ data.frame(r = format(round(r, digits = 2), nsmall = 2),
             index = c("tau2", "I2", "H2")) 
@@
   map_dfr(fitter, .id = "effect_type") %>%
-  mutate(r = ifelse(r == 0.15, -0.15, r), #should be negative, but I took squared root of R^2 to get correlations so needs correction
-         lab = paste0("b = ", b, ", r = ", r, " ", fig3_ci$ci)) #put output into one variable for improved plotting
+  mutate(lab = paste0("r = ", r, " ", fig3_ci$ci)) #put output into one variable for improved plotting
 
@@
 ```{r corr_per_effect_type-plot, cache = FALSE}
-#tau2plot----
-tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
+#tau plot----
+tau_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = sqrt(tau2))) + #NB! Taking sqrt of tau2 here
   geom_point(alpha = 0.5) +
@@
   geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
-  scale_y_continuous(name = expression(paste("Between Studies Variance ", italic(tau)^2))) +
+  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", italic(tau)))) +
   scale_x_continuous(name = "Absolute Effect Size") +
@@
 #combined----
-combo <- cowplot::plot_grid(tau2_facet, I2_facet, H2_facet, labels = "AUTO")
+combo <- cowplot::plot_grid(tau_facet, I2_facet, H2_facet, labels = "AUTO")
 # ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
@@
 Figure 3.
-The correlation between absolute effect size and A) tau2, B) I2 and C) H2 respectively for 40 effects that were measured as mean or standardized mean differences and 10 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects.
-Effects reported as mean differences were standardized and risk differences computed as log odds ratios.
+The Pearson correlation between absolute effect size and A) $\hat{\tau}$, B) $I^2$ and C) $H^2$ respectively for 40 effects that were measured as mean or standardized mean differences and 10 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects.
+Effects reported as mean differences were standardized and odds ratios/risk differences computed as log odds ratios.
 Square brackets contain 95% bootstrapped percentile confidence intervals.
+Code to reproduce figure: osf.io/zuwpg/?view_only=e6639d8d4f924739a7310782fbbb4e06
 

### 2019-12-03 code/04_tables.rmd
updated script names for clarity + minor updates to correlations code

--- 2019-11-29 code/tables.rmd
@@
 
-source("helper_functions_tables_figures.r") #Load functions to prep data for figures
+source("03_helper_functions_tables_figures.r") #Load functions to prep data for figures
 ```
@@
 ### Heterogeneity across primary effects and statistical power of thirteen multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
-```{r prep-heterogeneity-table, cache = TRUE}
+```{r prep-heterogeneity-table, cache = TRUE, results = 'hide'}
 #library(metafor)
@@
   ungroup()
+
+#****************
+#Results for "Heterogeneity Estimates and Confidence Intervals" section in paper
+
+sum(het$s_I2 >= 62.5) #what number of I2 estimates would be rounded to "large" (75% I2) heterogeneity
+sum(het$s_I2 >= 37.5 & het$s_I2 < 62.5) #what number of I2 estimates would be rounded to "medium" (50% I2) heterogeneity
+sum(het$s_I2 >= 12.5 & het$s_I2 < 37.5) #what number of I2 estimates would be rounded to "small" (25% I2) heterogeneity
+sum(het$s_I2 < 12.5) #what number of I2 estimates would be rounded to zero (0% I2) heterogeneity
+
+quantile(het$tau[het$effect_type == "r"]) #quantiles of tau for correlation tau scale
+quantile(het$tau[het$effect_type == "SMD"]) ##quantiles of tau for SMD tau scale
+
+sum(het$s_ci.lb == 0) #number of meta-analysis with lower I2 CI containing zero
+sum(het$s_ci.lb == 0 & het$tau_ci.lb == 0) #All above also have lower tau CI containing zero
+
+sum(het$s_I2 == 0) #number of meta-analyses with I2 estimates of zero
+sum(het$s_I2 == 0 & het$tau == 0) #all these also have tau estimates of zero
+
+#****************
+
+#continue prepping table 3
 

### 2019-12-03 code/05_figures-and-correlations.rmd
updated script names for clarity + minor updates to correlations code

--- 2019-11-29 code/figures.rmd
@@
 #1. Standardized mean differences----
-SMDs <- tau2_per_type %>% filter(effect_type == "Standardized Mean Difference")
+SMDs <- tau2_per_type %>% filter(effect_type == "Standardized Mean Difference") %>% 
+  mutate(tau = sqrt(tau2))
 
-cor.test(SMDs$tau2, SMDs$eff_size) #pearson tau2
+cor.test(SMDs$tau, SMDs$eff_size) #pearson tau2
 cor.test(SMDs$s_I2, SMDs$eff_size) #pearson I2
@@
 
-cor.test(SMDs$tau2, SMDs$eff_size, method = "spearman") #spearman
+cor.test(SMDs$tau, SMDs$eff_size, method = "spearman") #spearman
 cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
@@
 
+cor.test(dropped_anchoring$tau, dropped_anchoring$eff_size) #pearson
 cor.test(dropped_anchoring$s_I2, dropped_anchoring$eff_size) #pearson
+cor.test(dropped_anchoring$H2, dropped_anchoring$eff_size) #pearson
 
@@
 
-bootfit <- boot(data=SMDs, statistic=pear, R=1000, formula= ~ eff_size + s_I2)
-I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+#bootfit <- boot(data=SMDs, statistic=pear, R=1000, formula= ~ eff_size + s_I2) #see Fig 3
+#I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
 
 #Excluding anchoring effects
+set.seed(234)
 bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + s_I2)
@@
      d <- data[indices,]
-     fit <- cor.test(formula = ~ tau2 + eff_size, data=d)
+     fit <- cor.test(formula = ~ tau + eff_size, data=d)
      return(fit$estimate)
@@
 
-bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + tau2)
-
-tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
+# bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + tau2) #see Fig 3
+# tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
 
@@
 
-bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + tau2)
-
-tau2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+set.seed(423)
+bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + tau)
+tau_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
 
@@
 
+set.seed(342)
 bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + H2)
-
 H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
@@
 
+set.seed(241)
 options(warn=-1)
@@
 
-#Second for tau2
+#Second for tau
 spear <- function(formula, data, indices){ #spearman
      d <- data[indices,]
-     fit <- cor.test(formula = ~ tau2 + eff_size, data=d, method = "spearman")
+     fit <- cor.test(formula = ~ tau + eff_size, data=d, method = "spearman")
      return(fit$estimate)
@@
 
+set.seed(5233)
+tau2_per_type <- tau2_per_type %>% mutate(tau = sqrt(tau2))
 options(warn=-1)
-bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + tau2)
+bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + tau)
 options(warn=0)
 
-tau2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
-
-#2. Fisher's z----
-fish <- tau2_per_type %>% filter(effect_type == "Fisher's z" )
-cor.test(fish$tau2, fish$eff_size) #pearson tau2
-cor.test(fish$s_I2, fish$eff_size) #pearson I2
-cor.test(fish$H2, fish$eff_size)
+tau_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
 

### 2019-12-03 code/06_Supplement-tables-figures.Rmd
updated script names for clarity + minor updates to correlations code

--- 2019-07-19 code/Supplement-figures-tables.Rmd
@@
 date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: pdf_document
+output: html_document
 ---
@@
 
-source("helper_functions_tables_figures.r") #Load functions to prep data for figures
+source("03_helper_functions_tables_figures.r") #Load functions to prep data for figures
 ```
 
-##Supplement A
+## Supplement A
 
@@
 res2 <- dat %>%
+  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales')) %>%
   split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
@@
 
-d <- het %>% filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "SMD.") %>% 
+d <- het %>% filter(effect_type == "SMD.") %>%
   mutate(sigma2 = tau2/(I2/100) - tau2) #add 'typical within study variance' per project
@@
 ```{r c-plot-1, cache = FALSE}
-c_plot_1 <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("Biserial r (transformed SMD)")
-
-```
-
-```{r untruncated-biserial, cache = TRUE}
-res3 <- dat %>%
-  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & outcomes1_2 == "mean _ SD") %>% 
-  split(.$effect) %>% 
-  map(~transform_SD(.$outcome_t1, .$outcome_c1, .$outcome_t2, .$outcome_c2, .$ntreatment, .$ncontrol)) %>% 
-  map(~untruncated_d_to_r(.$d, .$n1, .$n2)) %>% 
-  map_dfr(summarizer, .id = "effect")
-```
-
-```{r c-plot, cache = FALSE}
-c_plot <- c_plot_1 + geom_point(data = res3, shape = 4, aes(x = I2, y = sqrt(tau2))) +
-  scale_x_continuous(name = expression(paste(italic(I)^2, " Index (biserial)"))) +
-  scale_y_continuous(name = "Tau (biserial)")
+c_plot <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("Point Biserial r (transformed SMD)")
 
@@
 b <- select(a, effect, tau2) %>%
-  left_join(select(d, effect, tau2), by = "effect") %>% #add truncated transformation tau2
-  left_join(select(res3, effect, tau2), by = "effect") #add untruncated transformation tau2
+  left_join(select(d, effect, tau2), by = "effect") #add truncated transformation tau2
 ```
@@
 ```{r b-plot-1}
-b_plot_1 <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) + 
-  geom_point()
+b_plot <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
+  geom_point() +
+  ggtitle("SMD vs. Point biserial") +
+  scale_x_continuous(name = "Tau (SMD)") +
+  scale_y_continuous(name = "Tau (Point biserial)")
 
-```
-
-```{r b-plot}
-b_plot <- b_plot_1 + geom_point(data = b, shape = 4, aes(x = sqrt(tau2.x), y = sqrt(tau2))) +
-  ggtitle("SMD vs. biserial") +
-  scale_x_continuous(name = "Tau (SMD)") +
-  scale_y_continuous(name = "Tau (biserial)")
 ```
@@
 
-##Supplement B
+## Supplement B
 
 ```{r Supplement-B-table}
+#Load simulation results (power/type 1 error for all effects)
+dens <- readRDS("../data/power_simulation_results.RDS")
+names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
 
@@
 ##Medium effect size results
-dens2 <- readRDS("../data/appendixA_power_simulation_results.RDS") 
+dens2 <- readRDS("../data/supplementB_power_simulation_results.RDS") 
 names(dens2) <-  sort(unique(dat$effect))
@@
 Estimated type I error and power for zero/small/medium/large heterogeneity when simulated with a true effect size of zero vs.
-medium are shown for each effect in Table A1.
+medium are shown for each effect in Table SB1.
 In both cases type I error is approximately nominal, as compared to the expected 5% error rate.

### 2019-12-03 code/03_helper_functions_tables_figures.r

@@ -68,7 +68,7 @@ est_heterogen_smd_raw <- function(x){
 
 
 #******************************************
-#Functions to transform all effect sizes to the same unit of measurement and meta-analyze----
+#Functions (for Supplement A) to transform all effect sizes to the same unit of measurement and meta-analyze----
 #******************************************
 
 #Formulas found in: 
@@ -101,15 +101,11 @@ transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean diff
 transform_d_to_r <- function(d, n1, n2){ 
   m <- n1 + n2 - 2 #Jacobs and Viechtbauer (2017), p.164
   h <- m/n1 + m/n2 #p. 164
-  rpb <- d / sqrt(d^2 + h) #point-biserial correlation, Jacobs and Viechtbauer (2017), equation 5
-  p <- n1 / (n1 + n2)
-  q <- n2 / (n1 + n2)
-  zp <- qnorm(p)
-  fzp <- dnorm(zp)
-  rb <- sqrt(p*q) / fzp * rpb #biserial correlation, Jacobs and Viechtbauer (2017), equation 8
-  rb_trunc <- ifelse(rb > 1, 1, rb) #truncate for > 1 when computing variance to avoid neg. variance. p. 166-167
-  var_rb <- 1/(n1 + n2 -1) * (sqrt(p*q) / fzp - rb_trunc^2)^2 #variance biserial r, approximate formula, eq. 13 
-  data.frame(r = rb, vi = var_rb, n = n1 + n2) #I use the approximate formula (eq 13) above to decrease the risk of coding error
+  r <- d / sqrt(d^2 + h) #point-biserial correlation, Jacobs and Viechtbauer (2017), equation 5 
+  var_r <- (1-r^2)^2 / (n1 + n2 -1) #Cooper and Hedges (2009), equation 12.27
+  # rz <- 0.5*ln((1+r)/(1-r)) #Fishers z transformation Cooper and Hedges (2009), equation 12.28
+  # var_rz <- 1 / (n1+n2 -3) #Fisher z variance, Cooper and Hedges (2009), equation 12.29
+  data.frame(r = r, vi = var_r, n = n1 + n2) 
 }
 
 #Note that above function gives the same result as
@@ -165,24 +161,6 @@ summarizer <- function(x){#Z-transformation not recommended by Jacobs and Viecht
[…]

### 2019-12-04 code/05_figures-and-correlations.rmd
Correction to Figure 3 and added Supplement C

@@
 ```{r corr_per_effect_type-prep}
-#Each set of input datapoints is meta-analyzed as per the original replication project
-#Then correlated with tau2 per effect type
+
 #Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
-tau2_per_type <- dat %>% 
+tau2_per_type <- dat %>% #First compute meta-analytic results for all effects (will save: SMDs results)
   split(.$effect) %>%  
@@
 
-MD_fit <- function(x){
-    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
-    hetero <- confint(fit)$random[c(1, 3), ] 
-    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
-             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
-             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
-             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
-}
-
-log_or_fit <- function(x){ #NB! if a cell is 0, 1/2 will be added to it
-    fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
-    hetero <- confint(fit)$random[c(1, 3), ] 
-    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
-             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
-             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
-             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
-}
-
 #Raw mean differences to SMD
 MD_standardized <- dat %>% 
-  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE study since no method in metafor to convert into standardized mean differences
+  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
   split(.$effect) %>% 
-  map_dfr(MD_fit, .id = "effect")
+  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced
 
@@
   split(.$effect) %>% 
-  map_dfr(log_or_fit, .id = "effect")
+  map_dfr(log_or_fit, .id = "effect") #log_or_fit function is sourced
 
-#One with NA values: ML2; Trolley dilemma 1; Site = 'cas'
-
-tau2_per_type <- dat %>% #This is to add the effect_type names
+tau_per_type <- dat %>% #This is to add the effect_type names
   select(effect, effect_type) %>% 
@@
          effect_type = ifelse(effect %in% log_odds_ratios$effect, "Log Odds Ratio", effect_type),
-         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
+         eff_size = abs(eff_size), #need the absolute values for plotting
+         tau = sqrt(tau2)) %>% 
   filter(effect_type %in% c("Standardized Mean Difference", "Log Odds Ratio"))
 
-#labels for figure 3----
-fitter <- function(df){  #function to fit correlations for annotating facet plots
- fit_tau2 <- summary(lm(tau2 ~ eff_size, data = df))
- fit_I2 <- summary(lm(s_I2 ~ eff_size, data = df))
- fit_H2 <- summary(lm(H2 ~ eff_size, data = df))
- r <- c(sqrt(fit_tau2$r.squared), sqrt(fit_I2$r.squared), sqrt(fit_H2$r.squared))
- data.frame(r = format(round(r, digits = 2), nsmall = 2),
-            index = c("tau2", "I2", "H2")) 
-}
+#lables
+set.seed(435) #for the bootstrapping
+fig3_ci <- tau_per_type %>% 
+  split(.$effect_type) %>% 
+  map_dfr(bootfitter, .id = "effect_type") #bootfitter is a sourced function
 
-#functions to estimate bootstrapped confidence intervals to add to plot correlations
-pear_tau2 <- function(formula, data, indices){ #pearson
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ tau2 + eff_size, data=d)
-     return(fit$estimate)
-}
-pear_I2 <- function(formula, data, indices){ #pearson
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d)
-     return(fit$estimate)
-}
-pear_H2 <- function(formula, data, indices){ #pearson
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ H2 + eff_size, data=d)
-     return(fit$estimate)
-}
-
-bootfitter <- function(x){ #function that computes the bootstrapped confidence intervals using above functions to annotate plots
-  bootfit <- boot(data=x, statistic=pear_tau2, R=1000, formula= ~ eff_size + tau2)
-  tau2_ci_pears <- boot.ci(bootfit, type="perc")
-  bootfit <- boot(data=x, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2)
-  I2_ci_pears <- boot.ci(bootfit, type="perc")
-  bootfit <- boot(data=x, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
-  H2_ci_pears <- boot.ci(bootfit, type="perc")
-
-  ci.lb <- c(tau2_ci_pears$percent[4], I2_ci_pears$percent[4], H2_ci_pears$percent[4])
-  ci.ub <- c(tau2_ci_pears$percent[5], I2_ci_pears$percent[5], H2_ci_pears$percent[5])
-
-  ci <- paste0("[", format(round(ci.lb, 2), nsmall = 2), ", ",
-       format(round(ci.ub, 2), nsmall = 2), "]")#percentile 
-  data.frame(ci, index = c("tau2", "I2", "H2"))
-}
-
-set.seed(435) #for the bootstrapping
-fig3_ci <- tau2_per_type %>% 
+labels <- tau_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
   split(.$effect_type) %>% 
-  map_dfr(bootfitter, .id = "effect_type")
-
-labels <- tau2_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
-  split(.$effect_type) %>% 
-  map_dfr(fitter, .id = "effect_type") %>%
+  map_dfr(fitter, .id = "effect_type") %>% #fitter is a sourced function
   mutate(lab = paste0("r = ", r, " ", fig3_ci$ci)) #put output into one variable for improved plotting
@@
 #tau plot----
-tau_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = sqrt(tau2))) + #NB! Taking sqrt of tau2 here
+tau_facet <- ggplot(tau_per_type, aes(x = eff_size, y = tau)) + 
   geom_point(alpha = 0.5) +
   geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
-  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
   scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", italic(tau)))) +
@@
 #I2plot----
-I2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = s_I2)) + 
+I2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = s_I2)) + 
   geom_point(alpha = 0.5) +
   geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
-  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
   scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
@@
 #H2plot----
-H2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = H2)) + 
+H2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = H2)) + 
   geom_point(alpha = 0.5) +
   geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
-  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
   scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
@@
 
-#This section gives the correlations reported in the section 'Heterogeneity and effect sizes' in the main manuscript
+#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript
 
 #1. Standardized mean differences----
-SMDs <- tau2_per_type %>% filter(effect_type == "Standardized Mean Difference") %>% 
-  mutate(tau = sqrt(tau2))
+SMDs <- tau_per_type %>% filter(effect_type == "Standardized Mean Difference")
 
@@
 cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman
+
+##When effect size == 0, what is average heterogeneity?
+mean(SMDs$tau[SMDs$eff_size < 0.05]) #for tau = 0.016
+mean(SMDs$s_I2[SMDs$eff_size < 0.05]) #I2 = 3.05
+mean(SMDs$H2[SMDs$eff_size < 0.05]) #H2 = 0.88
 
@@
 #bootstrap confidence intervals
-#code by Amir Abdol
+#code contribution by Amir Abdol
 
 #1.1 I2 confidence intervals----
-pear <- function(formula, data, indices){ #pearson
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d)
-     return(fit$estimate)
-}
 
-#bootfit <- boot(data=SMDs, statistic=pear, R=1000, formula= ~ eff_size + s_I2) #see Fig 3
+#bootfit <- boot(data=SMDs, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #see Fig 3
 #I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
@@
 set.seed(234)
-bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + s_I2)
+bootfit <- boot(data=dropped_anchoring, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #statistic function is sourced
 
@@
 
-#1.2 Tau2 confidence intervals----
-pear <- function(formula, data, indices){
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ tau + eff_size, data=d)
-     return(fit$estimate)
-}
+#1.2 Tau confidence intervals----
 
-# bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + tau2) #see Fig 3
+# bootfit <- boot(data=tau_per_type, statistic=pear_tau, R=1000, formula= ~ eff_size + tau2) #see Fig 3
 # tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
@@
 set.seed(423)
-bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + tau)
+bootfit <- boot(data=dropped_anchoring, statistic=pear_tau, R=1000, formula= ~ eff_size + tau)
 tau_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
@@
 #1.3 H2 confidence intervals----
-pear <- function(formula, data, indices){
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ H2 + eff_size, data=d)
-     return(fit$estimate)
-}
-
 set.seed(342)
-bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + H2)
+bootfit <- boot(data=tau_per_type, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
 H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
@@
 #First for I2
-spear <- function(formula, data, indices){ #spearman
+spear_I2 <- function(formula, data, indices){ #spearman
      d <- data[indices,]
@@
 options(warn=-1)
-bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + s_I2)
+bootfit <- boot(data=tau_per_type, statistic=spear_I2, R=1000, formula= ~ eff_size + s_I2)
 options(warn=0)
@@
 #Second for tau
-spear <- function(formula, data, indices){ #spearman
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ tau + eff_size, data=d, method = "spearman")
-     return(fit$estimate)
-}
 
 set.seed(5233)
-tau2_per_type <- tau2_per_type %>% mutate(tau = sqrt(tau2))
 options(warn=-1)
-bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + tau)
+bootfit <- boot(data=tau_per_type, statistic=spear_tau, R=1000, formula= ~ eff_size + tau)
 options(warn=0)

### 2019-12-04 code/06_Supplement-tables-figures.Rmd
Correction to Figure 3 and added Supplement C

@@
 if(!require(kableExtra)){install.packages("kablExxtra")}
+if(!require(ggplot2)){install.packages("ggplot2")}
+if(!require(cowplot)){install.packages("cowplot")}
+if(!require(boot)){install.packages("boot")}
 
@@
 library(kableExtra) #create fancy pdf tables
+library(boot) #Bootstrap confidence intervals for correlations
 
@@
 Code to reproduce table: https://osf.io/j9zyd/?view_only=e6639d8d4f924739a7310782fbbb4e06
+
+## Supplement C
+
+```{r, preprocessing}
+
+SMDs_raw <- dat %>% filter(outcomes1_2 == "mean _ SD") %>% 
+  mutate(wi = compute_precision(SD1 = outcome_t2, SD2 = outcome_c2, n1 = ntreatment, n2 = ncontrol)) #compute_precision function is sourced
+
+average_within <- SMDs_raw %>% #these values we now wish to correlate with meta-analytic results
+  group_by(effect) %>% 
+  summarize(s2 = sum(wi) * (n()-1) / (sum(wi)^2 - sum(wi^2))) %>% #Average within study variance; equation 9. Higgins and Thompson (2003). n() = k [number of studies in a meta-analysis]
+  ungroup()
+
+#Raw mean differences to SMD
+MD_standardized <- dat %>% 
+  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
+  split(.$effect) %>% 
+  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced
+
+tau_per_type <- MD_standardized %>% 
+  left_join(average_within) %>%
+  mutate(sigma = sqrt(s2),
+         eff_size = abs(eff_size),
+         tau = sqrt(tau2)) #needed for bootfitter function below to work but not used
+
+#Add labels
+#lables
+set.seed(499) #for the bootstrapping
+all_effects_ci <- tau_per_type %>% 
+  bootfitter_sigma(.) #bootfitter is a sourced function
+
+labels_all <- tau_per_type %>% #
+  fitter_sigma(.) %>% #fitter is a sourced function
+  mutate(lab = paste0("r = ", r, " ", all_effects_ci$ci)) #put output into one variable for improved plotting
+
+#As above but dropping the 4 largest effect sizes (Anchoring effects)----
+without_anchoring <- tau_per_type %>% 
+  filter(!grepl("Anchoring", effect))
+
+#lables
+set.seed(500) #for the bootstrapping
+restricted_effects_ci <- without_anchoring %>% 
+  bootfitter_sigma(.) #bootfitter is a sourced function
+
+labels_restricted <- without_anchoring %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
+  fitter_sigma(.) %>% #fitter is a sourced function
+  mutate(lab = paste0("r = ", r, " ", restricted_effects_ci$ci)) #put output into one variable for improved plotting
+
+```
+
+```{r}
+
+within_plot_full <- ggplot(tau_per_type, aes(x = eff_size, y = sigma)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels_all[labels_all$index == "sigma",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  scale_y_continuous(name = expression(paste("Within Studies Standard Deviation"))) +
+  scale_x_continuous(name = "Absolute Effect Size") +
+  theme_classic() +
+  theme(strip.background = element_blank(), #remove box around titles
+        strip.text = element_text(size = 12),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid"))
+
+without_anchoring_plot <- ggplot(without_anchoring, aes(x = eff_size, y = sigma)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels_restricted[labels_restricted$index == "sigma",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  scale_y_continuous(name = expression(paste("Within Studies Standard Deviation"))) +
+  scale_x_continuous(name = "Absolute Effect Size") +
+  theme_classic() +
+  theme(strip.background = element_blank(), #remove box around titles
+        strip.text = element_text(size = 12),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid"))
+
+cowplot::plot_grid(within_plot_full, without_anchoring_plot, nrow = 2, labels = "AUTO")
+ggsave("../figures/figure-S2.png", dpi = 600, height =  7, width = 7)
+```
+
+Figure S2.
+The Pearson correlation (_r_) between average absolute effect size and average within studies standard deviation for 40 effects that were measured as mean or standardized mean differences.
+Panel A shows results for all 40 effect sizes and panel B with the four largest (Anchoring 1 - 4) excluded.
+Effects reported as mean differences were standardized.
+Square brackets contain 95% bootstrapped percentile confidence intervals.

### 2019-12-04 code/03_helper_functions_tables_figures.r

@@ -66,7 +66,116 @@ est_heterogen_smd_raw <- function(x){
              H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
 }
 
+#******************************************
+#Function for Figure 3 and Supplement C----
+#******************************************
 
+MD_fit <- function(x){ #standardize mean differences in the meta-analysis
+  fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
+  hetero <- confint(fit)$random[c(1, 3), ] 
+  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
+             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
+}
+
+
+log_or_fit <- function(x){ #NB! if a cell is 0, 1/2 will be added to it. Fit log odds meta-analysis
+  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
+  hetero <- confint(fit)$random[c(1, 3), ] 
+  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
+             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
+}
+
+#labels for figure 3----
+fitter <- function(df){  #function to fit correlations for annotating facet plots
+  fit_tau <- summary(lm(tau ~ eff_size, data = df))
+  fit_I2 <- summary(lm(s_I2 ~ eff_size, data = df))
+  fit_H2 <- summary(lm(H2 ~ eff_size, data = df))
+  r <- c(sqrt(fit_tau$r.squared), sqrt(fit_I2$r.squared), sqrt(fit_H2$r.squared))
[…]

### 2019-12-11 code/06_Supplement-tables-figures.Rmd
Supplement C reported as a correlation matrix instead of figure

--- 2019-12-03 code/06_Supplement-tables-figures.Rmd
@@
 
-#Table S1.
+#Table S1A.
 ###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
@@
 Code to reproduce table: https://osf.io/j9zyd/?view_only=e6639d8d4f924739a7310782fbbb4e06
+
+## Supplement C
+
+```{r, preprocessing}
+
+SMDs_raw <- dat %>% filter(outcomes1_2 == "mean _ SD") %>% 
+  mutate(wi = compute_precision(SD1 = outcome_t2, SD2 = outcome_c2, n1 = ntreatment, n2 = ncontrol)) #compute_precision function is sourced
+
+average_within <- SMDs_raw %>% #these values we now wish to correlate with meta-analytic results
+  group_by(effect) %>% 
+  summarize(s2 = sum(wi) * (n()-1) / (sum(wi)^2 - sum(wi^2))) %>% #Average within study variance; equation 9. Higgins and Thompson (2002). n() = k [number of studies in a meta-analysis]
+  ungroup()
+
+#Raw mean differences to SMD
+MD_standardized <- dat %>% 
+  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
+  split(.$effect) %>% 
+  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced
+
+tau_per_type <- MD_standardized %>% 
+  left_join(average_within) %>%
+  mutate(sigma = sqrt(s2),
+         eff_size = abs(eff_size),
+         tau = sqrt(tau2)) #needed for bootfitter function below to work but not used
+
+#As above but dropping the 4 largest effect sizes (Anchoring effects)----
+without_anchoring <- tau_per_type %>% 
+  filter(!grepl("Anchoring", effect))
+
+corr_data <- tau_per_type %>%
+  select(s2, eff_size, s_I2, H2) %>% 
+  rename("$\\hat{\\mu}$" = "eff_size", "$I^2$" = "s_I2", "$H^2$" = "H2", "$s^2$" = s2)
+
+corr_data_no_anchoring <- without_anchoring %>%
+  select(s2, eff_size, s_I2, H2) %>% 
+  rename("$\\hat{\\mu}$" = "eff_size", "$I^2$" = "s_I2", "$H^2$" = "H2", "$s^2$" = s2)
+
+```
+
+Table S1C.
+The Pearson correlations from 40 meta-analyses estimated with the random effects model and restricted maximum likelihood.
+$s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis.
+This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless.
+In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences.
+Effects reported as mean differences were standardized for the meta-analyses.
+
+```{r, corr-table}
+
+cors <- round(cor(corr_data), digits = 2)
+cors[upper.tri(cors)] <- "" #make upper triangle empty in correlation matrix
+
+knitr::kable(cors, booktabs = TRUE, escape = FALSE)
+```
+
+Table S2C.
+The Pearson correlations from 36 meta-analyses estimated with the random effects model and restricted maximum likelihood.
+The sample of effects is identical to Table S1C but with 4 Anchoring effects excluded.
+$s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis.
+This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless.
+In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences.
+Effects reported as mean differences were standardized for the meta-analyses.
+
+```{r, no-anchoring-corr}
+cors_anch <- round(cor(corr_data_no_anchoring), digits = 2)
+cors_anch[upper.tri(cors_anch)] <- "" #make upper triangle empty in correlation matrix
+
+knitr::kable(cors_anch, booktabs = TRUE, escape = FALSE)
+
+```

### 2019-12-11 code/03_helper_functions_tables_figures.r

@@ -151,31 +151,7 @@ spear_tau <- function(formula, data, indices){ #spearman
   return(fit$estimate)
 }
 
-#Supplement C labels----
-pear_sigma <- function(formula, data, indices){ #pearson
-  d <- data[indices,]
-  fit <- cor.test(formula = ~ sigma + eff_size, data=d)
-  return(fit$estimate)
-}
 
-fitter_sigma <- function(df){  #function to fit correlations for annotating facet plots
-  fit_sigma <- summary(lm(sigma ~ eff_size, data = df))
-  r <- sqrt(fit_sigma$r.squared)
-  data.frame(r = format(round(r, digits = 2), nsmall = 2),
-             index = "sigma") 
-}
-
-bootfitter_sigma <- function(x){ #function that computes the bootstrapped confidence intervals using above functions to annotate plots
-  bootfit <- boot(data=x, statistic=pear_sigma, R=1000, formula= ~ eff_size + sigma)
-  sigma_ci_pears <- boot.ci(bootfit, type="perc")
-  
-  ci.lb <- sigma_ci_pears$percent[4]
-  ci.ub <- sigma_ci_pears$percent[5]
-  
-  ci <- paste0("[", format(round(ci.lb, 2), nsmall = 2), ", ",
-               format(round(ci.ub, 2), nsmall = 2), "]")#percentile 
-  data.frame(ci, index = "sigma")
-}
 #******************************************
 #Functions (for Supplement A) to transform all effect sizes to the same unit of measurement and meta-analyze----
 #******************************************

### 2019-12-11 code/06_Supplement-tables-figures.Rmd
Dropped table from Supplement A

@@
 ---
-title: "Tables and Figures - Supplement A and B"
+title: "Tables and Figures - Supplement A, B and C"
 date: "`r format(Sys.time(), '%d %B, %Y')`"
-output: html_document
+output: pdf_document
 ---
 
-This document contains the code to reproduce tables and figures from Supplement A and Supplement B for the project "Heterogeneity in direct replications in psychology and its association with effect size".
+This document contains the tables and figures from Supplement A, B and C for the project "Heterogeneity in direct replications in psychology and its association with effect size".
 
@@
 
-## Supplement A
+# Supplement A
 
@@
 
-#Table S1A.
-###Heterogeneity across primary effects and statistical power of ten multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
-```{r prep-heterogeneity-table, cache = TRUE}
-#library(metafor)
-#library(dplyr)
-#library(purrr)
-
-#fit a random effects model to all empirical data
-#Each set of input datapoints is meta-analyzed as per the original replication project
-#Function 'est_heterogen_smd_raw' is sourced
-res <- dat %>%
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map_dfr(est_heterogen_smd_raw, .id = "effect") %>% #apply function, rbind results into dataframe ('dfr'), make sure purrr is up to date
-  mutate(tau = sqrt(tau2),
-         tau_ci.lb = sqrt(tau2_ci.lb),
-         tau_ci.ub = sqrt(tau2_ci.ub)) %>%
-  select(-tau2, - tau2_ci.lb, -tau2_ci.ub) #drop redundant variables
-
-#Transform effect sizes to biserial correlations (pearson's correlations left as is)
-#estimate tau2 for correlations
-#'transform_MA' and 'summarizer' are sourced functions
-res2 <- dat %>%
-  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
-  map(transform_MA) %>% #
-  map_dfr(summarizer, .id = "effect")
-
-res <- res %>%
-  mutate(r = res2$r,
-         tau_r = sqrt(res2$tau2), #For table 3, report tau and transformed effect sizes (biserial correlations)
-         tau_r_ci.lb = sqrt(res2$tau2.lb),
-         tau_r_ci.ub = sqrt(res2$tau2.ub))
-
-#Add rp and k to the data-frame and prep for table
-het <- dat %>%
-  select(rp, Site, effect, effect_type) %>%
-  group_by(rp, effect) %>%
-  summarize(effect_type = unique(effect_type),
-            k = n_distinct(Site)) %>%
-  left_join(res) %>%
-  mutate(effect_type = recode(effect_type,
-                              d = "SMD",
-                              'Raw mean difference' = "MD",
-                              'Risk difference' = "RD")) %>%
-  ungroup()
-
-#Load simulation results (power/type 1 error for all effects)
-dens <- readRDS("../data/power_simulation_results.RDS")
-names(dens) <-  sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort
-
-#Summary of simulation results, needs to be combined with main part of table
-I2_power <- dens %>%
-  bind_rows(.id = "effect") %>%
-  group_by(effect, tau_index) %>%
-  summarize(power = mean(Qp <= 0.05)) %>% #Estimate power/type 1 error for each tau level and effect
-  ungroup() %>%
-  tidyr::spread(key = tau_index, value = power) %>% #prep for table
-  rename(zero = '1', small = '2', medium = '3', large = '4')
-
-#Combine dataframes to create full table
-het <-  het %>%
-  left_join(I2_power) %>%
-  arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by I2 and upper CI bound
-  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 1), nsmall = 1)), ", ", trimws(format(round(s_ci.ub, 1), nsmall = 1)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
-         s_I2 = format(round(s_I2, 1), nsmall = 1),
-         tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),
-         tau = format(round(tau, 3), nsmall = 3),
-         tau_r = format(round(tau_r, 3), nsmall = 3),
-         tau_r_ci = paste0("[", trimws(format(round(tau_r_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_r_ci.ub, 3), nsmall = 3)), "]")) %>% #rounded here instead of in table function because should have 4 digits
-  select(rp, effect, k, effect_type, eff_size, s_I2, I2_ci, tau, tau_ci, r, tau_r, tau_r_ci, zero, small, medium, large)
-
-```
-
-```{r heterogeneity-table, cache = FALSE}
-#library(kableExtra)
-
-het %>% knitr::kable(align = "c", booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\tau$", "$\\tau$ 95\\% CI", "r*" , "r* $\\tau$", "r* $\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
-  add_header_above(c(" " = 12, "Level of heterogeneity" = 4)) %>%
-  add_header_above(c(" " = 12, "Type I Error Rate & Statistical Power" = 4)) %>%
-  kable_styling("scale_down", font_size = 7) %>% #comment out if outputting html file
-  column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped
-  footnote(threeparttable = TRUE, escape = FALSE,
-           general = "Effects were estimated in metafor using REML.
-The following effects are odds ratios transformed into standardized mean differences: 'Allowed vs.
-forbidden', 'Gain vs.
-loss framing', 'Norm of reciprocity', 'Low vs.
-high category scales'.
-RP = Replication Project, K = no.
-primary studies, CI = confidence intervals, r* = effect sizes as correlations and biserial correlations.
-$I^2$ and its confidence intervals are for original effect size specifications whereas $\tau$ and its confidence intervals are for transformed r* effect sizes.
-Statistical power and type I error rates were simulated, where Zero = simulated type 1 error, and the other headers represent simulated power under small/medium/large heterogeneity ($I^2$ = 25/50/75\\\\%) respectively.
-SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-Code to reproduce table: https://osf.io/j9zyd/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06",
-           alphabet = "These effects were simulated as standardized mean differences") %>%
-  landscape()
-
-```
-
-## Supplement B
+# Supplement B
 
@@
 
+## Table S1B
+
 _Type I error and power to detect four heterogeneity levels under two true effect sizes_
@@
 ```{r}
-knitr::kable(comparison, digits = 2)
+knitr::kable(comparison, digits = 2, longtable = TRUE, booktabs = TRUE) %>% 
+  add_header_above(c(" " = 1, "True effect size zero" = 4, "True effect size medium" = 4)) %>% 
+  add_header_above(c(" " = 1, "Type I error rate and power for different heterogeneity levels" = 8))
 ```
@@
 
-## Supplement C
+# Supplement C
 
@@
 
-Table S1C.
-The Pearson correlations from 40 meta-analyses estimated with the random effects model and restricted maximum likelihood.
-$s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis.
-This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless.
-In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences.
-Effects reported as mean differences were standardized for the meta-analyses.
+## Table S1C.
 
@@
 
-Table S2C.
-The Pearson correlations from 36 meta-analyses estimated with the random effects model and restricted maximum likelihood.
-The sample of effects is identical to Table S1C but with 4 Anchoring effects excluded.
+**Note:** The Pearson correlations from 40 meta-analyses estimated with the random effects model and restricted maximum likelihood.
 $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis.
@@
 Effects reported as mean differences were standardized for the meta-analyses.
+
+## Table S2C.
 
@@
 ```
+
+**Note:** The Pearson correlations from 36 meta-analyses estimated with the random effects model and restricted maximum likelihood.
+The sample of effects is identical to Table S1C but with 4 Anchoring effects excluded.
+$s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis.
+This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless.
+In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences.
+Effects reported as mean differences were standardized for the meta-analyses.

### 2019-12-13 code/05_figures-and-correlations.rmd
Updated heterogeneity sub-analysis when MA ES = 0

@@
 #1. Standardized mean differences----
-SMDs <- tau_per_type %>% filter(effect_type == "Standardized Mean Difference")
+SMDs <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
+  filter(effect_type == "Standardized Mean Difference")
 
@@
 
-##When effect size == 0, what is average heterogeneity?
-mean(SMDs$tau[SMDs$eff_size < 0.05]) #for tau = 0.016
-mean(SMDs$s_I2[SMDs$eff_size < 0.05]) #I2 = 3.05
-mean(SMDs$H2[SMDs$eff_size < 0.05]) #H2 = 0.88
-
 ##Excluding anchoring effects
@@
 cor.test(dropped_anchoring$H2, dropped_anchoring$eff_size) #pearson
+
+#1.05 When ES not sig. diff from zero----
+##When effect size not sig diff from 0 (alpha = .05), what is average heterogeneity?
+nrow(SMDs[SMDs$eff_size_p > 0.05,]) #20/40 SMDs have ES not sig. diff from zero
+sum(SMDs$tau[SMDs$eff_size_p > 0.05] == 0) #13/20 of these have taus == 0
+
+mean(SMDs$tau[SMDs$eff_size_p > 0.05]) #for tau = 0.017
+mean(SMDs$s_I2[SMDs$eff_size_p > 0.05]) #I2 = 3.49
+mean(SMDs$H2[SMDs$eff_size_p > 0.05]) #H2 = 0.89
+
+SMDs_not_sig <- SMDs[SMDs$eff_size_p > 0.05,]$effect
+
+dat %>% filter(effect %in% SMDs_not_sig) %>% #amongst the non-sig SMDS
+  group_by(effect) %>% 
+  summarize(K = n()) %>% #compute number of labs (K) per effect
+  ungroup() %>% 
+  summarize(mean_k = mean(K), #average number of K = 32.8
+            median = quantile(K)['50%']) #median 22.5
+
+#% estimates that should be non-zero under central chi-square distribution. For I2 any effect size where Q <= DF ->  I2 zero
+pchisq(23, 23, lower.tail = FALSE)
+
+#logs
+logOR <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
+  filter(effect_type == "Log Odds Ratio")
+
+nrow(logOR[logOR$eff_size_p > 0.05,]) #only 1 log odds ratio not signifcant
 

### 2019-12-13 code/03_helper_functions_tables_figures.r

@@ -60,10 +60,10 @@ est_heterogen_smd_raw <- function(x){
   }
   
   hetero <- confint(fit)$random[c(1, 3), ] #Gives us the tau2 and I2 estimates with confidence intervals
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
-             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
-             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
-             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
+  data.frame(eff_size = fit$b[[1]], eff_size_p = fit$pval, #effect size (point estimate) + its p-value 
+             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3], #I2 with Confidenc intervals
+             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3], #tau2 with confidence intervals
+             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1)) #General H2  (H2trunc) and DerSimonian-Laird H2
 }
 
 #******************************************
@@ -73,7 +73,7 @@ est_heterogen_smd_raw <- function(x){
 MD_fit <- function(x){ #standardize mean differences in the meta-analysis
   fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
   hetero <- confint(fit)$random[c(1, 3), ] 
-  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
+  data.frame(eff_size = fit$b[[1]], eff_size_p = fit$pval, #effect size (point estimate) 
              s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
              tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
              H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
[…]

### 2019-12-13 code/06_Supplement-tables-figures.Rmd
Updated figure for supplement A

@@
 a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("SMD (untransformed)") +
-  scale_x_continuous(name = expression(paste(italic(I)^2, "Index"))) +
+  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
   scale_y_continuous(name = "Tau")
@@
 
-```{r trunc-biserial, cache = TRUE}
-#Transform effect sizes to biserial correlations (pearson's correlations left as is)
+```{r point-biserial, cache = TRUE}
+#Transform effect sizes to point-biserial correlations (pearson's correlations left as is)
 #estimate tau2 for correlations
@@
 res2 <- dat %>%
-  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales')) %>%
+  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "d") %>%
   split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
@@
 het <- dat %>%
+  filter(effect %in% res2$effect) %>% 
   select(rp, Site, effect, effect_type) %>%
@@
 ```{r c-plot-1, cache = FALSE}
-c_plot <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + geom_point() + ggtitle("Point Biserial r (transformed SMD)")
+c_plot <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + 
+  geom_point() + 
+  scale_y_continuous(name = "Tau") +
+  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
+  ggtitle("Point-Biserial r (transformed SMD)")
 
@@
 b <- select(a, effect, tau2) %>%
-  left_join(select(d, effect, tau2), by = "effect") #add truncated transformation tau2
+  left_join(select(d, effect, tau2), by = "effect") #add point-biserial transformation tau2 to untransformed
 ```
@@
   scale_x_continuous(name = "Tau (SMD)") +
-  scale_y_continuous(name = "Tau (Point biserial)")
+  scale_y_continuous(name = "Tau (Point-biserial r)")
 
@@
 
-_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into biserial correlations for all effects reported as SMDs in ManyLabs 1.
+_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1.
 Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text).
-Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to biserial correlations, either with truncation of correlations over 1 (circles) or without (crosses) when estimating variance.
-Panel C  shows the associations between estimates of $I^2$ on the SMD metric and estimates of $\tau$ after transformation, either with truncation or not.
+Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations.
+Panel C  shows the associations between estimates of $I^2$ on the SMD metric and estimates of $\tau$ after transformation.
 

### 2019-12-16 code/06_Supplement-tables-figures.Rmd
Dropped Panel C from Supplement A

@@
 if(!require(purrr)){install.packages("purrr")}
-if(!require(kableExtra)){install.packages("kablExxtra")}
+if(!require(kableExtra)){install.packages("kablExtra")}
 if(!require(ggplot2)){install.packages("ggplot2")}
 if(!require(cowplot)){install.packages("cowplot")}
+if(!require(ggrepel)){install.packages("ggrepel")}
 if(!require(boot)){install.packages("boot")}
@@
 library(cowplot) #combine plots
+library(ggrepel) #easy labels for plots (supplement A identification of points)
 library(kableExtra) #create fancy pdf tables
@@
 
-```{r c-plot-1, cache = FALSE}
-c_plot <- ggplot(d, aes(x = I2, y = sqrt(tau2))) + 
-  geom_point() + 
-  scale_y_continuous(name = "Tau") +
-  scale_x_continuous(name = expression(paste(italic(I)^2, " Index"))) +
-  ggtitle("Point-Biserial r (transformed SMD)")
-
-```
-
 ```{r tau-vs-tau}
@@
 ```{r, fig.width = 6, fig.asp = 1.3}
-cowplot::plot_grid(a_plot, b_plot, c_plot, ncol = 1, labels = "AUTO")
+
+cowplot::plot_grid(a_plot, b_plot, ncol = 1, labels = "AUTO")
 
@@
 Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations.
-Panel C  shows the associations between estimates of $I^2$ on the SMD metric and estimates of $\tau$ after transformation.
+
+```{r text-results, eval = FALSE}
+#Not printed if knitting the document.
+
+#to find out which point is which effect in Panel B. 
+b_plot + ggrepel::geom_label_repel(data = b, aes(label = effect))
+
+#Examine effects of larger effect size on transformation
+transform_d_to_r(c(0, 0.1, 1, 1.1, 2, 2.1), n1 = 100, n2 = 100) #sourced function
+
+#to find out which point is which effect in Panel c. 
+c_plot + ggrepel::geom_label_repel(data = d, aes(label = effect))
+
+```
 

### 2019-12-18 code/04_tables.rmd
General code cleanup

@@
 rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
-ma <- c("I: $\\mu = 0.0$", "II: $\\mu = 0.3$", "III: $\\mu = 0.5$")
+ma <- c("I: $\\rho_{xy} = 0.0$", "II: $\\rho_{xy} = 0.3$", "III: $\\rho_{xy} = 0.5$")
 
@@
 # 
-# table1b %>% knitr::kable(booktabs = T, col.names = c("Study and Measurement Error", "I: $\\mu = 0$", "II: $\\mu = .3$", "III: $\\mu = .5$"), escape = FALSE, digits = 2) %>% 
+# table1b %>% knitr::kable(booktabs = T, col.names = c("Study and Measurement Error", "I: $\\rho_{xy} = 0$", "II: $\\rho_{xy} = .3$", "III: $\\rho_{xy} = .5$"), escape = FALSE, digits = 2) %>% 
 #   add_header_above(c(" " = 1, "Meta-Analysis" = 3)) %>% 
@@
 ```
-*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\mu$ when within study sample size is infinite.
+*Note:* The values under Study 1, 2 and 3 are observed effect sizes for that study given its measurement reliability $\sqrt{R_{xx'}}\times\sqrt{R_{yy'}}$ and the true effect size $\rho_{xy}$ when within study sample size is infinite.
 SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite within study sample sizes.
@@
                      "All samples consisted of in-lab undergraduate students aged 18-25", #RRR8
-               "All samples consisted of in-lab students aged 18-25",
-               "All samples consisted of in-lab students aged 18-25")
+               "All samples consisted of in-lab students aged 18-25", #RRR9
+               "All samples consisted of in-lab students aged 18-25") #RRR10
 
@@
 ```
-Note: For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
+**Note:** For studies with several effects the number of participants is the average across effects, rounded to the closest whole number.
 N = Participants used for primary analyses by original authors (i.e., after exclusions).
@@
 #****************
-#Results for "Heterogeneity Estimates and Confidence Intervals" section in paper
+#Results for "Heterogeneity Estimates and Confidence Intervals" section in paper----
 

### 2019-12-18 code/05_figures-and-correlations.rmd
General code cleanup

@@
 
-```{r cor_het_effect_size, results = "hide", cache=TRUE}
+```{r cor_het_effect_size, eval= FALSE}
 
-#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript
+#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript (not printed if .rmd is knit)
 

### 2019-12-18 code/06_Supplement-tables-figures.Rmd
General code cleanup

@@
 
-```{r, cache = FALSE}
+```{r a-plot, cache = FALSE}
 a_plot <- ggplot(a, aes(x = s_I2, y = sqrt(tau2))) + geom_point() + ggtitle("SMD (untransformed)") +
@@
 
-```{r, fig.width = 6, fig.asp = 1.3}
+```{r combine-plots, fig.width = 6, fig.asp = 1.3}
 
@@
 
-_Figure S.1_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1.
+_Figure S1A_ Association between estimates of $\tau$ and $I^2$ after and before standardized mean differences (SMD) effects were transformed into point-biserial correlations for all effects reported as SMDs in Many Labs 1.
 Panel A shows the association between estimates of $\tau$ and $I^2$ without transformation when using the meta-analytic specification of the original authors (see main text).
@@
 
-```{r}
+```{r table-S1B}
 knitr::kable(comparison, digits = 2, longtable = TRUE, booktabs = TRUE) %>% 
@@
 
-```{r, preprocessing}
+```{r preprocessing-supp-C}
 
@@
 
-```{r, corr-table}
+```{r table-S1C}
 
@@
 
-```{r, no-anchoring-corr}
+```{r table-S2C-no-anchoring-SMD}
 cors_anch <- round(cor(corr_data_no_anchoring), digits = 2)

### 2019-12-18 code/02_power_simulation.r

@@ -193,7 +193,8 @@ system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progr
 
 ##Simulation results
 dat3 <- readRDS("../data/tau_simulation_results.RDS")
-names(dat3) <- names(dat2) #names are lost when looping instead of using lapply
+# dat3 <- readRDS("../supplementB_tau_simulation_results.RDS") #for supplement
+names(dat3) <- names(dat2) #names are lost when looping instead of using lapply so must be re-added
 
 dat3 <- dat3 %>% #create dataframe with identifier
   bind_rows(.id = "effect") %>% 
@@ -244,6 +245,8 @@ system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progr
 #*********************
 #Effect size sensitivity simulation for Supplement B
 
+#Note dat5 from above is needed
+
 # set.seed(50)
 #  res2_a <- vector("list", length(dat2)) #output of below loop
 # 
@@ -257,6 +260,7 @@ system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progr
 
 ##Simulation results
 dens <- readRDS("../data/power_simulation_results.RDS") #very large if saved as .csv
+# dens <- readRDS("../data/supplementB_power_simulation_results.RDS") #If supplement simulation
 names(dens) <-  names(dat2)
 
 #Summary of results. These are incorporated into the main table in the paper, see tables.rmd

### 2019-12-18 code/03_helper_functions_tables_figures.r

@@ -4,7 +4,7 @@
 #Script purpose: Helper functions to prep data for tables and figures
 #Code: 
 #Additional comments: These functions are intended to be 'sourced' into the 
-#                     tables.rmd and figures.rmd files 
+#                     tables.rmd, figures.rmd, and supplement-tables-figures.rmd files 
 
 #******************************************
 
@@ -67,7 +67,7 @@ est_heterogen_smd_raw <- function(x){
 }
 
 #******************************************
-#Function for Figure 3 and Supplement C----
+#Functions for Figure 3 (first also used in Supplement C)----
 #******************************************
 
 MD_fit <- function(x){ #standardize mean differences in the meta-analysis
@@ -153,8 +153,9 @@ spear_tau <- function(formula, data, indices){ #spearman
 
 
 #******************************************
-#Functions (for Supplement A) to transform all effect sizes to the same unit of measurement and meta-analyze----
+#Functions for Supplement A----
 #******************************************
+
 
 #Formulas found in: 
 #Borenstein, M. (2009). Effect sizes for continuous data. In H. Cooper, L. V. Hedges, & J. C. Valentine (Eds.), 
@@ -162,19 +163,10 @@ spear_tau <- function(formula, data, indices){ #spearman
 
 #Jacobs, P., & Viechtbauer, W. (2017). Estimation of the biserial correlation and its sampling variance for use
 #in meta-analysis. Research Synthesis Methods, 8(2), 161-180.
-#(provide an exact computation of the point-biserial correlation rather than the approximate [Hunter & Schmitd] in Borenstein)
-#Jacobs and Viechbauers version has the advantage that it can compute variance even if r = 1
 
-#Jacobs and Viechtbauer (2017) recommend transforming the point-biserial correlation to a 
-#biserial correlation. 
+#Cooper, H., Hedges, L. V., & Valentine, J. C. (2009). The handbook of research synthesis and meta-analysis 2nd
+#edition. In The Hand. of Res. Synthesis and Meta-Analysis, 2nd Ed. (pp. 1-615). Russell Sage Foundation.
 
-
-##For raw mean difference + SE -> Hedge's g
-transform_SE <- function(ES, SE, n1, n2){ 
[…]

### 2019-12-18 code/05_figures-and-correlations.rmd
Made Figure 1 more color blind friendly

@@
 #combined line plot gives good overview.
-ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type)) +
+ggplot(dat3, aes(x = tau, y = I2, group = effect, color = effect_type, linetype = effect_type)) +
   geom_line(alpha = 0.6) +
@@
                      minor_breaks = NULL) +
+  scale_linetype_manual(name = "Effect type", 
+                        values = c( "dotdash", "dotted", "solid", "dashed"),
+                        breaks = "Fisher's z", "Cohen's q", "MD", "SMD") + 
+  scale_color_brewer(name = "Effect type", 
+                     palette = "Dark2", 
+                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) +
   coord_cartesian(ylim = c(0, 100)) +
-  scale_color_brewer(name = "Effect type", palette = "Dark2", 
-                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) +
   theme(legend.position = c(0.8, 0.4),

### 2019-12-18 code/05_figures-and-correlations.rmd
Figure 1 correction of coding error in update

--- 2019-12-18 code/05_figures-and-correlations.rmd
@@
                      minor_breaks = NULL) +
+  scale_linetype_manual(name = "Effect type", 
+                        values = c( "dotdash", "dotted", "solid", "dashed"),
+                        breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) + 
+  scale_color_brewer(name = "Effect type", 
+                     palette = "Dark2", 
+                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) +
   coord_cartesian(ylim = c(0, 100)) +
-  scale_color_brewer(name = "Effect type", palette = "Dark2", 
-                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) +
   theme(legend.position = c(0.8, 0.4),
         legend.background = element_rect(linetype = "solid", color = "black")) +
-  guides(color = guide_legend(override.aes = list(size = 1.4)))
+  guides(color = guide_legend(override.aes = list(size = 1.2)))
 

### 2019-12-20 code/06_Supplement-tables-figures.Rmd
Updated Figure S1A with a Fisher's z panel

@@
 This document contains the tables and figures from Supplement A, B and C for the project "Heterogeneity in direct replications in psychology and its association with effect size".
+This file can be found at: osf.io/bm2wa/?view_only=e6639d8d4f924739a7310782fbbb4e06
 
@@
 
-#Add rp and k to the data-frame
-het <- dat %>%
-  filter(effect %in% res2$effect) %>% 
-  select(rp, Site, effect, effect_type) %>%
-  group_by(rp, effect) %>%
-  summarize(effect_type = unique(effect_type),
-            k = n_distinct(Site)) %>%
-  left_join(res2) %>%
-  mutate(effect_type = recode(effect_type,
-                              d = "SMD.",
-                              'Raw mean difference' = "MD",
-                              'Risk difference' = "RD")) %>%
-  ungroup()
-
-d <- het %>% filter(effect_type == "SMD.") %>%
-  mutate(sigma2 = tau2/(I2/100) - tau2) #add 'typical within study variance' per project
+b <- select(a, effect, tau2) %>%
+  left_join(select(res2, effect, tau2), by = "effect") #add point-biserial transformation tau2 to untransformed
 
@@
 
-```{r tau-vs-tau}
-b <- select(a, effect, tau2) %>%
-  left_join(select(d, effect, tau2), by = "effect") #add point-biserial transformation tau2 to untransformed
-```
-
-```{r b-plot-1}
+```{r b-plot}
 b_plot <- ggplot(b, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
@@
 
+```{r fisher-transformed}
+res3 <- dat %>%
+  filter(rp == "ML1" & !effect %in% c('Allowed vs. forbidden', 'Gain vs. loss framing','Norm of reciprocity', 'Low vs. high category scales') & effect_type == "d") %>%
+  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
+  map(transform_MA, fisher = TRUE) %>% #Fisher-transformed
+  map_dfr(summarizer, .id = "effect")
+
+d <- select(a, effect, tau2) %>%
+  left_join(select(res3, effect, tau2), by = "effect") #add fisher-transformed point-biserial transformation tau2 to untransformed
+```
+
+```{r c-plot}
+c_plot <- ggplot(d, aes(x = sqrt(tau2.x), y = sqrt(tau2.y))) +
+  geom_point() +
+  ggtitle(expression(bold(paste("SMD vs. Fisher's ", italic(z))))) +
+  scale_x_continuous(name = "Tau (SMD)") +
+  scale_y_continuous(name = expression(paste("Tau (Fisher's ", italic(z), ")")))
+```
+
 ```{r combine-plots, fig.width = 6, fig.asp = 1.3}
 
-cowplot::plot_grid(a_plot, b_plot, ncol = 1, labels = "AUTO")
+cowplot::plot_grid(a_plot, b_plot, c_plot, ncol = 1, labels = "AUTO")
 
@@
 Panel B shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations.
+Panel C shows the association between estimates of $\tau$ for the same effects before and after transformation to point-biserial correlations and subsequently to Fisher's _z_.
 
@@
 
-#Examine effects of larger effect size on transformation
+#Examine effects of larger effect size on transformation to point-biserial
 transform_d_to_r(c(0, 0.1, 1, 1.1, 2, 2.1), n1 = 100, n2 = 100) #sourced function
 
-#to find out which point is which effect in Panel c. 
+#to find out which point is which effect in Panel C. 
 c_plot + ggrepel::geom_label_repel(data = d, aes(label = effect))
+
+#Examine effects of larger effect size on transformation to Fisher's z
+transform_d_to_r(c(0, 0.1, 1, 1.1, 2, 2.1), n1 = 100, n2 = 100, fisher = TRUE) #sourced function
 
@@
 Medium effect size is as defined by Cohen (1988).
-Code to reproduce table: https://osf.io/j9zyd/?view_only=e6639d8d4f924739a7310782fbbb4e06
 

### 2019-12-20 code/03_helper_functions_tables_figures.r

@@ -175,22 +175,24 @@ transform_SD <- function(m1, m2, SD1, SD2, n1, n2){ #assumes ES is raw mean diff
   data.frame(d = d, n1 = n1, n2 = n2)
 }
 
-transform_d_to_r <- function(d, n1, n2){ 
+transform_d_to_r <- function(d, n1, n2, fisher = FALSE){ 
   m <- n1 + n2 - 2 #Jacobs and Viechtbauer (2017), p.164
   h <- m/n1 + m/n2 #p. 164
   r <- d / sqrt(d^2 + h) #point-biserial correlation, Jacobs and Viechtbauer (2017), equation 5 
   var_r <- (1-r^2)^2 / (n1 + n2 -1) #Cooper and Hedges (2009), equation 12.27
-  # r <- 0.5*ln((1+r)/(1-r)) #Fishers z transformation Cooper and Hedges (2009), equation 12.28
-  # var_r <- 1 / (n1+n2 -3) #Fisher z variance, Cooper and Hedges (2009), equation 12.29
+  if(fisher){ #if fisher = TRUE, do fisher transform
+  r <- 0.5*log((1+r)/(1-r)) #Fishers z transformation Cooper and Hedges (2009), equation 12.28
+  var_r <- 1 / (n1+n2 -3) #Fisher z variance, Cooper and Hedges (2009), equation 12.29
+  }
   data.frame(r = r, vi = var_r, n = n1 + n2) 
 }
 
 
 #Function to apply the transformation functions to the (in the end only to data where x[, "outcomes1_2"] == "mean _ SD")
-transform_MA <- function(x){
+transform_MA <- function(x, fisher = FALSE){
   
   d_conversion <- transform_SD(x$outcome_t1, x$outcome_c1, x$outcome_t2, x$outcome_c2, x$ntreatment, x$ncontrol)
-  transform_d_to_r(d_conversion$d, d_conversion$n1, d_conversion$n2)
+  transform_d_to_r(d_conversion$d, d_conversion$n1, d_conversion$n2, fisher = fisher)
   
 }
 

### 2020-03-26 code/02_power_simulation.r
Added simulation results for RRR09 - hostility

@@ -173,7 +173,7 @@ set.seed(112)
 res <- vector("list", length(dat2)) #output of below loop
 
 system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
- res[[e]] <- simulate_I2(dat2[[e]], reps = 1, tau = tau_values, effect_size = "zero") #NB! 1e3 reps here is about 36 hours on my (fairly slow) machine
+ res[[e]] <- simulate_I2(dat2[[e]], reps = 1000, tau = tau_values, effect_size = "zero") #NB! 1e3 reps here is about 36 hours on my (fairly slow) machine
  cat("...RS",e, "/37") #see progress
  if (e%%5 == 0 | e == 37) saveRDS(res, "../data/tau_simulation_results.RDS") #save ocassionally and at finish
 })
@@ -185,7 +185,7 @@ system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progr
 # res_a <- vector("list", length(dat2)) #output of below loop
 
 # system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progress (lapply otherwise option)
-  # res_a[[e]] <- simulate_I2(dat2[[e]], reps = 1, tau = tau_values, effect_size = "medium") #NB! 1000 reps here is about 24 hours on my (fairly slow) machine
+  # res_a[[e]] <- simulate_I2(dat2[[e]], reps = 1000, tau = tau_values, effect_size = "medium") #NB! 1000 reps here is about 24 hours on my (fairly slow) machine
   # cat("...RS",e, "/37") #see progress
   # if (e%%5 == 0 | e == 37) saveRDS(res_a, "../data/supplementB_tau_simulation_results.RDS") #save ocassionally and at finish
 # })
@@ -195,6 +195,7 @@ system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progr
 dat3 <- readRDS("../data/tau_simulation_results.RDS")
 # dat3 <- readRDS("../supplementB_tau_simulation_results.RDS") #for supplement
 names(dat3) <- names(dat2) #names are lost when looping instead of using lapply so must be re-added
+
 
 dat3 <- dat3 %>% #create dataframe with identifier
   bind_rows(.id = "effect") %>% 
@@ -232,7 +233,8 @@ dat5 <- dat4 %>% #add the extracted tau-values as a vector to each list-element 
 
 ##Simulation
 set.seed(56)
[…]

### 2020-03-27 code/01_collate_summary_data.r
Missed one author (Bialobrzeska) when adding SD to RRR8

@@ -1484,10 +1484,13 @@ rrr7 <- rrr7 %>%
 #   Error in rbind(deparse.level, ...) : 
 #   numbers of columns of arguments do not match
 
-# 5) In the file dijksterhuis_meta_analysis_2.R run lines 1 - 120, make sure working directory is set to the file location
+# 5) Rename the Bialobrzeska folder and inside the folder the Bialobrzeska_data_complete file 
+#    to not use a special 'l' (or else didn't load on my machine)
+
+# 6) In the file dijksterhuis_meta_analysis_2.R run lines 1 - 120, make sure working directory is set to the file location
 #     [not sure which packages in line 1-7 actually need to be loaded, I had them all installed already so just loaded them all]
 
-# 6) Save the collated data file with the following line of code:
+# 7) Save the collated data file with the following line of code:
 #   write.csv(all_dat, file = "RRR08_summary_stats.csv", row.names = FALSE)
 
 #Extract data
@@ -1731,4 +1734,3 @@ rrr10 <- rrr10 %>%
 effects <- rbind(ml1, ml2, ml3, rrr1_2, rrr3, rrr4, rrr5, rrr6, rrr7, rrr8, rrr9, rrr10)
 
 # write.csv(effects, "../data/collated_summary_data.csv", row.names = FALSE)
-

### 2020-03-27 code/04_tables.rmd
Updated Figures to be APA consistent, minor table fix

@@
 rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
-ma <- c("I: $\\rho_{xy} = 0.0$", "II: $\\rho_{xy} = 0.3$", "III: $\\rho_{xy} = 0.5$")
+ma <- c("I", "II", "III")
 
@@
 devs <- apply(rooted_relabilities, 2, sd)
-table1 <- data.frame(ma, t(rooted_relabilities), devs)
+table1 <- data.frame(ma, rho, t(rooted_relabilities), devs)
 
-table1 %>% knitr::kable(booktabs = T, col.names = c("Meta-Analysis", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)"), escape = FALSE, digits = 2) %>%
+table1 %>% knitr::kable(booktabs = T, col.names = c("Meta-Analysis", "$\\rho_{xy}$", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8", "SD(ES)"), escape = FALSE, digits = 2) %>%
   kable_styling(position = "left") %>% 
-  add_header_above(c(" " = 1, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>% 
-  add_header_above(c(" " = 1, "Observed Effect Sizes" = 3))
+  add_header_above(c(" " = 2, "Study 1"= 1, "Study 2" = 1, "Study 3" = 1)) %>% 
+  add_header_above(c(" " = 2, "Observed Effect Sizes" = 3))
 
@@
 SD(ES) is the standard deviation of the observed effect sizes for meta-analysis I, II and III; equivalent to heterogeneity given infinite within study sample sizes.
-Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06
+Code to reproduce table: osf.io/gtfjn/
 
@@
                  "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.", #RRR8
-            "Hostility priming; Independent two-group experiment. Participants descrambled sentences, either 20% or 80% were hostile, then rated ambiguous behavior.", #RRR9
+            "Hostility priming; Independent two-group experiment with two outcome variables.
+Participants descrambled sentences, either 20% or 80% were hostile, then rated an individual and a list of ambiguous behaviors on perceived hostility.", #RRR9
             "Moral reminder; Independent two-group experiment. Participants either recalled the Ten Commandments or books they'd read. Outcome was degree of cheating when reporting results. ") #RRR10
@@
 primary studies (number of US studies), ML = Many Labs, RRR = Registered Replication Report.
-Code to reproduce table: osf.io/kf6pt/?view_only=e6639d8d4f924739a7310782fbbb4e06"
+Code to reproduce table: osf.io/gtfjn/
 
@@
 ### Heterogeneity across primary effects and statistical power of thirteen multi-lab replication projects, ordered with respect to estimated heterogeneity ($I^2$).
-```{r prep-heterogeneity-table, cache = TRUE, results = 'hide'}
+```{r prep-heterogeneity-table, results = 'hide'}
 #library(metafor) 
@@
 het$effect <- gsub("&", "\\\\&", het$effect)
+
+#highlight the effects in Figure 3
+fig3_smds <- unique(dat$effect[dat$outcomes1_2 == "mean _ SD"]) 
+fig3_logor <- c('Allowed vs. forbidden', 'Gain vs. loss framing', 'Norm of reciprocity', 'Low vs. high category scales', #ML1 (OR2d)
+                "Affect & Risk", "Trolley Dilemma 1", "Framing", "Trolley Dilemma 2", #ML2
+                "Verbal overshadowing 1", "Verbal overshadowing 2") #RRR1
+
+het$effect <- ifelse(het$effect %in% fig3_smds, paste0(het$effect, footnote_marker_symbol(1)), het$effect)
+het$effect <- ifelse(het$effect %in% fig3_logor, paste0(het$effect, footnote_marker_symbol(2)), het$effect)
+
 ```
@@
 
-het %>% knitr::kable(align = "c", longtable = TRUE, booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
+het %>% knitr::kable(longtable = TRUE, booktabs = TRUE, escape = FALSE, digits = 2, col.names = c("RP", "Effect", "K", "Effect type", "Effect size estimate",  "$I^2$(\\%)", "$I^2$ 95\\% CI", "$\\hat\\tau$", "$\\hat\\tau$ 95\\% CI", "Zero", "Small", "Medium", "Large")) %>%
   add_header_above(c(" " = 9, "Level of heterogeneity" = 4)) %>%
@@
   column_spec(5, width = "5em") %>% #make sure the 'Effect size estimate' header is wrapped
+  column_spec(4, width = "3em") %>% #wrap 'Effect Type' header 
   footnote(threeparttable = TRUE, escape = FALSE,
@@
 SMD = Standardized Mean difference (Hedge's g), MD = Mean Difference, RD = Risk Difference, r = correlation.
-Code to reproduce table: osf.io/kf6pt/?view\\\\_only=e6639d8d4f924739a7310782fbbb4e06" ,
-           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences")) %>% landscape()
+Code to reproduce table: osf.io/gtfjn/" ,
+           alphabet = c("Value rounded to zero", "These effects were simulated as standardized mean differences"),
+symbol = c("SMD effect size in Figure 3", "Log odds ratio effect size in Figure 3")) %>% landscape()
 ```

### 2020-03-27 code/05_figures-and-correlations.rmd
Made the heterogeneity estimates a little clearer for sole non-sig log odds ratio
Updated Figures to be APA consistent, minor table fix

--- 2019-12-18 code/05_figures-and-correlations.rmd
@@
                      minor_breaks = NULL) +
+  scale_linetype_manual(name = "Effect type", 
+                        values = c( "dotdash", "dotted", "solid", "dashed"),
+                        breaks = c("Fisher's z", "Cohen's q", "MD", "SMD"),
+                        labels = c(expression(paste("Fisher's ", italic(z))),
+                                   expression(paste("Cohen's ", italic(q))),
+                                   expression(paste(italic(MD))),
+                                   expression(paste(italic(SMD))))) + 
+  scale_color_brewer(name = "Effect type", 
+                     palette = "Dark2", 
+                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD"),
+                     labels = c(expression(paste("Fisher's ", italic(z))),
+                                   expression(paste("Cohen's ", italic(q))),
+                                   expression(paste(italic(MD))),
+                                   expression(paste(italic(SMD))))) +
   coord_cartesian(ylim = c(0, 100)) +
-  scale_color_brewer(name = "Effect type", palette = "Dark2", 
-                     breaks = c("Fisher's z", "Cohen's q", "MD", "SMD")) +
   theme(legend.position = c(0.8, 0.4),
         legend.background = element_rect(linetype = "solid", color = "black")) +
-  guides(color = guide_legend(override.aes = list(size = 1.4)))
+  guides(color = guide_legend(override.aes = list(size = 1.2)))
 
@@
 ```{r Density-plot, fig.height=4, fig.width=6.47}
-I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity, fill = Heterogeneity, linetype = Heterogeneity)) +
-  geom_histogram(data = observed, aes(y = ..density.., x = I2), bins = 100, alpha = 1) +
-  geom_density(alpha = 0.3) +
+I2_plot <- ggplot(I2_dist, aes(x = I2, group = Heterogeneity)) + 
+  geom_histogram(data = observed, aes(y = ..density.., x = I2, fill = Heterogeneity), bins = 100, alpha = 0.6)   +
+  stat_density(geom="line", position="identity", #we use stat_density instead of geom_density to get only the density lines (and no fill)
+               aes(linetype = Heterogeneity, color = Heterogeneity), size = 0.75)+ 
   theme_classic() +
   coord_cartesian(xlim = c(0, 100))  +
-  scale_fill_brewer(palette = "Dark2",
-                    breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                    labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "solid", "dashed"),
-                        breaks = c("Zero", "Small", "Medium", "Large", "Observed"), 
-                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  scale_color_brewer(palette = "Dark2", 
-                     breaks = c("Zero", "Small", "Medium", "Large", "Observed"),
-                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)", "Observed")) +
-  theme(legend.position = c(0.85, 0.71),
-        legend.background = element_rect(linetype = "solid", color = "black")) +
+  scale_linetype_manual(values = c( "dotdash", "dotted", "solid", "dashed"),
+                        breaks = c("Zero", "Small", "Medium", "Large"), 
+                        labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)")) +
+  scale_fill_manual(name = NULL, #drop legend title so that can place directly under other legend
+                    values = "#666666", #fill color
+                    breaks = "Observed",
+                    labels = "Observed") +
+  scale_color_manual(values = c("#D95F02", "#E6AB02", "#1B9E77","#E7298A"), #fill colors
+                     breaks = c("Zero", "Small", "Medium", "Large"),
+                     labels = c("Zero (0%)", "Small (25%)", "Medium (50%)", "Large (75%)")) +
+  theme(legend.position = c(0.85, 0.71), #placement of legend
+        legend.spacing = unit(-0.4, "cm"), #move the two legends close to each other to seem like one
+        legend.background = element_blank(), #remove legend background so that we can put a shared box around the two legends
+        legend.box.background = element_rect(colour = "black")) + #create the shared box
   scale_y_continuous(name = "Density") +
-  scale_x_continuous(name = expression(paste(I^2," index", sep = ""))) +
-  guides(fill = guide_legend(override.aes = list(alpha = c(rep(0.3, 4), 1))))
+  scale_x_continuous(name = expression(paste(italic(I)^2," index", sep = ""))) +
+  guides(linetype = guide_legend(order = 1),
+         color  = guide_legend(order = 1))
+#*****************
 
@@
 Figure 2.
-Simulated $I^2$  densities across 67 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 67 meta-analyses.
-Each simulated density consists of approximately 670,000 estimates.
+Simulated $I^2$  densities across 68 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 68 meta-analyses.
+Each simulated density consists of approximately 680,000 estimates.
 
@@
 
-#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
-tau2_per_type <- dat %>% #First compute meta-analytic results for all effects (will save: SMDs results)
-  split(.$effect) %>%  
-  map_dfr(est_heterogen_smd_raw, .id = "effect")
-
 #Raw mean differences to SMD
 MD_standardized <- dat %>% 
-  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
+  filter(outcomes1_2 == "mean _ SD") %>% 
   split(.$effect) %>% 
-  map_dfr(MD_fit, .id = "effect") #MD_fit function is sourced
+  map_dfr(MD_fit, .id = "effect") %>% #MD_fit function is sourced
+  mutate(effect_type = "Standardized Mean Difference")
 
@@
   split(.$effect) %>% 
-  map_dfr(log_or_fit, .id = "effect") #log_or_fit function is sourced
+  map_dfr(log_or_fit, .id = "effect") %>% #log_or_fit function is sourced
+  mutate(effect_type = "Log Odds Ratio")
 
-tau_per_type <- dat %>% #This is to add the effect_type names
-  select(effect, effect_type) %>% 
-  distinct() %>% #get unique rows
-  mutate(effect_type = recode(effect_type, 
-                              d = "Standardized Mean Difference")) %>% 
-  left_join(tau2_per_type) %>% #Add the meta-analytic results
-  filter(!effect %in% c(log_odds_ratios$effect, MD_standardized$effect)) %>% #drop old odds ratio effects and unstandardized MD
-  bind_rows(MD_standardized) %>% #add MD after standardization
-  bind_rows(log_odds_ratios) %>% #add odds ratios
-  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
-         effect_type = ifelse(effect %in% log_odds_ratios$effect, "Log Odds Ratio", effect_type),
-         eff_size = abs(eff_size), #need the absolute values for plotting
-         tau = sqrt(tau2)) %>% 
-  filter(effect_type %in% c("Standardized Mean Difference", "Log Odds Ratio"))
+#combine into one dataframe for plotting
+tau_per_type <- MD_standardized %>% 
+  bind_rows(log_odds_ratios) %>% 
+  mutate(eff_size = abs(eff_size), #need the absolute values for plotting
+         tau = sqrt(tau2))
 
@@
   geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
-  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", italic(tau)))) +
+  scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", tau))) +
   scale_x_continuous(name = "Absolute Effect Size") +
@@
 
-nrow(logOR[logOR$eff_size_p > 0.05,]) #only 1 log odds ratio not signifcant
+logOR[logOR$eff_size_p > 0.05,] #only 1 log odds ratio not signifcant. tau = 0.13, I2 = 11.8, H2 = 1.05
 

### 2020-03-27 code/06_Supplement-tables-figures.Rmd
Updated Figures to be APA consistent, minor table fix

@@
 ```
+
+## Figure S1A
 
@@
 MD_standardized <- dat %>% 
-  filter(outcomes1_2 == "mean _ SD") %>% #Note, drops Mean _ SE studies (two) since no method in metafor to convert into standardized mean differences
+  filter(outcomes1_2 == "mean _ SD") %>% 
   split(.$effect) %>% 
@@
 $s^2$ = "typical" within studies variance (Higgins and Thompson, 2002, equation 9), $\hat{\mu}$ = average absolute effect size, $I^2$ = $\hat{\tau}^2$ / $(\hat{\tau}^2 + s^2)$ , $H^2$ = $Q/(K-1)$ where $Q$ is the Q-statistic and $K$ is the number of studies in a meta-analysis.
-This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nontheless.
+This expression for $H^2$ is strictly only correct when using the DerSimonian-Laird estimator, see main manuscript for why we use it nonetheless.
 In all 40 meta-analyses effect sizes were measured as mean or standardized mean differences.
 Effects reported as mean differences were standardized for the meta-analyses.
+
+## Figure S1C
+
+```{r plotC prep}
+
+#Create plot labels
+set.seed(499) #for the bootstrapping
+all_effects_ci <- tau_per_type %>% 
+  bootfitter_sigma2(.) #bootfitter is a sourced function
+
+labels_all <- tau_per_type %>% #
+  fitter_sigma2(.) %>% #fitter is a sourced function
+  mutate(lab = paste0("r = ", r, " ", all_effects_ci$ci)) #put output into one variable for improved plotting
+
+set.seed(500) #for the bootstrapping
+restricted_effects_ci <- without_anchoring %>% 
+  bootfitter_sigma2(.) #bootfitter is a sourced function
+
+labels_restricted <- without_anchoring %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
+  fitter_sigma2(.) %>% #fitter is a sourced function
+  mutate(lab = paste0("r = ", r, " ", restricted_effects_ci$ci)) #put output into one variable for improved plotting
+```
+
+```{r fig C}
+within_plot_full <- ggplot(tau_per_type, aes(x = eff_size, y = s2)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels_all[labels_all$index == "sigma",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  scale_y_continuous(name = expression(paste(italic(s^2)))) +
+  scale_x_continuous(name = "Absolute Effect Size") +
+  theme_classic() +
+  theme(strip.background = element_blank(), #remove box around titles
+        strip.text = element_text(size = 12),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid"))
+
+without_anchoring_plot <- ggplot(without_anchoring, aes(x = eff_size, y = s2)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
+  geom_text(data = labels_restricted[labels_restricted$index == "sigma",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  scale_y_continuous(name = expression(paste(italic(s^2)))) +
+  scale_x_continuous(name = "Absolute Effect Size") +
+  theme_classic() +
+  theme(strip.background = element_blank(), #remove box around titles
+        strip.text = element_text(size = 12),
+        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
+                                    size = 0.5, linetype = "solid"))
+
+cowplot::plot_grid(within_plot_full, without_anchoring_plot, nrow = 2, labels = "AUTO")
+
+ggsave("../figures/figure-S1C.png", dpi = 600, height =  7, width = 7)
+```
+
+Figure S1C.
+The Pearson correlation (_r_) between average absolute effect size and average within studies standard deviation for 40 effects that were measured as mean or standardized mean differences.
+Panel A shows results for all 40 effect sizes and panel B with the four largest (Anchoring 1 - 4) excluded.
+Effects reported as mean differences were standardized.
+Square brackets contain 95% bootstrapped percentile confidence intervals.
+```

### 2020-03-27 code/02_power_simulation.r

@@ -2,7 +2,7 @@
 
 #Project: Heterogeneity in direct replications in psychology and its association with effect size
 #Script purpose: Simulate I2 distribution for different levels of heterogeneity given data weights
-#Code: 
+#Code: Anton Olsson Collentine (anton@olssoncollentine.com) 
 
 #******************************************
 

### 2020-03-27 code/03_helper_functions_tables_figures.r

@@ -2,7 +2,7 @@
 
 #Project: Heterogeneity in direct replications in psychology and its association with effect size
 #Script purpose: Helper functions to prep data for tables and figures
-#Code: 
+#Code: Anton Olsson Collentine (anton@olssoncollentine.com)
 #Additional comments: These functions are intended to be 'sourced' into the 
 #                     tables.rmd, figures.rmd, and supplement-tables-figures.rmd files 
 
@@ -19,10 +19,6 @@ est_heterogen_smd_raw <- function(x){
   if(any(x[, "effect_type"] == "Risk difference")){ #without the 'any' we will get warnings because we apply 'if' to a vector
     
     fit <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2,  n1i = ntreatment, n2i = ncontrol,  data = x)
-    
-  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){  
-    
-    fit <-  rma(yi = effect_size, sei = outcome_c2,  data = x) 
     
   } else if(any(x[, "effect_type"] == "Raw mean difference")){
     if(any(x[, "rp"] %in% c("RRR5", "RRR7"))){ #For these us the Knapp and Hartung adjustment of standard errors
@@ -198,8 +194,8 @@ transform_MA <- function(x, fisher = FALSE){
 
 
 #function to run random effect meta-analysis on transformed effect sizes
-summarizer <- function(x){#Z-transformation not recommended by Jacobs and Viechtbauer (2017) for biserial correlations, p. 176
-  fitr <- rma(yi = x$r, vi = x$vi, data = x) #rma for biserial and pearson correlations (distinct per effect!)
+summarizer <- function(x){
+  fitr <- rma(yi = x$r, vi = x$vi, data = x) 
   ci <- confint(fitr)$random[c(1, 3), ] #I2 and tau2 confidence intervals
   
   data.frame(r = fitr$b[[1]], tau2 = fitr$tau2, tau2.lb = ci[1, 2], tau2.ub = ci[1, 3],
@@ -223,4 +219,32 @@ compute_precision <- function(SD1, SD2, n1, n2){
   var_pooled <- ((n1 - 1)*SD1^2 + (n2 - 1)*SD2^2) / (n1 + n2 - 2) #Borenstein, M. (2009), p. 226. 
   sampling_var <- var_pooled / (n1 + n2)
[…]

### 2020-03-27 code/05_figures-and-correlations.rmd
Made Fig 2 legend keys wider to distinguis between linetypes better

@@
                     breaks = "Observed",
-                    labels = "Observed") +
+                    labels = "     Observed") + #space before Observed to align label with other labels since this guide has a different width to the others (see last line)
   scale_color_manual(values = c("#D95F02", "#E6AB02", "#1B9E77","#E7298A"), #fill colors
@@
         legend.spacing = unit(-0.4, "cm"), #move the two legends close to each other to seem like one
+        legend.key.width = unit(0.8, "cm"), #set default keywidth wider, so we can distinguis linetypes dashed and dotdash
         legend.background = element_blank(), #remove legend background so that we can put a shared box around the two legends
@@
   scale_x_continuous(name = expression(paste(italic(I)^2," index", sep = ""))) +
-  guides(linetype = guide_legend(order = 1),
-         color  = guide_legend(order = 1))
+  guides(linetype = guide_legend(order = 1), #place linetype/color guides above fill guide
+         color  = guide_legend(order = 1),
+         fill = guide_legend(keywidth = unit(0.2, "cm"), #Make fill legend thinner to look like the histogram bars
+                             direction = "horizontal")) #needed in combination with above
 #*****************

### 2020-03-30 code/05_figures-and-correlations.rmd
Updated and made sure bootstrapped values are reproducible in 'heterogeneity and effect sizes' section

@@
 
-#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript (not printed if .rmd is knit)
+#This section gives the correlations and values reported in the section 'Heterogeneity and effect sizes' in the main manuscript (not printed if .rmd is knit).
 
-#1. Standardized mean differences----
+#bootstrap confidence intervals code contribution by Amir Abdol.
+
+set.seed(435) #same seed as for plot
+
+#Pearson bootstrap percentile confidence intervals for SMD and logOR
+cis <- tau_per_type %>% #same as in Figure 3
+  split(.$effect_type) %>% 
+  map_dfr(bootfitter, .id = "effect_type") #bootfitter is a sourced function
+
+#1.1. Standardized mean differences Pearsons----
 SMDs <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
@@
 
-cor.test(SMDs$tau, SMDs$eff_size) #pearson tau2
-cor.test(SMDs$s_I2, SMDs$eff_size) #pearson I2
-cor.test(SMDs$H2, SMDs$eff_size) #pearson H2
+#pearson tau2
+cor.test(SMDs$tau, SMDs$eff_size) 
+#pearson I2
+cor.test(SMDs$s_I2, SMDs$eff_size)
+#pearson H2
+cor.test(SMDs$H2, SMDs$eff_size)
 
-cor.test(SMDs$tau, SMDs$eff_size, method = "spearman") #spearman
-cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
-cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman
+#1.2. log OR Pearson's----
+logOR <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
+  filter(effect_type == "Log Odds Ratio")
 
-##Excluding anchoring effects
+#pearson tau2
+cor.test(logOR$tau, logOR$eff_size) 
+#pearson I2
+cor.test(logOR$s_I2, logOR$eff_size)
+#pearson H2
+cor.test(logOR$H2, logOR$eff_size)
+
+#1.3 Excluding anchoring effects Pearson's ---- 
 dropped_anchoring <- SMDs %>%
@@
 
-cor.test(dropped_anchoring$tau, dropped_anchoring$eff_size) #pearson
+#tau
+cor.test(dropped_anchoring$tau, dropped_anchoring$eff_size) 
+bootfit <- boot(data=dropped_anchoring, statistic=pear_tau, R=1000, formula= ~ eff_size + tau)
+boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+#I2
 cor.test(dropped_anchoring$s_I2, dropped_anchoring$eff_size) #pearson
+bootfit <- boot(data=dropped_anchoring, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #statistic function is sourced
+boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
+
+#H2
 cor.test(dropped_anchoring$H2, dropped_anchoring$eff_size) #pearson
+bootfit <- boot(data=dropped_anchoring, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
+boot.ci(bootfit, type=c("perc", "bca"))
 
-#1.05 When ES not sig. diff from zero----
+#1.4. Spearman's rank order correlation----
+
+#tau
+cor.test(SMDs$tau, SMDs$eff_size, method = "spearman") #spearman
+options(warn=-1)
+bootfit <- boot(data=SMDs, statistic=spear_tau, R=1000, formula= ~ eff_size + tau)
+options(warn=0)
+
+boot.ci(bootfit, type=c("perc", "bca"))
+
+#I2
+cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
+options(warn=-1)
+bootfit <- boot(data=SMDs, statistic=spear_I2, R=1000, formula= ~ eff_size + s_I2)
+options(warn=0)
+
+boot.ci(bootfit, type=c("perc", "bca"))
+
+#H2
+
+cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman
+options(warn=-1)
+bootfit <- boot(data=SMDs, statistic=spear_H2, R=1000, formula= ~ eff_size + H2)
+options(warn=0)
+
+boot.ci(bootfit, type=c("perc", "bca"))
+
+#2. When ES not sig. diff from zero----
+
 ##When effect size not sig diff from 0 (alpha = .05), what is average heterogeneity?
@@
 #logs
-logOR <- tau_per_type %>% #tau_per_type object from code section two up 'cor_per_effect_type_prep'
-  filter(effect_type == "Log Odds Ratio")
 
@@
 
-#bootstrap confidence intervals
-#code contribution by Amir Abdol
-
-#1.1 I2 confidence intervals----
-
-#bootfit <- boot(data=SMDs, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #see Fig 3
-#I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
-
-#Excluding anchoring effects
-set.seed(234)
-bootfit <- boot(data=dropped_anchoring, statistic=pear_I2, R=1000, formula= ~ eff_size + s_I2) #statistic function is sourced
-
-I2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
-
-#1.2 Tau confidence intervals----
-
-# bootfit <- boot(data=tau_per_type, statistic=pear_tau, R=1000, formula= ~ eff_size + tau2) #see Fig 3
-# tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
-
-#Excluding anchoring effects
-cor.test(dropped_anchoring$tau2, dropped_anchoring$eff_size)
-
-set.seed(423)
-bootfit <- boot(data=dropped_anchoring, statistic=pear_tau, R=1000, formula= ~ eff_size + tau)
-tau_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)
-
-#1.3 H2 confidence intervals----
-set.seed(342)
-bootfit <- boot(data=tau_per_type, statistic=pear_H2, R=1000, formula= ~ eff_size + H2)
-H2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))
-
-#1.4 spearman bootstrap CIs----
-#First for I2
-spear_I2 <- function(formula, data, indices){ #spearman
-     d <- data[indices,]
-     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d, method = "spearman")
-     return(fit$estimate)
-}
-
-set.seed(241)
-options(warn=-1)
-bootfit <- boot(data=tau_per_type, statistic=spear_I2, R=1000, formula= ~ eff_size + s_I2)
-options(warn=0)
-
-I2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
-
-#Second for tau
-
-set.seed(5233)
-options(warn=-1)
-bootfit <- boot(data=tau_per_type, statistic=spear_tau, R=1000, formula= ~ eff_size + tau)
-options(warn=0)
-
-tau_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))
-
 ```

### 2020-03-30 code/03_helper_functions_tables_figures.r

@@ -147,7 +147,12 @@ spear_tau <- function(formula, data, indices){ #spearman
   return(fit$estimate)
 }
 
-
+#third for  H2
+spear_H2 <- function(formula, data, indices){ #spearman
+  d <- data[indices,]
+  fit <- cor.test(formula = ~ H2 + eff_size, data=d, method = "spearman")
+  return(fit$estimate)
+}
 #******************************************
 #Functions for Supplement A----
 #******************************************

### 2020-03-30 code/05_figures-and-correlations.rmd
Made legend wider in Fig 1 for better clarity

@@
   theme(legend.position = c(0.8, 0.4),
-        legend.background = element_rect(linetype = "solid", color = "black")) +
-  guides(color = guide_legend(override.aes = list(size = 1.2)))
+        legend.background = element_rect(linetype = "solid", color = "black"),
+        legend.key.width = unit(0.9, "cm")) +
+  guides(color = guide_legend(override.aes = list(size = 0.85)))
 

### 2020-03-30 code/02_power_simulation.r
Fixed Supplement B hostility power analysis

@@ -193,9 +193,8 @@ system.time(for(e in seq_along(dat2)){ #As loop to be able to see and save progr
 
 ##Simulation results
 dat3 <- readRDS("../data/tau_simulation_results.RDS")
-# dat3 <- readRDS("../supplementB_tau_simulation_results.RDS") #for supplement
+# dat3 <- readRDS("../data/supplementB_tau_simulation_results.RDS") #for supplement
 names(dat3) <- names(dat2) #names are lost when looping instead of using lapply so must be re-added
-
 
 dat3 <- dat3 %>% #create dataframe with identifier
   bind_rows(.id = "effect") %>% 
@@ -250,7 +249,7 @@ system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progr
 
 # set.seed(50)
  # res2_a <- vector("list", length(dat2)) #output of below loop
-
+# 
  # system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progress (lapply otherwise option)
    # res2_a[[e]] <- simulate_I2(dat5[[e]][[1]], reps = 1e4,
                             # tau = c(0, dat5[[e]][[2]]), effect_size = "medium") #NB! 1e4 reps here is about 9.5 hours on my (fairly slow) machine
@@ -258,13 +257,6 @@ system.time(for(e in seq_along(dat5)){ #As loop to be able to see and save progr
    # if (e%%5 == 0 | e == 37) saveRDS(res2_a, "../data/supplementB_power_simulation_results.RDS") #save ocassionally and at finish
  # })
 #********************
-
-
-##Simulation results
-dens <- readRDS("../data/power_simulation_results.RDS") #very large if saved as .csv
-# dens <- readRDS("../data/supplementB_power_simulation_results.RDS") #If supplement simulation
-names(dens) <-  names(dat2)
-
 
 
 #Summary of results. These are incorporated into the main table in the paper, see tables.rmd

### 2020-03-30 code/05_figures-and-correlations.rmd
Made Fig 3 correlations APA compliant

@@
 
-Figure 1. Result of simulation relating $I^2$-values to between studies standard deviation. Each line represent one of 67 effects. Tau is not directly comparable across effect size measures.
+*Figure 1.* Result of simulation relating $I^2$-values to between studies standard deviation.
+Each line represent one of 67 effects.
+Tau ($\tau$) is not directly comparable across effect size measures.
+Code to reproduce table: osf.io/u2t3r
 
@@
 
-Figure 2.
-Simulated $I^2$  densities across 68 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 68 meta-analyses.
+*Figure 2.* Simulated $I^2$  densities across 68 meta-analyses for zero, small, medium, and large heterogeneity according to the definitions of Higgins (2003), and the distribution of the observed $I^2$ estimates (bars) for the 68 meta-analyses.
 Each simulated density consists of approximately 680,000 estimates.
+*MD* = Mean Difference, *SMD* = Standardized Mean Difference.
+Code to reproduce table: osf.io/u2t3r
 
@@
   map_dfr(fitter, .id = "effect_type") %>% #fitter is a sourced function
-  mutate(lab = paste0("r = ", r, " ", fig3_ci$ci)) #put output into one variable for improved plotting
+  mutate(lab = paste0("r (", c(rep(8, 3), rep(41, 3)), ") = ",
+                      gsub("0\\.", "\\.", r),
+                      ", 95% CI ",
+                      gsub("0\\.", "\\.", fig3_ci$ci))) #put output into one variable for improved plotting
 
@@
   geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
-  geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  geom_text(data = labels[labels$index == "tau",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.06, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
   scale_y_continuous(name = expression(paste("Between Studies Standard Deviation ", tau))) +
@@
 I2_facet <- ggplot(tau_per_type, aes(x = eff_size, y = s_I2)) + 
+  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.06, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
   geom_point(alpha = 0.5) +
   geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
-  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
   scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
@@
   geom_smooth(method = "lm", se = FALSE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
-  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.05, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
+  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.06, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
   scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
@@
 
-Figure 3.
-The Pearson correlation between absolute effect size and A) $\hat{\tau}$, B) $I^2$ and C) $H^2$ respectively for 40 effects that were measured as mean or standardized mean differences and 10 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects.
+*Figure 3.* The Pearson correlation between absolute effect size and A) $\hat{\tau}$, B) $I^2$ and C) $H^2$ respectively for 43 effects that were measured as mean or standardized mean differences and 10 effects measured as odds ratios or risk differences from 13 pre-registered multi-lab replication projects.
 Effects reported as mean differences were standardized and odds ratios/risk differences computed as log odds ratios.
-Square brackets contain 95% bootstrapped percentile confidence intervals.
-Code to reproduce figure: osf.io/zuwpg/?view_only=e6639d8d4f924739a7310782fbbb4e06
+*r* = Product-moment correlation, square brackets contain 95% bootstrapped percentile confidence intervals.
+Code to reproduce figure: osf.io/u2t3r
 

### 2020-03-31 code/04_tables.rmd
Updated decimal places in Table 3

@@
 #library(kableExtra)
-rooted_relabilities <- matrix(rep(c(.6, .7,.8), 3), ncol = 3)
-rho <- c(0, .3, .5)
+rooted_relabilities <- matrix(rep(c(.60, .70,.80), 3), ncol = 3)
+rho <- c(0.0, .30, .50)
 rel <- c("$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .6", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .7", "$\\sqrt{R_{xx'}}\\times\\sqrt{R_{yy'}}$ = .8")
@@
   arrange(desc(s_I2),  desc(s_ci.ub)) %>% #sort by I2 and upper CI bound
-  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 1), nsmall = 1)), ", ", trimws(format(round(s_ci.ub, 1), nsmall = 1)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
-         s_I2 = format(round(s_I2, 1), nsmall = 1),
+  mutate(I2_ci = paste0("[", trimws(format(round(s_ci.lb, 2), nsmall = 2)), ", ", trimws(format(round(s_ci.ub, 2), nsmall = 2)), "]"), #Round and put confidence interval between brackets, e.g., [0, 0.41]
+         s_I2 = format(round(s_I2, 2), nsmall = 2),
          tau_ci = paste0("[", trimws(format(round(tau_ci.lb, 3), nsmall = 3)), ", ", trimws(format(round(tau_ci.ub, 3), nsmall = 3)), "]"),

### 2020-06-25 code/05_figures-and-correlations.rmd
Added pdf versions of figures

@@
 # ggsave("../figures/tau-I2.png", dpi = 600, height =  4 , width = 6.47)
-
+# ggsave("../figures/Figure1_tau-I2.pdf", dpi = 600, height =  4 , width = 6.47, device = cairo_pdf())
 ```
@@
 I2_plot
-# ggsave("../figures/density-I2.png", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
+# ggsave("../figures/density-I2.png", dpi = 600, height =  4, width = 6.47)
+# ggsave("../figures/Figure2_density-I2.pdf", dpi = 600, height =  4, width = 6.47, device = cairo_pdf())
 
@@
 # ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
+# ggsave("../figures/Figure3_effect-het.pdf", dpi = 600, height =  7, width = 7, device = cairo_pdf)
 combo
